### 2010-02-22 trunk/paper/semsearch10/paper.tex
first versions of semsearch

\documentclass{www2010-submission}
\begin{document}

\title{Leveraging Semantics for a Deep Web Question and Answering System} 
\numberofauthors{5}
\author{
	\alignauthor Christan Grant\\
	\email{cgrant@cise.ufl.edu}

	\alignauthor Clint P. George\\
	\email{clintpg@gmail.com}

	\alignauthor Joseph N. Wilson\\
	\email{jnw@cise.ufl.edu}

	\alignauthor Joir-dan Gumbs\\
	\email{jgumbs@cise.ufl.edu}

	\alignauthor Christopher A. Shields\\
	\email{cshields@cise.ufl.edu}

	\sharedaffiliation
	\affaddr{Department of Computer and Information Science and Engineering }  \\
	\affaddr{University of Florida} \\
	\affaddr{Gainesville, Florida 32611-6120}
}
\date{April 26,2010}

\maketitle

\begin{abstract}
\end{abstract}

\category{H.4.m}{Information Systems Applications}{Miscellaneous}

\terms{SSQ}

\keywords{Questions Answering, re-finding}

\section{Introduction}
% Christan

\section{Statistical Hierarchy}
\subsection*{Class Hierarchy}
%clint
\subsection*{Markov Blanket}
%joir-dan

\section{Semantic Query Representation}
% Christan - fois

\section{Building Query Store}
\subsection{Query Resolution Recorder}
% Chris
\subsection{Generalization}
% Christan

\section{Semantic Query Answering}
\subsection{Semi-Structured Query}
% Joir-dan
\subsection{SSQ Ranking}
% Clint
\subsection{Query Re-Execution}
% Chris

\section{Results}
% Walk through of example query

\section{Future Work}

\section{Conclusion}

\section{Acknowledgements}

\section{References}

\end{document}            % End of document.

### 2010-02-22 paper/semsearch10/paper.tex
latest

--- 2010-02-22 trunk/paper/semsearch10/paper.tex
@@
 \title{Leveraging Semantics for a Deep Web Question and Answering System} 
-\numberofauthors{5}
+\numberofauthors{7}
 \author{
@@
 
-	\alignauthor Joir-dan Gumbs\\
-	\email{jgumbs@cise.ufl.edu}
+	\alignauthor Peter J. Dobbins\\
+	\email{pjd@cise.ufl.edu}
+
+	\alignauthor Jeff T. Depree\\
+	\email{jepree@cise.ufl.edu}
 
@@
 	\email{cshields@cise.ufl.edu}
+
+	\alignauthor Joir-dan Gumbs\\
+	\email{jgumbs@cise.ufl.edu}
 
@@
 \begin{abstract}
+- It is difficult to answer question that change over time
+- However, if the method of answering the question can be realized, the question can be easily answered
+- We are building a system that supports a learning how to answer particular questions
+- We can answer questions that are semantically similar to our store of questions
+- We do this by building a semantic library ...
 \end{abstract}
@@
 % Christan
+- The best way to answer questions is to see/know if a question has been asked before.
+- IEEE potentials talks about the the beaten trail.
+- Use reuse in the specific domain of question answering
 

### 2010-02-24 trunk/generalizer/Highlight.py
debugging the qre

@@ -14,21 +14,23 @@ class Highlight(Page,object):
 		self.meetpoint = ""
 		self.startOffset = 0
 		self.endOffset = 0
+		self.classId = -1;
 		self.isAnswer = False
 		self.actionType = ActionType.Highlight
 		pass
-	
-def New(mx, sx, ex, so, eo, url, pagesrc, timestamp):
+
+def New(meet, startxpath, endxpath, startos, endos, url, pagesrc, timestamp, classId):
 	h = Highlight()
-	h.startXpath = sx
-	h.endXpath = ex
-	h.meetpoint = mx
-	h.startOffset = so
-	h.endOffset = eo
+	h.startXpath = startxpath
+	h.endXpath = endxpath
+	h.meetpoint = meet
+	h.startOffset = startos
+	h.endOffset = endos
 	h.pagesrc = pagesrc
 	h.timestamp = timestamp
 	h.url = url
 	h.isAnswer = False
+	h.classId = classId
 	h.actionType = ActionType.Highlight
 	return h
 		

### 2010-02-24 trunk/generalizer/ScriptBuilder.py

@@ -60,12 +60,14 @@ class ScriptBuilder():
 
 			#save previous action for use in next iteration
 			previousAction = action
-			
-
+		
+		
 		#add action data - now that we have built the hashtable of highlight and ssq info
-		actionData = etree.SubElement(qre, 'actiondata')
+		actionData = etree.Element('actiondata')
 		
 		writeActionData(actionData,actionHash)
+
+		qre.insert(0,actionData)
 		
 		qre = etree.tostring(qre, pretty_print=True)
 	
@@ -185,7 +187,6 @@ def writeFormAction(xmlNode, action, sequenceNumber,actionHash):
 		#we need to assign the context and class information along with the appropriate id		
 		if i.highlightid != None and i.highlightid != -1:
 			
-			pdb.set_trace()
 			type = "highlight"
 			classContextAndTimestamp = Loader.getNeededScriptInfo(i.highlightid, False)
 			newHashElem = actionHash[ classContextAndTimestamp[TIME] ]
@@ -268,7 +269,7 @@ def writeHighlightAction(xmlNode, action, sequenceNumber, actionHash):
 	xmlNode.set("number",str(sequenceNumber))
 
 	#add data to actionHash
-	#actionHash[key] = HashElement(action.meetpoint,'highlight','','')
+	actionHash[key] = HashElement(key,'highlight','',str(action.classId))
 
 	pass
 

### 2010-02-24 trunk/qre/ActionState.py

@@ -15,14 +15,16 @@ class ActionState:
 		It requires that you supply the (key,value) (key,type) and action tables
 
 	"""
-	def __init__(self, _action_list, _kv_hash, _kt_hash, _user_hash ):
+	def __init__(self, _action_list, _kv_hash, _kt_hash, _kclass_hash, _kcontext_hash, _user_hash ):
 		self.page = None # The current response page and dom source
 		self.user_agent = None # Header for user agent and browser info
 		self.cookie = cookielib.CookieJar()# Cookie object
 		self.values = None # Values for form evaluation
 		
 		self.kv_hash = _kv_hash.copy() # Make a copy of the hash table
-		self.kt_hash = _kt_hash.copy() # Make a copy of the hash table
+		self.kt_hash = _kt_hash.copy() # Make a copy of the hash table		
+		self.kclass_hash = _kclass_hash.copy() # Make a copy of the hash table
+		self.kcontext_hash = _kcontext_hash.copy() # Make a copy of the hash table
 		self.user_hash = _user_hash.copy() # Copy hash table
 
 		self.action_list = copy.copy(_action_list) # The list of actions 

### 2010-02-24 generalizer/Loader.py
debugging the qre

@@ -302,8 +302,17 @@ def getHighlight(row):
 	hpagesrc = 8
 	htimestamp = 7
 	hUrl = 6
+	classid = 9
 
-        h = Highlight.New(lower(row[meetpoint]),lower(row[startxpath]),lower(row[endxpath]),row[beginoffset],row[endoffset], row[hUrl], row[hpagesrc], row[htimestamp])
+        h = Highlight.New(lower(row[meetpoint]),
+		lower(row[startxpath]),
+		lower(row[endxpath]),
+		row[beginoffset],
+		row[endoffset], 
+		row[hUrl], 
+		row[hpagesrc], 
+		row[htimestamp],
+		row[classid])
 
 	return h
 

### 2010-02-24 generalizer/QueryGeneralizer.py

@@ -65,7 +65,7 @@ def GeneralizeQueries(qrmid, queryid):
 
     genQrm = generalizeQRMS(qrm1,qrm2)
 
-#Script generation
+    #Script generation
 
     scriptGenerator = ScriptBuilder()
 	
@@ -312,7 +312,7 @@ def generalizeActions(p1, p2):
         print("xpath after: "+genXpath+"\n")
 
         #Currently, start and end xpaths are not used. 
-        genh = Highlight.New(genXpath,None,None,0,0,p1.url,None,p1.timestamp)        
+        genh = Highlight.New(genXpath,None,None,0,0,p1.url,None,p1.timestamp,p1.classId)        
 
         #Check the validity of the result
         if compareExtractions(genh.meetpoint,p1.meetpoint,p1.pagesrc) != NO_SIMILARITY:

### 2010-02-24 qre/ActionObject.py

@@ -28,6 +28,7 @@ class URLAction(ActionObject):
 
 	def do(self, state):
 		"""Does URLAction and returns the state"""
+
 		url = self.xmlnode.text.strip() # Extract the url from <starturl>URL</starturl>
 		request = urllib2.Request(url)
 		response = urllib2.urlopen(request)
@@ -99,16 +100,16 @@ class FormAction(ActionObject):
 		inputs = list()
 
 		querystring = ""
-
+		
 		#get the base url for this form
 		for e in self.xmlnode.getchildren():
-			if e.tag == 'baseurl':
-				querystring = e.text	
+			if e.tag == 'url':
+				querystring = e.text.strip()	
 				break
 
 		querystring += "?"
 		first = False
-
+		
 		#iterate through the list and find the input elements		
 		for e in self.xmlnode.getchildren():
 
@@ -119,11 +120,12 @@ class FormAction(ActionObject):
 	
 				v = state.kv_hash[ e.text ]
 					
-				querystring += e['name'] + "=" + v 
+				querystring += e.get('name').strip() + "=" + v.strip()
 
-	
+		pdb.set_trace()
+		querystring = urllib2.quote(querystring)
 		#perform form submission 
-		result = urllib2.open( querystring )		
+		result = urllib2.urlopen( querystring )		
 
 		print(result)
 		pass

### 2010-02-24 qre/main.py

@@ -17,11 +17,6 @@ __connect_string = "dbname='%(db)s' user='%(user)s' host='%(server)s' password='
 __connect_params = {'server': "babylon.cise.ufl.edu", 'user' : "morpheus3",'pwd' : "crimson03.sql", 'db' : "Morpheus3DB"}
 __code_query = "SELECT code FROM qrm WHERE qrmid = %(id)s"
 
-kv_hash = {}
-kt_hash = {}
-kclass_hash = {}
-kcontext_hash = {}
-
 def main(argv):
 	
 	"""Run the Executor script
@@ -57,7 +52,7 @@ def main(argv):
 	assert(len(code) > 0) # ensure text was returned
 
 	root = etree.fromstring(code)
-	print(etree.tostring(root,pretty_print=True))
+	#print(etree.tostring(root,pretty_print=True))
 
 	action_list = []
 	kv_hash = {}	
@@ -65,6 +60,7 @@ def main(argv):
 	kclass_hash = {}
 	kcontext_hash = {}
 	user_hash = {}
+
 	# Traversal of code script
 	for child in root:
 		if child.tag == 'actiondata':
@@ -91,10 +87,12 @@ def main(argv):
 					action_list.append(ActionObject.FormAction(ao))
 
 	#parse the ssq to populate the value hashes with the user input	
-	if read_ssq(sys.argv[-2]) == False:
+	txt = read_ssq(sys.argv[-2])
+	if read_ssq_text(txt,kv_hash,kclass_hash, kcontext_hash, kt_hash) == False:	
 		return
 	
 	state = ActionState.ActionState(action_list, kv_hash, kt_hash, kclass_hash, kcontext_hash, user_hash)
+	
 	state.run()
 	
 	return state
@@ -108,10 +106,10 @@ def read_ssq(xml):
 
 	file.close()
 
-	return read_ssq_text(text)
+	return text
 
 #populate the value hash from a string
-def read_ssq_text(xmlstring):
+def read_ssq_text(xmlstring, valueHash, classHash, contextHash, typeHash):
 
 	tree = etree.fromstring(xmlstring)
 	
@@ -120,24 +118,24 @@ def read_ssq_text(xmlstring):
 
 		if e.tag == 'input_list':
 			for input in e.getchildren():
-				if loadValueIntoHash(input) == False:	
+				if loadValueIntoHash(input, valueHash, classHash, contextHash, typeHash) == False:	
 					print('The given ssq does not match this qrm\'s ssq, aborting')
 					return False
 	return True
 
[…]

### 2010-02-24 dobson/DobsonGUI/MainWindow.cs
fixing bugs in recognizing invalid scraper data

@@ -338,7 +338,7 @@ namespace DobsonGUI
 
         }
 
-        private void gatherXML(string path, Query thisQuery, int answerid)
+        private void gatherXML(string path, Query thisQuery, int answerid, int sequenceNumber)
         {
 
             using (TransactionScope scope = new TransactionScope())
@@ -404,13 +404,9 @@ namespace DobsonGUI
 
                 string expression;
 
-
-
                 expression = xmlStringStarter + "/*";
 
                 iterator = nav.Select(expression);
-
-
 
                 if (iterator != null && iterator.MoveNext())
                 {
@@ -435,7 +431,7 @@ namespace DobsonGUI
 
                         case "link":
 
-                            processPageAndPageReferences(thisQuery, iterator);
+                            processPageAndPageReferences(thisQuery, iterator, sequenceNumber,true);
 
                             break;
 
@@ -443,7 +439,7 @@ namespace DobsonGUI
 
                         case "form":
 
-                            processPageAndPageReferences(thisQuery, iterator);
+                            processPageAndPageReferences(thisQuery, iterator, sequenceNumber,false);
 
                             break;
 
@@ -713,19 +709,8 @@ namespace DobsonGUI
         {
             int index = url.IndexOf("?");
 
-            //bool isgoogle = false;
-
-            //if (index == -1)
-            //{
-            //    index = url.IndexOf("/#");
-            //    isgoogle = true;
-            //}
-
             if (index != -1)
             {
-                ////the delimeter for google querystring is longer than the standard one so increment
-                //if (isgoogle)
-                //    index++;
 
                 PageReferenceBL prefbiz = new PageReferenceBL();
 
@@ -823,7 +808,7 @@ namespace DobsonGUI
 
 
 
-        private static void processPageAndPageReferences(Query thisQuery, XPathNodeIterator iterator)
+        private static void processPageAndPageReferences(Query thisQuery, XPathNodeIterator iterator, int sequenceNumber, bool islink)
 
         {
 
@@ -932,6 +917,10 @@ namespace DobsonGUI
                 }
 
             }
+
+            if (islink == false && thisPage.baseURL.Contains("www.google.com") && sequenceNumber == 0)
+                throw new Exception("Scraping from google is not supported at this time, please re-run this query " +
+                    "using a different site.");
 
             //Insert the page object
 
@@ -1250,29 +1239,34 @@ namespace DobsonGUI
 
                         }
 
-                        if (excep)
-                            startButton.Text = "STOP";
-
[…]

### 2010-02-24 trunk/dobson/DobsonGUI/MainWindow.Designer.cs
fixing bugs in recognizing invalid scraper data

@@ -62,6 +62,7 @@
             this.subjectMenuDropDown = new System.Windows.Forms.ToolStripComboBox();
             this.modifierDoneToolStripMenuItem = new System.Windows.Forms.ToolStripMenuItem();
             this.modifierCancelToolStripMenuItem = new System.Windows.Forms.ToolStripMenuItem();
+            this.cancelButton = new System.Windows.Forms.Button();
             this.statusStrip1.SuspendLayout();
             this.menuStrip1.SuspendLayout();
             this.groupBox1.SuspendLayout();
@@ -113,7 +114,7 @@
             this.startButton.Anchor = ((System.Windows.Forms.AnchorStyles)((System.Windows.Forms.AnchorStyles.Top | System.Windows.Forms.AnchorStyles.Right)));
             this.startButton.Enabled = false;
             this.startButton.Font = new System.Drawing.Font("Microsoft Sans Serif", 8.25F, System.Drawing.FontStyle.Bold, System.Drawing.GraphicsUnit.Point, ((byte)(0)));
-            this.startButton.Location = new System.Drawing.Point(279, 301);
+            this.startButton.Location = new System.Drawing.Point(208, 307);
             this.startButton.Name = "startButton";
             this.startButton.Size = new System.Drawing.Size(115, 40);
             this.startButton.TabIndex = 12;
@@ -253,7 +254,7 @@
             this.outItem,
             this.modifierItem});
             this.selectionMenu.Name = "selectionMenu";
-            this.selectionMenu.Size = new System.Drawing.Size(153, 92);
+            this.selectionMenu.Size = new System.Drawing.Size(122, 70);
             // 
             // inItem
             // 
@@ -263,7 +264,7 @@
             this.inputDoneToolStripMenuItem,
             this.inCancelToolStripMenuItem});
             this.inItem.Name = "inItem";
-            this.inItem.Size = new System.Drawing.Size(152, 22);
+            this.inItem.Size = new System.Drawing.Size(121, 22);
             this.inItem.Text = "In";
             // 
             // contextMenuDropDown
@@ -303,7 +304,7 @@
             this.outputDoneToolStripMenuItem,
             this.outCancelToolStripMenuItem});
             this.outItem.Name = "outItem";
-            this.outItem.Size = new System.Drawing.Size(152, 22);
+            this.outItem.Size = new System.Drawing.Size(121, 22);
             this.outItem.Text = "Out";
             // 
[…]

### 2010-02-24 paper/semsearch10/paper.tex
text stuff

@@
 - Use reuse in the specific domain of question answering
+- 
+-
 
@@
 %joir-dan
+Once the semantic hierarchy is created, the next step is to create training data for the system.
+The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
+The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
+The problem with this approach is the page density varies greatly across the heterarchy.
+Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
+Considering that the categorical structure is a directed acyclic graph (Suchanek et al., 2008), we consider the use of a Markov Blanket (Friedman et al., 1997) in describing a particular category.
+The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
+While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
+
+Consider the abbreviated Markov blanket for the category Basketball:
+\includegraphics[width=4in,height=4in,viewport=0 0 300 300]{abbreviated_basketball_blanket.png}
+
+The subcategories of the category Basketball (… Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams…) can be seen as grabbing information specifc to the category.
+The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
+The spousal categories are an abstract description of the subcategories.
+
+Clustering the categories alone does not guarantee adequate corpus creation.
+Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
+In the case of Wikipedia, there are an average of 25.7 pages per category (Yu et al., 2007).
+The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
+Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
+This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
+We set this number to 10 * average, or 39.
+level represents how many extra levels we are to go down in the hierarchy, if necessary.
+SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
+
+\begin{algorithmic}
+\function BlanketSubjectRetrieval(blanket, maxLevel):
+	\for{category in blanket}
+		subjectSet.add(grabSubjects(category))
+		diff = afterSize - beforeSize;
+		\if{ diff \leq \alpha \and category is a subcategory}
+			PlusOneMechanism(category, maxLevel)
+		\endif
+	\endfor
+	return subjectSet
+\end{algorithmic}
+
+\begin{algorithmic}
+\function PlusOneMechanism(category, level)
+	plusOneSet = grabPlusOneSubcategories(category)
+	\for{ subcategory in plusOneSet do}
+		subjectSet.add(grabSubjects(subcategory));
+		diff = afterSize - beforeSize
+		\if{ diff \leq \alpha \and level \gt 0}
+			PlusOneMechanism(subcategory, level - 1);
+		\endif
+	\endfor
+\end{algorithmic}
+
+The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
+Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
+
+When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
 
@@
 \section{References}
+Bayesian Network Classifers
+Friedman, Geiger, Goldszmidt 1997
+
+YAGO: A Large Ontology from Wikipedia and WordNet
+Fabian M. Suchanek, Gjergji Kasnecia, and Gerhard Weikuma 2008
+
+Ontology Evaluation: Using Wikipedia Categories for Browsing
+Yu, Thom, Tam 2007
 

### 2010-02-24 qre/ActionObject.py

@@ -126,6 +126,9 @@ class FormAction(ActionObject):
 		querystring = urllib2.quote(querystring)
 		#perform form submission 
 		result = urllib2.urlopen( querystring )		
-
 		print(result)
+
+		self.page = result
+
 		pass
+

### 2010-02-24 trunk/qre/main.py

@@ -126,7 +126,7 @@ def read_ssq_text(xmlstring, valueHash, classHash, contextHash, typeHash):
 #parse the xml node and load its values into the appropriate spots
 #in the value hash
 def loadValueIntoHash(xml, valueHash, classHash, contextHash, typeHash):
-
+	pdb.set_trace()
 	#for the given xml node, we must find the matching key
 	for entry in valueHash.keys():
 		cls = classHash[entry]

### 2010-02-25 dobson/DobsonGUI/MainWindow.cs
updates

@@ -705,16 +705,17 @@ namespace DobsonGUI
 
         }
 
-        private static void parseQuerystring(string url)
+        private static string parseQuerystring(string url)
         {
             int index = url.IndexOf("?");
+            string qs = "";
 
             if (index != -1)
             {
 
                 PageReferenceBL prefbiz = new PageReferenceBL();
 
-                string qs = url.Substring(index, url.Length - index);
+                qs = url.Substring(index, url.Length - index);
 
                 //The querystring on fthis page is actually for the previous page reference
                 //so we need to update the database to reflect this
@@ -784,6 +785,8 @@ namespace DobsonGUI
                 }
 
             }
+
+            return qs;
         }
 
 
@@ -851,7 +854,7 @@ namespace DobsonGUI
 
                         pref.queryString = "";
 
-                        parseQuerystring(url);
+                        pref.queryString = parseQuerystring(url);
 
                         break;
 
@@ -1004,7 +1007,7 @@ namespace DobsonGUI
                 
                 if (parentNode != null)
                 {
-                    HtmlAgilityPack.HtmlNode selectedNode = parentNode.ParentNode.SelectSingleNode("//input[@name='" + inputName + "']");
+                    HtmlAgilityPack.HtmlNode selectedNode = parentNode.ParentNode.SelectSingleNode("//node()[@name='" + inputName + "']");
 
                     if (selectedNode != null)
                     {
@@ -1013,6 +1016,8 @@ namespace DobsonGUI
                             txt = selectedNode.Attributes["value"].Value.ToUpper();
                         else if (selectedNode.Attributes["title"] != null)
                             txt = selectedNode.Attributes["title"].Value.ToUpper();
+                        else if (selectedNode.Name.Equals("select", StringComparison.CurrentCultureIgnoreCase))
+                            txt = parseSelectValue(inputName, selectedNode, pref.queryString);
 
                         elem = queryElementManager.FindSsqInput(classId, txt);
                     }
@@ -1058,6 +1063,18 @@ namespace DobsonGUI
 
             }
 
+        }
+        //Parse the querystring to extract the dropdown selected value 
+        private static string parseSelectValue(string inputName, HtmlAgilityPack.HtmlNode selectedNode, string qs)
+        {
+            string[] parts = qs.Split(new char[] { '&' });
+
+            //find the appropriate key/value pair in the querystring
+            foreach (string nvp in parts)
+                if (nvp.StartsWith(inputName))
+                    return nvp.Substring(inputName.Length + 1);
+
[…]

### 2010-03-01 paper/fois2010/foisOct2010.tex
added the fois

\documentclass{IOS-Book-Article}
\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}
\usepackage{setspace} 
%\usepackage[mtplusscr,mtbold]{mathtime}
\usepackage{times}
\normalfont
\usepackage[T1]{fontenc}

\begin{document}
\begin{frontmatter}

\title{An Ontological Query Model to Support Question Answering in the Deep Web%
\thanks{The Morpheus Project is funded by NSF Grant 0712799}}
\runningtitle{An Ontological Query Model to Support Question Answering in the Deep Web}

\author[A]{\fnms{Christan} \snm{Grant}%
\thanks{Corresponding Author: Christan Grant, CSE E457-8, PO Box 116120, Gainesville, Florida, 32611-6120; Email: cgrant@cise.ufl.edu.}},
\author[A]{\fnms{Clint} \snm{P. George}},
\author[A]{\fnms{Jeff T.} \snm{DePree}},
\author[A]{\fnms{Peter J.} \snm{Dobbins}}
and
\author[A]{\fnms{Joseph N.} \snm{Wilson}}

\runningauthor{C. Grant et al.}
\address[A]{Database Research Center, Computer and Information Science and Engineering Department, University of Florida, Gainesville, FL, USA}

\begin{abstract}
The \emph{deep web} holds millions of data sources that are available for use within question answering systems.  But access to the information they provide is difficult because of ad-hoc search methods, varied structures, and restrictions imposed by terms of use.  Efficient methods to discover and obtain these data are a key to developing more powerful question answering systems.  In order to support discovery in this setting, we propose an ontological model to act as a \textit{lingua franca} to translate between natural language imperative or interrogative clauses and deep web page interaction specifications.  As a corollary, we present an ontology matching algorithm to support the translation of clauses to answers.
\end{abstract}

\begin{keyword}
Deep Web\sep NLP\sep Question Answering\sep Ontology Matching
\end{keyword}

\end{frontmatter}

\thispagestyle{empty}
\pagestyle{empty}

%-------------------------------------------------------------------------------

\section*{Introduction}

The \emph{deep web} consists of all the on-line information that is not subject to direct search by traditional search engines.  It is estimated to contain two to three orders of magnitude of structured data beyond the information that is currently accessible via traditional search engine techniques \cite{1454163}.  In addition to containing more information than the shallow web, the deep web is more dynamic and is not indexed.  Methodologies are now being investigated to improve the ability of search and discovery engines to locate relevant deep web information \cite{1080042, 1244355, 1065407, 1060760}.

Some early deep web resource discovery systems try to use sample queries to extract information from forms and index the resulting pages \cite{10.1109/WIIAT.2008.392}. They then use entity extraction techniques to discover the type of information provided.  However, sampling web forms can overload web servers and violate their terms of use agreements.  Other systems create \emph{wrappers} around the deep web form, that is, programs that treat web forms as functions with inputs and outputs.  For these wrappers to support an intelligent deep web discovery engine, they must be accurate and robust.

Estimates from early work suggest that it takes users an average of 30 minutes to create a traditional wrapper for a deep website \cite{transformscout}.  Consider a specific vertical market, such as travel or aftermarket auto parts. Relevant deep web sources can be hosted on up to 10,000 different web servers, thus wrapping all of them would take about 5,000 hours, or 2.5 person years.  It is clear that traditional deep web wrapping techniques cannot scale to solve such problems.

To address the problem of exploiting information in the deep web, we are developing a deep web question answering system.  We use sample user interactions to build a large body of answerable questions. When presented with a question, a user searches the web, querying deep web sources to find an answer. We record the search process associated with answering each question. Questions are represented using an ontological model and the search process is formalized as a \emph{query resolution mechanism} (QRM).

We choose to represent queries using ontologies because they provide a proven method of knowledge transfer \cite{DBLP:conf/kr/CiocoiuN00}. In particular, we employ the popular OWL markup language.\footnote{OWL Web Ontology Language. http://www.w3.org/TR/owl-ref/} This choice allows us to exploit work in ontology alignment to compare new queries to example queries for which QRMs exist and also to rank those QRMs by their relevance.

This paper includes the following:  
\begin{itemize}
\item It presents a model for supporting question answering with deep web page interactions.

\item It provides an ontological model that acts as an intermediate language for natural language queries and their associated deep web page interactions.

\item It presents an ontological matching algorithm that can be used to identify and rank relevant sample queries and their associated QRMs. 
\end{itemize}

\section{Ontology Representation}
%-------------------------------------------------------------------------------
To motivate our modeling problem, we consider the following question: "What is the cheapest five-star hotel in Zurich on October 4, 2010?" Natural language queries of this sort cannot be processed directly by our current system. Instead, we use a \emph{semi-structured query} (SSQ) representation. Each SSQ is associated with a realm (such as travel, sporting events, recreation, etc.) and can contain four types of contextual clauses: \emph{who, what, when,} and \emph{where}, possibly having modifiers.  Each context represents an input or an output of the query but not both. For our example, the inputs are \emph{where} (Zurich) and \emph{when} (4, October 2010), and the output is \emph{what} (cheapest five-star hotel).

If an input or an output of an SSQ has a contextual class association, it is said to be \emph{qualified}.  Each input and output of the sample queries used to build our QRMs is qualified, thus, we refer to these as fully-qualified SSQs.

\subsection{Deep Web Model}
%-------------------------------------------------------------------------------
Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.  Many of the accesses involve clicks through web forms to resulting pages.  We have developed a model that represents the various actions a user may carry out during this process.  We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).

During the answer retrieval process, a user discovers an element of the query's result on a web page.  Next, she highlights that element, typically a text string.  This highlight allows the QRR to record the source of  the query's answer.  The QRR stores all information from the user query in our data store.  When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.

The discovery process can be broken down into three cases:
\begin{enumerate}
\item The user typed in a URL  and highlighted part of or all the answer. 
\item The user typed in a URL, clicked a link, and found part or all of the answer. 
\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
\end{enumerate}

Any discovery process  consists of a sequence of these transactions.  Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.  An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.  The QRR builds the completed user collection process into a QRM.  The following is a mathematical formulation of information collected for user web interactions.\\

A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:

\begin{enumerate}

\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.

\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.

\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$. $P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
\\
Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
\\
Let $K$ be the set of all string constants.
\begin{itemize}
\item URI $U_1 \in K$ is a string and \\
for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,

\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
\end{itemize}

\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.

\item $R$ is an ontological realm.

\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.

\end{enumerate}

%TODOAdd more explanaition to the

\subsection{Query Model}
%-------------------------------------------------------------------------------

It is straight-forward to translate a fully-qualified SSQ, represented by $\Upsilon$ and $\Omega$, into a class in an OWL ontology.  Any ontology that characterizes SSQs must define object properties for each of the different contexts that qualify the inputs and outputs of the query.

A member of the Context class contains a reference to an individual belonging to a given Context, as well as zero or more modifiers that determine the desired qualities of the referenced individual.  In most cases, the Context properties contained within an SSQ will reference subclasses of this base Context class. Here is the hotel Context from the motivating example given above.
\texttt{\small{
\\
\\
\indent <owl:Class rdf:ID=\textquotedbl{}HotelContext\textquotedbl{}>\\
\indent \indent <rdfs:subClassOf rdf:resource=\textquotedbl{}\#ContextClass\textquotedbl{} />\\
\indent \indent <owl:Restriction>\\
\indent \indent \indent <owl:onProperty rdf:resource=\textquotedbl{}\#ValueWithinContext\textquotedbl{} />\\
\indent \indent \indent <owl:maxCardinality \\
\indent \indent \indent \qquad rdf:datatype=\textquotedbl{}\&xsd;nonNegativeInteger\textquotedbl{}>
\\\indent \indent \indent \qquad 1</owl:maxCardinality>\\
\indent \indent \indent <owl:allValuesFrom rdf:resource=\textquotedbl{}\#Hotel\textquotedbl{} />\\
\indent \indent </owl:Restriction>\\
\indent \indent <owl:Restriction>\\
\indent \indent \indent <owl:onProperty rdf:resource=\textquotedbl{}\#Modifier\textquotedbl{} />\\
\indent \indent \indent <owl:hasValue rdf:resource=\textquotedbl{}\#Cheapest\textquotedbl{} />\\
\indent \indent </owl:Restriction>\\
\indent \indent <owl:Restriction>\\
\indent \indent \indent <owl:onProperty rdf:resource=\textquotedbl{}\#Modifier\textquotedbl{} />\\
\indent \indent \indent <owl:hasValue rdf:resource=\textquotedbl{}\#Five-Star\textquotedbl{} />\\
\indent \indent </owl:Restriction>\\
\indent </owl:Class>\\
\\	 
}}
The object property \emph{hasRealm} maps each query to the subject matter to which it relates.  The elements that can serve as the realm of a query can be individuals of any type.

For each SSQ, a class is constructed that defines a specific type of query which has input and output contexts that belong to a limited set of classes.  Here is the SSQ class from the motivating example given above.
\texttt{\small{
\\
\\
\indent <owl:Class rdf:ID=\textquotedbl{}SSQ-0\textquotedbl{}>\\
\indent \indent <hasRealm rdf:resource=\textquotedbl{}\#Travel\textquotedbl{}/>\\
\indent \indent <owl:Restriction>\\
\indent \indent \indent <owl:onProperty rdf:resource=\textquotedbl{}\#Where\_IN\textquotedbl{} />\\
\indent \indent \indent <owl:allValuesFrom rdf:resource=\textquotedbl{}\#CityContext\textquotedbl{} />\\
\nopagebreak\indent \indent </owl:Restriction>\\
\indent \indent <owl:Restriction>\\
\nopagebreak\indent \indent \indent <owl:onProperty rdf:resource=\textquotedbl{}\#When\_IN\textquotedbl{} />\\
\indent\indent\indent <owl:allValuesFrom
rdf:resource=\textquotedbl{}\#DateContext\textquotedbl{} />\\
\indent\indent </owl:Restriction>\\
\indent \indent <owl:Restriction>\nopagebreak\\
\nopagebreak\indent \indent \indent <owl:onProperty 
rdf:resource=\textquotedbl{}\#What\_OUT\textquotedbl{} />\\
\indent \indent \indent <owl:allValuesFrom rdf:resource=\textquotedbl{}\#HotelContext\textquotedbl{} />\\
\indent \indent </owl:Restriction>\\
\indent </owl:Class>\\
}}

This class restricts its properties in such a way that it will only be matched to other SSQs if they involve inputs and outputs from the same classes, that is, ones that make queries about hotels for a given city and date.

%-------------------------------------------------------------------------------

\section{Ontology Matching}

In order to match a new query with a QRM within our data store, we have defined similarity measures between the ontologies of the new query and the canidate QRMs. These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs. The similarity measures are implemented in two scenarios: \textit{online execution} and \textit{offline mode}. The \textit{online execution} is time sensitive and is used primarily for relating newly defined QRMs to the QRMs in the store. During \textit{offline execution}, the system clusters similar QRMs.

The similarity measure for the QRM ontologies is determined by the following components.
\begin{enumerate}
    \item QueryClass: an OWL class and the root of the QRM ontology structure.
    \item hasRealm: an OWL object property with its domain as the QRM Query class and its range as a realm class.
    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
    \item QRMClass: an OWL class which is created from the components described above.
\end{enumerate}
Based on this ontology structure and the execution scenarios, we have created two algorithms for finding the matches between QRM ontologies. The first algorithm is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches. We use this algorithm for \textit{online excution}, where we consider the realm class and context property ranges for determining QRM similarity. The second algorithm is based on the ontology structure and semantics \cite{ST05}. This algorithm is used for \textit{offline execution}, where it finds the similarity between the QRM ontology classes, properties, and individuals and merges the similar ontology entities. Subsections \ref{sec:ctd}, \ref{sec:oqom}, and \ref{sec:oss} explain how we can make use of our algorithms for finding the similarities between the QRM Ontologies.

%-------------------------------------------------------------------------------

\subsection{Class Divergence}
\label{sec:ctd}
We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology. We write $S \prec T$ for the reflexive transitive closure of the superclass relation. Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$. The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).  Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:

\begin{equation}
d_{class}(S, T) =  \begin{cases}

0&if S.{uri} \equiv T.{uri}\\
d(S, T)&if S \prec T\\
1&if T \prec S\\
d(S,root) + d(S,C) + d(T,C)&otherwise
\end{cases}
\end{equation}

We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.

Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor. This is an important property in determining the compatibility of classes for answering queries.  If a QRM answers queries concerning an ancestor class, it is more relevant that a QRM that answers queries from any non-ancestral class.

% Algorithm 1: figure  
\begin{figure}[t]
\centering
\includegraphics[width=120mm]{algorithm1.png}
\caption{Graphical representation of an Ontology}
\label{fig:graphonto}
\end{figure}

Figure \ref{fig:graphonto} illustrates the calculation of class divergence. This sample ontology is rooted at the class \textit{Accommodations}. The arrows represent the inheritance relationship between the classes in the topology.
Suppose we want to find the divergence $d_{class}(Hotel,Motel)$. Both are subclasses of the class \textit{Hotel/Motel} ($C$). They share the path from \textit{Hotel/Motel} to the $root$. So, the unnormalized divergence $d(Hotel, root)$ is two (shown by bold arrows), $d(Motel, Hotel/Motel)$ is one (dashed arrow), and $d(Hotel, Hotel/Motel)$ is one (dashed arrow). Thus, $d(Hotel, Motel)$ is four, which corresponds to a normalized value of $2/3$. 
Consider $d_{class}(Motel,Hostel)$. The classes $root$ and $C$ in the definition of $d_{class}$ are the same in this case so we add $d(Motel,Accommodations)$ (two), $d(Hostel, Accommodations)$ (one), and $d(Motel,Accommodations)$ (two), yielding a total unnormalized divergence of five, or a normalized divergence of $5/6$.

%-------------------------------------------------------------------------------

\subsection{QRM Ontology Matching}
\label{sec:oqom}

We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.  Each SSQ will have four input classes, four output classes, and one realm.  We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ. If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.

The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \Omega_{Q_1}, ... , \Omega_{Q_4}, R_Q \rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \Omega_{S_1}, ... , \Omega_{S_4}, R_S \rangle$ is

\begin{equation}
\label{qrmsimilarity}
R\left({S,Q}\right) = 1- \pi_9 d_{class}(R_S,R_Q) + \sum_{k=1}^4\pi_k d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})+ \sum_{j=1}^4\pi_{4+j}d_{class}(\Omega_{S_j},\Omega_{Q_j})
\end{equation}

\noindent where the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
\begin{equation}
\label{piconstraint1}
\sum_{k=1}^{9} {{\pi}_k} = 1
\end{equation}
\noindent and for $1 \leq i \leq 9$
\begin{equation}
\label{piconstraint2}
{\pi}_i > 0
\end{equation}

If an SSQ and a QRM have identical classes for all inputs, all outputs, and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.

%-------------------------------------------------------------------------------

\subsection{Ontological Structural Similarity}
\label{sec:oss}
Employing user input brings about the likelihood that redundant ontological elements will be inserted into our context class ontology. The work described here is aimed at finding ontological similarities between our context classes and QRMs so that we can reduce the number of redundant and incomparable elements. The ontological structural measure is determined by examining the ontological structure and semantics of each QRM. Our analysis depends on the ontology entities such as classes, individuals, properties, superclasses, and subclasses. The structural similarity is obtained from the following dissimilarity measures.

\textit{\textbf{(a)}} class dissimilarity: This measure ($dist_{class}$) is determined by these features of the source and target classes: class URIs, parent classes, and class properties.

\textit{\textbf{(b)}} property dissimilarity: This measure ($dist_{property}$) is determined by these features of the source and target class properties: property URIs, property domains ($classes$), and property ranges ($classes$).

\textit{\textbf{(c)}} individual dissimilarity: This measure ($dist_{individual}$) for the source and target individuals is determined by their URIs, properties, and class types.

\subsubsection{Class dissimilarity}
Let $S$ be a source class and $T$ be a target class. The set of all the parent classes of the class $C$ is $parent(C)$ and the set of all the properties of the class $C$ is $property(C)$. We define two levels of class dissimilarity.\\
\indent \textit{\textbf{Level 0:}} In this level, the distance is measured using the dissimilarity between the OWL entity URIs ($dist_{URI}$):

\begin{enumerate}

\item URI dissimilarity for source and target classes 
\\ $f_1(S, T) = dist_{URI}(S.{uri},T.{uri})$

\item URI dissimilarity for all the class properties
\\$f_2(S, T) = dist_{URI}(property_i.{uri},property_j.{uri}), 
\\\forall property_i \in property(S),\quad\forall property_j \in property(T) $

\item URI dissimilarity for all the parent classes
\\$f_3(S, T) = dist_{URI}(class_i.{uri},class_j.{uri}), 
\\\forall class_i \in parent(S),\quad \forall class_j \in parent(T) $

\end{enumerate}

\indent \textit{\textbf{Level 1:}} Here we calculate the URI dissimilarity in the same manner as in Level 0. It calculates class dissimilarity [Eq. \eqref{classsimilarity}] and property dissimilarity [Eq. \eqref{propertysimilarity} ] for each parent classes and the properties of the source and target classes.  The two additional steps are:
\begin{enumerate}

\item Compute property dissimilarity for all of the class properties 
\\$f_4(S, T) = dist_{property}(property_i,property_j), 
\\ \forall property_i \in property(S),\quad \forall property_j \in property(T) $

\item Compute class dissimilarity for all of the super classes of the class 
\\$f_5(S, T) = dist_{class}(class_i,class_j),
\\\forall class_i \in parent(S),\quad\forall class_j \in parent(T) $

\end{enumerate}

\indent Finally, we combine all these distances into a combinatorial measure for the complete OWL class dissimilarity measure

\begin{equation}
\label{classsimilarity}
dist_{class}(S, T)= \sum_{i=1}^N {{\alpha}_i f_i(s, t)}
\end{equation}
\noindent where ${\alpha}_i$ is the weight for a feature $i$, $N$ is the number of features, and satisfies the conditions
\begin{equation}
\label{alphaconstraint1}
\sum_{i=1}^{N} {{\alpha}_i} = 1
\end{equation}
\noindent and 
\begin{equation}
\label{alphaconstraint2}
{\alpha}_i \geq 0  
\end{equation}

\subsubsection{Property dissimilarity}
Let $S_P$ be a source property and $T_P$ be a target property. The set of all the domain classes of the OWL property $P$ is $domain(P)$ and the set of all the range classes of the OWL property $P$ is $range(P)$. We define two levels of property dissimilarity.\\
\indent\textit{\textbf{Level 0:}} In this level, the distance is measured using the dissimilarity between the OWL entity URIs ($dist_{URI}$):
\begin{enumerate}
    \item URI dissimilarity for source and target properties 
    \\ $f_1(S_P, T_P)= dist_{URI}(S_P.{uri}, T_P.{uri})$

    \item URI dissimilarity for source and target property domains
    \\ $f_2(S_P, T_P)= dist_{URI}(class_i, class_j ), 
    \\ \forall class_i \in domain(S_P),\quad\forall class_j \in domain(T_P)$

    \item URI dissimilarity for source and target property ranges
    \\ $f_3(S_P, T_P)= dist_{URI}(class_i, class_j ),
    \\ \forall class_i \in range(S_P),\quad\forall class_j \in range(T_P)$
\end{enumerate}

\indent\textit{\textbf{Level 1:}} Here we calculate the URI dissimilarity for domain and ranges of both the  source and target properties, in the same manner as in Level 0. Additionally, we calculate class dissimilarity [Eq. \eqref{classsimilarity}] for both domain and range. The two additional steps are:
\begin{enumerate}
    \item Compute property domain dissimilarity for all domains 
    \\ $f_4((S_P, T_P)= dist_{class}(class_i, class_j ),
    \\ \forall class_i \in domain(S_P),\quad \forall class_j \in domain(T_P)$

    \item Compute property range dissimilarity for all ranges  
    \\ $f_5(S_P, T_P)= dist_{class}(class_i, class_j),
    \\\forall class_i \in range(S_P),\quad \forall class_j \in range(T_P)$
\end{enumerate}
\indent Finally, we combine all these distances into a combinatorial measure for the complete OWL property dissimilarity measure
\begin{equation}
\label{propertysimilarity}
dist_{property}(S_P, T_P) = \sum_{i=1}^N {{\beta}_i f_i(S_P, T_P)} 
\end{equation}
where ${\beta}_i$ is the weight for a feature $i$ and satisfies the conditions 
\begin{equation}
\label{betaconstraint1}
\sum_{i=1} {{\beta}_i} = 1
\end{equation}
and 
\begin{equation}
\label{betaconstraint2}
{\beta}_i \geq 0
\end{equation}

% --------------------------------------------------------------------------------

\section*{Future Work}
The QRMS are generalized representations of actual user queries. We are currently building the application engine that executes QRMs which are matched to a user query. Additionaly, we are working on leveraging our matching algorithm to chain multiple QRMs to create new web interactions.

We are building a statisical translation model to take natural language questions and turn them in to SSQs. We have begun a user study to identify how users can naturally translate their queries into our SSQ model. We anticipate that the user will not need to define the SSQ in the future but the translation will be automatic.

The current implementation does not consider \textit{modifiers} in finding the dissimilariy measure between context properties.  If the order of the \textit{modifiers} is changed within a context class, there could be an impact on the meaning of a query.  We will incorporate this consideration into our matching algorithms.

In addition, another step is to consider \textit{online execution} as a class similarity matching problem.  We can then build classifier systems using the machine learning techniques. Similarly, we can extend the QRM merging process during \textit{offline execution} to a clustering problem and implement conventional statistical methods to solve it. Finally, the parameters $\alpha$, $\beta$, and $\pi$ mentioned in the equations [Eq. \eqref{classsimilarity}, \eqref{propertysimilarity}, and \eqref{qrmsimilarity}] are defined manually. We are considering estimation methods that will be able to capture the relevance of the contexts, realm, and modifers of the QRM ontologies.

% --------------------------------------------------------------------------------

\section*{Conclusion}
We have developed ontologies to model user web interaction and user web queries. We have also presented a matching algorithm to discover user web interactions based on a query. Our descriptions are in the OWL language. While we develop our own classes, because of the unified language, our class structure works well with existing ontologies such as \emph{dbpedia} and the \emph{New York Times} corpus. This model will allow question answering systems to use the deep web as a corpus.

% --------------------------------------------------------------------------------

\bibliography{citations}
\bibliographystyle{acm}

\end{document}

### 2010-03-01 paper/semsearch10/paper.tex
latest changes

@@
 \documentclass{www2010-submission}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \begin{document}
@@
 \title{Leveraging Semantics for a Deep Web Question and Answering System} 
-\numberofauthors{7}
+\numberofauthors{1}
 \author{
-	\alignauthor Christan Grant\\
-	\email{cgrant@cise.ufl.edu}
+	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
+	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
+\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
+}
 
-	\alignauthor Clint P. George\\
-	\email{clintpg@gmail.com}
-
-	\alignauthor Joseph N. Wilson\\
-	\email{jnw@cise.ufl.edu}
-
-	\alignauthor Peter J. Dobbins\\
-	\email{pjd@cise.ufl.edu}
-
-	\alignauthor Jeff T. Depree\\
-	\email{jepree@cise.ufl.edu}
-
-	\alignauthor Christopher A. Shields\\
-	\email{cshields@cise.ufl.edu}
-
-	\alignauthor Joir-dan Gumbs\\
-	\email{jgumbs@cise.ufl.edu}
-
-	\sharedaffiliation
-	\affaddr{Department of Computer and Information Science and Engineering }  \\
-	\affaddr{University of Florida} \\
-	\affaddr{Gainesville, Florida 32611-6120}
-}
 \date{April 26,2010}
@@
 % Christan
-- The best way to answer questions is to see/know if a question has been asked before.
-- IEEE potentials talks about the the beaten trail.
-- Use reuse in the specific domain of question answering
+- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
+- Typical search engines have several repeat queries.
+- We believe that treating these repeat visits as special visits will enhance user search experience
+- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
 - 
@@
 Consider the abbreviated Markov blanket for the category Basketball:
-\includegraphics[width=4in,height=4in,viewport=0 0 300 300]{abbreviated_basketball_blanket.png}
+%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}
 
-The subcategories of the category Basketball (… Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams…) can be seen as grabbing information specifc to the category.
+The subcategories of the category Basketball (...
+Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
 The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
@@
 
+\begin{algorithm}
+\caption{Blanket Subject Retrieval}
+\label{alg1}
 	\begin{algorithmic}
-\function BlanketSubjectRetrieval(blanket, maxLevel):
-	\for{category in blanket}
-		subjectSet.add(grabSubjects(category))
-		diff = afterSize - beforeSize;
-		\if{ diff \leq \alpha \and category is a subcategory}
-			PlusOneMechanism(category, maxLevel)
-		\endif
-	\endfor
-	return subjectSet
+	\STATE BlanketSubjectRetrieval(blanket, maxLevel):
+		\FOR{category c in blanket}
+			\STATE subjectSet.add(grabSubjects(c))
+			\STATE diff = afterSize - beforeSize
+			\IF{ diff \leq \alpha and c is a subcategory}
+				\STATE PlusOneMechanism(category, maxLevel)
+			\ENDIF
+		\ENDFOR
+	\STATE return subjectSet
 	\end{algorithmic}
+\end{algorithm}
 
+\begin{algorithm}
+\caption{Plus One Mechanism}
+\label{alg2}
 	\begin{algorithmic}
-\function PlusOneMechanism(category, level)
-	plusOneSet = grabPlusOneSubcategories(category)
-	\for{ subcategory in plusOneSet do}
-		subjectSet.add(grabSubjects(subcategory));
-		diff = afterSize - beforeSize
-		\if{ diff \leq \alpha \and level \gt 0}
-			PlusOneMechanism(subcategory, level - 1);
-		\endif
-	\endfor
+	\STATE PlusOneMechanism(category, level)
+		\STATE plusOneSet = grabPlusOneSubcategories(category)
+		\FOR{ subcategory in plusOneSet}
+			\STATE subjectSet.add(grabSubjects(subcategory))
+			\STATE diff = afterSize - beforeSize
+			\IF{ diff \leq \alpha \and level \gt 0}
+				\STATE PlusOneMechanism(subcategory, level - 1);
+			\ENDIF
+		\ENDFOR
 	\end{algorithmic}
+\end{algorithm}
 

### 2010-03-01 trunk/paper/semsearch10/paper.tex
latest

@@
 \title{Leveraging Semantics for a Deep Web Question and Answering System} 
-\numberofauthors{5}
+\numberofauthors{1}
 \author{
-	\alignauthor Christan Grant\\
-	\email{cgrant@cise.ufl.edu}
+	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
+	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
+\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
+}
 
-	\alignauthor Clint P. George\\
-	\email{clintpg@gmail.com}
-
-	\alignauthor Joseph N. Wilson\\
-	\email{jnw@cise.ufl.edu}
-
-	\alignauthor Joir-dan Gumbs\\
-	\email{jgumbs@cise.ufl.edu}
-
-	\alignauthor Christopher A. Shields\\
-	\email{cshields@cise.ufl.edu}
-
-	\sharedaffiliation
-	\affaddr{Department of Computer and Information Science and Engineering }  \\
-	\affaddr{University of Florida} \\
-	\affaddr{Gainesville, Florida 32611-6120}
-}
 \date{April 26,2010}
@@
 % Christan
+- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
+- Typical search engines have several repeat queries.
+- We believe that treating these repeat visits as special visits will enhance user search experience
+- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
+- 
+-
 
@@
 %joir-dan
+Once the semantic hierarchy is created, the next step is to create training data for the system.
+The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
+The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
+The problem with this approach is the page density varies greatly across the heterarchy.
+Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
+Considering that the categorical structure is a directed acyclic graph (Suchanek et al., 2008), we consider the use of a Markov Blanket (Friedman et al., 1997) in describing a particular category.
+The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
+While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
+
+Consider the abbreviated Markov blanket for the category Basketball:
+%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}
+
+The subcategories of the category Basketball (...
+Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
+The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
+The spousal categories are an abstract description of the subcategories.
+
+Clustering the categories alone does not guarantee adequate corpus creation.
+Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
+In the case of Wikipedia, there are an average of 25.7 pages per category (Yu et al., 2007).
+The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
+Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
+This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
+We set this number to 10 * average, or 39.
+level represents how many extra levels we are to go down in the hierarchy, if necessary.
+SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
+
+\begin{algorithm}
+\caption{Blanket Subject Retrieval}
+\label{alg1}
+	\begin{algorithmic}
+		\STATE BlanketSubjectRetrieval(blanket, maxLevel):
+		\FOR{category c in blanket}
+			\STATE subjectSet.add(grabSubjects(c))
+			\STATE diff = afterSize - beforeSize
+			\IF{ diff \leq \alpha and c is a subcategory}
+				\STATE PlusOneMechanism(category, maxLevel)
+			\ENDIF
+		\ENDFOR
+		\STATE return subjectSet
+	\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Plus One Mechanism}
+\label{alg2}
+	\begin{algorithmic}
+		\STATE PlusOneMechanism(category, level)
+		\STATE plusOneSet = grabPlusOneSubcategories(category)
+		\FOR{ subcategory in plusOneSet}
+			\STATE subjectSet.add(grabSubjects(subcategory))
+			\STATE diff = afterSize - beforeSize
+			\IF{ diff \leq \alpha \and level \gt 0}
+				\STATE PlusOneMechanism(subcategory, level - 1);
+			\ENDIF
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+
+The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
+Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
+
+When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
 
@@
 % Christan
+The response pages created by querying web forms are
+dynamically generated with a templated structure.
+This
+generalization per page is done using the GenPath algorithm developed by Badica et al.
+\cite{Badica06}.
+Additionally, the community may be able to answer a particular SSQ using many different page interactions.
+Therefore, we proposed a method of generalizing extraction path to a result across pages.
+This method removes unnecessary page interactions and finds the shortest path to the result pages.
+
+The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
+Generalizing the extraction paths help to overcome small structural changes.
+If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
+Morpheus allows users to rate the freshness of QRMs.
 

### 2010-03-01 trunk/paper/semsearch10/paper.tex
latest

@@
 \documentclass{www2010-submission}
-\usepackage{algorithm}
-\usepackage{algorithmic}
 \begin{document}
@@
 	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
+\email{\{ cgrant, cpj, jnw, pjd, jdepree, cshields, jg \} @cise.ufl.edu}
 }
-
 \date{April 26,2010}
@@
 % Christan
-- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
+- IEEE potentials article talks discussed the idea of using the beaten trail. \cite{5379671} To solve problems
 - Typical search engines have several repeat queries.
@@
 - To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
-- 
--
 
-\section{Statistical Hierarchy}
-\subsection*{Class Hierarchy}
-%clint
+\section{Establishing the Semantic Hierarchy}
+\subsection{Class Hierarchy} 
+% Author: Clint P. George 
+Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
+The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
+We cannot find any robust existing ontology library of that nature for this purpose.
+So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
+Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
+The OWL ontology [citation needed] format is followed in this process.
+The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
+Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
+
+%-------------------------------------------------------------------------------
+
 \subsection*{Markov Blanket}
@@
 Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph (Suchanek et al., 2008), we consider the use of a Markov Blanket (Friedman et al., 1997) in describing a particular category.
+Considering that the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
 The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
@@
 
-Consider the abbreviated Markov blanket for the category Basketball:
-%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}
+% figure: abbreviated Markov blanket for the category Basketball  
+\begin{figure}[t]
+\centering
+\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
+\caption{Abbreviated Markov blanket for the category Basketball}
+\label{fig:abbrv_bb_blanket}
+\end{figure}
 
@@
 Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category (Yu et al., 2007).
+In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
 The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
@@
 SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{algorithm}
-\caption{Blanket Subject Retrieval}
-\label{alg1}
-	\begin{algorithmic}
-		\STATE BlanketSubjectRetrieval(blanket, maxLevel):
-		\FOR{category c in blanket}
-			\STATE subjectSet.add(grabSubjects(c))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha and c is a subcategory}
-				\STATE PlusOneMechanism(category, maxLevel)
-			\ENDIF
-		\ENDFOR
-		\STATE return subjectSet
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Plus One Mechanism}
-\label{alg2}
-	\begin{algorithmic}
-		\STATE PlusOneMechanism(category, level)
-		\STATE plusOneSet = grabPlusOneSubcategories(category)
-		\FOR{ subcategory in plusOneSet}
-			\STATE subjectSet.add(grabSubjects(subcategory))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha \and level \gt 0}
-				\STATE PlusOneMechanism(subcategory, level - 1);
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
 
@@
 % Chris
+Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
+Many of the accesses involve clicks through web forms to resulting pages.
+We have developed a model that represents the various actions a user may carry out during this process.
+We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
+
+During the answer retrieval process, a user discovers an element of the query's result on a web page.
+Next, she highlights that element, typically a text string.
+This highlight allows the QRR to record the source of  the query's answer.
+The QRR stores all information from the user query in our data store.
+When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
+
+The discovery process can be broken down into three cases:
+\begin{enumerate}
+\item The user typed in a URL  and highlighted part of or all the answer. 
+\item The user typed in a URL, clicked a link, and found part or all of the answer. 
+\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
+\end{enumerate}
+
+Any discovery process  consists of a sequence of these transactions.
+Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
+An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
+The QRR builds the completed user collection process into a QRM.
+The following is a mathematical formulation of information collected for user web interactions.\\
+
+A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
+
+\begin{enumerate}
+
+\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
+
+\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
+
+\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
+$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
+\\
+Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
+\\
+Let $K$ be the set of all string constants.
+\begin{itemize}
+\item URI $U_1 \in K$ is a string and \\
+for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
+
+\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
+for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
+\end{itemize}
+
+\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
+
+\item $R$ is an ontological realm.
+
+\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
+
+\end{enumerate}
+
+%-------------------------------------------------------------------------------
+
 \subsection{Generalization}
 % Christan
-The response pages created by querying web forms are
-dynamically generated with a templated structure.
-This
-generalization per page is done using the GenPath algorithm developed by Badica et al.
+The response pages created by querying web forms are dynamically generated with a templated structure.
+This generalization per page is done using the GenPath algorithm developed by Badica et al.
 \cite{Badica06}.
@@
 
-\section{Semantic Query Answering}
+%-------------------------------------------------------------------------------
+
+\section{Natural Language Queries}
 \subsection{Semi-Structured Query}
@@
 \subsection{SSQ Ranking}
-% Clint
+In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
+These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
+The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
+The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
+During \textit{off-line execution}, the system clusters similar SSQs.
+
+The similarity measure for the SSQ ontologies is determined by the following components.
+\begin{enumerate}
+    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
+    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
+    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
+    \item SSQClass: an OWL class which is created from the components described above.
+\end{enumerate}
+Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
+It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
+We consider the realm class and context property ranges for determining SSQ similarity.
+Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
+
+%-------------------------------------------------------------------------------
+
+\subsubsection{Class Divergence}
+\label{sec:ctd}
+We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
+We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
+Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
+The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
+Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
+The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
+
+\begin{equation}
+d_{class}(S, T) = \begin{cases}
+0 & if S.{uri} \equiv T.{uri}\\
+d(S, T) & if S \prec T\\
+1 & if T \prec S\\
+d(S,root) \\+ d(S,C) + d(T,C) & otherwise
+\end{cases}
+\end{equation}
+
+We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
+
+Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
+that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
+This is an important property in determining the compatibility of classes for answering queries.
+If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
+
+% Algorithm 1: figure  
+\begin{figure}[t]
+\centering
+\includegraphics[width=90mm]{class_divergence.eps}
+\caption{Graphical representation of an Ontology}
+\label{fig:class_divergence}
+\end{figure}
+
+Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
+This sample ontology is rooted at the class \textit{Accommodations}.
+The arrows represent the inheritance relationship between the classes in the topology.
+
+Suppose we want to find the divergence $d_{class}$\textit{(Hotel, Motel)}.
+Both are subclasses of the class \textit{Hotel/Motel} ($C$).
+They share the path from \textit{Hotel/Motel} to the $root$.
+So, the unnormalized divergence \textit{d(Hotel, root)} is two (shown by bold arrows), \textit{d(Motel, Hotel/Motel)} is one (dashed arrow), and \textit{d(Hotel, Hotel/Motel)} is one (dashed arrow).
+Thus, \textit{d(Hotel, Motel)} is four, which corresponds to a normalized value of $2/3$.
+
+Consider $d_{class}$\textit{(Motel, Hostel)}.
+The classes $root$ and $C$ in the definition of $d_{class}$ are the same in this case so we add \textit{d(Motel, Accommodations)} (two), \textit{d(Hostel, Accommodations)} (one), and \textit{d(Motel, Accommodations)} (two), yielding a total unnormalized divergence of five, or a normalized divergence of $5/6$.
+
+%-------------------------------------------------------------------------------
+\subsubsection{SSQ Ontology Matching}
+\label{sec:oqom}
+
+We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
+Each SSQ will have four input classes, four output classes, and one realm.
+We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
+If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
+
+The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
+, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
+, \Omega_{S_4}, R_S \rangle$ is
+
+\begin{eqnarray}
+\label{qrmsimilarity}
+ R(S,Q) = 1 - (d_{R} + d_{\Upsilon} + d_{\Omega})
+\end{eqnarray}
+\noindent where 
+\begin{eqnarray}
+d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
+\end{eqnarray}
+\begin{eqnarray}
+d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
+\end{eqnarray}
+\begin{eqnarray}
+ d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
+\end{eqnarray}
+\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
+\begin{equation}
+\label{piconstraint1}
+\sum_{k=1}^{9} {{\pi}_k} = 1
+\end{equation}
+\noindent and for $1 \leq i \leq 9$
+
+\begin{equation}
+\label{piconstraint2}
+{\pi}_i > 0
+\end{equation}
+
+If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
+
+%-------------------------------------------------------------------------------
+
 \subsection{Query Re-Execution}
@@
 
-\section{References}
-Bayesian Network Classifers
-Friedman, Geiger, Goldszmidt 1997
-
-YAGO: A Large Ontology from Wikipedia and WordNet
-Fabian M. Suchanek, Gjergji Kasnecia, and Gerhard Weikuma 2008
-
-Ontology Evaluation: Using Wikipedia Categories for Browsing
-Yu, Thom, Tam 2007
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{citations}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
 

### 2010-03-01 trunk/paper/semsearch10/paper_old.tex
latest

--- 2010-03-01 trunk/paper/semsearch10/paper.tex
@@
 \subsection*{Class Hierarchy}
-%clint
+% Author: Clint P. George 
+Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
+The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
+We cannot find any robust existing ontology library of that nature for this purpose.
+So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
+Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
+The OWL ontology [citation needed] format is followed in this process.
+The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
+Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
+
+%-------------------------------------------------------------------------------
+
 \subsection*{Markov Blanket}
@@
 
-\begin{algorithm}
-\caption{Blanket Subject Retrieval}
+\begin{algorithmic}
 \label{alg1}
-	\begin{algorithmic}
 \STATE BlanketSubjectRetrieval(blanket, maxLevel):
@@
 	\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha and c is a subcategory}
+	\IF{ diff \leq a \and c is a subcategory}
 		\STATE PlusOneMechanism(category, maxLevel)
@@
 \end{algorithmic}
-\end{algorithm}
 
-\begin{algorithm}
-\caption{Plus One Mechanism}
 \label{alg2}
@@
 	\end{algorithmic}
-\end{algorithm}
 
@@
 % Christan
-The response pages created by querying web forms are
-dynamically generated with a templated structure.
-This
-generalization per page is done using the GenPath algorithm developed by Badica et al.
+The response pages created by querying web forms are dynamically generated with a templated structure.
+This generalization per page is done using the GenPath algorithm developed by Badica et al.
 \cite{Badica06}.

### 2010-03-01 generalizer/Form.py
working on Qre

@@ -9,7 +9,7 @@ from Page import Page
 class Form(Page, object):
 
         def __init__(self):
-		super(Form, self).__init__()
+		super(Form,self).__init__()
                 self.formInputs = list()
 		self.actionType = ActionType.Form
 

### 2010-03-01 generalizer/Link.py

@@ -7,7 +7,8 @@ from Page import Page
 class Link(Page,object):
 
 	def __init__(self):
-		super(Link,self).__init__()		
+		super(Link, self).__init__()		
+		self.actionType = ActionType.Link
 		pass
 
 def New(url, destinationUrl, xpath, pagesrc, timestamp):

### 2010-03-01 generalizer/Loader.py

@@ -65,7 +65,7 @@ def getNeededScriptInfo(id, isInput):
 		return results[0]
 
 #loads list of inputs for the given pagereference id
-def getPageInputs(pid):
+def getPageInputs(pid, formNode):
     
         NAME = 3
   
@@ -82,13 +82,31 @@ def getPageInputs(pid):
 	for r in forminputs:
 	
 		type = ""
+		
+		#need to deermine the input type
+		nodes = formNode.xpath("//node()[@name='"+r[NAME]+"']")
+		
+		if len(nodes) == 0:
+			return None	
+	
+		nodeTag = nodes[0].tag.lower()
 
-		if r[HILITE] != None and r[HILITE] != -1:	
-			type="highlight"	
-		elif r[SSQINPUT] != None and r[SSQINPUT] != -1:
-			type="userinput"
-		else: #if the value is a default, then parse the pagesrc to get the default value
-			type="default"
+		if nodeTag == 'select':
+			type = "select"
+		elif nodeTag == 'input':
+
+			if nodes[0].get('type') != None:
+				nodeTag = nodes[0].get('type').lower()
+				if nodeTag == 'textbox':	
+					type = 'textbox'
+				if nodeTag == 'radio':
+					type = 'radio'
+				else:
+					type = 'input'
+			else:
+				type = 'input'
+		else:
+			type = 'textbox'	
 			
 		inputList.append(Input.New(r[NAME], type, r[HILITE], r[SSQINPUT],""))
 
@@ -152,7 +170,7 @@ def GetQRMFromQuery (queryID):
 	
 #This function gets page references and page outputs and returns a query object	
 def getqrm(rowArray, qid, isQRMID, realmid):
-	
+
 	pageRows = rowArray[0]
 	
 	outputRows = rowArray[1]
@@ -225,7 +243,7 @@ def getqrm(rowArray, qid, isQRMID, realmid):
 		ssqClasses = executeQuery(classQuery)
 
 	qrm.ssqClasses = extractSsqElements(ssqClasses)
-		
+
 	return qrm
 
 #get the class data into ssqelement objects and return a list of them
@@ -253,7 +271,7 @@ def exciseRange(i,j,a):
 def getCondensedQrm(pps, outs):
 
 	condensedList = list()
-	
+		
 	HILITE_HLID = 0
 	ANSWERID = 10
 	ppsTime = 8
[…]

### 2010-03-01 generalizer/QueryGeneralizer.py

@@ -54,9 +54,9 @@ def GeneralizeQueries(qrmid, queryid):
     #Need to ensure the usages of the SSQ inputs and highlights is the same between both entities
      
     #Normalize each query separately
-    qrm1 = normalize(qrm1)
+    #qrm1 = normalize(qrm1)
     
-    qrm2 = normalize(qrm2)
+    #qrm2 = normalize(qrm2)
     
     #Generalization
     #generalize all matching pages (same page, same form)
@@ -186,7 +186,7 @@ def compareExtractions(genXpath, nonGenXpath, src):
     return STRONG_SIMILARITY
         
 def generalizeQRMS(q1, q2):
-    
+
     qS = None
     qL = None
     
@@ -272,9 +272,9 @@ def generalizeActions(p1, p2):
 
 	print('Processing link click action')
 
-       	p1Epath.xpath_to_epath(p1.pagesrc,p1.links[i])
+       	p1Epath.xpath_to_epath(p1.pagesrc,p1.xpath)
         
-       	p2Epath.xpath_to_epath(p2.pagesrc,p2.links[i])
+       	p2Epath.xpath_to_epath(p2.pagesrc,p2.xpath)
         
        	p3Epath = g.Learn([p1Epath,p2Epath])
         
@@ -283,11 +283,11 @@ def generalizeActions(p1, p2):
 	p3 = Link.New(p1.url, p1.destinationUrl, "", "", "")
 
        	#Check the validity of the result
-       	if compareExtractions(newxpath,p1.links[i],p1.pagesrc) != NO_SIMILARITY:
+       	if compareExtractions(newxpath,p1.xpath,p1.pagesrc) != NO_SIMILARITY:
        	    p3.xpath = newxpath
        	else:
 	    print("Generalized link xpath is not valid, using non-generalized xpath\n")
-            p3.xpath = p1.links[i]
+            p3.xpath = p1.xpath
 
         print("Done with link\n")
 

### 2010-03-01 generalizer/ScriptBuilder.py

@@ -39,7 +39,6 @@ class ScriptBuilder():
 		actionHash = dict()
 
 		#write out ssq data
-	
 		#for the current qrm, we need  the data section
 		for action in qrm.pageList:
 			
@@ -60,7 +59,9 @@ class ScriptBuilder():
 
 			#save previous action for use in next iteration
 			previousAction = action
-		
+
+			#increment sequence number
+			sequenceNumber+=1		
 		
 		#add action data - now that we have built the hashtable of highlight and ssq info
 		actionData = etree.Element('actiondata')
@@ -254,7 +255,7 @@ def writeLinkAction(xmlNode, action, sequenceNumber):
 	
 	link = etree.SubElement(xmlNode, 'link')
 	link.text = action.destinationUrl
- 	xmlNode.set("number",str(sequenceNumber))
+ 	link.set("number",str(sequenceNumber))
 	pass
 
 def writeHighlightAction(xmlNode, action, sequenceNumber, actionHash):
@@ -266,7 +267,7 @@ def writeHighlightAction(xmlNode, action, sequenceNumber, actionHash):
 	hilite = etree.SubElement(xmlNode, 'highlight')
 	hilite.text = action.meetpoint
 	hilite.set("id",key)
-	xmlNode.set("number",str(sequenceNumber))
+	hilite.set("number",str(sequenceNumber))
 
 	#add data to actionHash
 	actionHash[key] = HashElement(key,'highlight','',str(action.classId))

### 2010-03-01 qre/ActionObject.py

@@ -49,6 +49,9 @@ class LinkAction(ActionObject):
 	def do(self, state):
 		"""Does LinkAction and returns the state"""
                 url = self.xmlnode.text.strip()
+	
+		pdb.set_trace()
+		
                 request = urllib2.Request(url)
                 response = urllib2.urlopen(request)
                 # state.cookie = CookieJar() -- initialized in state
@@ -109,7 +112,11 @@ class FormAction(ActionObject):
 
 		querystring += "?"
 		first = False
-		
+
+		pdb.set_trace()
+		#get the form node from the page
+		form = self.xmlnode						
+
 		#iterate through the list and find the input elements		
 		for e in self.xmlnode.getchildren():
 
@@ -121,8 +128,8 @@ class FormAction(ActionObject):
 				v = state.kv_hash[ e.text ]
 					
 				querystring += e.get('name').strip() + "=" + v.strip()
-
-		pdb.set_trace()
+		
+	
 		querystring = urllib2.quote(querystring)
 		#perform form submission 
 		result = urllib2.urlopen( querystring )		

### 2010-03-01 qre/main.py

@@ -52,7 +52,7 @@ def main(argv):
 	assert(len(code) > 0) # ensure text was returned
 
 	root = etree.fromstring(code)
-	#print(etree.tostring(root,pretty_print=True))
+	print(etree.tostring(root,pretty_print=True))
 
 	action_list = []
 	kv_hash = {}	
@@ -126,7 +126,7 @@ def read_ssq_text(xmlstring, valueHash, classHash, contextHash, typeHash):
 #parse the xml node and load its values into the appropriate spots
 #in the value hash
 def loadValueIntoHash(xml, valueHash, classHash, contextHash, typeHash):
-	pdb.set_trace()
+
 	#for the given xml node, we must find the matching key
 	for entry in valueHash.keys():
 		cls = classHash[entry]

### 2010-03-01 trunk/generalizer/Page.py
working on Qre

@@ -14,7 +14,7 @@ class Page(object):
 		self.actionType = ""
 		self.querystring = ""
 		pass
-		
+	
 def New(self, url, dest, time, xpath, src):
 	p = Page()
         p.url = url

### 2010-03-02 paper/semsearch10/paper.tex
latest paper version

@@
 	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
+\email{\{ cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs \} @cise.ufl.edu}
 }
-
 \date{April 26,2010}
@@
 - To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
-- 
--
 
-\section{Statistical Hierarchy}
-\subsection*{Class Hierarchy}
-%clint
-\subsection*{Markov Blanket}
+\section{Establishing the Semantic Hierarchy}
+\subsection{Class Hierarchy} 
+% Author: Clint P. George 
+Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
+The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
+We cannot find any robust existing ontology library of that nature for this purpose.
+So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
+Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
+The OWL ontology [citation needed] format is followed in this process.
+The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
+Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
+
+%-------------------------------------------------------------------------------
+
+\subsection{Markov Blanket}
 %joir-dan
@@
 SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{algorithm}
-\caption{Blanket Subject Retrieval}
-\label{alg1}
-	\begin{algorithmic}
-	\STATE BlanketSubjectRetrieval(blanket, maxLevel):
-		\FOR{category c in blanket}
-			\STATE subjectSet.add(grabSubjects(c))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha and c is a subcategory}
-				\STATE PlusOneMechanism(category, maxLevel)
-			\ENDIF
-		\ENDFOR
-	\STATE return subjectSet
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Plus One Mechanism}
-\label{alg2}
-	\begin{algorithmic}
-	\STATE PlusOneMechanism(category, level)
-		\STATE plusOneSet = grabPlusOneSubcategories(category)
-		\FOR{ subcategory in plusOneSet}
-			\STATE subjectSet.add(grabSubjects(subcategory))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha \and level \gt 0}
-				\STATE PlusOneMechanism(subcategory, level - 1);
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
 
@@
 % Chris
+Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
+Many of the accesses involve clicks through web forms to resulting pages.
+We have developed a model that represents the various actions a user may carry out during this process.
+We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
+
+During the answer retrieval process, a user discovers an element of the query's result on a web page.
+Next, she highlights that element, typically a text string.
+This highlight allows the QRR to record the source of  the query's answer.
+The QRR stores all information from the user query in our data store.
+When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
+
+The discovery process can be broken down into three cases:
+\begin{enumerate}
+\item The user typed in a URL  and highlighted part of or all the answer. 
+\item The user typed in a URL, clicked a link, and found part or all of the answer. 
+\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
+\end{enumerate}
+
+Any discovery process  consists of a sequence of these transactions.
+Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
+An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
+The QRR builds the completed user collection process into a QRM.
+The following is a mathematical formulation of information collected for user web interactions.\\
+
+A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
+
+\begin{enumerate}
+
+\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
+
+\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
+
+\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
+$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
+\\
+Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
+\\
+Let $K$ be the set of all string constants.
+\begin{itemize}
+\item URI $U_1 \in K$ is a string and \\
+for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
+
+\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
+for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
+\end{itemize}
+
+\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
+
+\item $R$ is an ontological realm.
+
+\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
+
+\end{enumerate}
+
+%-------------------------------------------------------------------------------
+
 \subsection{Generalization}
 % Christan
+The response pages created by querying web forms are dynamically generated with a templated structure.
+This generalization per page is done using the GenPath algorithm developed by Badica et al.
+\cite{Badica06}.
+Additionally, the community may be able to answer a particular SSQ using many different page interactions.
+Therefore, we proposed a method of generalizing extraction path to a result across pages.
+This method removes unnecessary page interactions and finds the shortest path to the result pages.
 
-\section{Semantic Query Answering}
+The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
+Generalizing the extraction paths help to overcome small structural changes.
+If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
+Morpheus allows users to rate the freshness of QRMs.
+
+%-------------------------------------------------------------------------------
+
+\section{Natural Language Queries}
 \subsection{Semi-Structured Query}

### 2010-03-02 trunk/paper/semsearch10/paper.tex
latest with changed name
Title change:  remove the and

@@
 
-\title{Leveraging Semantics for a Deep Web Question and Answering System} 
+\title{Leveraging Semantics for a Deep Web Question Answering System} 
 \numberofauthors{1}
@@
 	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{\{ cgrant, cpj, jnw, pjd, jdepree, cshields, jg \} @cise.ufl.edu}
+\email{\{ cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs \} @cise.ufl.edu}
 }
@@
 - To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
+-
 
@@
 
-\subsection*{Markov Blanket}
+\subsection{Markov Blanket}
 %joir-dan

### 2010-03-02 paper/semsearch10/paper.tex
Update of the introduction

@@
 	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{\{ cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs \} @cise.ufl.edu}
+\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
 }
@@
 % Christan
+- When traveling though a jungle to a destination, it is easy to get lost.
+If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
+However if you are the \emph{n}th person, there is a beaten trail of the most commonly used path.
 - IEEE potentials article talks discussed the idea of using the beaten trail. \cite{5379671} To solve problems

### 2010-03-02 trunk/paper/semsearch10/paper.tex

@@
 -
+\section{Semantic Query Representation}
+% Christan - fois
 
 \section{Establishing the Semantic Hierarchy}
+
 \subsection{Class Hierarchy} 
-% Author: Clint P. George 
+% Author: Clint 
 Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
@@
 When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Semantic Query Representation}
-% Christan - fois
 
@@
 \includegraphics[width=90mm]{class_divergence.eps}
-\caption{Graphical representation of an Ontology}
+\caption{Abbrv. graphical representation of an automotive ontology}
 \label{fig:class_divergence}
@@
 Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample ontology is rooted at the class \textit{Accommodations}.
+This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
 The arrows represent the inheritance relationship between the classes in the topology.
 
-Suppose we want to find the divergence $d_{class}$\textit{(Hotel, Motel)}.
-Both are subclasses of the class \textit{Hotel/Motel} ($C$).
-They share the path from \textit{Hotel/Motel} to the $root$.
-So, the unnormalized divergence \textit{d(Hotel, root)} is two (shown by bold arrows), \textit{d(Motel, Hotel/Motel)} is one (dashed arrow), and \textit{d(Hotel, Hotel/Motel)} is one (dashed arrow).
-Thus, \textit{d(Hotel, Motel)} is four, which corresponds to a normalized value of $2/3$.
-
-Consider $d_{class}$\textit{(Motel, Hostel)}.
-The classes $root$ and $C$ in the definition of $d_{class}$ are the same in this case so we add \textit{d(Motel, Accommodations)} (two), \textit{d(Hostel, Accommodations)} (one), and \textit{d(Motel, Accommodations)} (two), yielding a total unnormalized divergence of five, or a normalized divergence of $5/6$.
+Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
+The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
+Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
+They share the path from \textit{Automobiles} to the $root$.
+So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
+Suppose, the ontology tree height is calculated as 294.
+Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
 
@@
 
+% Need to show an example ?
+
 %-------------------------------------------------------------------------------
@@
 \section{Future Work}
+% Talk about the offline execution mode and class structural matching algorithm
+
+% Sort classes based on the prior
 
@@
 %
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+% The bibliography for the citations in the paper 
 \bibliographystyle{abbrv}
-\bibliography{citations}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
+\bibliography{citations}  						% citations.bib is the name of the Bibliography
 

### 2010-03-02 trunk/paper/semsearch10/paper.tex
latest

@@
 If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However if you are the \emph{n}th person, there is a beaten trail of the most commonly used path.
-- IEEE potentials article talks discussed the idea of using the beaten trail. \cite{5379671} To solve problems
-- Typical search engines have several repeat queries.
-- We believe that treating these repeat visits as special visits will enhance user search experience
-- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
--
+However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
+An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
+This idea translates to the arena of semantic search.
+
+Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
+Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
+This means there is a large missing area for optimization for search engines.
+We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
+
+... expand here...
+
+The paper proceeds as follows:
+
 \section{Semantic Query Representation}
@@
 \section{Future Work}
-% Talk about the offline execution mode and class structural matching algorithm
+- Talk about the offline execution mode and class structural matching algorithm
+- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
+We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
+We plan to investigate this.
 

### 2010-03-03 qre/ActionObject.py
fixing qre

@@ -5,11 +5,14 @@
 __authors__ = ['"Christan Earl Grant" <cgrant@cise.ufl.edu>']
 
 import lxml
+from lxml.html import parse, make_links_absolute, fromstring
 from lxml import etree
 import re
 import urllib, urllib2
 import pdb
-
+import sys
+sys.path.append("../generalizer")
+import Loader
 class ActionObject:
 	"""Base Class of all actions"""
 
@@ -30,6 +33,11 @@ class URLAction(ActionObject):
 		"""Does URLAction and returns the state"""
 
 		url = self.xmlnode.text.strip() # Extract the url from <starturl>URL</starturl>
+
+		state.page = parse(url).getroot()
+
+		"""
+		url = self.xmlnode.text.strip() # Extract the url from <starturl>URL</starturl>
 		request = urllib2.Request(url)
 		response = urllib2.urlopen(request)
 		# state.cookie = CookieJar() -- initialized in state
@@ -38,7 +46,7 @@ class URLAction(ActionObject):
 		redirect_handler = urllib2.HTTPRedirectHandler()
 		opener = urllib2.build_opener(redirect_handler,cookie_handler)
 		state.page = opener.open(request)
-
+		"""
 
 class LinkAction(ActionObject):
 
@@ -48,22 +56,52 @@ class LinkAction(ActionObject):
 
 	def do(self, state):
 		"""Does LinkAction and returns the state"""
-                url = self.xmlnode.text.strip()
+                xpath = self.xmlnode.text.strip()
 	
-		pdb.set_trace()
+		#for some reason, tbody tags annoy lxml, must remove them
+		xpath = removeTBodies(xpath)
 		
-                request = urllib2.Request(url)
-                response = urllib2.urlopen(request)
-                # state.cookie = CookieJar() -- initialized in state
-                state.cookie.extract_cookies(response,request)
-                cookie_handler = urllib2.HTTPCookieProcessor( state.cookie )
-                redirect_handler = urllib2.HTTPRedirectHandler()
-                opener = urllib2.build_opener(redirect_handler,cookie_handler)
-                state.page = opener.open(request)
+		doc = fix_links(state, self.xmlnode.get('number'), etree.tostring(state.page),state.page.base_url)
+
+		page = fromstring(doc)
+	
+		link_node = page.xpath(xpath)[0]
+
+		#TODO: figure out what is going on with the sessionids 
[…]

### 2010-03-03 trunk/generalizer/Loader.py
fixing qre

@@ -27,6 +27,30 @@ def GetQRMFromDb(qrmid):
 	rowArray = retrieveRecordsFromQRM(qrmid)
 
 	return getqrm(rowArray, qrmid, True, rowArray[3][0])
+def getHiLiteXpath(id):
+
+	q = 'select meetpoint from highlight where timestamp = '+id
+
+	rows = executeQuery(q)[0][0]
+
+	return rows	
+
+def getFormXpath(url, snum):
+
+	snum += 1
+	q = """select 
+			formxpath
+		from 
+			pagereference,page
+		where 
+			pagereference.pageid = page.pageid AND
+			page.baseurl = '{0}'
+		ORDER BY timestamp
+		LIMIT {1}""".format(url,snum)
+
+	rows = executeQuery(q)
+	
+	return rows[-1][0]
 
 #get the class and context information for the given input/highlight
 def getNeededScriptInfo(id, isInput):

### 2010-03-03 trunk/generalizer/ScriptBuilder.py

@@ -136,9 +136,10 @@ def writeFormAction(xmlNode, action, sequenceNumber,actionHash):
 	form = etree.SubElement(xmlNode, 'form')
 	form.set("number",str(sequenceNumber))
 		
+	#TODO: fix this, using this because scraper isn't working for xpaths 
 	#handle the xpath for this form
 	xpath = etree.SubElement(form, 'xpath')
-	xpath.text = action.xpath
+	xpath.text = action.xpath 
 
 	#handle the url for this form
 	url = etree.SubElement(form, 'url')
@@ -150,7 +151,7 @@ def writeFormAction(xmlNode, action, sequenceNumber,actionHash):
 
 	#obtain the form element from the page, we need it get info about its inputs
 	formElemList = lxml.html.fromstring(action.pagesrc).xpath(action.xpath)
-	
+
 	#keep a count of the inputs for use as an id
 	inputIndex = 0	
 
@@ -252,9 +253,9 @@ def getDefaultValue(form, input):
 
 	
 def writeLinkAction(xmlNode, action, sequenceNumber):
-	
+
 	link = etree.SubElement(xmlNode, 'link')
-	link.text = action.destinationUrl
+	link.text = action.xpath
  	link.set("number",str(sequenceNumber))
 	pass
 

### 2010-03-03 trunk/qre/ActionState.py

@@ -29,7 +29,7 @@ class ActionState:
 
 		self.action_list = copy.copy(_action_list) # The list of actions 
 		#self.iter = action_list.__iter__() # The action iterator
-
+		self.resolved_seq = -1
 
 	def run(self):
 		""" This function call the do function on all the items im action_list"""

### 2010-03-03 trunk/qre/main.py

@@ -52,7 +52,6 @@ def main(argv):
 	assert(len(code) > 0) # ensure text was returned
 
 	root = etree.fromstring(code)
-	print(etree.tostring(root,pretty_print=True))
 
 	action_list = []
 	kv_hash = {}	
@@ -94,8 +93,14 @@ def main(argv):
 	state = ActionState.ActionState(action_list, kv_hash, kt_hash, kclass_hash, kcontext_hash, user_hash)
 	
 	state.run()
-	
-	return state
+
+	result = ''
+	for k in state.kv_hash.keys():
+		if state.kv_hash[k] != '':
+			result += state.kv_hash[k] 
+
+	print(result)
+	return result
 
 #read in the ssq from an xml file or xml string
 def read_ssq(xml):
@@ -112,21 +117,29 @@ def read_ssq(xml):
 def read_ssq_text(xmlstring, valueHash, classHash, contextHash, typeHash):
 
 	tree = etree.fromstring(xmlstring)
-	
+	total = 0
+	#any highlights present need to be counted first
+	for k in valueHash.keys():
+		if valueHash[k] != '':total+=1
+
 	#find the input list and load the values into the kv_hash
 	for e in tree.getchildren():
 
 		if e.tag == 'input_list':
 			for input in e.getchildren():
-				if loadValueIntoHash(input, valueHash, classHash, contextHash, typeHash) == False:	
-					print('The given ssq does not match this qrm\'s ssq, aborting')
-					return False
-	return True
+				total += loadValueIntoHash(input, valueHash, classHash, contextHash, typeHash)	
+
+	if total == len(valueHash.keys()):
+		return True
+	
+	print('The given ssq does not match this qrm\'s ssq, aborting')
+	return False
 
 #parse the xml node and load its values into the appropriate spots
 #in the value hash
 def loadValueIntoHash(xml, valueHash, classHash, contextHash, typeHash):
 
+	found = 0
 	#for the given xml node, we must find the matching key
 	for entry in valueHash.keys():
 		cls = classHash[entry]
@@ -136,10 +149,9 @@ def loadValueIntoHash(xml, valueHash, classHash, contextHash, typeHash):
 		#to the data hash at the current key
 		if cls.lower() == xml.get('dataclass').lower() and context.lower() == xml.get('type').lower():
 			valueHash[entry] = xml.text
-			return True
+			found+=1
 
-	#if we reach this point then we haven't found a match
-	return False			
+	return found
 
 if __name__ == '__main__':
 

### 2010-03-03 dobson/DobsonGUI/MainWindow.cs
working on dobson to improve robustness

@@ -724,13 +724,16 @@ namespace DobsonGUI
                 {
                     int NAME = 0;
 
-                    int VALUE = 0;
+                    int VALUE = 1;
 
                     prefbiz.updatePageReferenceQuerystring(previousPageReferenceId, qs);
 
                     // Check if any pending input object inserts are waiting on data from 
                     //this querystring
                     Hashtable elems = (Hashtable)unresolvedInputs[previousPageReferenceId];
+
+                    if (qs[0] == '?')
+                        qs = qs.Substring(1);
 
                     //split the querystring into substrings which consist of name/value pairs
                     string[] nameValuePairs = qs.Split(new char[] { '&' });
@@ -1016,9 +1019,7 @@ namespace DobsonGUI
                             txt = selectedNode.Attributes["value"].Value.ToUpper();
                         else if (selectedNode.Attributes["title"] != null)
                             txt = selectedNode.Attributes["title"].Value.ToUpper();
-                        else if (selectedNode.Name.Equals("select", StringComparison.CurrentCultureIgnoreCase))
-                            txt = parseSelectValue(inputName, selectedNode, pref.queryString);
-
+                       
                         elem = queryElementManager.FindSsqInput(classId, txt);
                     }
                 }

### 2010-03-03 dobson/DobsonLibrary/DataAccess/SsqElementManager.cs

@@ -34,11 +34,11 @@ namespace DobsonLibrary.DataAccess
             highlights[elem.ClassId] = elems;
         }
 
-        public SsqElement FindSsqInput(int classID, string name)
+        public SsqElement FindSsqInput(int classID, string val)
         {
             List<SsqElement> elems = (List<SsqElement>)ssqInputs[classID];
 
-            SsqElement elem = getElement(name, elems);
+            SsqElement elem = getElement(val, elems);
 
             return elem;
         }

### 2010-03-03 trunk/qre/main.py
final changes

@@ -1,4 +1,4 @@
-"""
+1"""
 This class runs the code
 """
 
@@ -86,7 +86,7 @@ def main(argv):
 					action_list.append(ActionObject.FormAction(ao))
 
 	#parse the ssq to populate the value hashes with the user input	
-	txt = read_ssq(sys.argv[-2])
+	txt = sys.argv[-2]
 	if read_ssq_text(txt,kv_hash,kclass_hash, kcontext_hash, kt_hash) == False:	
 		return
 	
@@ -99,19 +99,7 @@ def main(argv):
 		if state.kv_hash[k] != '':
 			result += state.kv_hash[k] 
 
-	print(result)
 	return result
-
-#read in the ssq from an xml file or xml string
-def read_ssq(xml):
-
-	file = open(xml,'r')
-
-	text = file.read()
-
-	file.close()
-
-	return text
 
 #populate the value hash from a string
 def read_ssq_text(xmlstring, valueHash, classHash, contextHash, typeHash):

### 2010-03-03 trunk/paper/semsearch10/paper.tex
latest
latest stuff

@@
 
-\title{Leveraging Semantics for a Deep Web Question Answering System} 
+\title{Re-finding to support a Deep Web Question Answering System} 
 \numberofauthors{1}
@@
 % Christan
-- When traveling though a jungle to a destination, it is easy to get lost.
+When traveling though a jungle to a destination, it is easy to get lost.
 If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
@@
 An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-This idea translates to the arena of semantic search.
+We use this insight to to improve the efficency of retrieval in semantic search.
 
@@
 Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large missing area for optimization for search engines.
+This means there is a large open area for optimization for search engines.
 We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
 
-... expand here...
+In this paper we describe a system for recording the answer to user queries and executing solutions to similar queries.
+To support this we use a structured query representation.
+The structured representation allows queries to be parameterized so that similar queries may be discovered at query-time.
+To recognizing these queries we build a semantic heterarchy and define algorithms for matching the classes.
 
 The paper proceeds as follows:
-
+\begin{itemize}
+\item Discussion of the query structure.  We call this structure an \emph{semi-structured query} SSQ.
+\item Next we discuss how we create the class heterarchy to support the semantic comparisons.
+\item In section \ref{sec:Building Query Store} we discuss how we record user web queries and correctly annotate them.
+\item Next, we discribe how we match rank 
+\item ....
+\item We will conclude by discussing the examples of the system.
+\end{itemize}
 \section{Semantic Query Representation}
 % Christan - fois
+- We translate natural language queries into a format we call - semi structured query
+- the semi structure query is formated as followed...
+- this format especially allows us to better match deep web parameters with queries
 

### 2010-03-03 trunk/paper/semsearch10/paper.tex
added new files in folder

@@
 Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
+It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic function type matches.
 We consider the realm class and context property ranges for determining SSQ similarity.

### 2010-03-03 trunk/paper/semsearch10/paper2.tex
added new files in folder

--- 2010-03-02 trunk/paper/semsearch10/paper.tex
@@
 
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
+\input{abstract.tex}
 
@@
 
-\section{Introduction}
-% Christan
-- When traveling though a jungle to a destination, it is easy to get lost.
-If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
-An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-This idea translates to the arena of semantic search.
+\input{content/introduction.tex}
+\input{content/example.tex}
+\input{content/nlp.tex}
+\input{content/qrr.tex}
+\input{content/ontological_realms.tex}
+\input{content/ssq_ranking.tex} % Joir-dan adds finding category stuff here
+\input{content/query_reexecution.tex}
+\input{content/results_futurework_conclusion.tex}
 
-Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
-Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large missing area for optimization for search engines.
-We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
+\bibliographystyle{abbrv}
+\bibliography{citations}
 
-... expand here...
-
-The paper proceeds as follows:
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Establishing the Semantic Hierarchy}
-
-\subsection{Class Hierarchy} 
-% Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
-
-%-------------------------------------------------------------------------------
-
-\subsection{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
-
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
-
-The discovery process can be broken down into three cases:
-\begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
-\end{enumerate}
-
-Any discovery process  consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
-
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
-
-\begin{enumerate}
-
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
-
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
-
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
-\begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
-
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
-\end{itemize}
-
-\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
-
-\item $R$ is an ontological realm.
-
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
-
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-%-------------------------------------------------------------------------------
-
-\section{Natural Language Queries}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
-
-The similarity measure for the SSQ ontologies is determined by the following components.
-\begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
-\end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
-
-%-------------------------------------------------------------------------------
-
-\subsubsection{Class Divergence}
-\label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
-
-\begin{equation}
-d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
-d(S, T) & if S \prec T\\
-1 & if T \prec S\\
-d(S,root) \\+ d(S,C) + d(T,C) & otherwise
-\end{cases}
-\end{equation}
-
-We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
-
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
-that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
-This is an important property in determining the compatibility of classes for answering queries.
-If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
-
-% Algorithm 1: figure  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{class_divergence.eps}
-\caption{Abbrv. graphical representation of an automotive ontology}
-\label{fig:class_divergence}
-\end{figure}
-
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
-
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
-
-%-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
-\label{sec:oqom}
-
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
-
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
-
-\begin{eqnarray}
-\label{qrmsimilarity}
- R(S,Q) = 1 - (d_{R} + d_{\Upsilon} + d_{\Omega})
-\end{eqnarray}
-\noindent where 
-\begin{eqnarray}
-d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
-\end{eqnarray}
-\begin{eqnarray}
-d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
-\end{eqnarray}
-\begin{eqnarray}
- d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
-\end{eqnarray}
-\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
-\begin{equation}
-\label{piconstraint1}
-\sum_{k=1}^{9} {{\pi}_k} = 1
-\end{equation}
-\noindent and for $1 \leq i \leq 9$
-
-\begin{equation}
-\label{piconstraint2}
-{\pi}_i > 0
-\end{equation}
-
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
-
-% Need to show an example ?
-
-%-------------------------------------------------------------------------------
-
-\subsection{Query Re-Execution}
-% Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-- Talk about the offline execution mode and class structural matching algorithm
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
-
-% Sort classes based on the prior
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-%
-% The bibliography for the citations in the paper 
-\bibliographystyle{abbrv}
-\bibliography{citations}  						% citations.bib is the name of the Bibliography
-
-\end{document}            						% End of document.
+\end{document}

### 2010-03-03 trunk/qre/main.py
fixing text error

@@ -1,4 +1,4 @@
-1"""
+"""
 This class runs the code
 """
 

### 2010-03-03 paper/semsearch10/content/abstract.tex
combined stuff

--- 2010-03-01 trunk/paper/semsearch10/paper.tex
@@
-\documentclass{www2010-submission}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\begin{document}
-
-\title{Leveraging Semantics for a Deep Web Question and Answering System} 
-\numberofauthors{1}
-\author{
-	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
-}
-
-\date{April 26,2010}
-
-\maketitle
-
 \begin{abstract}
@@
 \end{abstract}
-
-\category{H.4.m}{Information Systems Applications}{Miscellaneous}
-
-\terms{SSQ}
-
-\keywords{Questions Answering, re-finding}
-
-\section{Introduction}
-% Christan
-- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
-- Typical search engines have several repeat queries.
-- We believe that treating these repeat visits as special visits will enhance user search experience
-- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
-- 
--
-
-\section{Statistical Hierarchy}
-\subsection*{Class Hierarchy}
-%clint
-\subsection*{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph (Suchanek et al., 2008), we consider the use of a Markov Blanket (Friedman et al., 1997) in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-Consider the abbreviated Markov blanket for the category Basketball:
-%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category (Yu et al., 2007).
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{algorithm}
-\caption{Blanket Subject Retrieval}
-\label{alg1}
-	\begin{algorithmic}
-		\STATE BlanketSubjectRetrieval(blanket, maxLevel):
-		\FOR{category c in blanket}
-			\STATE subjectSet.add(grabSubjects(c))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha and c is a subcategory}
-				\STATE PlusOneMechanism(category, maxLevel)
-			\ENDIF
-		\ENDFOR
-		\STATE return subjectSet
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Plus One Mechanism}
-\label{alg2}
-	\begin{algorithmic}
-		\STATE PlusOneMechanism(category, level)
-		\STATE plusOneSet = grabPlusOneSubcategories(category)
-		\FOR{ subcategory in plusOneSet}
-			\STATE subjectSet.add(grabSubjects(subcategory))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha \and level \gt 0}
-				\STATE PlusOneMechanism(subcategory, level - 1);
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are
-dynamically generated with a templated structure.
-This
-generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-\section{Semantic Query Answering}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-% Clint
-\subsection{Query Re-Execution}
-% Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-\section{References}
-Bayesian Network Classifers
-Friedman, Geiger, Goldszmidt 1997
-
-YAGO: A Large Ontology from Wikipedia and WordNet
-Fabian M. Suchanek, Gjergji Kasnecia, and Gerhard Weikuma 2008
-
-Ontology Evaluation: Using Wikipedia Categories for Browsing
-Yu, Thom, Tam 2007
-
-\end{document}            % End of document.

### 2010-03-03 paper/semsearch10/content/introduction.tex
combined stuff

--- 2010-03-03 trunk/paper/semsearch10/paper.tex
@@
-\documentclass{www2010-submission}
-\begin{document}
-
-\title{Re-finding to support a Deep Web Question Answering System} 
-\numberofauthors{1}
-\author{
-	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
-}
-\date{April 26,2010}
-
-\maketitle
-
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
-
-\category{H.4.m}{Information Systems Applications}{Miscellaneous}
-
-\terms{SSQ}
-
-\keywords{Questions Answering, re-finding}
-
 \section{Introduction}
@@
 \end{itemize}
-\section{Semantic Query Representation}
-% Christan - fois
-- We translate natural language queries into a format we call - semi structured query
-- the semi structure query is formated as followed...
-- this format especially allows us to better match deep web parameters with queries
-
-\section{Establishing the Semantic Hierarchy}
-
-\subsection{Class Hierarchy} 
-% Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
-
-%-------------------------------------------------------------------------------
-
-\subsection{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
-
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
-
-The discovery process can be broken down into three cases:
-\begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
-\end{enumerate}
-
-Any discovery process  consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
-
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
-
-\begin{enumerate}
-
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
-
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
-
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
-\begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
-
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
-\end{itemize}
-
-\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
-
-\item $R$ is an ontological realm.
-
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
-
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-%-------------------------------------------------------------------------------
-
-\section{Natural Language Queries}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
-
-The similarity measure for the SSQ ontologies is determined by the following components.
-\begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
-\end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
-
-%-------------------------------------------------------------------------------
-
-\subsubsection{Class Divergence}
-\label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
-
-\begin{equation}
-d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
-d(S, T) & if S \prec T\\
-1 & if T \prec S\\
-d(S,root) \\+ d(S,C) + d(T,C) & otherwise
-\end{cases}
-\end{equation}
-
-We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
-
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
-that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
-This is an important property in determining the compatibility of classes for answering queries.
-If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
-
-% Algorithm 1: figure  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{class_divergence.eps}
-\caption{Abbrv. graphical representation of an automotive ontology}
-\label{fig:class_divergence}
-\end{figure}
-
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
-
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
-
-%-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
-\label{sec:oqom}
-
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
-
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
-
-\begin{eqnarray}
-\label{qrmsimilarity}
- R(S,Q) = 1 - (d_{R} + d_{\Upsilon} + d_{\Omega})
-\end{eqnarray}
-\noindent where 
-\begin{eqnarray}
-d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
-\end{eqnarray}
-\begin{eqnarray}
-d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
-\end{eqnarray}
-\begin{eqnarray}
- d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
-\end{eqnarray}
-\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
-\begin{equation}
-\label{piconstraint1}
-\sum_{k=1}^{9} {{\pi}_k} = 1
-\end{equation}
-\noindent and for $1 \leq i \leq 9$
-
-\begin{equation}
-\label{piconstraint2}
-{\pi}_i > 0
-\end{equation}
-
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
-
-% Need to show an example ?
-
-%-------------------------------------------------------------------------------
-
-\subsection{Query Re-Execution}
-% Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-- Talk about the offline execution mode and class structural matching algorithm
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
-
-% Sort classes based on the prior
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-%
-% The bibliography for the citations in the paper 
-\bibliographystyle{abbrv}
-\bibliography{citations}  						% citations.bib is the name of the Bibliography
-
-\end{document}            						% End of document.

### 2010-03-03 trunk/paper/semsearch10/content/ontological_realms.tex
combined stuff

--- 2010-03-02 trunk/paper/semsearch10/paper.tex
@@
-\documentclass{www2010-submission}
-\begin{document}
-
-\title{Leveraging Semantics for a Deep Web Question Answering System} 
-\numberofauthors{1}
-\author{
-	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
-}
-\date{April 26,2010}
-
-\maketitle
-
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
-
-\category{H.4.m}{Information Systems Applications}{Miscellaneous}
-
-\terms{SSQ}
-
-\keywords{Questions Answering, re-finding}
-
-\section{Introduction}
-% Christan
-- When traveling though a jungle to a destination, it is easy to get lost.
-If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
-An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-This idea translates to the arena of semantic search.
-
-Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
-Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large missing area for optimization for search engines.
-We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
-
-... expand here...
-
-The paper proceeds as follows:
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Establishing the Semantic Hierarchy}
-
-\subsection{Class Hierarchy} 
+\subsection{Class Heterarchy} 
 % Author: Clint 
@@
 
-\subsection{Markov Blanket}
+\subsection{Associating Terms with Categories}
 %joir-dan
@@
 When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
-
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
-
-The discovery process can be broken down into three cases:
-\begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
-\end{enumerate}
-
-Any discovery process  consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
-
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
-
-\begin{enumerate}
-
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
-
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
-
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
-\begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
-
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
-\end{itemize}
-
-\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
-
-\item $R$ is an ontological realm.
-
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
-
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-%-------------------------------------------------------------------------------
-
-\section{Natural Language Queries}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
-
-The similarity measure for the SSQ ontologies is determined by the following components.
-\begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
-\end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
-
-%-------------------------------------------------------------------------------
-
-\subsubsection{Class Divergence}
-\label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
-
-\begin{equation}
-d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
-d(S, T) & if S \prec T\\
-1 & if T \prec S\\
-d(S,root) \\+ d(S,C) + d(T,C) & otherwise
-\end{cases}
-\end{equation}
-
-We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
-
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
-that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
-This is an important property in determining the compatibility of classes for answering queries.
-If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
-
-% Algorithm 1: figure  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{class_divergence.eps}
-\caption{Abbrv. graphical representation of an automotive ontology}
-\label{fig:class_divergence}
-\end{figure}
-
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
-
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
-
-%-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
-\label{sec:oqom}
-
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
-
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
-
-\begin{eqnarray}
-\label{qrmsimilarity}
- R(S,Q) = 1 - (d_{R} + d_{\Upsilon} + d_{\Omega})
-\end{eqnarray}
-\noindent where 
-\begin{eqnarray}
-d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
-\end{eqnarray}
-\begin{eqnarray}
-d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
-\end{eqnarray}
-\begin{eqnarray}
- d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
-\end{eqnarray}
-\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
-\begin{equation}
-\label{piconstraint1}
-\sum_{k=1}^{9} {{\pi}_k} = 1
-\end{equation}
-\noindent and for $1 \leq i \leq 9$
-
-\begin{equation}
-\label{piconstraint2}
-{\pi}_i > 0
-\end{equation}
-
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
-
-% Need to show an example ?
-
-%-------------------------------------------------------------------------------
-
-\subsection{Query Re-Execution}
-% Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-- Talk about the offline execution mode and class structural matching algorithm
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
-
-% Sort classes based on the prior
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-%
-% The bibliography for the citations in the paper 
-\bibliographystyle{abbrv}
-\bibliography{citations}  						% citations.bib is the name of the Bibliography
-
-\end{document}            						% End of document.

### 2010-03-03 trunk/paper/semsearch10/content/qrr.tex
combined stuff

--- 2010-03-01 paper/semsearch10/paper.tex
@@
-\documentclass{www2010-submission}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\begin{document}
-
-\title{Leveraging Semantics for a Deep Web Question and Answering System} 
-\numberofauthors{1}
-\author{
-	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
-}
-
-\date{April 26,2010}
-
-\maketitle
-
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
-
-\category{H.4.m}{Information Systems Applications}{Miscellaneous}
-
-\terms{SSQ}
-
-\keywords{Questions Answering, re-finding}
-
-\section{Introduction}
-% Christan
-- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
-- Typical search engines have several repeat queries.
-- We believe that treating these repeat visits as special visits will enhance user search experience
-- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
-- 
--
-
-\section{Statistical Hierarchy}
-\subsection*{Class Hierarchy}
-%clint
-\subsection*{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph (Suchanek et al., 2008), we consider the use of a Markov Blanket (Friedman et al., 1997) in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-Consider the abbreviated Markov blanket for the category Basketball:
-%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category (Yu et al., 2007).
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{algorithm}
-\caption{Blanket Subject Retrieval}
-\label{alg1}
-	\begin{algorithmic}
-	\STATE BlanketSubjectRetrieval(blanket, maxLevel):
-		\FOR{category c in blanket}
-			\STATE subjectSet.add(grabSubjects(c))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha and c is a subcategory}
-				\STATE PlusOneMechanism(category, maxLevel)
-			\ENDIF
-		\ENDFOR
-	\STATE return subjectSet
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Plus One Mechanism}
-\label{alg2}
-	\begin{algorithmic}
-	\STATE PlusOneMechanism(category, level)
-		\STATE plusOneSet = grabPlusOneSubcategories(category)
-		\FOR{ subcategory in plusOneSet}
-			\STATE subjectSet.add(grabSubjects(subcategory))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha \and level \gt 0}
-				\STATE PlusOneMechanism(subcategory, level - 1);
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Building Query Store}
 \subsection{Query Resolution Recorder}
 % Chris
+Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
+Many of the accesses involve clicks through web forms to resulting pages.
+We have developed a model that represents the various actions a user may carry out during this process.
+We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
+
+During the answer retrieval process, a user discovers an element of the query's result on a web page.
+Next, she highlights that element, typically a text string.
+This highlight allows the QRR to record the source of  the query's answer.
+The QRR stores all information from the user query in our data store.
+When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
+
+The discovery process can be broken down into three cases:
+\begin{enumerate}
+\item The user typed in a URL  and highlighted part of or all the answer. 
+\item The user typed in a URL, clicked a link, and found part or all of the answer. 
+\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
+\end{enumerate}
+
+Any discovery process  consists of a sequence of these transactions.
+Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
+An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
+The QRR builds the completed user collection process into a QRM.
+The following is a mathematical formulation of information collected for user web interactions.\\
+
+A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
+
+\begin{enumerate}
+
+\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
+
+\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
+
+\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
+$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
+\\
+Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
+\\
+Let $K$ be the set of all string constants.
+\begin{itemize}
+\item URI $U_1 \in K$ is a string and \\
+for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
+
+\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
+for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
+\end{itemize}
+
+\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
+
+\item $R$ is an ontological realm.
+
+\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
+
+\end{enumerate}
+
+%-------------------------------------------------------------------------------
+
 \subsection{Generalization}
 % Christan
+The response pages created by querying web forms are dynamically generated with a templated structure.
+This generalization per page is done using the GenPath algorithm developed by Badica et al.
+\cite{Badica06}.
+Additionally, the community may be able to answer a particular SSQ using many different page interactions.
+Therefore, we proposed a method of generalizing extraction path to a result across pages.
+This method removes unnecessary page interactions and finds the shortest path to the result pages.
 
-\section{Semantic Query Answering}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-% Clint
-\subsection{Query Re-Execution}
-% Chris
+The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
+Generalizing the extraction paths help to overcome small structural changes.
+If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
+Morpheus allows users to rate the freshness of QRMs.
 
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-\section{References}
-Bayesian Network Classifers
-Friedman, Geiger, Goldszmidt 1997
-
-YAGO: A Large Ontology from Wikipedia and WordNet
-Fabian M. Suchanek, Gjergji Kasnecia, and Gerhard Weikuma 2008
-
-Ontology Evaluation: Using Wikipedia Categories for Browsing
-Yu, Thom, Tam 2007
-
-\end{document}            % End of document.
+%-------------------------------------------------------------------------------

### 2010-03-03 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
combined stuff

--- 2010-03-02 trunk/paper/semsearch10/paper.tex
@@
-\documentclass{www2010-submission}
-\begin{document}
-
-\title{Leveraging Semantics for a Deep Web Question Answering System} 
-\numberofauthors{1}
-\author{
-	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
-}
-\date{April 26,2010}
-
-\maketitle
-
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
-
-\category{H.4.m}{Information Systems Applications}{Miscellaneous}
-
-\terms{SSQ}
-
-\keywords{Questions Answering, re-finding}
-
-\section{Introduction}
-% Christan
-- When traveling though a jungle to a destination, it is easy to get lost.
-If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
-An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-This idea translates to the arena of semantic search.
-
-Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
-Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large missing area for optimization for search engines.
-We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
-
-... expand here...
-
-The paper proceeds as follows:
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Establishing the Semantic Hierarchy}
-
-\subsection{Class Hierarchy} 
-% Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
-
-%-------------------------------------------------------------------------------
-
-\subsection{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
-
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
-
-The discovery process can be broken down into three cases:
-\begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
-\end{enumerate}
-
-Any discovery process  consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
-
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
-
-\begin{enumerate}
-
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
-
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
-
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
-\begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
-
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
-\end{itemize}
-
-\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
-
-\item $R$ is an ontological realm.
-
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
-
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-%-------------------------------------------------------------------------------
-
-\section{Natural Language Queries}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
-
-The similarity measure for the SSQ ontologies is determined by the following components.
-\begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
-\end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
-
-%-------------------------------------------------------------------------------
-
-\subsubsection{Class Divergence}
-\label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
-
-\begin{equation}
-d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
-d(S, T) & if S \prec T\\
-1 & if T \prec S\\
-d(S,root) \\+ d(S,C) + d(T,C) & otherwise
-\end{cases}
-\end{equation}
-
-We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
-
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
-that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
-This is an important property in determining the compatibility of classes for answering queries.
-If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
-
-% Algorithm 1: figure  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{class_divergence.eps}
-\caption{Abbrv. graphical representation of an automotive ontology}
-\label{fig:class_divergence}
-\end{figure}
-
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
-
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
-
-%-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
-\label{sec:oqom}
-
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
-
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
-
-\begin{eqnarray}
-\label{qrmsimilarity}
- R(S,Q) = 1 - (d_{R} + d_{\Upsilon} + d_{\Omega})
-\end{eqnarray}
-\noindent where 
-\begin{eqnarray}
-d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
-\end{eqnarray}
-\begin{eqnarray}
-d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
-\end{eqnarray}
-\begin{eqnarray}
- d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
-\end{eqnarray}
-\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
-\begin{equation}
-\label{piconstraint1}
-\sum_{k=1}^{9} {{\pi}_k} = 1
-\end{equation}
-\noindent and for $1 \leq i \leq 9$
-
-\begin{equation}
-\label{piconstraint2}
-{\pi}_i > 0
-\end{equation}
-
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
-
-% Need to show an example ?
-
-%-------------------------------------------------------------------------------
-
-\subsection{Query Re-Execution}
-% Chris
-
 \section{Results}
@@
 \section{Acknowledgements}
-
-%
-% The bibliography for the citations in the paper 
-\bibliographystyle{abbrv}
-\bibliography{citations}  						% citations.bib is the name of the Bibliography
-
-\end{document}            						% End of document.

### 2010-03-03 trunk/paper/semsearch10/content/ssq_ranking.tex
combined stuff

--- 2010-03-02 trunk/paper/semsearch10/paper.tex
@@
-\documentclass{www2010-submission}
-\begin{document}
-
-\title{Leveraging Semantics for a Deep Web Question Answering System} 
-\numberofauthors{1}
-\author{
-	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
-}
-\date{April 26,2010}
-
-\maketitle
-
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
-
-\category{H.4.m}{Information Systems Applications}{Miscellaneous}
-
-\terms{SSQ}
-
-\keywords{Questions Answering, re-finding}
-
-\section{Introduction}
-% Christan
-- When traveling though a jungle to a destination, it is easy to get lost.
-If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
-An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-This idea translates to the arena of semantic search.
-
-Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
-Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large missing area for optimization for search engines.
-We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
-
-... expand here...
-
-The paper proceeds as follows:
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Establishing the Semantic Hierarchy}
-
-\subsection{Class Hierarchy} 
-% Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
-
-%-------------------------------------------------------------------------------
-
-\subsection{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
-
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
-
-The discovery process can be broken down into three cases:
-\begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
-\end{enumerate}
-
-Any discovery process  consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
-
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
-
-\begin{enumerate}
-
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
-
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
-
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
-\begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
-
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
-\end{itemize}
-
-\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
-
-\item $R$ is an ontological realm.
-
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
-
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-%-------------------------------------------------------------------------------
-
-\section{Natural Language Queries}
-\subsection{Semi-Structured Query}
-% Joir-dan
 \subsection{SSQ Ranking}
@@
 Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
+It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic function type matches.
 We consider the realm class and context property ranges for determining SSQ similarity.
 Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
-
-%-------------------------------------------------------------------------------
 
@@
 %-------------------------------------------------------------------------------
-
-\subsection{Query Re-Execution}
-% Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-- Talk about the offline execution mode and class structural matching algorithm
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
-
-% Sort classes based on the prior
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-%
-% The bibliography for the citations in the paper 
-\bibliographystyle{abbrv}
-\bibliography{citations}  						% citations.bib is the name of the Bibliography
-
-\end{document}            						% End of document.

### 2010-03-03 trunk/paper/semsearch10/paper_old_old.tex
combined stuff

--- 2010-03-02 trunk/paper/semsearch10/paper.tex
@@
 
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
-
 \category{H.4.m}{Information Systems Applications}{Miscellaneous}
@@
 
-\section{Introduction}
-% Christan
-- When traveling though a jungle to a destination, it is easy to get lost.
-If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
-An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-This idea translates to the arena of semantic search.
-
-Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
-Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large missing area for optimization for search engines.
-We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
-
-... expand here...
-
-The paper proceeds as follows:
-
 \section{Semantic Query Representation}
 % Christan - fois
+- We translate natural language queries into a format we call - semi structured query
+- the semi structure query is formated as followed...
+- this format especially allows us to better match deep web parameters with queries
 
@@
 
-\subsection{Class Hierarchy} 
-% Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
-
-%-------------------------------------------------------------------------------
-
-\subsection{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
 \section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
-
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
-
-The discovery process can be broken down into three cases:
-\begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
-\end{enumerate}
-
-Any discovery process  consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
-
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
-
-\begin{enumerate}
-
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
-
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
-
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
-\begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
-
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
-\end{itemize}
-
-\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.
-
-\item $R$ is an ontological realm.
-
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
-
-\end{enumerate}
-
-%-------------------------------------------------------------------------------
-
-\subsection{Generalization}
-% Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
-
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
-
-%-------------------------------------------------------------------------------
 
@@
 % Joir-dan
-\subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
-
-The similarity measure for the SSQ ontologies is determined by the following components.
-\begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
-\end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{Dylan_MultipleInheritance} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
-
-%-------------------------------------------------------------------------------
-
-\subsubsection{Class Divergence}
-\label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
-
-\begin{equation}
-d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
-d(S, T) & if S \prec T\\
-1 & if T \prec S\\
-d(S,root) \\+ d(S,C) + d(T,C) & otherwise
-\end{cases}
-\end{equation}
-
-We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
-
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
-that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
-This is an important property in determining the compatibility of classes for answering queries.
-If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
-
-% Algorithm 1: figure  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{class_divergence.eps}
-\caption{Abbrv. graphical representation of an automotive ontology}
-\label{fig:class_divergence}
-\end{figure}
-
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
-
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
-
-%-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
-\label{sec:oqom}
-
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
-
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
-
-\begin{eqnarray}
-\label{qrmsimilarity}
- R(S,Q) = 1 - (d_{R} + d_{\Upsilon} + d_{\Omega})
-\end{eqnarray}
-\noindent where 
-\begin{eqnarray}
-d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
-\end{eqnarray}
-\begin{eqnarray}
-d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
-\end{eqnarray}
-\begin{eqnarray}
- d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
-\end{eqnarray}
-\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
-\begin{equation}
-\label{piconstraint1}
-\sum_{k=1}^{9} {{\pi}_k} = 1
-\end{equation}
-\noindent and for $1 \leq i \leq 9$
-
-\begin{equation}
-\label{piconstraint2}
-{\pi}_i > 0
-\end{equation}
-
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
-
-% Need to show an example ?
 
@@
 % Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-- Talk about the offline execution mode and class structural matching algorithm
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
-
-% Sort classes based on the prior
-
-\section{Conclusion}
-
-\section{Acknowledgements}
 

### 2010-03-04 paper/semsearch10/content/query_reexecution.tex
updating

\subsection{Query Re-execution}
% Chris
	I ASSUME CLINT HAS COVERED QRM SELECTION ALREADY
	When a user submits a new query to the Morpheus system, one or more stored 
Query Resolution Methods are executed to obtain results. These QRMs are sorted based
on their relevance to the query at hand and are chosen by the ontology matching subsystem.
	A QRM consists of an XML script which instructs the Query Resolution Executor how to 
obtain the required result. The QRE may "click" links, submit forms or highlight and save
important pieces of html, including answers. Once it has visited all pages included in the 
script the QRE returns the HTML snippet containing the answer. This answer can then be
rendered in a browser. As mentioned above, normally a list or relevant QRMs will be given
to the QRE which will in turn be executed using the provided SSQ, the results will be 
displayed in order for the user.

### 2010-03-04 paper/semsearch10/content/query_reexecution.tex
my section

@@
 	When a user submits a new query to the Morpheus system, one or more stored 
-Query Resolution Methods are executed to obtain results. These QRMs are sorted based
-on their relevance to the query at hand and are chosen by the ontology matching subsystem.
-	A QRM consists of an XML script which instructs the Query Resolution Executor how to 
-obtain the required result. The QRE may "click" links, submit forms or highlight and save
-important pieces of html, including answers. Once it has visited all pages included in the 
-script the QRE returns the HTML snippet containing the answer. This answer can then be
-rendered in a browser. As mentioned above, normally a list or relevant QRMs will be given
-to the QRE which will in turn be executed using the provided SSQ, the results will be 
-displayed in order for the user.
+Query Resolution Methods are executed to obtain results.
+A QRM consists of an XML script which instructs the Query Resolution Executor how to obtain the required result.
+The Query Resolution Executor may "click" links, submit forms or highlight and save important pieces of html, including answers.
+At the present, the GET form submission method is used.
+	There is greater complexity in dealing with web forms than with links. For a given
+form, there may be text fields, drop-down boxes, radio buttons etc.
+In order to support form submission in such circumstances the QRE will take different actions based on the input type.
+For text fields, simply adding a key/value pair to the querystring suffices.
+For a drop-down box, the QRE extracts the form element and performs a lookup on its options to find the appropriate value to include in the querystring.
+	All input data as well as highlighted HTML is kept in an internal hash table.
+The QRM script contains keys which allow the QRE to map SSQ inputs from the table to the appropriate form inputs.
+Furthermore, highlights which are collected during execution are stored in the hash table.
+	Once all pages included in the script have been visited, the QRE returns the HTML snippet containing the answer.
+This answer can then be rendered in a browser.
+Normally a list of QRMs, sorted by relevance, are given to the QRE.
+Therefore after execution a list of results is returned in order of relevance.

### 2010-03-04 trunk/paper/semsearch10/content/nlp.tex
latest...

% Joir-dan stuff

When we have completed our Wikipedia corpora from all the blankets in the category hierarchy, our system needs to make sense of the data for execution. The learning process involves the calculation of two n-gram frequency distributions: an n-gram/vocabulary distribution, and an n-gram/category distribution. The first value is the count of individual n-grams in the combined vocabulary of all corpora, and the second one is just the count of individual n-grams within a category’s blanket. The categories’ corpora reflect one long context per category, instead of breaking up sentences into different contexts. The idea behind this is that Wikipedia pages are already grouped into categories, that we can assume are related to the topics of each sentence within the corpus. We store distributions, rather than priors, primarily because if at anytime a blanket vocabulary seems inadequate, we can append terms from other sources to both distribution types and recalculate our values. We can simply calculate probabilities and store these separately for the execution of our natural query engine.

The goal, is to choose that category for use in the SSQ structure. This process requires the tagging and parsing of our natural query, the extraction of key elements, primarily adjectives and nouns, and then using n-gram priors to calculate the appropriate category associated with that term.

Picking out these terms requires knowledge of the structure of the question being passed to the system. The ideal situation would be that we could recognize question patterns, and decide where key information is within the question based on a given pattern. Currently, we only work with questions in an “answer” form, which means there is little to no transformation of the structure, to go from a question to an answer.

Example

Question: A 1997 Toyota Corolla needs what size tires?
Answer:   A 1997 Toyota Corolla needs 17” tires.

### 2010-03-04 paper/semsearch10/content/ontological_realms.tex
latest...

--- 2010-03-03 trunk/paper/semsearch10/content/ontological_realms.tex
@@
 %joir-dan
+
+Building Ontological Realms
+
 Once the semantic hierarchy is created, the next step is to create training data for the system.
@@
 The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
+Each category within the DBpedia/Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
 Considering that the categorical structure is a directed acyclic graph  \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
+The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
 While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
+
+Consider the abbreviated Markov blanket for the category Automobiles:
 
@@
 
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
+The subcategories of the category Automobiles (… Driving, Traffic Law, Automobiles by Decade, Auto Racing…) can be seen as grabbing information specific to the category.
+The supercategories (Road Vehicles) place the category in a higher perspective, abstractly describing basketball as a concept.
+The spousal categories (...Motorsport, Individual Sport...) are an abstract description of the subcategories.
 
 Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
+Since the above model relies on the subcategories to describe specifics of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a significant amount of information per page.
 In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
@@
 Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
+This mechanism checks if a subcategory has an adequate number of pages α to fully describe its subtopic.
+We set this number to ten times the average, or 260.
+$Level$ represents how many extra levels we are to go down in the hierarchy, if necessary.
 SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
 
+\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival]
+def BlanketSubjectRetreival(blanket, maxLevel):
+	for category in blanket:
+		subjectSet.add(grabsubjects(category))
+		diff = afterSize - beforeSize
+		if diff <= \alpha and category is subcategory:
+			PlusOneMechanism(category, maxLevel)
+	return subjectSet
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism]
+def PlusOneMechanism(category, level):
+	plusOneSet = grabPlusOneSubcategories(category)
+	for subcategory in plusOneSet:
+		subject.add(grabSubjects
+
+\end{lstlisting}
+
 The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
+Using this method on the category Automobiles, we can construct a corpus of 2255 subject pages and 6,084,260 terms.
 
 When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
+For the purpose of calculating term importance to a blanket, we aggregate the frequencies of all blankets and store this information as well.
+For this system, term importance refers to the prior probability of a category given an n-gram.
+We calculate this using Bayes Rule, since we can easily obtain the n-gram-category and n-gram-vocabulary probabilities.
+The higher the probability, the more likely a term is referring to a category.
+
+\begin{equation}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}

### 2010-03-04 paper/semsearch10/paper.tex
latest stuff

--- 2010-03-01 paper/semsearch10/paper.tex
@@
 \documentclass{www2010-submission}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+\usepackage{listings}
 \begin{document}
 
-\title{Leveraging Semantics for a Deep Web Question and Answering System} 
+\title{Re-finding to support a Deep Web Question Answering System} 
 \numberofauthors{1}
@@
 	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
-\email{cgrant@cise.ufl.edu, cpj@cise.ufl.edu, jnw@cise.ufl.edu, pjd@cise.ufl.edu, jdepree@cise.ufl.edu, cas@cise.ufl.edu, jg@cise.ufl.edu}
+\email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}
 }
-
 \date{April 26,2010}
@@
 
-\begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
-\end{abstract}
+\input{content/abstract.tex}
 
@@
 
-\section{Introduction}
-% Christan
-- IEEE potentials article talks discussed the idea of using the beaten trail. To solve problems
-- Typical search engines have several repeat queries.
-- We believe that treating these repeat visits as special visits will enhance user search experience
-- To demonstrate this concept we are building a tool that facilitates reuse in the specific domain of question answering
-- 
--
+\input{content/introduction.tex}
+\input{content/example.tex}
+\input{content/nlp.tex}
+\input{content/qrr.tex}
+\input{content/ontological_realms.tex}
+\input{content/ssq_ranking.tex} % Joir-dan adds finding category stuff here
+\input{content/query_reexecution.tex}
+\input{content/results_futurework_conclusion.tex}
 
-\section{Statistical Hierarchy}
-\subsection*{Class Hierarchy}
-%clint
-\subsection*{Markov Blanket}
-%joir-dan
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/ Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph (Suchanek et al., 2008), we consider the use of a Markov Blanket (Friedman et al., 1997) in describing a particular category.
-The category's that The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
+\bibliographystyle{abbrv}
+\bibliography{citations}
 
-Consider the abbreviated Markov blanket for the category Basketball:
-%\includegraphics[width=1in,height=1in,viewport=0 0 100 100]{abbreviated_basketball_blanket.png}
-
-The subcategories of the category Basketball (...
-Basketball Organizations, Basketball Competitions, Basketball Terminology, Basketball Teams...) can be seen as grabbing information specifc to the category.
-The supercategories (Ball Games, Olympic Sports, Team Sports) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifcs of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a signifcant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category (Yu et al., 2007).
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{algorithm}
-\caption{Blanket Subject Retrieval}
-\label{alg1}
-	\begin{algorithmic}
-	\STATE BlanketSubjectRetrieval(blanket, maxLevel):
-		\FOR{category c in blanket}
-			\STATE subjectSet.add(grabSubjects(c))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha and c is a subcategory}
-				\STATE PlusOneMechanism(category, maxLevel)
-			\ENDIF
-		\ENDFOR
-	\STATE return subjectSet
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-\caption{Plus One Mechanism}
-\label{alg2}
-	\begin{algorithmic}
-	\STATE PlusOneMechanism(category, level)
-		\STATE plusOneSet = grabPlusOneSubcategories(category)
-		\FOR{ subcategory in plusOneSet}
-			\STATE subjectSet.add(grabSubjects(subcategory))
-			\STATE diff = afterSize - beforeSize
-			\IF{ diff \leq \alpha \and level \gt 0}
-				\STATE PlusOneMechanism(subcategory, level - 1);
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-
-\section{Semantic Query Representation}
-% Christan - fois
-
-\section{Building Query Store}
-\subsection{Query Resolution Recorder}
-% Chris
-\subsection{Generalization}
-% Christan
-
-\section{Semantic Query Answering}
-\subsection{Semi-Structured Query}
-% Joir-dan
-\subsection{SSQ Ranking}
-% Clint
-\subsection{Query Re-Execution}
-% Chris
-
-\section{Results}
-% Walk through of example query
-
-\section{Future Work}
-
-\section{Conclusion}
-
-\section{Acknowledgements}
-
-\section{References}
-Bayesian Network Classifers
-Friedman, Geiger, Goldszmidt 1997
-
-YAGO: A Large Ontology from Wikipedia and WordNet
-Fabian M. Suchanek, Gjergji Kasnecia, and Gerhard Weikuma 2008
-
-Ontology Evaluation: Using Wikipedia Categories for Browsing
-Yu, Thom, Tam 2007
-
-\end{document}            % End of document.
+\end{document}

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
latest stuff

@@
 \centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
+\includegraphics[width=90mm]{BlanketExample.eps}
+\caption{Abbreviated Markov blanket for the category Automobiles}
 \label{fig:abbrv_bb_blanket}
@@
 Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages a to fully describe its subtopic.
-We set this number to 10 * average, or 39.
-level represents how many extra levels we are to go down in the hierarchy, if necessary.
+This mechanism checks if a subcategory has an adequate number of pages α to fully describe its subtopic.
+We set this number to ten times the average, or 260.
+$Level$ represents how many extra levels we are to go down in the hierarchy, if necessary.
 SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
 
+\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival]
+def BlanketSubjectRetreival(blanket, maxLevel):
+	for category in blanket:
+		subjectSet.add(grabsubjects(category))
+		diff = afterSize - beforeSize
+		if diff <= a and category is subcategory:
+			PlusOneMechanism(category, maxLevel)
+	return subjectSet
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism]
+def PlusOneMechanism(category, level):
+	plusOneSet = grabPlusOneSubcategories(category)
+	for subcategory in plusOneSet:
+		subject.add(grabSubjects(subcategory))
+		diff = afterSize - beforeSize
+		if diff <= a and level > 0:
+			PlusOneMechanism(subcategory, level-1)
+
+\end{lstlisting}
+
 The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Basketball, we can construct a corpus of 1843 subject pages and 1,301,006 terms.
+Using this method on the category Automobiles, we can construct a corpus of 2255 subject pages and 6,084,260 terms.
 
 When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
+For the purpose of calculating term importance to a blanket, we aggregate the frequencies of all blankets and store this information as well.
+For this system, term importance refers to the prior probability of a category given an n-gram.
+We calculate this using Bayes Rule, since we can easily obtain the n-gram-category and n-gram-vocabulary probabilities.
+The higher the probability, the more likely a term is referring to a category.
+
+\begin{equation}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}

### 2010-03-04 trunk/paper/semsearch10/content/example.tex
first round of changes by jnw

The end-user employs the Morpheus question-answering system much like a
search engine with a natural-language interface. One can type a question
in a text box and receive a response from the system. Those questions
dealing with an ontological realm familiar to the system, whose form is
similar to previously answered queries in that realm, and that can be
answered using (possibly deep web) information from a source the system
has encountered can yield relevant responses.

\begin{figure}
\caption{Typical Morpheus interaction}
\label{fig:screenshot}
\end{figure}

Figure \ref{fig:screenshot} shows a screenshot of a typical Morpheus
interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
received a response together with information describing assumptions
about the question, the likely relevance of the answer provided,
the source of information, and the method of answer production.

Each answer to a question is created using a {\it query response
  method} (QRM). A QRM is constructed when a special user, known as a
{\it guide} answers a question using an instrumented web browser (the
{\it query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a {\it semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the inputs and output
contexts---the {\it who, what, when,} and {\it where}
categories---that characterize the question together with an
appropriately generalized representation of the guide's browser
interactions.  The {\it query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

To answer a user's question, we must identify likely contextual
categories associated with the terms in the question to form an SSQ,
find those QRMs having contextually compatible SSQs, then use the QRE to
generate a response.

In what follows, we detail the elements of the system.  We first
discuss the processing of natural language queries to generate SSQs.
Next, we discuss the recording of guide behavior with the QRR.  We
then discuss how the categorical heterarchies associated with
ontological realms are constructed in a semi-automated fashion.  We
describe the method we use to assess how well a stored QRM matches a
user SSQ.  We then discuss the QRM evaluation process and discuss the
system's behavior on example queries. We conclude with a discussion of
future work.

### 2010-03-04 trunk/paper/semsearch10/content/introduction.tex
first round of changes by jnw

\section{Introduction}
% Christan
When traveling though a jungle to a destination, it is easy to get
lost.  The first person to take blaze a trail may make a number of
mistakes in trying to find the best path to any destination.  However,
those who come later can easily follow a well-marked trail without the
level of effort required by the path-finder. Olsen and Malizia
describe this idea as \emph{exploiting trails} \cite{5379671}.  The
Morpheus Question Answering System uses this insight to improve the
efficency of retrieval in semantic search.

Rather than treating each user's search as a unique entity and working
from first principles, we exploit the fact that a similar search may
have been performed already.
Researchers have shown that almost 40 percent of the all
queries are repetitions of previous queries.\cite{1277770}
This points to an  area for optimization for search engines.
We have built a prototype system for answering questions using deep-web sources
that employs previously answered questions to obtain new answers.

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
third round of changes by jnw

@@
-\subsection{Class Heterarchy} 
+\subsection{Category Heterarchy} 
 % Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
+Since, our representation of semi structured query [citation needed]
+is in OWL ontology format, and our aim is to compare and rank the
+queries in this format, we had to define a similarity measure between
+ontologies. The defined ontology class comparison measure "class
+divergence" [citation needed] assumes that we have an ontology store
+with unambiguous interpretation of classes and strict hierarchical
+subclass super class relationships and the classes to be compared
+should belong to it. We cannot find any robust existing ontology
+library of that nature for this purpose. So we decided to build a new
+ontology store and as an initial step the categories from DBPedia
+store [citation needed] are used. Even though, some of these
+categories are loosely coupled and not fully agreed upon the sub
+category and super category relationships, this DBPedia has enormous
+amount of data in linked form [citation needed]. The OWL ontology
+[citation needed] format is followed in this process. The DBPedia
+categories are converted into OWL ontology classes and the super class
+- sub class relationships are built using the OWL super class sub
+class axioms [citation needed]. Another reason for selecting OWL for
+this purpose is that we can make use of the existing APIs for building
+and reasoning [citation needed] the ontology relationships.
 
@@
 
-\subsection{Associating Terms with Categories}
-%joir-dan
+\subsection{Associating Terms with Categories} %joir-dan The
+subcategories of the category Automobiles (… Driving, Traffic Law,
+Automobiles by Decade, Auto Racing…) can be seen as grabbing
+information specific to the category. The supercategories (Road
+Vehicles) place the category in a higher perspective, abstractly
+describing basketball as a concept. The spousal categories
+(...Motorsport, Individual Sport...) are an abstract description of
+the subcategories.
 
-Building Ontological Realms
+Clustering the categories alone does not guarantee adequate corpus
+creation. Since the above model relies on the subcategories to
+describe specifics of a given category, the ideal situation would be
+that the subcategories have many more pages than the supercategories
+and that there is a significant amount of information per page.  In
+the case of Wikipedia, there are an average of 25.7 pages per category
+\cite{1321474}. The assumption for collecting the training data is the
+more subcategory data we have, the more detailed our description of
+our category. Considering that there are many categories that have
+much more than 26 pages, we instituted a PlusOne mechanism to extract
+extra information. This mechanism checks if a subcategory has an
+adequate number of pages α to fully describe its subtopic. We set this
+number to ten times the average, or 260. $Level$ represents how many
+extra levels we are to go down in the hierarchy, if
+necessary. SubjectSet is the overall set of all pages associated with
+the blanket structure along with any plusOne subjects obtained.
 
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph  \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-Consider the abbreviated Markov blanket for the category Automobiles:
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{BlanketExample.eps}
-\caption{Abbreviated Markov blanket for the category Automobiles}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Automobiles (… Driving, Traffic Law, Automobiles by Decade, Auto Racing…) can be seen as grabbing information specific to the category.
-The supercategories (Road Vehicles) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories (...Motorsport, Individual Sport...) are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifics of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a significant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages α to fully describe its subtopic.
-We set this number to ten times the average, or 260.
-$Level$ represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival]
+\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=BlanketSubjectRetreival,label=BlanketSubjectRetreival,basicstyle=\small]
 def BlanketSubjectRetreival(blanket, maxLevel):
@@
 
-\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism]
+\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism,basicstyle=\small]
 def PlusOneMechanism(category, level):
@@
 
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Automobiles, we can construct a corpus of 2255 subject pages and 6,084,260 terms.
+The overall mechanism does not take into account the amount of
+information within each page, but generally that can be ignored when
+considering the size of the blanket corpus when we extract the text
+from the Wikipedia subject pages. Using this method on the category
+Automobiles, we can construct a corpus of 2255 subject pages and
+6,084,260 terms.
 
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-For the purpose of calculating term importance to a blanket, we aggregate the frequencies of all blankets and store this information as well.
-For this system, term importance refers to the prior probability of a category given an n-gram.
-We calculate this using Bayes Rule, since we can easily obtain the n-gram-category and n-gram-vocabulary probabilities.
-The higher the probability, the more likely a term is referring to a category.
+When a category's corpus is built, we then build our n-gram frequency
+distributions and store them in a database for the NLP processing. For
+the purpose of calculating term importance to a blanket, we aggregate
+the frequencies of all blankets and store this information as
+well. For this system, term importance refers to the prior probability
+of a category given an n-gram. We calculate this using Bayes Rule,
+since we can easily obtain the n-gram-category and n-gram-vocabulary
+probabilities. The higher the probability, the more likely a term is
+referring to a category.
 

### 2010-03-04 trunk/paper/semsearch10/content/qrr.tex
third round of changes by jnw

@@
-\subsection{Query Resolution Recorder}
+\section{Query Resolution Recorder (QRR)}
+\label{sec:qrr}
 % Chris
-Answering a question using the deep web requires one to navigate through a sequence of one or more web pages and links.
-Many of the accesses involve clicks through web forms to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
-We record the user actions with a browser plugin called the \emph{query resolution recorder} (QRR).
+Answering a question using the deep web requires one to navigate
+through a sequence of one or more web pages and links.  Many of the
+accesses involve clicks through web forms to resulting pages.  We have
+developed a model that represents the various actions a user may carry
+out during this process.
 
-During the answer retrieval process, a user discovers an element of the query's result on a web page.
-Next, she highlights that element, typically a text string.
-This highlight allows the QRR to record the source of  the query's answer.
-The QRR stores all information from the user query in our data store.
-When the user submits a web form she may associate each of the form's inputs with one of our stored context classes.
+During the answer retrieval process, a user discovers an element of
+the query's result on a web page.  Next, she highlights that element,
+typically a text string.  This highlight allows the QRR to record the
+source of the query's answer.  The QRR stores all information from the
+user query in our data store.  When the user submits a web form she
+may associate each of the form's inputs with one of our stored context
+classes.
 
@@
 \begin{enumerate}
-\item The user typed in a URL  and highlighted part of or all the answer. 
-\item The user typed in a URL, clicked a link, and found part or all of the answer. 
-\item The user typed in a URL, filled out a form, and found part or all of the answer on a subsequent page. 
+\item The user typed in a URL and highlighted part of or all the
+  answer.
+\item The user typed in a URL, clicked a link, and found part or all
+  of the answer.
+\item The user typed in a URL, filled out a form, and found part or
+  all of the answer on a subsequent page.
 \end{enumerate}
@@
 Any discovery process consists of a sequence of these transactions.
-Additionally, data collected for inputs and outputs may be found during any stage of the complete discovery process.
-An output collected during one stage of an extraction may be the input to a subsequent stage in the extraction.
-The QRR builds the completed user collection process into a QRM.
-The following is a mathematical formulation of information collected for user web interactions.\\
+Additionally, data collected for inputs and outputs may be found
+during any stage of the complete discovery process.  An output
+collected during one stage of an extraction may be the input to a
+subsequent stage in the extraction.  The QRR builds the completed user
+collection process into a QRM.  The following is a mathematical
+formulation of information collected for user web interactions.
 
@@
 
-\item $\Upsilon$ is the sequence of input classes $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of the associated query, $\Upsilon_{2}$ represents the \emph{what} context, $\Upsilon_{3}$ represents the \emph{when} context, and $\Upsilon_{4}$ represents the \emph{where} context.
+\item $\Upsilon$ is the sequence of input categories $\left<
+  \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$
+  where $\Upsilon_{1}$ represents the \emph{who} context of the
+  associated query, $\Upsilon_{2}$ represents the \emph{what} context,
+  $\Upsilon_{3}$ represents the \emph{when} context, and
+  $\Upsilon_{4}$ represents the \emph{where} context.
 
-\item $\Omega$ is the sequence of output classes $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$ represents the \emph{who} context of the associated query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$ represents the \emph{when} context, and $\Omega_{4}$ represents the \emph{where} context.
+\item $\Omega$ is the sequence of output categories $\left<\Omega_{1},
+  \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$
+  represents the \emph{who} context of the associated query,
+  $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
+  represents the \emph{when} context, and $\Omega_{4}$ represents the
+  \emph{where} context.
 
-\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,..., P_n\right>$ where $P_h = \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$ for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h \right|$.
-$P_h$ is a triple comprised of a URL $U_h$, a sequence of input arguments, and a sequence of output results.
-\\
-Let $I_{\$} = \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector expressions for the inputs of a query and $O_{\$} = \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors expressions for the outputs of a query.
-\\
-Let $K$ be the set of all string constants.
+\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,...,
+  P_n\right>$ where $P_h =
+  \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$
+  for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h
+  \right|$. $P_h$ is a triple comprised of a URL $U_h$, a sequence of
+  input arguments, and a sequence of output results.  \\ Let $I_{\$} =
+  \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector
+  expressions for the inputs of a query and $O_{\$} =
+  \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors
+  expressions for the outputs of a query.  \\ Let $K$ be the set of
+  all string constants.
 \begin{itemize}
-\item URI $U_1 \in K$ is a string and \\
-for $1 < g \leq n$, URI $U_g \in K \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1 \leq h \leq \left| O_p \right| $,
+\item URI $U_1 \in K$ is a string and \\ for $1 < g \leq n$, URI $U_g
+  \in K \cup \left( \bigcup^{g-1}_{p=1} \left(
+  \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1
+  \leq h \leq \left| O_p \right| $,
 
-\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup I_{\$} \cup O_{\$}$ and \\
-for $1 < g <= n$, then for $1 < h < \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$} \cup \left( \bigcup^{g-1}_{p=1} \left( \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
+\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup
+  I_{\$} \cup O_{\$}$ and \\ for $1 < g <= n$, then for $1 < h <
+  \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$}
+  \cup \left( \bigcup^{g-1}_{p=1} \left(
+  \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
 \end{itemize}
@@
 
-\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and $\Omega$ representing the answer.
+\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and
+  $\Omega$ representing the answer.
 
@@
 
-\subsection{Generalization}
+%\subsection{Generalization}
 % Christan
-The response pages created by querying web forms are dynamically generated with a templated structure.
-This generalization per page is done using the GenPath algorithm developed by Badica et al.
-\cite{Badica06}.
-Additionally, the community may be able to answer a particular SSQ using many different page interactions.
-Therefore, we proposed a method of generalizing extraction path to a result across pages.
-This method removes unnecessary page interactions and finds the shortest path to the result pages.
+The response pages created by querying web forms are dynamically
+generated with a templated structure. This generalization per page is
+done using the GenPath algorithm developed by Badica et
+al. \cite{Badica06}. Additionally, the community may be able to answer
+a particular SSQ using many different page interactions. Therefore, we
+use a method of generalizing extraction path to a result across
+pages. This method removes unnecessary page interactions and finds the
+shortest path to the result pages.
 
-The websites that are wrapped are highly susceptible to structural changes \cite{TanZMG07}.
-Generalizing the extraction paths help to overcome small structural changes.
-If a website changes to the point where a QRM is no longer useful, the QRM not considered fresh.
-Morpheus allows users to rate the freshness of QRMs.
+Websites wrapped by a system such as this are highly susceptible to
+structural changes \cite{TanZMG07}. Generalizing the extraction paths
+helps overcome small structural changes. If a website changes to the
+point where a QRM is no longer useful, the QRM is not considered
+fresh. User ratings of QRM freshness can be employed in the SSQ matching
+process detailed in Section \ref{sec:ssq}.
 

### 2010-03-04 paper/semsearch10/content/example.tex
third round of changes by jnw

--- 2010-03-04 trunk/paper/semsearch10/content/example.tex
@@
+%jnw
+
 The end-user employs the Morpheus question-answering system much like a
@@
 
-Each answer to a question is created using a {\it query response
+Each answer to a question is created using a \emph{query response
   method} (QRM). A QRM is constructed when a special user, known as a
-{\it guide} answers a question using an instrumented web browser (the
-{\it query response recorder} or QRR) that records web
+\emph{guide} answers a question using an instrumented web browser (the
+\emph{query response recorder} or QRR) that records web
 interactions. The system extracts the relevant artifacts of the
 guide's actions and stores them in the QRM. The QRM is characterized
-by a {\it semi-structured query} (SSQ), a schematic representation of
+by a \emph{semi-structured query} (SSQ), a schematic representation of
 the information contained in the query, namely the inputs and output
-contexts---the {\it who, what, when,} and {\it where}
+contexts---the \emph{who, what, when,} and \emph{where}
 categories---that characterize the question together with an
 appropriately generalized representation of the guide's browser
-interactions.  The {\it query response evaluator} (QRE) evaluates a
+interactions.  The \emph{query response evaluator} (QRE) evaluates a
 query by binding specific arguments to its input parameters and

### 2010-03-04 paper/semsearch10/content/introduction.tex
third round of changes by jnw

@@
 % Christan
-When traveling though a jungle to a destination, it is easy to get lost.
-If you are the first person to take a path then you have to make a lot of mitakes in order to find the best path to a destination.
-However, if you are the \emph{n}th person to take a path, you may be able to follow the path that was left by the \emph{n-1} other people to walk the path.
-An article by Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-We use this insight to to improve the efficency of retrieval in semantic search.
-
-Instead of treating each user search as a unique search, it is beneficial to assume that a similar search has been previously performed.
-Researchers have shown that almost 40 percent of the all queries are repeats \cite{1277770}.
-This means there is a large open area for optimization for search engines.
-We have built a prototype system for deep web question answering that uses previously answered questions to obtain new answers.
-
-In this paper we describe a system for recording the answer to user queries and executing solutions to similar queries.
-To support this we use a structured query representation.
-The structured representation allows queries to be parameterized so that similar queries may be discovered at query-time.
-To recognizing these queries we build a semantic heterarchy and define algorithms for matching the classes.
-
-The paper proceeds as follows:
-\begin{itemize}
-\item Discussion of the query structure.  We call this structure an \emph{semi-structured query} SSQ.
-\item Next we discuss how we create the class heterarchy to support the semantic comparisons.
-\item In section \ref{sec:Building Query Store} we discuss how we record user web queries and correctly annotate them.
-\item Next, we discribe how we match rank 
-\item ....
-\item We will conclude by discussing the examples of the system.
-\end{itemize}
+When traveling though a jungle to a destination, it is easy to get
+lost.  The first person to go somewhere may make a number of mistakes
+in trying to find the best path to their destination.  However, those
+who come later will find it easy to reach that destination if a
+well-marked trail without the has been created. Olsen and Malizia
+describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather
+than treating each user's search as a unique entity and working from
+first principles, one can exploit the fact that a similar search may
+have been performed already.  In one study, almost 40 percent of all
+queries were found to be repetitions of previous
+queries.\cite{1277770} This points to way to optimize the search
+process.  We have built a prototype system for answering questions
+using deep-web sources that employs previously answered questions to
+obtain new answers.  Using our analogy, the Morpheus question
+answering system follows path-finders to their destinations and not
+only marks the trail, but provides a taxi service to take followers to
+similar destinations.

### 2010-03-04 paper/semsearch10/content/query_reexecution.tex
third round of changes by jnw

@@
 % Chris
-	I ASSUME CLINT HAS COVERED QRM SELECTION ALREADY
-	When a user submits a new query to the Morpheus system, one or more stored 
-Query Resolution Methods are executed to obtain results.
-A QRM consists of an XML script which instructs the Query Resolution Executor how to obtain the required result.
-The Query Resolution Executor may "click" links, submit forms or highlight and save important pieces of html, including answers.
-At the present, the GET form submission method is used.
-	There is greater complexity in dealing with web forms than with links. For a given
-form, there may be text fields, drop-down boxes, radio buttons etc.
-In order to support form submission in such circumstances the QRE will take different actions based on the input type.
-For text fields, simply adding a key/value pair to the querystring suffices.
-For a drop-down box, the QRE extracts the form element and performs a lookup on its options to find the appropriate value to include in the querystring.
-	All input data as well as highlighted HTML is kept in an internal hash table.
-The QRM script contains keys which allow the QRE to map SSQ inputs from the table to the appropriate form inputs.
-Furthermore, highlights which are collected during execution are stored in the hash table.
-	Once all pages included in the script have been visited, the QRE returns the HTML snippet containing the answer.
-This answer can then be rendered in a browser.
-Normally a list of QRMs, sorted by relevance, are given to the QRE.
-Therefore after execution a list of results is returned in order of relevance.
+When a user submits a new query to the Morpheus system, one or more
+stored Query Resolution Methods are executed to obtain results. A QRM
+consists of an XML script which instructs the Query Resolution
+Executor how to obtain the required result. The Query Resolution
+Executor may "click" links, submit forms or highlight and save
+important pieces of html, including answers. At the present, the GET
+form submission method is used.  There is greater complexity in
+dealing with web forms than with links. For a given form, there may be
+text fields, drop-down boxes, radio buttons etc. In order to support
+form submission in such circumstances the QRE will take different
+actions based on the input type. For text fields, simply adding a
+key/value pair to the querystring suffices. For a drop-down box, the
+QRE extracts the form element and performs a lookup on its options to
+find the appropriate value to include in the querystring.  All input
+data as well as highlighted HTML is kept in an internal hash
+table. The QRM script contains keys which allow the QRE to map SSQ
+inputs from the table to the appropriate form inputs. Furthermore,
+highlights which are collected during execution are stored in the hash
+table.  Once all pages included in the script have been visited, the
+QRE returns the HTML snippet containing the answer. This answer can
+then be rendered in a browser. Normally a list of QRMs, sorted by
+relevance, are given to the QRE. Therefore after execution a list of
+results is returned in order of relevance.

### 2010-03-04 paper/semsearch10/content/ssq_ranking.tex
third round of changes by jnw

--- 2010-03-03 trunk/paper/semsearch10/content/ssq_ranking.tex
@@
 \subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
+\label{sec:ssq}
+In order to match a new query with a SSQ within our data store, we
+have defined similarity measures between the ontologies of the new
+query and the candidate SSQs. These measures capture the distance
+between the ontology classes, properties, and individuals at the
+conceptual level in addition to simply matching URIs. The similarity
+measures are implemented in two scenarios: \textit{on-line execution}
+and \textit{off-line mode}. The \textit{on-line execution} is time
+sensitive and is used primarily for relating newly defined SSQs to the
+SSQs in the store. During \textit{off-line execution}, the system
+clusters similar SSQs.
 
-The similarity measure for the SSQ ontologies is determined by the following components.
+The similarity measure for the SSQ ontologies is determined by the
+following components.
 \begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
+    \item QueryClass: an OWL class and the root of the SSQ ontology
+      structure.
+    \item hasRealm: an OWL object property with its domain as the SSQ
+      Query class and its range as a realm class.
+    \item Contexts such as who, what, when, and where are OWL object
+      properties, whose domains are the query classes and ranges are
+      OWL classes.
+    \item SSQClass: an OWL class which is created from the components
+      described above.
 \end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
+Based on this ontology structure and the execution scenarios, we have
+created an algorithm for finding the matches between SSQ
+ontologies. It is based on class divergence, which is motivated by the
+concept of multiple dispatch in CLOS \cite{95411} and Dylan
+programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic
+function type matches. We consider the realm class and context
+property ranges for determining SSQ similarity. Subsections
+\ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
 
@@
 \label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
+We employ a measure of compatibility, which we call \textit{class
+  divergence}, between a source class and a target class using the
+\textit{topological structure} of the context classes in the
+ontology. We write $S \prec T$ for the reflexive transitive closure of
+the superclass relation. Let $d(P,Q)$ represent the hop distance in
+the directed ontology inheritance graph from $P$ to $Q$. The
+divergence between a source and target class ranges from zero (for
+identical classes) to one (for incompatible classes).  Let $S$ be the
+source class, $T$ be the target class, and let $C$ be a common
+ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class
+divergence between $S$ and $T$, the unnormalized class dissimilarity,
+is defined as follows:
 
@@
 
-We normalize $d_{class}(S, T)$ by dividing by three times the height of the ontology tree.
+We normalize $d_{class}(S, T)$ by dividing by three times the height
+of the ontology tree.
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) < d_{class}(S,Q)$,
-that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
-This is an important property in determining the compatibility of classes for answering queries.
-If a SSQ answers queries concerning an ancestor class, it is more relevant that a SSQ that answers queries from any non-ancestral class.
+Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) <
+d_{class}(S,Q)$, that is, the divergence of a source class to a target
+ancestor class is smaller than the divergence of a source class to any
+class that is not an ancestor. This is an important property in
+determining the compatibility of classes for answering queries.  If a
+SSQ answers queries concerning an ancestor class, it is more relevant
+that a SSQ that answers queries from any non-ancestral class.
 
@@
 
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
+Figure \ref{fig:class_divergence} illustrates the calculation of class
+divergence. This sample abbreviated ontology that was created from the
+DBpedia category heirarchy is rooted at the class
+\textit{DBpediaRoot}. The arrows represent the inheritance
+relationship between the classes in the topology.
 
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
+Suppose we want to find the divergence $d_{class}$\textit{(Automotive
+  Industry, Racing Cars)}. The \textit{Automotive Industry} is the
+subclass of \textit{Automobiles} and \textit{Racing Cars} is the
+subclass of \textit{Auto Racinng}. Therefore, the common ancestor for
+these two can be determined as \textit{Automobiles} ($C$). They share
+the path from \textit{Automobiles} to the $root$. So, the unnormalized
+divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from
+the path to root), \textit{d(Automotive Industry, Automobiles)} is one
+(dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two
+(dashed arrow). Suppose, the ontology tree height is calculated as
+294. Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which
+corresponds to a normalized value of $35/294$.
 
@@
 
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
+We use class divergence to calculate the relevance between a source
+SSQ and a target SSQ associated with a QRM.  Each SSQ will have four
+input classes, four output classes, and one realm.  We refer to the
+sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4,
+\Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ. If an
+input or output class is unspecified in the query, it is associated
+with the class $bottom$, which has no subclasses or individuals.
 
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
+The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ...,
+\Upsilon_{Q_4}, \\\Omega_{Q_1}, ... , \Omega_{Q_4}, R_Q\rangle$ to SSQ
+$S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4},
+\\\Omega_{S_1}, ... , \Omega_{S_4}, R_S \rangle$ is
 
@@
 
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
+If an SSQ and a QRM have identical classes for all inputs and their
+realms then the QRM relevance value will be one. Otherwise, the
+relevance of the QRM will be in the range $[0, 1)$.
 

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
fourth round of changes by jnw

@@
+\section{Representing and Ontological Realms}
 \subsection{Category Heterarchy} 
 % Author: Clint 
-Since, our representation of semi structured query [citation needed]
-is in OWL ontology format, and our aim is to compare and rank the
-queries in this format, we had to define a similarity measure between
-ontologies. The defined ontology class comparison measure "class
-divergence" [citation needed] assumes that we have an ontology store
-with unambiguous interpretation of classes and strict hierarchical
-subclass super class relationships and the classes to be compared
-should belong to it. We cannot find any robust existing ontology
-library of that nature for this purpose. So we decided to build a new
-ontology store and as an initial step the categories from DBPedia
-store [citation needed] are used. Even though, some of these
-categories are loosely coupled and not fully agreed upon the sub
-category and super category relationships, this DBPedia has enormous
-amount of data in linked form [citation needed]. The OWL ontology
-[citation needed] format is followed in this process. The DBPedia
-categories are converted into OWL ontology classes and the super class
-- sub class relationships are built using the OWL super class sub
-class axioms [citation needed]. Another reason for selecting OWL for
-this purpose is that we can make use of the existing APIs for building
-and reasoning [citation needed] the ontology relationships.
+Two types of ontologies are used by our system:
+\begin{enumerate}
+\item Realm ontologies, comprising a heterarchy of categories that
+  characterize terms that can appear in queries.
+\item SSQ ontologies, used to describe the form of particular
+  realm-specific queries.
+\end{enumerate}
+For any particular ontological realm, the number of potential
+terms and their associated categories can be quite large.
+Construction of a realm ontology and the terms associated
+with its categories would be an extremely laborious task
+for any non-trivial realm. The realm of automobiles (which
+we use for illustration in this paper) contains, for example,
+over XXXX categories and XXXX terms. We were unable to find
+an appropriate ontology for this realm, so we constructed it
+using categories from the DBPedia [!!!! citation needed].
+The primary benefit of using the DBPedia for this purpose is
+that not only does it supply a categorical heterarchy, but it
+also links to wikipedia documents which provides us with a large
+realm-specific document corpus.
+
+To support our process, we map DBPedia categories into classes in our
+realm ontology with the superclass/subclass relationships built using
+DBPedia properties broader/narrower.  By using OWL, we can exploit the
+OWL API for matching SSQ ontologies that reference these realm
+ontologies.
 
@@
 
-\subsection{Associating Terms with Categories} %joir-dan The
-subcategories of the category Automobiles (… Driving, Traffic Law,
+\subsection{Associating Terms with Categories}
+%joir-dan
+
+Once the semantic hierarchy is created, the next step is to create
+training data for the system. The task is then to grab the pages,
+build a corpus relating to a given category, and then compile the
+information in a meaningful way. The overall goal is to grab enough
+information to properly characterize a category while limiting the
+amount of unnecessary content within the corpus. The problem with this
+approach is the page density varies greatly across the
+heterarchy. Each category within the DBpedia/ Wikipedia heterarchy
+contains a set of information pages, P, that correspond to concepts
+that share said category. Considering that the categorical structure
+is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the
+use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing
+a particular category. The category's that The assumption is that a
+node can be fully described by its ancestor, descendant, and spousal
+nodes (parent node of subcategory not equal to the category). While
+this does not completely solve the issue of a category residing in a
+sparse area of the graph, the amount of information that can be
+obtained per blanket is usually more helpful than per category.
+
+The subcategories of the category Automobiles (… Driving, Traffic Law,
 Automobiles by Decade, Auto Racing…) can be seen as grabbing

### 2010-03-04 trunk/paper/semsearch10/content/query_reexecution.tex
fourth round of changes by jnw

\subsection{Query Re-execution}
% Chris
When a user submits a new query to the Morpheus system, one or more
stored Query Resolution Methods are executed to obtain results. A QRM
contains an XML script that represents an algorithm that will obtain
the required result.  The evaluation of this script by the QRE
simulates the behavior of a human browsing the web, that is, clicking
buttons to follow links, submitting forms, highlighting and cutting
and pasting text, and constructing an answer in the form of a text
string.

At present, the GET form submission method is used.  There is greater
complexity in dealing with web forms than with links. For a given
form, there may be text fields, drop-down boxes, radio buttons etc.
To support form submission in such circumstances the QRE takes
different actions based on the input type. For text fields, simply
adding a key/value pair to the querystring suffices. For a drop-down
box, the QRE extracts the form element find the appropriate value to
include in the querystring.

All input data as well as data highlighted during the evaluation are
kept in an internal table. The QRM script contains keys that allow the
QRE to map SSQ inputs from the table to the appropriate form
inputs. Furthermore, highlighted text segments collected during
execution of the script are stored in the table.  Once all actions in
the script have been carried out, the QRE returns textual answer this
process has created. This answer can then be rendered in a
browser.

### 2010-03-04 paper/semsearch10/content/ontological_realms.tex
After Dr. Wilson's improvements

@@
-\subsection{Class Heterarchy} 
-% Author: Clint 
-Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies.
-The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it.
-We cannot find any robust existing ontology library of that nature for this purpose.
-So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used.
-Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed].
-The OWL ontology [citation needed] format is followed in this process.
-The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed].
-Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.
+\section{Representing and Ontological Realms}
+Two types of ontologies are used by our system:
+\begin{enumerate}
+\item Realm ontologies, comprising a heterarchy of categories that
+  characterize terms that can appear in queries.
+\item SSQ ontologies, used to describe the form of particular
+  realm-specific queries.
+\end{enumerate}
+For any particular ontological realm, the number of potential
+terms and their associated categories can be quite large.
+Construction of a realm ontology and the terms associated
+with its categories would be an extremely laborious task
+for any non-trivial realm. The realm of automobiles (which
+we use for illustration in this paper) contains, for example,
+over XXXX categories and XXXX terms. We were unable to find
+an appropriate ontology for this realm, so we constructed it
+using categories from the DBPedia [!!!! citation needed].
+The primary benefit of using the DBPedia for this purpose is
+that not only does it supply a categorical heterarchy, but it
+also links to wikipedia documents which provides us with a large
+realm-specific document corpus.
+\subsection{Category Heterarchy}
 
-%-------------------------------------------------------------------------------
+To support our process, we map DBPedia categories into classes in our
+realm ontology with the superclass/subclass relationships built using
+DBPedia properties broader/narrower.  By using OWL, we can exploit the
+OWL API for matching SSQ ontologies that reference these realm
+ontologies.
+
+%Start with a collection of relevant categories
+
+Once the semantic hierarchy is created, the next step is to create
+training data for the system. The task is then to grab the pages,
+build a corpus relating to a given category, and then compile the
+information in a meaningful way. The overall goal is to grab enough
+information to properly characterize a category while limiting the
+amount of unnecessary content within the corpus. The problem with this
+approach is the page density varies greatly across the
+heterarchy. Each category within the DBpedia/ Wikipedia heterarchy
+contains a set of information pages, P, that correspond to concepts
+that share said category. Considering that the categorical structure
+is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the
+use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing
+a particular category. The category's that The assumption is that a
+node can be fully described by its ancestor, descendant, and spousal
+nodes (parent node of subcategory not equal to the category). While
+this does not completely solve the issue of a category residing in a
+sparse area of the graph, the amount of information that can be
+obtained per blanket is usually more helpful than per category.
+
+The subcategories of the category Automobiles (… Driving, Traffic Law,
+Automobiles by Decade, Auto Racing…) can be seen as grabbing
+information specific to the category. The supercategories (Road
+Vehicles) place the category in a higher perspective, abstractly
+describing basketball as a concept. The spousal categories
+(...Motorsport, Individual Sport...) are an abstract description of
+the subcategories.
+
+Clustering the categories alone does not guarantee adequate corpus
+creation. Since the above model relies on the subcategories to
+describe specifics of a given category, the ideal situation would be
+that the subcategories have many more pages than the supercategories
+and that there is a significant amount of information per page.  In
+the case of Wikipedia, there are an average of 25.7 pages per category
+\cite{1321474}. The assumption for collecting the training data is the
+more subcategory data we have, the more detailed our description of
+our category. Considering that there are many categories that have
+much more than 26 pages, we instituted a PlusOne mechanism to extract
+extra information. This mechanism checks if a subcategory has an
+adequate number of pages α to fully describe its subtopic. We set this
+number to ten times the average, or 260. $Level$ represents how many
+extra levels we are to go down in the hierarchy, if
+necessary. SubjectSet is the overall set of all pages associated with
+the blanket structure along with any plusOne subjects obtained.
+
+\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=BlanketSubjectRetreival,label=BlanketSubjectRetreival,basicstyle=\small]
+def BlanketSubjectRetreival(blanket, maxLevel):
+	for category in blanket:
+		subjectSet.add(grabsubjects(category))
+		diff = afterSize - beforeSize
+		if diff <= a and category is subcategory:
+			PlusOneMechanism(category, maxLevel)
+	return subjectSet
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism,basicstyle=\small]
+def PlusOneMechanism(category, level):
+	plusOneSet = grabPlusOneSubcategories(category)
+	for subcategory in plusOneSet:
+		subject.add(grabSubjects(subcategory))
+		diff = afterSize - beforeSize
+		if diff <= a and level > 0:
+			PlusOneMechanism(subcategory, level-1)
+
+\end{lstlisting}
 
@@
 
-Building Ontological Realms
+The overall mechanism does not take into account the amount of
+information within each page, but generally that can be ignored when
+considering the size of the blanket corpus when we extract the text
+from the Wikipedia subject pages. Using this method on the category
+Automobiles, we can construct a corpus of 2255 subject pages and
+6,084,260 terms.
 
-Once the semantic hierarchy is created, the next step is to create training data for the system.
-The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way.
-The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus.
-The problem with this approach is the page density varies greatly across the heterarchy.
-Each category within the DBpedia/Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category.
-Considering that the categorical structure is a directed acyclic graph  \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category.
-The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category).
-While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.
-
-Consider the abbreviated Markov blanket for the category Automobiles:
-
-% figure: abbreviated Markov blanket for the category Basketball  
-\begin{figure}[t]
-\centering
-\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
-\caption{Abbreviated Markov blanket for the category Basketball}
-\label{fig:abbrv_bb_blanket}
-\end{figure}
-
-The subcategories of the category Automobiles (… Driving, Traffic Law, Automobiles by Decade, Auto Racing…) can be seen as grabbing information specific to the category.
-The supercategories (Road Vehicles) place the category in a higher perspective, abstractly describing basketball as a concept.
-The spousal categories (...Motorsport, Individual Sport...) are an abstract description of the subcategories.
-
-Clustering the categories alone does not guarantee adequate corpus creation.
-Since the above model relies on the subcategories to describe specifics of a given category, the ideal situation would be that the subcategories have many more pages than the supercategories and that there is a significant amount of information per page.
-In the case of Wikipedia, there are an average of 25.7 pages per category \cite{1321474}.
-The assumption for collecting the training data is the more subcategory data we have, the more detailed our description of our category.
-Considering that there are many categories that have much more than 26 pages, we instituted a PlusOne mechanism to extract extra information.
-This mechanism checks if a subcategory has an adequate number of pages α to fully describe its subtopic.
-We set this number to ten times the average, or 260.
-$Level$ represents how many extra levels we are to go down in the hierarchy, if necessary.
-SubjectSet is the overall set of all pages associated with the blanket structure along with any plusOne subjects obtained.
-
-\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival]
-def BlanketSubjectRetreival(blanket, maxLevel):
-	for category in blanket:
-		subjectSet.add(grabsubjects(category))
-		diff = afterSize - beforeSize
-		if diff <= \alpha and category is subcategory:
-			PlusOneMechanism(category, maxLevel)
-	return subjectSet
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism]
-def PlusOneMechanism(category, level):
-	plusOneSet = grabPlusOneSubcategories(category)
-	for subcategory in plusOneSet:
-		subject.add(grabSubjects
-
-\end{lstlisting}
-
-The overall mechanism does not take into account the amount of information within each page, but generally that can be ignored when considering the size of the blanket corpus when we extract the text from the Wikipedia subject pages.
-Using this method on the category Automobiles, we can construct a corpus of 2255 subject pages and 6,084,260 terms.
-
-When a category's corpus is built, we then build our n-gram frequency distributions and store them in a database for the NLP processing.
-For the purpose of calculating term importance to a blanket, we aggregate the frequencies of all blankets and store this information as well.
-For this system, term importance refers to the prior probability of a category given an n-gram.
-We calculate this using Bayes Rule, since we can easily obtain the n-gram-category and n-gram-vocabulary probabilities.
-The higher the probability, the more likely a term is referring to a category.
+When a category's corpus is built, we then build our n-gram frequency
+distributions and store them in a database for the NLP processing. For
+the purpose of calculating term importance to a blanket, we aggregate
+the frequencies of all blankets and store this information as
+well. For this system, term importance refers to the prior probability
+of a category given an n-gram. We calculate this using Bayes Rule,
+since we can easily obtain the n-gram-category and n-gram-vocabulary
+probabilities. The higher the probability, the more likely a term is
+referring to a category.
 

### 2010-03-04 paper/semsearch10/content/results_futurework_conclusion.tex
After Dr. Wilson's improvements

\section{Results}
% Walk through of example query

\section{Future Work}

Currently, the category hierarchy that is generated from the DBpedia categories and our SSQ ontologies are stored in separate XML files. We are in the process of storing these ontologies into an efficient ontology database. Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store. We are working on merging the similar SSQs [\label{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.

In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belongs to all the realms. [e.g. musical bands]. We are planning to define new categories from the deep web [or find out new sources to fill those \textit{weak} realms] in our ontology hierarchy.

- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.  We plan to investigate this.

% Sort classes based on the prior

\section{Conclusion}

\section{Acknowledgements}

### 2010-03-04 paper/semsearch10/content/ssq_ranking.tex
After Dr. Wilson's improvements

@@
-\subsection{SSQ Ranking}
+\section{SSQ Ranking}
 \label{sec:ssq}
@@
 function type matches. We consider the realm class and context
-property ranges for determining SSQ similarity. Subsections
-\ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
+property ranges for determining SSQ similarity.
+Once we have the similarity measures between the user defined SSQ and relevant QRMs in the store, we can order the relevant QRMs.
+The order provides a ranking for the results to the user.
+Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
 
@@
 
-% Need to show an example ?
-
 %-------------------------------------------------------------------------------

### 2010-03-04 trunk/paper/semsearch10/content/ssq_ranking.tex

@@
-\subsection{SSQ Ranking}
-In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs.
-These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs.
-The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}.
-The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store.
-During \textit{off-line execution}, the system clusters similar SSQs.
+\section{SSQ Ranking}
+\label{sec:ssq}
+In order to match a new query with a SSQ within our data store, we
+have defined similarity measures between the ontologies of the new
+query and the candidate SSQs. These measures capture the distance
+between the ontology classes, properties, and individuals at the
+conceptual level in addition to simply matching URIs. The similarity
+measures are implemented in two scenarios: \textit{on-line execution}
+and \textit{off-line mode}. The \textit{on-line execution} is time
+sensitive and is used primarily for relating newly defined SSQs to the
+SSQs in the store. During \textit{off-line execution}, the system
+clusters similar SSQs.
 
-The similarity measure for the SSQ ontologies is determined by the following components.
+The similarity measure for the SSQ ontologies is determined by the
+following components.
 \begin{enumerate}
-    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
-    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
-    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
-    \item SSQClass: an OWL class which is created from the components described above.
+    \item QueryClass: an OWL class and the root of the SSQ ontology
+      structure.
+    \item hasRealm: an OWL object property with its domain as the SSQ
+      Query class and its range as a realm class.
+    \item Contexts such as who, what, when, and where are OWL object
+      properties, whose domains are the query classes and ranges are
+      OWL classes.
+    \item SSQClass: an OWL class which is created from the components
+      described above.
 \end{enumerate}
-Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies.
-It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic function type matches.
-We consider the realm class and context property ranges for determining SSQ similarity.
+Based on this ontology structure and the execution scenarios, we have
+created an algorithm for finding the matches between SSQ
+ontologies. It is based on class divergence, which is motivated by the
+concept of multiple dispatch in CLOS \cite{95411} and Dylan
+programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic
+function type matches. We consider the realm class and context
+property ranges for determining SSQ similarity.
+Once we have the similarity measures between the user defined SSQ and relevant QRMs in the store, we can order the relevant QRMs.
+The order provides a ranking for the results to the user.
 Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.
 
-\subsubsection{Class Divergence}
+\subsection{Class Divergence}
 \label{sec:ctd}
-We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology.
-We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
-Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).
-Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:
+We employ a measure of compatibility, which we call \textit{class
+  divergence}, between a source class and a target class using the
+\textit{topological structure} of the context classes in the
+ontology. We write $S \prec T$ for the reflexive transitive closure of
+the superclass relation. Let $d(P,Q)$ represent the hop distance in
+the directed ontology inheritance graph from $P$ to $Q$. The
+divergence between a source and target class ranges from zero (for
+identical classes) to one (for incompatible classes).  Let $S$ be the
+source class, $T$ be the target class, and let $C$ be a common
+ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class
+divergence between $S$ and $T$, the unnormalized class dissimilarity,
+is defined as follows:
 
@@
 
-Figure \ref{fig:class_divergence} illustrates the calculation of class divergence.
-This sample abbreviated ontology that was created from the DBpedia category heirarchy is rooted at the class \textit{DBpediaRoot}.
-The arrows represent the inheritance relationship between the classes in the topology.
+Figure \ref{fig:class_divergence} illustrates the calculation of class
+divergence. This sample abbreviated ontology that was created from the
+DBpedia category heirarchy is rooted at the class
+\textit{DBpediaRoot}. The arrows represent the inheritance
+relationship between the classes in the topology.
 
-Suppose we want to find the divergence $d_{class}$\textit{(Automotive Industry, Racing Cars)}.
-The \textit{Automotive Industry} is the subclass of \textit{Automobiles} and \textit{Racing Cars} is the subclass of \textit{Auto Racinng}.
-Therefore, the common ancestor for these two can be determined as \textit{Automobiles} ($C$).
-They share the path from \textit{Automobiles} to the $root$.
-So, the unnormalized divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from the path to root), \textit{d(Automotive Industry, Automobiles)} is one (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two (dashed arrow).
-Suppose, the ontology tree height is calculated as 294.
-Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
+Suppose we want to find the divergence $d_{class}$\textit{(Automotive
+  Industry, Racing Cars)}. The \textit{Automotive Industry} is the
+subclass of \textit{Automobiles} and \textit{Racing Cars} is the
+subclass of \textit{Auto Racinng}. Therefore, the common ancestor for
+these two can be determined as \textit{Automobiles} ($C$). They share
+the path from \textit{Automobiles} to the $root$. So, the unnormalized
+divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from
+the path to root), \textit{d(Automotive Industry, Automobiles)} is one
+(dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two
+(dashed arrow). Suppose, the ontology tree height is calculated as
+294. Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which
+corresponds to a normalized value of $35/294$.
 
 %-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
+\subsection{SSQ Ontology Matching}
 \label{sec:oqom}
 
-We use class divergence to calculate the relevance between a source SSQ and a target SSQ associated with a QRM.
-Each SSQ will have four input classes, four output classes, and one realm.
-We refer to the sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4, \Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ.
-If an input or output class is unspecified in the query, it is associated with the class $bottom$, which has no subclasses or individuals.
+We use class divergence to calculate the relevance between a source
+SSQ and a target SSQ associated with a QRM.  Each SSQ will have four
+input classes, four output classes, and one realm.  We refer to the
+sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4,
+\Omega_1, ..., \Omega_4, R \rangle$ as the signature of an SSQ. If an
+input or output class is unspecified in the query, it is associated
+with the class $bottom$, which has no subclasses or individuals.
 
-The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ..., \Upsilon_{Q_4}, \\\Omega_{Q_1}, ...
-, \Omega_{Q_4}, R_Q\rangle$ to SSQ $S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4}, \\\Omega_{S_1}, ...
-, \Omega_{S_4}, R_S \rangle$ is
+The relevance of QRM $Q$ with signature $\langle \Upsilon_{Q_1}, ...,
+\Upsilon_{Q_4}, \\\Omega_{Q_1}, ... , \Omega_{Q_4}, R_Q\rangle$ to SSQ
+$S$ with signature $\langle \Upsilon_{S_1}, ..., \Upsilon_{S_4},
+\\\Omega_{S_1}, ... , \Omega_{S_4}, R_S \rangle$ is
 
@@
 
-If an SSQ and a QRM have identical classes for all inputs and their realms then the QRM relevance value will be one. Otherwise, the relevance of the QRM will be in the range $[0, 1)$.
-
-% Need to show an example ?
+If an SSQ and a QRM have identical classes for all inputs and their
+realms then the QRM relevance value will be one. Otherwise, the
+relevance of the QRM will be in the range $[0, 1)$.
 

### 2010-03-04 paper/semsearch10/content/abstract.tex
latest version all of jnw & pete 1st changes made

@@
 \begin{abstract}
-- It is difficult to answer question that change over time
+- It is difficult to answer questions that change over time
 - However, if the method of answering the question can be realized, the question can be easily answered

### 2010-03-04 paper/semsearch10/content/example.tex
latest version all of jnw & pete 1st changes made

@@
 
-The end-user employs the Morpheus question-answering system much like a
-search engine with a natural-language interface. One can type a question
-in a text box and receive a response from the system. Those questions
-dealing with an ontological realm familiar to the system, whose form is
-similar to previously answered queries in that realm, and that can be
-answered using (possibly deep web) information from a source the system
-has encountered can yield relevant responses.
+The end-user employs the Morpheus question-answering system much like a search engine with a natural-language interface.
+One can type a question in a text box and receive a response from the system.
+The system uses previously answered queries to answer new questions.
+The reused questions have have a similar form, and the same ontological realm, and employ sources that will yield relevant solutions.
+We focus our on the sources that are hidden behind web forms, or the \emph{deep web}.
 
@@
 interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
-received a response together with information describing assumptions
+received a response data.  Included with the response is together with information describing assumptions
 about the question, the likely relevance of the answer provided,
@@
   method} (QRM). A QRM is constructed when a special user, known as a
-\emph{guide} answers a question using an instrumented web browser (the
+\emph{guide}, answers a question using an instrumented web browser (the
 \emph{query response recorder} or QRR) that records web
@@
 by a \emph{semi-structured query} (SSQ), a schematic representation of
-the information contained in the query, namely the inputs and output
+the information contained in the query, namely the input and output
 contexts---the \emph{who, what, when,} and \emph{where}
-categories---that characterize the question together with an
+categories---that characterize the question.  In addition the QRR has categorized an
 appropriately generalized representation of the guide's browser

### 2010-03-04 trunk/paper/semsearch10/content/introduction.tex
latest version all of jnw & pete 1st changes made

@@
 % Christan
-When traveling though a jungle to a destination, it is easy to get
-lost.  The first person to take blaze a trail may make a number of
-mistakes in trying to find the best path to any destination.  However,
-those who come later can easily follow a well-marked trail without the
-level of effort required by the path-finder. Olsen and Malizia
-describe this idea as \emph{exploiting trails} \cite{5379671}.  The
-Morpheus Question Answering System uses this insight to improve the
-efficency of retrieval in semantic search.
-
-Rather than treating each user's search as a unique entity and working
-from first principles, we exploit the fact that a similar search may
-have been performed already.
-Researchers have shown that almost 40 percent of the all
-queries are repetitions of previous queries.\cite{1277770}
-This points to an  area for optimization for search engines.
-We have built a prototype system for answering questions using deep-web sources
-that employs previously answered questions to obtain new answers.
+When traveling though a jungle to a destination, it is easy to get lost.
+The first person to go somewhere may make a number of mistakes in trying to find the best path to their destination.
+However, those who come later will find it easy to reach that destination if a well-marked trail has been created.
+Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
+Rather than treating a user's search as a unique entity and working without an example context, one can exploit the fact that a similar search may have been performed already.
+In one study, almost 40 percent of all queries were found to be repetitions of previous queries\cite{1277770}.
+This indicates the reuse of prior searches is a way to optimize the search process.
+We have built a prototype system for answering questions using deep-web sources that employs previously answered questions to obtain new answers.
+Using our analogy, the Morpheus question answering system follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

### 2010-03-04 paper/semsearch10/content/ssq_ranking.tex
Modifications for the class divergence example

@@
 clusters similar SSQs.
-
+% Move to QRR or make a reference  
 The similarity measure for the SSQ ontologies is determined by the
@@
 
-\subsubsection{Class Divergence}
+\subsection{Class Divergence}
 \label{sec:ctd}
@@
 d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
+0 & if S.{Uri} \equiv T.{Uri}\\
 d(S, T) & if S \prec T\\
@@
 \includegraphics[width=90mm]{class_divergence.eps}
-\caption{Abbrv. graphical representation of an automotive ontology}
+\caption{Abbrev. graphical representation of an automotive ontology}
 \label{fig:class_divergence}
@@
 divergence. This sample abbreviated ontology that was created from the
-DBpedia category heirarchy is rooted at the class
+DBpedia category hierarchy is rooted at the class
 \textit{DBpediaRoot}. The arrows represent the inheritance
@@
 subclass of \textit{Automobiles} and \textit{Racing Cars} is the
-subclass of \textit{Auto Racinng}. Therefore, the common ancestor for
+subclass of \textit{Auto Racing}, which is a subclass of \textit{Automobiles}. Therefore, the common ancestor for
 these two can be determined as \textit{Automobiles} ($C$). They share
 the path from \textit{Automobiles} to the $root$. So, the unnormalized
-divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from
-the path to root), \textit{d(Automotive Industry, Automobiles)} is one
+divergence \textit{d(Automotive Industry, root)} is 32 that is calculated from the path to the root \textit{DBpediaRoot}, \textit{d(Automotive Industry, Automobiles)} is one
 (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two
 (dashed arrow). Suppose, the ontology tree height is calculated as
-294. Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which
-corresponds to a normalized value of $35/294$.
+294. Thus, $d_{class}$\textit{(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
 
 %-------------------------------------------------------------------------------
-\subsubsection{SSQ Ontology Matching}
+\subsection{SSQ Ontology Matching}
 \label{sec:oqom}
 
-We use class divergence to calculate the relevance between a source
-SSQ and a target SSQ associated with a QRM.  Each SSQ will have four
-input classes, four output classes, and one realm.  We refer to the
+We use class divergence to calculate the relevance between a new 
+SSQ and a SSQ associated with a QRM in the store.  Each SSQ will have four input classes, four output classes, and one realm.  We refer to the
 sequence of these classes $\langle \Upsilon_1, ..., \Upsilon_4,
@@
 \\\Omega_{S_1}, ... , \Omega_{S_4}, R_S \rangle$ is
-
 \begin{eqnarray}
@@
 \begin{eqnarray}
-d_{R} = \pi_9 d_{class}(R_S,R_Q) \nonumber
+d_{R} = \pi_9 d_{class}(R_S,R_Q) 
 \end{eqnarray}
 \begin{eqnarray}
-d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} \nonumber
+d_{\Upsilon}  = \sum_{k=1}^4 {\pi_k} {d_{class}(\Upsilon_{S_k},\Upsilon_{Q_k})} 
 \end{eqnarray}
 \begin{eqnarray}
- d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j})  \nonumber
+ d_{\Omega} = \sum_{j=1}^4 \pi_{4+j} d_{class}(\Omega_{S_j},\Omega_{Q_j}) 
 \end{eqnarray}
-\noindent the weights ${\pi}_k$ of the property hasRealm and other context properties satisfies the conditions 
+\noindent the weights ${\pi}_i$ of the property hasRealm and other context properties satisfies the conditions
 \begin{equation}
 \label{piconstraint1}
-\sum_{k=1}^{9} {{\pi}_k} = 1
+\sum_{i=1}^{9} {{\pi}_i} = 1
 \end{equation}
-\noindent and for $1 \leq i \leq 9$
-
 \begin{equation}
@@
 \end{equation}
+\noindent and for $1 \leq i \leq 9$
 

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
Added a citation for DBpedia to the section ontological realms

@@
 \section{Representing and Ontological Realms}
-\subsection{Category Heterarchy} 
-% Author: Clint 
 Two types of ontologies are used by our system:
@@
 an appropriate ontology for this realm, so we constructed it
-using categories from the DBPedia [!!!! citation needed].
+using categories from the DBPedia \cite{Auer07dbpedia:a}.
 The primary benefit of using the DBPedia for this purpose is
 that not only does it supply a categorical heterarchy, but it
-also links to wikipedia documents which provides us with a large
+also links to Wikipedia documents which provides us with a large
 realm-specific document corpus.
 
-To support our process, we map DBPedia categories into classes in our
-realm ontology with the superclass/subclass relationships built using
-DBPedia properties broader/narrower.  By using OWL, we can exploit the
-OWL API for matching SSQ ontologies that reference these realm
-ontologies.
+\subsection{Category Heterarchy}
 
-%-------------------------------------------------------------------------------
+To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass/subclass} relationships built using DBPedia properties \textit{broader/narrower}.
+By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.
 
-\subsection{Associating Terms with Categories}
-%joir-dan
+%Start with a collection of relevant categories
 
@@
 The subcategories of the category Automobiles (… Driving, Traffic Law,
-Automobiles by Decade, Auto Racing…) can be seen as grabbing
-information specific to the category. The supercategories (Road
+Automobiles by Decade, Auto Racing …) can be seen as grabbing
+information specific to the category. The super categories (Road
 Vehicles) place the category in a higher perspective, abstractly
 describing basketball as a concept. The spousal categories
-(...Motorsport, Individual Sport...) are an abstract description of
+(...Motor Sport, Individual Sport...) are an abstract description of
 the subcategories.
@@
 describe specifics of a given category, the ideal situation would be
-that the subcategories have many more pages than the supercategories
+that the subcategories have many more pages than the super categories
 and that there is a significant amount of information per page.  In
@@
 
-\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=BlanketSubjectRetreival,label=BlanketSubjectRetreival,basicstyle=\small]
+\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival, basicstyle=\small]
 def BlanketSubjectRetreival(blanket, maxLevel):
@@
 
-\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism,basicstyle=\small]
+\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=PlusOneMechanism, label=PlusOneMechanism, basicstyle=\small]
 def PlusOneMechanism(category, level):
@@
 \end{lstlisting}
+
+\subsection{Associating Terms with Categories}
+%joir-dan
 

### 2010-03-04 paper/semsearch10/content/qrr.tex
Fixing description of qrr

--- 2010-03-04 trunk/paper/semsearch10/content/qrr.tex
@@
 Answering a question using the deep web requires one to navigate
-through a sequence of one or more web pages and links.  Many of the
-accesses involve clicks through web forms to resulting pages.  We have
-developed a model that represents the various actions a user may carry
-out during this process.
+through a sequence of one or more web pages.
+Many of the accesses involve clicks through web forms or links to resulting pages.
+We have developed a model that represents the various actions a user may carry out during this process.
 
-During the answer retrieval process, a user discovers an element of
-the query's result on a web page.  Next, she highlights that element,
-typically a text string.  This highlight allows the QRR to record the
-source of the query's answer.  The QRR stores all information from the
-user query in our data store.  When the user submits a web form she
-may associate each of the form's inputs with one of our stored context
-classes.
-
-The discovery process can be broken down into three cases:
+Web interactions can be broken down into three types:
 \begin{enumerate}
-\item The user typed in a URL and highlighted part of or all the
-  answer.
-\item The user typed in a URL, clicked a link, and found part or all
-  of the answer.
-\item The user typed in a URL, filled out a form, and found part or
-  all of the answer on a subsequent page.
+\item The user highlights text that is needed in the query or forms part of the answer.
+\item The user clicks a link.
+\item The user fills in and submits a web form. 
 \end{enumerate}
 
-Any discovery process consists of a sequence of these transactions.
+When a user submits a web form they are prompted for the classes of each of the form inputs.
+Here, class refers to categorization of data, e.g.
+name, date, etc.
+These classes allow the QRR to map the user's input SSQ tokens (which are also categorized) to their usage in a given form.
+For a clicked link, the QRR simply records the target url and nothing more.
+Finally, during the answer retrieval process when a user discovers all or part of the desired information on a web page, she highlights the text in question.
+This highlight allows the QRR to record the source of the query's answer.
+All information gathered during the recording process is saved in our data store.
+
+Any query answering process consists of a sequence of these transactions.
 Additionally, data collected for inputs and outputs may be found
-during any stage of the complete discovery process.  An output
+during any stage of the complete query process.  An output
 collected during one stage of an extraction may be the input to a
 subsequent stage in the extraction. The QRR builds the completed user
-collection process into a QRM.  The following is a mathematical
-formulation of information collected for user web interactions.
+collection process into a Query Resolution Method (QRM).  The following is a mathematical formulation of information collected for user web interactions.
 

### 2010-03-04 paper/semsearch10/content/qrr.tex
merged chris's changes

@@
 subsequent stage in the extraction.  The QRR builds the completed user
-collection process into a Query Resolution Method (QRM).  The following is a mathematical formulation of information collected for user web interactions.
+collection process into a QRM.
+
+Conceptually, a QRM is the data structure that models the question answering process.
+All QRMs are associated with a SSQ set of possible input categories and also output catgories.
+It contains representations for every page visited and the order of visitation.
+For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlight portions of the webpage).
+
+The ontologcal representation of the SSQ is described in section {{XXX}}.  The following is a mathematical description of the information collected for user web interactions.
 
@@
 \begin{enumerate}
-
+%%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------
 \item $\Upsilon$ is the sequence of input categories $\left<

### 2010-03-04 paper/semsearch10/content/example.tex
general editing

@@
 The system uses previously answered queries to answer new questions.
-The reused questions have have a similar form, and the same ontological realm, and employ sources that will yield relevant solutions.
-We focus our on the sources that are hidden behind web forms, or the \emph{deep web}.
+The reused questions have a similar form and the same ontological realm, and employ sources that will yield relevant solutions.
+We focus our reuse on the sources that are hidden behind web forms, or the \emph{deep web}.
 
@@
 interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
-received a response data.  Included with the response is together with information describing assumptions
-about the question, the likely relevance of the answer provided,
+received the result data.  Included with the result is information describing assumptions about the question, the likely relevance of the answer provided,
 the source of information, and the method of answer production.
@@
 contexts---the \emph{who, what, when,} and \emph{where}
-categories---that characterize the question.  In addition the QRR has categorized an
-appropriately generalized representation of the guide's browser
+categories---that characterize the question.  In addition, the QRR has categorized a generalized representation of the guide's browser
 interactions.  The \emph{query response evaluator} (QRE) evaluates a
@@
 categories associated with the terms in the question to form an SSQ,
-find those QRMs having contextually compatible SSQs, then use the QRE to
+find those QRMs having contextually compatible SSQs, and then use the QRE to
 generate a response.
@@
 In what follows, we detail the elements of the system.  We first
-discuss the processing of natural language queries to generate SSQs.
+discuss how the processing of natural language queries generates SSQs.
 Next, we discuss the recording of guide behavior with the QRR.  We
@@
 describe the method we use to assess how well a stored QRM matches a
-user SSQ.  We then discuss the QRM evaluation process and discuss the
-system's behavior on example queries. We conclude with a discussion of
+user SSQ.  We then discuss the QRM evaluation process and the
+system's behavior for example queries. We conclude with a discussion of
 future work.

### 2010-03-05 paper/semsearch10/content/nlp.tex
general editing

% Joir-dan stuff

When we have completed our Wikipedia corpora from all the blankets in the category hierarchy, our system needs to make sense of the data for execution. The learning process involves the calculation of two n-gram frequency distributions: an n-gram/vocabulary distribution and an n-gram/category distribution. The first value is the count of the individual n-grams in the combined vocabulary of all corpora. The second value is the count of the individual n-grams within a category's blanket. The categories corpora reflect one long context per category, instead of breaking up sentences into different contexts. The idea behind this is that Wikipedia pages are already grouped into categories, that we can assume are related to the topics of each sentence within the corpus. We store distributions, rather than priors, primarily because if at anytime a blanket vocabulary seems inadequate, we can append terms from other sources to both distribution types and recalculate our values. We can simply calculate probabilities and store these separately for the execution of our natural language query engine.

Our goal is to choose that category for use in the SSQ structure. This process requires the tagging and parsing of our natural language query, the extraction of key parts of speech, such as adjectives and nouns, and then using n-gram priors to calculate the appropriate category associated with each term.

Picking out these terms requires knowledge of the structure of the queThe ideal situation would be that we could recognize question patterns, and decide where key information is within the question based upon a given pattern.stion being passed to the system.  Currently, we only work with questions in an answer form, which means there is little to no transformation of the structure, to go from a question to an answer.

Consider the example question: "A 1997 Toyota Corolla needs what size tires?" The answer is: "A 1997 Toyota Corolla needs 17 inch tires."

### 2010-03-05 paper/semsearch10/content/example.tex
edited the qrr

@@
 by a \emph{semi-structured query} (SSQ), a schematic representation of
-the information contained in the query, namely the input and output
+the information contained in the natural language question, namely the input and output
 contexts---the \emph{who, what, when,} and \emph{where}

### 2010-03-05 paper/semsearch10/content/qrr.tex
edited the qrr

@@
 Conceptually, a QRM is the data structure that models the question answering process.
-All QRMs are associated with a SSQ set of possible input categories and also output catgories.
-It contains representations for every page visited and the order of visitation.
+Each QRMs contains an ontilogical realm, an SSQ, and information to support the query answering process.
+The realm may be one or more descriptive categories and is used for is used for classification of the QRMs.
+The SSQ describes the set of possible input categories and also output catgories from the associated natural language query.
+The possible set of input phrase inputs and outputs are grouped in to contextual bins labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.
+The ontilogical realm and the SSQ parameters act as a signature for the the QRM object, analogous to a function signature.
+The ontologcal representation of the SSQ is described in section {{XXX}}.
+
+Additionally, the QRM contains representations for every page visited and the order of visitation.
 For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlight portions of the webpage).
+There is a mapping between the SSQ the possible inputs user inputs or outputs used on any page to the specific page input.
+Finally, there is a structure with mappings to the user inputs or outputs that are displayed to the user as answers.
 
-The ontologcal representation of the SSQ is described in section {{XXX}}.  The following is a mathematical description of the information collected for user web interactions.
+The following is a mathematical description of the information collected for user web interactions.
 
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
+A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ \footnote{It is important to not that both $\Upsilon$ and $\Omega$ make up the SSQ structure.} such that:
 

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
results future work and stuff

@@
 \section{Future Work}
+
+The largest limitation to our current work is the the QRR.
+In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.
+However, a significant amount user interaction is required to understand the answer retrieval process.
+By continuing to studying the methods of user data collection we plan to develop a model to support a unsupervised question resolution process.
+This will increase the scalability and efficiency of the system.
+
+Because each QRM may be treated as a function, we plan on leveraging previous work to allow new questions to be solved by connecting together several QRMs \cite{morpheus1, transformscout}.
+This method would expand the types of queries that are answerable be the system.
 
@@
 
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
+Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
+We believe that an even higher number of those are parametrizable, meaning, a set of queries are all related and may be answered using a single QRM.
+It is difficult to discover this property.
+Previous work suggest techniques to find related queries but it will take a new method to discover parametrizable queries.
 
@@
 
+In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.
+We described our method of modelling a users question answering process and how we are able to discover semantically similar queries.
+
+MORE
+
 \section{Acknowledgements}

### 2010-03-05 paper/semsearch10/content/qrr.tex
general editing

--- 2010-03-04 paper/semsearch10/content/qrr.tex
@@
 \begin{enumerate}
+\item The user fills in and submits a web form.
+\item The user clicks a link.
 \item The user highlights text that is needed in the query or forms part of the answer. 
-\item The user clicks a link.
-\item The user fills in and submits a web form. 
 \end{enumerate}
 
-When a user submits a web form they are prompted for the classes of each of the form inputs.
+When a users submit a web form they are prompted for the classes of each of the form inputs.
 Here, class refers to categorization of data, e.g.
@@
 Conceptually, a QRM is the data structure that models the question answering process.
-All QRMs are associated with a SSQ set of possible input categories and also output catgories.
-It contains representations for every page visited and the order of visitation.
-For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlight portions of the webpage).
+Each QRM contains an ontilogical realm, an SSQ, and information to support the query answering process.
+The realm may be one or more descriptive categories and is used for classification of the QRMs.
+The SSQ describes the set of possible input and output categories from the associated natural language query.
+The possible set of phrase inputs and outputs are grouped into contextual bins labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.
+The ontilogical realm and the SSQ parameters act as a signature for the QRM object, analogous to a function signature.
+The ontological representation of the SSQ is described in section {{XXX}}.
 
-The ontologcal representation of the SSQ is described in section {{XXX}}.  The following is a mathematical description of the information collected for user web interactions.
+Additionally, the QRM contains representations for every page visited and the order of visitation.
+For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlighted portions of the webpage).
+There is a mapping between the SSQ inputs and outputs used on any page to the specific page input.
+Finally, there is a structure with mappings to the user inputs or outputs that are displayed to the user as answers.
 
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
+The following is a mathematical description of the information collected for user web interactions.
+
+A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ \footnote{It is important to not that both $\Upsilon$ and $\Omega$ make up the SSQ structure.} such that:
 

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
Some corrections in future work sections

@@
 
-The largest limitation to our current work is the the QRR.
+The largest limitation to our current work is the QRR.
 In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.
@@
 Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store.
-We are working on merging the similar SSQs [\label{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.
+We are working on merging the similar SSQs [\ref{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.
 
@@
 Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parametrizable, meaning, a set of queries are all related and may be answered using a single QRM.
+We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
 It is difficult to discover this property.
-Previous work suggest techniques to find related queries but it will take a new method to discover parametrizable queries.
+Previous work suggest techniques to find related queries but it will take a new method to discover parameterizable queries.
 
@@
 In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.
-We described our method of modelling a users question answering process and how we are able to discover semantically similar queries.
+We described our method of modeling a users question answering process and how we are able to discover semantically similar queries.
 

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
general editing

@@
 \item Realm ontologies, comprising a heterarchy of categories that
-  characterize terms that can appear in queries.
-\item SSQ ontologies, used to describe the form of particular
+  characterize terms appearing in queries.
+\item SSQ ontologies, describing the form of particular
   realm-specific queries.
@@
 with its categories would be an extremely laborious task
-for any non-trivial realm. The realm of automobiles (which
-we use for illustration in this paper) contains, for example,
+for any non-trivial realm. For example, the realm of automobiles (which
+we use for illustration in this paper) contains 
 over XXXX categories and XXXX terms. We were unable to find
@@
 
-To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass/subclass} relationships built using DBPedia properties \textit{broader/narrower}.
+To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass} and \textit{subclass} relationships built using the DBPedia properties \textit{broader} and \textit{narrower}.
 By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.
@@
 approach is the page density varies greatly across the
-heterarchy. Each category within the DBpedia/ Wikipedia heterarchy
-contains a set of information pages, P, that correspond to concepts
-that share said category. Considering that the categorical structure
-is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the
-use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing
-a particular category. The category's that The assumption is that a
+heterarchy. Each category within the DBpedia/Wikipedia heterarchy
+contains a set of information pages, P, corresponding to the concepts shared by the category.
+Since the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket \cite{Friedman97bayesiannetwork} to describe
+a particular category. Our assumption is that a
 node can be fully described by its ancestor, descendant, and spousal
@@
 
-The subcategories of the category Automobiles (… Driving, Traffic Law,
-Automobiles by Decade, Auto Racing …) can be seen as grabbing
+The subcategories of the category Automobiles (Driving, Traffic Law,
+Automobiles by Decade, and Auto Racing) can be seen as grabbing
 information specific to the category. The super categories (Road

### 2010-03-05 paper/semsearch10/content/query_reexecution.tex
general editing

--- 2010-03-04 paper/semsearch10/content/query_reexecution.tex
@@
-\subsection{Query Re-execution}
+\section{Query Re-execution}
 % Chris
-	I ASSUME CLINT HAS COVERED QRM SELECTION ALREADY
-	When a user submits a new query to the Morpheus system, one or more stored 
-Query Resolution Methods are executed to obtain results. These QRMs are sorted based
-on their relevance to the query at hand and are chosen by the ontology matching subsystem.
-	A QRM consists of an XML script which instructs the Query Resolution Executor how to 
-obtain the required result. The QRE may "click" links, submit forms or highlight and save
-important pieces of html, including answers. Once it has visited all pages included in the 
-script the QRE returns the HTML snippet containing the answer. This answer can then be
-rendered in a browser. As mentioned above, normally a list or relevant QRMs will be given
-to the QRE which will in turn be executed using the provided SSQ, the results will be 
-displayed in order for the user.
+When a user submits a new query to the Morpheus system, one or more
+stored QRMs are executed to obtain results.
+A QRM contains an XML script representing an algorithm that will obtain the required result.
+The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, highlighting data, cutting and pasting text, and constructing an answer in the form of a text string.
+
+At present, the GET form submission method is used.  There is greater
+complexity in dealing with web forms than with links. For a given
+form, there may be text fields, drop-down boxes, and among other components.
+In order to support form submission in such circumstances, the QRE performs
+different actions based upon the input type. For text fields, simply
+adding a key/value pair to the query string suffices. For a drop-down
+box, the QRE extracts the form element to find the appropriate value to
+include in the query string.
+
+All input data are kept in an internal table. The QRM script contains keys that allow the QRE to map SSQ inputs from the table to the appropriate form
+inputs. Furthermore, highlighted text segments collected during
+execution of the script are stored in the table.  Once all actions in
+the script have been carried out, the QRE returns the textual answer this
+process has created. This answer is then be rendered in a browser displayed to the user.

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
general editing

@@
 
-The largest limitation to our current work is the QRR.
+The greatest limitation to our current work is the diversity of the QRR.
 In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.
-However, a significant amount user interaction is required to understand the answer retrieval process.
-By continuing to studying the methods of user data collection we plan to develop a model to support a unsupervised question resolution process.
+However, a significant number of user interactions is required to understand the answer retrieval process.
+By continuing to study the methods of user data collection we plan to develop a model to support an unsupervised question resolution process.
 This will increase the scalability and efficiency of the system.
@@
 Because each QRM may be treated as a function, we plan on leveraging previous work to allow new questions to be solved by connecting together several QRMs \cite{morpheus1, transformscout}.
-This method would expand the types of queries that are answerable be the system.
+This method would expand the types of queries that are answerable by the system.
 
-Currently, the category hierarchy that is generated from the DBpedia categories and our SSQ ontologies are stored in separate XML files.
-We are in the process of storing these ontologies into an efficient ontology database.
+Currently, the category heterarchy generated from the DBpedia categories and our SSQ ontologies is stored in separate XML files.
+We are in the process of moving these ontologies into an efficient ontology database.
 Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store.
@@
 
-In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belongs to all the realms.
+In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belonging to all realms.
 [e.g.
@@
 
-In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.
+In this paper we provide a discussion on a new type of question answering system that uses previously answered user questions.
 We described our method of modeling a users question answering process and how we are able to discover semantically similar queries.

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
tried to address changes for results section

@@
 
+%% I may have misstated the statistics that are unique/repeats
+% need to clarify the statistics 
+%% Add language about how we 
 Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-It is difficult to discover this property.
-Previous work suggest techniques to find related queries but it will take a new method to discover parameterizable queries.
+We believe that a large percentage of the stated unique queries are in-fact related and parameterizable, meaning, several subsets of unique queries may be all related and may be answered using a single QRM.
+It is difficult to discover this property between queries.
+Previous work suggest techniques to find related queries but it will take new efficient methods to discover parameterizable queries.
 

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
ontological_realms.tex - Paragraph 2 #1 (modification based on the below comment)
Content: "By using OWL, we can exploit the OWL API for matching SSQ
ontologies that reference these realm ontologies."

Comment: OWL is just thrown in without any prior reference (that I
saw), we need to introduce what OWL is so we have a better context for
this (one of the reasons why we are using OWL).

@@
 To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass} and \textit{subclass} relationships built using the DBPedia properties \textit{broader} and \textit{narrower}.
-By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.
+This  semantic heterarchy can be easily represented using the OWL ontology and by using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.
 
@@
 
-Once the semantic hierarchy is created, the next step is to create
+Once the semantic heterarchy is created, the next step is to create
 training data for the system. The task is then to grab the pages,

### 2010-03-05 trunk/paper/semsearch10/content/nlp.tex
More New stuff from jnw

@@
+\section{Natuarl Language Queries}
 % Joir-dan stuff
+The first step in answering a user query is to determine what, in
+fact, is being asked.  Any system that supports user queries places
+some constraints on the required input.  These constraints can be
+relatively minimal (``Users must type their input on a keyboard in
+French.'') or quite constrained (``Users must constuct fully
+categorized semi-structured queries employing only those terms and
+categories supplied by our database.'')  Our initial goal in Morpheus
+is two-fold:
 
-When we have completed our Wikipedia corpora from all the blankets in the category hierarchy, our system needs to make sense of the data for execution.
-The learning process involves the calculation of two n-gram frequency distributions: an n-gram/vocabulary distribution, and an n-gram/category distribution.
-The first value is the count of individual n-grams in the combined vocabulary of all corpora, and the second one is just the count of individual n-grams within a category’s blanket.
-The categories’ corpora reflect one long context per category, instead of breaking up sentences into different contexts.
-The idea behind this is that Wikipedia pages are already grouped into categories, that we can assume are related to the topics of each sentence within the corpus.
-We store distributions, rather than priors, primarily because if at anytime a blanket vocabulary seems inadequate, we can append terms from other sources to both distribution types and recalculate our values.
-We can simply calculate probabilities and store these separately for the execution of our natural query engine.
+\begin{enumerate}
+\item Implement an initial natural language interface that allows
+  users to make queries in a loosely constrained English language
+  subset.
+\item Provide a framework that can support a robust
+  interface that employs statistical language processing
+  methods.  
+\end{enumerate}
 
-The goal, is to choose that category for use in the SSQ structure.
-This process requires the tagging and parsing of our natural query, the extraction of key elements, primarily adjectives and nouns, and then using n-gram priors to calculate the appropriate category associated with that term.
+At present, we can process English language questions posed in answer
+form.  This requires minimal structural transformation in order to
+represent the semantic information contained within the question.  We
+translate these questions into semi-structured queries that associate
+English language terms and modifier phrases with contexts (\emph{who,
+  what, when, where})
 
-Picking out these terms requires knowledge of the structure of the question being passed to the system.
-The ideal situation would be that we could recognize question patterns, and decide where key information is within the question based on a given pattern.
-Currently, we only work with questions in an “answer” form, which means there is little to no transformation of the structure, to go from a question to an answer.
-
-Example
-
-Question: A 1997 Toyota Corolla needs what size tires?
-Answer:   A 1997 Toyota Corolla needs 17” tires.
+Input contexts of such a semi-structured query are generally given as
+terms (particular dates, names of cars, etc.) while output contexts
+are given as categories (tire type, tire size). Thus the inputs of the
+user SSQ are uncategorized, while their outputs are categorized.  The
+SSQs associated with a QRM are fully categorized (as will be discussed
+in section \ref{sec:qrr}). To match a user SSQ to existing QRMs, we
+must be able to match their SSQ input and output contexts.  This
+requires matching the input terms to their categories, a process we
+discuss in section \ref{sec:terms}.

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
More New stuff from jnw

@@
 
-To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass} and \textit{subclass} relationships built using the DBPedia properties \textit{broader} and \textit{narrower}.
-This  semantic heterarchy can be easily represented using the OWL ontology and by using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.
+To support our process, we map DBPedia categories into classes in our
+realm ontology with the \textit{superclass} and \textit{subclass}
+relationships built using the DBPedia properties \textit{broader} and
+\textit{narrower}. This semantic heterarchy can be easily represented
+using the OWL ontology and by using OWL, we can exploit the OWL API
+for matching SSQ ontologies that reference these realm ontologies.
 
@@
 heterarchy. Each category within the DBpedia/Wikipedia heterarchy
-contains a set of information pages, P, corresponding to the concepts shared by the category.
-Since the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket \cite{Friedman97bayesiannetwork} to describe
-a particular category. Our assumption is that a
-node can be fully described by its ancestor, descendant, and spousal
-nodes (parent node of subcategory not equal to the category). While
-this does not completely solve the issue of a category residing in a
-sparse area of the graph, the amount of information that can be
-obtained per blanket is usually more helpful than per category.
+contains a set of information pages, P, corresponding to the concepts
+shared by the category. Since the categorical structure is a directed
+acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket
+\cite{Friedman97bayesiannetwork} to describe a particular
+category. Our assumption is that a node can be fully described by its
+ancestor, descendant, and spousal nodes (parent node of subcategory
+not equal to the category). While this does not completely solve the
+issue of a category residing in a sparse area of the graph, the amount
+of information that can be obtained per blanket is usually more
+helpful than per category.
 
@@
 \subsection{Associating Terms with Categories}
+\label{sec:terms}
 %joir-dan

### 2010-03-05 trunk/paper/semsearch10/content/qrr.tex
More New stuff from jnw

@@
 Answering a question using the deep web requires one to navigate
-through a sequence of one or more web pages and links.  Many of the
-accesses involve clicks through web forms to resulting pages.  We have
+through a sequence of one or more web pages. Many of the accesses
+involve clicks through web forms or links to resulting pages.  We have
 developed a model that represents the various actions a user may carry
@@
 
-During the answer retrieval process, a user discovers an element of
-the query's result on a web page.  Next, she highlights that element,
-typically a text string.  This highlight allows the QRR to record the
-source of the query's answer.  The QRR stores all information from the
-user query in our data store.  When the user submits a web form she
-may associate each of the form's inputs with one of our stored context
-classes.
-
-The discovery process can be broken down into three cases:
+Web interactions can be broken down into three types:
 \begin{enumerate}
-\item The user typed in a URL and highlighted part of or all the
-  answer.
-\item The user typed in a URL, clicked a link, and found part or all
-  of the answer.
-\item The user typed in a URL, filled out a form, and found part or
-  all of the answer on a subsequent page.
+\item The user fills in and submits a web form.
+\item The user clicks a link.
+\item The user highlights text that is needed in the query or forms
+  part of the answer.
 \end{enumerate}
 
-Any discovery process consists of a sequence of these transactions.
+When a users submit a web form they are prompted for the classes of
+each of the form inputs. Here, class refers to categorization of data,
+e.g. name, date, etc. These classes allow the QRR to map the user's
+input SSQ tokens (which are also categorized) to their usage in a
+given form. For a clicked link, the QRR simply records the target url
+and nothing more. Finally, during the answer retrieval process when a
+user discovers all or part of the desired information on a web page,
+she highlights the text in question. This highlight allows the QRR to
+record the source of the query's answer. All information gathered
+during the recording process is saved in our data store.
+
+Any query answering process consists of a sequence of these transactions.
 Additionally, data collected for inputs and outputs may be found
-during any stage of the complete discovery process.  An output
+during any stage of the complete query process.  An output
 collected during one stage of an extraction may be the input to a
 subsequent stage in the extraction.  The QRR builds the completed user
-collection process into a QRM.  The following is a mathematical
-formulation of information collected for user web interactions.
+collection process into a QRM.
 
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:
+Conceptually, a QRM is the data structure that models the question
+answering process.  Each QRM contains an ontilogical realm, an SSQ,
+and information to support the query answering process.  The realm may
+be one or more descriptive categories and is used for classification
+of the QRMs.  The SSQ describes the set of possible input and output
+categories from the associated natural language query.  The possible
+set of phrase inputs and outputs are grouped into contextual bins
+labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.  The
+ontilogical realm and the SSQ parameters act as a signature for the
+QRM object, analogous to a function signature.  The ontological
+representation of the SSQ is described in section \ref{sec:ssq}.
+
+Additionally, the QRM contains representations for every page visited
+and the order of visitation.  For each page, we store the list of
+inputs to the URL such as form inputs and the possible outputs
+(highlighted portions of the webpage).  There is a mapping between the
+SSQ inputs and outputs used on any page to the specific page input.
+Finally, there is a structure with mappings to the user inputs or
+outputs that are displayed to the user as answers.
+
+The following is a mathematical description of the information
+collected for user web interactions.
+
+A QRM is a 4-tuple $Z = \left< \Sigma, P, M, A
+\right>$ with the following structure:
 
 \begin{enumerate}
+%%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------
 
-\item $\Upsilon$ is the sequence of input categories $\left<
-  \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$
-  where $\Upsilon_{1}$ represents the \emph{who} context of the
-  associated query, $\Upsilon_{2}$ represents the \emph{what} context,
-  $\Upsilon_{3}$ represents the \emph{when} context, and
+\item $\Sigma = ( R, \Upsilon, \Omega )$ is the SSQ associated with the QRM.
+
+  $R$ is the ontological realm associated with the QRM.
+
+  $\Upsilon$ is the sequence of input categories drawn from $R$
+  $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4}
+  \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of
+  the associated query, $\Upsilon_{2}$ represents the \emph{what}
+  context, $\Upsilon_{3}$ represents the \emph{when} context, and
   $\Upsilon_{4}$ represents the \emph{where} context.
 
-\item $\Omega$ is the sequence of output categories $\left<\Omega_{1},
-  \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$
-  represents the \emph{who} context of the associated query,
-  $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
+  $\Omega$ is the sequence of output categories drawn from $R$
+  $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where
+  $\Omega_{1}$ represents the \emph{who} context of the associated
+  query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
   represents the \emph{when} context, and $\Omega_{4}$ represents the
@@
 
-\item $R$ is an ontological realm.
-
 \item $A$ is the sequence of outputs from $\Upsilon$, $K$, and
@@
 % Christan
+
 The response pages created by querying web forms are dynamically
-generated with a templated structure. This generalization per page is
-done using the GenPath algorithm developed by Badica et
-al. \cite{Badica06}. Additionally, the community may be able to answer
-a particular SSQ using many different page interactions. Therefore, we
-use a method of generalizing extraction path to a result across
-pages. This method removes unnecessary page interactions and finds the
-shortest path to the result pages.
+generated with a template structure. This template structure contains
+XPath [!!!!!need reference] selectors to access particular web page
+elements.  One could employ XPath selectors that exactly match the
+selection paths to the web page elements accessed by the guide during
+query recording, however, using such specific paths fails to provide
+robust performance because web sites are highly susceptible to
+structural changes \cite{TanZMG07}.  To overcome this difficulty, we
+generalize these XPaths using the \emph{GenPath algorithm} developed by
+Badica et al. \cite{Badica06}.
 
-Websites wrapped by a system such as this are highly susceptible to
-structural changes \cite{TanZMG07}. Generalizing the extraction paths
-helps overcome small structural changes. If a website changes to the
-point where a QRM is no longer useful, the QRM is not considered
-fresh. User ratings of QRM freshness can be employed in the SSQ matching
-process detailed in Section \ref{sec:ssq}.
+Generalizing the extraction paths helps overcome small structural
+changes. However, If a website changes to the point where a QRM is no
+longer useful, the QRM is not considered fresh. User ratings of QRM
+freshness can be employed in the SSQ matching process detailed in
+Section \ref{sec:oqom}.
 
+In many cases, the same information may be found by a number of guides
+from the same deep web source, but by a different navigation path.
+Therefore, we also employ a method of generalizing extraction paths
+across page interactions. By doing this, one can remove unnecessary
+page interactions and finds the most effective navigation path
+necessary to produce a result.
 %-------------------------------------------------------------------------------

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
More New stuff from jnw

@@
 \section{Future Work}
-- Talk about the offline execution mode and class structural matching algorithm
-- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.
-We plan to investigate this.
+
+The greatest limitation to our current work is the diversity of the
+QRR.  In order to efficiently answer new user questions the systems
+needs a large amount of user annotated queries.  However, a
+significant number of user interactions is required to understand the
+answer retrieval process.  By continuing to study the methods of user
+data collection we plan to develop a model to support an unsupervised
+question resolution process.  This will increase the scalability and
+efficiency of the system.
+
+Because each QRM may be treated as a function, we plan on leveraging
+previous work to allow new questions to be solved by connecting
+together several QRMs \cite{morpheus1, transformscout}.  This method
+would expand the types of queries that are answerable by the system.
+
+Currently, the category heterarchy generated from the DBpedia
+categories and our SSQ ontologies is stored in separate XML files. We
+are in the process of moving these ontologies into an efficient
+ontology database. Similarly, employing user input brings about the
+likelihood that redundant SSQ ontological elements will be inserted
+into our ontology store. We are working on merging the similar SSQs
+[\ref{sec:ssq}] based on the SSQ realms and other ontological
+structural information so that we can remove the redundancy in the
+database.
+
+We cannot rely on the DBpedia categories and the associated Wikipedia
+pages to provide corpora for all our realms.  The categories in
+DBpedia store and documents in the Wikipedia are insufficient to
+characterize the linguistic space of queries belonging to many
+different realms.  Reasonable prior probabilities for the names of
+musical groups within the category \emph{musical groups}, for example,
+will be significantly different from what would be manufactured by
+simply finding n-gram frequency within the related Wikipedia
+documents. We are investigating methods to identify categories within
+the deep web and to find new sources to construct \textit{weak} realms
+in our ontology hierarchy.
+
+%% I may have misstated the statistics that are unique/repeats
+% need to clarify the statistics 
+%% Add language about how we 
+Researchers have stated that somewhere from 39 to 63 percent of web
+queries are unique \cite{1277770,331405,621942}.  We believe that a
+large percentage of the stated unique queries are in-fact related and
+parameterizable, meaning, several subsets of unique queries may be all
+related and may be answered using a single QRM.  It is difficult to
+discover this property between queries.  Previous work suggest
+techniques to find related queries but it will take new efficient
+methods to discover parameterizable queries.
 
@@
 
+In this paper we provide a discussion on a new type of question
+answering system that uses previously answered user questions.  We
+described our method of modeling a users question answering process
+and how we are able to discover semantically similar queries.
+
 \section{Acknowledgements}

### 2010-03-05 trunk/paper/semsearch10/content/ssq_ranking.tex
More New stuff from jnw

@@
 d_{class}(S, T) = \begin{cases}
-0 & if S.{uri} \equiv T.{uri}\\
-d(S, T) & if S \prec T\\
+0 & if S.{Uri} \equiv T.{Uri}\\
+d(S, T)/3h & if S \prec T\\
 1 & if T \prec S\\
-d(S,root) \\+ d(S,C) + d(T,C) & otherwise
+(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/3h & otherwise
 \end{cases}
@@
 
-We normalize $d_{class}(S, T)$ by dividing by three times the height
-of the ontology tree.
+where $h$ is three times the height of the ontology tree.
 
@@
 subclass of \textit{Automobiles} and \textit{Racing Cars} is the
-subclass of \textit{Auto Racinng}. Therefore, the common ancestor for
+subclass of \textit{Auto Racing}, which is a subclass of \textit{Automobiles}. Therefore, the common ancestor for
 these two can be determined as \textit{Automobiles} ($C$). They share
 the path from \textit{Automobiles} to the $root$. So, the unnormalized
-divergence \textit{d(Automotive Industry, root)} is 32 (calcuted from
-the path to root), \textit{d(Automotive Industry, Automobiles)} is one
+divergence \textit{d(Automotive Industry, root)} is 32 that is calculated from the path to the root \textit{DBpediaRoot}, \textit{d(Automotive Industry, Automobiles)} is one
 (dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two
 (dashed arrow). Suppose, the ontology tree height is calculated as
-294. Thus, \textit{d(Automotive Industry, Racing Cars)} is 35, which
-corresponds to a normalized value of $35/294$.
+294. Thus, $d_{class}$\textit{(Automotive Industry, Racing Cars)} is 35, which corresponds to a normalized value of $35/294$.
 
@@
 
-We use class divergence to calculate the relevance between a source
-SSQ and a target SSQ associated with a QRM.  Each SSQ will have four
+We use class divergence to calculate the relevance between a new SSQ
+and a SSQ associated with a QRM in the store.  Each SSQ will have four
 input classes, four output classes, and one realm.  We refer to the
@@
 input or output class is unspecified in the query, it is associated
-with the class $bottom$, which has no subclasses or individuals.
+with the class $\perp$, which is a subclass of every other class has
+no subclasses or individuals.
 

### 2010-03-05 paper/semsearch10/content/introduction.tex
More New stuff from jnw

@@
 who come later will find it easy to reach that destination if a
-well-marked trail without the has been created. Olsen and Malizia
-describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather
-than treating each user's search as a unique entity and working from
-first principles, one can exploit the fact that a similar search may
-have been performed already.  In one study, almost 40 percent of all
-queries were found to be repetitions of previous
-queries.\cite{1277770} This points to way to optimize the search
+well-marked trail has been created. Olsen and Malizia describe this
+idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
+a user's search as a unique entity and working without an example
+context, one can exploit the fact that a similar search may have been
+performed already.  In one study, almost 40 percent of all queries
+were found to be repetitions of previous queries\cite{1277770}. This
+indicates the reuse of prior searches is a way to optimize the search
 process.  We have built a prototype system for answering questions
@@
 answering system follows path-finders to their destinations and not
-only marks the trail, but provides a taxi service to take followers to
-similar destinations.
+only marks the trail, but also provides a taxi service to take
+followers to similar destinations.

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
More More New stuff from jnw

@@
 We cannot rely on the DBpedia categories and the associated Wikipedia
-pages to provide corpora for all our realms.  The categories in
-DBpedia store and documents in the Wikipedia are insufficient to
+pages to provide corpora for all our realms.  The DBpedia categories
+and the associated Wikipedia documents are insufficient to
 characterize the linguistic space of queries belonging to many

### 2010-03-05 paper/semsearch10/content/nlp.tex
Fixed misspelling

@@
+\section{Natural Language Queries}
 % Joir-dan stuff
+The first step in answering a user query is to determine what, in
+fact, is being asked.  Any system that supports user queries places
+some constraints on the required input.  These constraints can be
+relatively minimal (``Users must type their input on a keyboard in
+French.'') or quite constrained (``Users must constuct fully
+categorized semi-structured queries employing only those terms and
+categories supplied by our database.'')  Our initial goal in Morpheus
+is two-fold:
 
-When we have completed our Wikipedia corpora from all the blankets in the category hierarchy, our system needs to make sense of the data for execution.
-The learning process involves the calculation of two n-gram frequency distributions: an n-gram/vocabulary distribution and an n-gram/category distribution.
-The first value is the count of the individual n-grams in the combined vocabulary of all corpora.
-The second value is the count of the individual n-grams within a category's blanket.
-The categories corpora reflect one long context per category, instead of breaking up sentences into different contexts.
-The idea behind this is that Wikipedia pages are already grouped into categories, that we can assume are related to the topics of each sentence within the corpus.
-We store distributions, rather than priors, primarily because if at anytime a blanket vocabulary seems inadequate, we can append terms from other sources to both distribution types and recalculate our values.
-We can simply calculate probabilities and store these separately for the execution of our natural language query engine.
+\begin{enumerate}
+\item Implement an initial natural language interface that allows
+  users to make queries in a loosely constrained English language
+  subset.
+\item Provide a framework that can support a robust
+  interface that employs statistical language processing
+  methods.  
+\end{enumerate}
 
-Our goal is to choose that category for use in the SSQ structure.
-This process requires the tagging and parsing of our natural language query, the extraction of key parts of speech, such as adjectives and nouns, and then using n-gram priors to calculate the appropriate category associated with each term.
+At present, we can process English language questions posed in answer
+form.  This requires minimal structural transformation in order to
+represent the semantic information contained within the question.  We
+translate these questions into semi-structured queries that associate
+English language terms and modifier phrases with contexts (\emph{who,
+  what, when, where})
 
-Picking out these terms requires knowledge of the structure of the queThe ideal situation would be that we could recognize question patterns, and decide where key information is within the question based upon a given pattern.stion being passed to the system.
-Currently, we only work with questions in an answer form, which means there is little to no transformation of the structure, to go from a question to an answer.
-
-Consider the example question: "A 1997 Toyota Corolla needs what size tires?" The answer is: "A 1997 Toyota Corolla needs 17 inch tires."
+Input contexts of such a semi-structured query are generally given as
+terms (particular dates, names of cars, etc.) while output contexts
+are given as categories (tire type, tire size). Thus the inputs of the
+user SSQ are uncategorized, while their outputs are categorized.  The
+SSQs associated with a QRM are fully categorized (as will be discussed
+in section \ref{sec:qrr}). To match a user SSQ to existing QRMs, we
+must be able to match their SSQ input and output contexts.  This
+requires matching the input terms to their categories, a process we
+discuss in section \ref{sec:terms}.

### 2010-03-05 trunk/paper/semsearch10/content/query_reexecution.tex
After Dr. Wilson's improvements
fixing comments in section

@@
-\subsection{Query Re-execution}
+\section{Query Re-execution}
 % Chris
 When a user submits a new query to the Morpheus system, one or more
-stored Query Resolution Methods are executed to obtain results. A QRM
-contains an XML script that represents an algorithm that will obtain
-the required result.  The evaluation of this script by the QRE
-simulates the behavior of a human browsing the web, that is, clicking
-buttons to follow links, submitting forms, highlighting and cutting
-and pasting text, and constructing an answer in the form of a text
-string.
+stored QRMs are executed to obtain results. A QRM contains an XML
+script representing an algorithm that will obtain the required result.
+The evaluation of this script by the QRE simulates the behavior of a
+human browsing the web, that is, clicking buttons to follow links,
+submitting forms, highlighting data, cutting and pasting text, and
+constructing an answer in the form of a text string.
 
-At present, the GET form submission method is used.  There is greater
-complexity in dealing with web forms than with links. For a given
-form, there may be text fields, drop-down boxes, radio buttons etc.
-To support form submission in such circumstances the QRE takes
-different actions based on the input type. For text fields, simply
-adding a key/value pair to the querystring suffices. For a drop-down
-box, the QRE extracts the form element find the appropriate value to
-include in the querystring.
+There is greater complexity in dealing with web forms than with links.
+At present, the GET form submission method is used. This means that in preparation to 
+submit a form, the Morpheus System builds a querystring consisting of name-value pairs.
+For a given form, there may be text fields, drop-down boxes, and among other components.
+In order to support form submission in such circumstances, the QRE performs
+different actions based upon the input type. For text fields, simply
+adding a key/value pair to the query string suffices. For a drop-down
+box, the QRE extracts the form element to find the appropriate value to
+include in the query string. It does this by examine each option in the drop-down and 
+matching the user's input to the text field in the option. The value attribute of the option
+is then added to the querystring. The value and text attributes of a drop-down option might 
+be the same, but they are not guaranteed to be.
 
-All input data as well as data highlighted during the evaluation are
-kept in an internal table. The QRM script contains keys that allow the
-QRE to map SSQ inputs from the table to the appropriate form
-inputs. Furthermore, highlighted text segments collected during
-execution of the script are stored in the table.  Once all actions in
-the script have been carried out, the QRE returns textual answer this
-process has created. This answer can then be rendered in a
-browser.
+All input data are kept in an internal table. The QRM script contains
+keys that allow the QRE to map SSQ inputs from the table to the
+appropriate form inputs. Furthermore, highlighted text segments
+collected during execution of the script are stored in the table.
+Once all actions in the script have been carried out, the QRE returns
+the textual answer this process has created. This answer is then be
+rendered in a browser displayed to the user.

### 2010-03-05 trunk/paper/semsearch10/content/ssq_ranking.tex
Added a foot note for the classes

@@
 We employ a measure of compatibility, which we call \textit{class
-  divergence}, between a source class and a target class using the
-\textit{topological structure} of the context classes in the
+  divergence}, between a source class\footnote{We use the term \textit{class} when dealing with our ontological structure, however the terms class and \textit{category} are analogous.} and a target class using the \textit{topological structure} of the context classes in the
 ontology. We write $S \prec T$ for the reflexive transitive closure of
@@
 0 & if S.{Uri} \equiv T.{Uri}\\
-d(S, T)/3h & if S \prec T\\
+d(S, T)/(3h) & if S \prec T\\
 1 & if T \prec S\\
-(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/3h & otherwise
+(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/(3h) & otherwise
 \end{cases}
@@
 
-where $h$ is three times the height of the ontology tree.
+\noindent where $h$ is the height of the ontology tree.
 

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
updated text

@@
 % Walk through of example query
+
+screen_intro.jpg caption:
+The user types a natural language query into the search box and clicks submit.
+The query is then converted into an SSQ and the process of locating appropriate QRMs begins.
+For any given query there may be several suitable QRMs, these are executed in order of relevance.
+
+screen_results.jpg caption:
+After execution has completed, the user is informed of how the query was parsed and what answers were found sorted by relevance.
+Furthermore, the sequence of pages visited is displayed for the most relevant result.
 

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
Added the results images

@@
 
+% Results: figure 1  
+\begin{figure}[t]
+\centering
+\includegraphics[width=85mm]{screen_intro.eps}
+\caption{Introductory screen}
+\label{fig:screen_intro}
+\end{figure}
+
+Initially, the user enters a query of interest, much as one would ask a question.
+When the user submits the query, the query is broken down into constituent parts of who, what when, and where.
+From there, a relevant answer is produced to respond to the requested information.
+
+% Results: figure 2  
+\begin{figure}[t]
+\centering
+\includegraphics[width=85mm]{screen_result.eps}
+\caption{Results screen}
+\label{fig:screen_result}
+\end{figure}
+
+After typing in a query, the user is presented with two sections.
+First, the user is shown the query and how it was broken down during the form submission.
+Second, the user is presented with the relevant answer, the realm to which it belongs, and the sites in which the answer was found.
+If multiple answers are retrieved, they are sorted by relevance, with the most relevant answer displaying at the top of the list.
+
 \section{Future Work}
 
-The greatest limitation to our current work is the diversity of the QRR.
-In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.
-However, a significant number of user interactions is required to understand the answer retrieval process.
-By continuing to study the methods of user data collection we plan to develop a model to support an unsupervised question resolution process.
-This will increase the scalability and efficiency of the system.
+The greatest limitation to our current work is the diversity of the
+QRR.  In order to efficiently answer new user questions the systems
+needs a large amount of user annotated queries.  However, a
+significant number of user interactions is required to understand the
+answer retrieval process.  By continuing to study the methods of user
+data collection we plan to develop a model to support an unsupervised
+question resolution process.  This will increase the scalability and
+efficiency of the system.
 
-Because each QRM may be treated as a function, we plan on leveraging previous work to allow new questions to be solved by connecting together several QRMs \cite{morpheus1, transformscout}.
-This method would expand the types of queries that are answerable by the system.
+Because each QRM may be treated as a function, we plan on leveraging
+previous work to allow new questions to be solved by connecting
+together several QRMs \cite{morpheus1, transformscout}.  This method
+would expand the types of queries that are answerable by the system.
 
-Currently, the category heterarchy generated from the DBpedia categories and our SSQ ontologies is stored in separate XML files.
-We are in the process of moving these ontologies into an efficient ontology database.
-Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store.
-We are working on merging the similar SSQs [\ref{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.
+Currently, the category heterarchy generated from the DBpedia
+categories and our SSQ ontologies is stored in separate XML files. We
+are in the process of moving these ontologies into an efficient
+ontology database. Similarly, employing user input brings about the
+likelihood that redundant SSQ ontological elements will be inserted
+into our ontology store. We are working on merging the similar SSQs
+[\ref{sec:ssq}] based on the SSQ realms and other ontological
+structural information so that we can remove the redundancy in the
+database.
 
-In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belonging to all realms.
-[e.g.
-musical bands].
-We are planning to define new categories from the deep web [or find out new sources to fill those \textit{weak} realms] in our ontology hierarchy.
+We cannot rely on the DBpedia categories and the associated Wikipedia
+pages to provide corpora for all our realms.  The DBpedia categories
+and the associated Wikipedia documents are insufficient to
+characterize the linguistic space of queries belonging to many
+different realms.  Reasonable prior probabilities for the names of
+musical groups within the category \emph{musical groups}, for example,
+will be significantly different from what would be manufactured by
+simply finding n-gram frequency within the related Wikipedia
+documents. We are investigating methods to identify categories within
+the deep web and to find new sources to construct \textit{weak} realms
+in our ontology hierarchy.
 
@@
 %% Add language about how we 
-Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.
-We believe that a large percentage of the stated unique queries are in-fact related and parameterizable, meaning, several subsets of unique queries may be all related and may be answered using a single QRM.
-It is difficult to discover this property between queries.
-Previous work suggest techniques to find related queries but it will take new efficient methods to discover parameterizable queries.
+Researchers have stated that somewhere from 39 to 63 percent of web
+queries are unique \cite{1277770,331405,621942}.  We believe that a
+large percentage of the stated unique queries are in-fact related and
+parameterizable, meaning, several subsets of unique queries may be all
+related and may be answered using a single QRM.  It is difficult to
+discover this property between queries.  Previous work suggest
+techniques to find related queries but it will take new efficient
+methods to discover parameterizable queries.
 
@@
 
-In this paper we provide a discussion on a new type of question answering system that uses previously answered user questions.
-We described our method of modeling a users question answering process and how we are able to discover semantically similar queries.
-
-MORE
+In this paper we provide a discussion on a new type of question
+answering system that uses previously answered user questions.  We
+described our method of modeling a users question answering process
+and how we are able to discover semantically similar queries.
 

### 2010-03-05 paper/semsearch10/content/qrr.tex

@@
 Answering a question using the deep web requires one to navigate
-through a sequence of one or more web pages.
-Many of the accesses involve clicks through web forms or links to resulting pages.
-We have developed a model that represents the various actions a user may carry out during this process.
+through a sequence of one or more web pages. Many of the accesses
+involve clicks through web forms or links to resulting pages.  We have
+developed a model that represents the various actions a user may carry
+out during this process.
 
@@
 \item The user clicks a link.
-\item The user highlights text that is needed in the query or forms part of the answer. 
+\item The user highlights text that is needed in the query or forms
+  part of the answer.
 \end{enumerate}
 
-When a users submit a web form they are prompted for the classes of each of the form inputs.
-Here, class refers to categorization of data, e.g.
-name, date, etc.
-These classes allow the QRR to map the user's input SSQ tokens (which are also categorized) to their usage in a given form.
-For a clicked link, the QRR simply records the target url and nothing more.
-Finally, during the answer retrieval process when a user discovers all or part of the desired information on a web page, she highlights the text in question.
-This highlight allows the QRR to record the source of the query's answer.
-All information gathered during the recording process is saved in our data store.
+When a users submit a web form they are prompted for the classes of
+each of the form inputs. Here, class refers to categorization of data,
+e.g. name, date, etc. These classes allow the QRR to map the user's
+input SSQ tokens (which are also categorized) to their usage in a
+given form. For a clicked link, the QRR simply records the target url
+and nothing more. Finally, during the answer retrieval process when a
+user discovers all or part of the desired information on a web page,
+she highlights the text in question. This highlight allows the QRR to
+record the source of the query's answer. All information gathered
+during the recording process is saved in our data store.
 
@@
 
-Conceptually, a QRM is the data structure that models the question answering process.
-Each QRM contains an ontilogical realm, an SSQ, and information to support the query answering process.
-The realm may be one or more descriptive categories and is used for classification of the QRMs.
-The SSQ describes the set of possible input and output categories from the associated natural language query.
-The possible set of phrase inputs and outputs are grouped into contextual bins labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.
-The ontilogical realm and the SSQ parameters act as a signature for the QRM object, analogous to a function signature.
-The ontological representation of the SSQ is described in section {{XXX}}.
+Conceptually, a QRM is the data structure that models the question
+answering process.  Each QRM contains an ontological realm, an SSQ,
+and information to support the query answering process.  The realm may
+be one or more descriptive categories and is used for classification
+of the QRMs.  The SSQ describes the set of possible input and output
+categories from the associated natural language query.  The possible
+set of phrase inputs and outputs are grouped into contextual bins
+labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.  The
+ontological realm and the SSQ parameters act as a signature for the
+QRM object, analogous to a function signature.  The ontological
+representation of the SSQ is described in section \ref{sec:ssq}.
 
-Additionally, the QRM contains representations for every page visited and the order of visitation.
-For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlighted portions of the webpage).
-There is a mapping between the SSQ inputs and outputs used on any page to the specific page input.
-Finally, there is a structure with mappings to the user inputs or outputs that are displayed to the user as answers.
+Additionally, the QRM contains representations for every page visited
+and the order of visitation.  For each page, we store the list of
+inputs to the URL such as form inputs and the possible outputs
+(highlighted portions of the web page).  There is a mapping between the
+SSQ inputs and outputs used on any page to the specific page input.
+Finally, there is a structure with mappings to the user inputs or
+outputs that are displayed to the user as answers.
 
-The following is a mathematical description of the information collected for user web interactions.
+The following is a mathematical description of the information
+collected for user web interactions.
 
-A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ \footnote{It is important to not that both $\Upsilon$ and $\Omega$ make up the SSQ structure.} such that:
+A QRM is a 4-tuple $Z = \left< \Sigma, P, M, A
+\right>$ with the following structure:
 
@@
 %%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------
-\item $\Upsilon$ is the sequence of input categories $\left<
-  \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$
-  where $\Upsilon_{1}$ represents the \emph{who} context of the
-  associated query, $\Upsilon_{2}$ represents the \emph{what} context,
-  $\Upsilon_{3}$ represents the \emph{when} context, and
+
+\item $\Sigma = ( R, \Upsilon, \Omega )$ is the SSQ associated with the QRM.
+
+  $R$ is the ontological realm associated with the QRM.
+
+  $\Upsilon$ is the sequence of input categories drawn from $R$
+  $\left< \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4}
+  \right>$ where $\Upsilon_{1}$ represents the \emph{who} context of
+  the associated query, $\Upsilon_{2}$ represents the \emph{what}
+  context, $\Upsilon_{3}$ represents the \emph{when} context, and
   $\Upsilon_{4}$ represents the \emph{where} context.
 
-\item $\Omega$ is the sequence of output categories $\left<\Omega_{1},
-  \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$
-  represents the \emph{who} context of the associated query,
-  $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
+  $\Omega$ is the sequence of output categories drawn from $R$
+  $\left<\Omega_{1}, \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where
+  $\Omega_{1}$ represents the \emph{who} context of the associated
+  query, $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
   represents the \emph{when} context, and $\Omega_{4}$ represents the

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
updating screenshot description

--- 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
@@
 % Walk through of example query
+
+% Results: figure 1  
+\begin{figure}[t]
+\centering
+\includegraphics[width=85mm]{screen_intro.eps}
+\caption{Introductory screen}
+\label{fig:screen_intro}
+\end{figure}
+
+Initially, the user enters a query of interest, much as one would ask a question.
+When the user submits the query, the query is broken down into constituent parts of who, what when, and where.
+From there, a relevant answer is produced to respond to the requested information.
+
+% Results: figure 2  
+\begin{figure}[t]
+\centering
+\includegraphics[width=85mm]{screen_result.eps}
+\caption{Results screen}
+\label{fig:screen_result}
+\end{figure}
+
+After execution, the user is presented with a list of relevant answers and a depiction of how the query was parsed.
+In the above example, the query about tire size was executed and the most relevant result has been returned and displayed.
+Furthermore, the sequence of pages visited during execution are displayed as well.
 

### 2010-03-05 paper/semsearch10/content/qrr.tex
some changes

@@
 input SSQ tokens (which are also categorized) to their usage in a
-given form. For a clicked link, the QRR simply records the target url
+given form. For a clicked link, the QRR simply records the target URL
 and nothing more. Finally, during the answer retrieval process when a
@@
 \begin{enumerate}
-%%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------
 
@@
 
-The response pages created by querying web forms are dynamically
-generated with a template structure. This template structure contains
-XPath [!!!!!need reference] selectors to access particular web page
-elements.  One could employ XPath selectors that exactly match the
+After executing web forms, several result pages are dynamically created but oftentimes has a fixed structure.
+Using the fixed structure property,  XPath allow simple selection of the resulting page element \cite{xpath_leashed}.
+One could employ XPath selectors that exactly match the
 selection paths to the web page elements accessed by the guide during

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
some changes

@@
 
-After typing in a query, the user is presented with two sections.
-First, the user is shown the query and how it was broken down during the form submission.
-Second, the user is presented with the relevant answer, the realm to which it belongs, and the sites in which the answer was found.
-If multiple answers are retrieved, they are sorted by relevance, with the most relevant answer displaying at the top of the list.
+After execution, the user is presented with a list of relevant answers and a depiction of how the query was parsed.
+In the above example, the query about tire size was executed and the most relevant result has been returned and displayed.
+Furthermore, the sequence of pages visited during execution are displayed as well.
 
@@
 \section{Acknowledgements}
+Our thanks to Jeff N. Depree, Guillermo Cordero, and Nick Antonelli for thier assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.

### 2010-03-05 trunk/paper/semsearch10/content/nlp.tex
new stuff

@@
-\section{Natuarl Language Queries}
+\section{Natural Language Queries}
 % Joir-dan stuff
@@
 some constraints on the required input.  These constraints can be
-relatively minimal (``Users must type their input on a keyboard in
-French.'') or quite constrained (``Users must constuct fully
-categorized semi-structured queries employing only those terms and
-categories supplied by our database.'')  Our initial goal in Morpheus
+relatively minimal ,``Users must type their input on a 104-key
+keyboard in English,'' or highly restrictive, ``Users must constuct
+fully categorized semi-structured queries employing only those terms and
+categories supplied by our database.''  Our initial goal in Morpheus
 is two-fold:
@@
 
-At present, we can process English language questions posed in answer
-form.  This requires minimal structural transformation in order to
-represent the semantic information contained within the question.  We
+At present, we can process English language questions posed in
+\emph{answer form}, for example, ``The closest Ford dealer to the University
+of Florida is where?'' This requires minimal structural transformation in order
+to represent the semantic information contained within the question.  We
 translate these questions into semi-structured queries that associate
-English language terms and modifier phrases with contexts (\emph{who,
-  what, when, where})
+English language terms and modifier phrases with contexts.
 
@@
 terms (particular dates, names of cars, etc.) while output contexts
-are given as categories (tire type, tire size). Thus the inputs of the
+are given as descriptions of categories or contexts, i.e.,
+\emph{tire type, what date, where}. Thus the inputs of the
 user SSQ are uncategorized, while their outputs are categorized.  The

### 2010-03-05 trunk/paper/semsearch10/paper.tex
new stuff

--- 2010-03-02 trunk/paper/semsearch10/paper.tex
@@
 \documentclass{www2010-submission}
+\usepackage{listings}
 \begin{document}
 
-\title{Leveraging Semantics for a Deep Web Question Answering System} 
+\title{Re-finding to support a Deep Web Question Answering System} 
 \numberofauthors{1}
@@
 	 \alignauthor Christan Grant, Clint P. George, Joseph N. Wilson, Peter J. Dobbins, Jeff T. Depree, Christopher A. Shields and Joir-dan Gumbs\\
-	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr{ Gainesville, Florida, USA} \\
+	 \affaddr{Dept. of Computer Science, University of Florida} \\ \affaddr
+{ Gainesville, Florida, USA} \\
 \email{\{cgrant, cgeorge, jnw, pjd, jepree, cshields, jgumbs\} @cise.ufl.edu}

### 2010-03-05 paper/semsearch10/content/abstract.tex
new stuff

--- 2010-03-03 paper/semsearch10/content/abstract.tex
@@
 \begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
+The Morpheus question answering system uses deep web search to answer
+user queries. Queries are represented as OWL ontologies that reference
+categories within specific ontological realms.
+The system answers questions by using methods identified in prior
+successful searches answering similar queries.
+Stored methods are ranked based on their ontological similarity to the
+question being answered.
+The similarity measure depends on finding the distance between
+ontological categories associated with their search terms.
+The DBpedia and Wikipedia provide information we use to identify the likely
+categories associated with those terms.
+Finally, we replay appropriately re-parameterized relevant prior searches
+to construct possible answers.
+The paper describes this entire process with emphasis on the matching of
+user queries to stored answering methods.
 \end{abstract}

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
added  new screen shot images
Added the probability table for Accord

@@
 Furthermore, the sequence of pages visited during execution are displayed as well.
+
+\begin{center}
+  \begin{tabular}{ | l | l | c | r | }
+    \hline
+    Category & Prior & Likelihood & Posterior \\ \hline
+    Automobiles & 0.59 & 3.76e-06 & 0.01 \\ 
+    Motorcycles & 0.13 & 4.30e-05 & 0.95 \\
+    Internet search engines & 0.16 & 6.29e-07 & 0.003 \\ 
+    Lists of countries & 0.06 & 3.08e-06 & 0.01 \\
+    Tires & 0.05 & 5.40e-06 & 0.03 \\
+    \hline
+
+  \end{tabular}
+
+\end{center}
 

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
more fixes

@@
 terms and their associated categories can be quite large.
-Construction of a realm ontology and the terms associated
+Manual construction of a realm ontology and the terms associated
 with its categories would be an extremely laborious task
-for any non-trivial realm. For example, the realm of automobiles (which
-we use for illustration in this paper) contains 
-over XXXX categories and XXXX terms. We were unable to find
-an appropriate ontology for this realm, so we constructed it
+for any non-trivial realm. For example, the realm of vehicles
+in our current ontology contains 32 categories and millions of terms.
+We were unable to find
+an existing ontology for this realm, so we constructed one
 using categories from the DBPedia \cite{Auer07dbpedia:a}.
@@
 that not only does it supply a categorical heterarchy, but it
-also links to Wikipedia documents which provides us with a large
-realm-specific document corpus.
+also links to Wikipedia documents which provide us with a large
+realm-specific corpus.
 
@@
 Once the semantic heterarchy is created, the next step is to create
-training data for the system. The task is then to grab the pages,
-build a corpus relating to a given category, and then compile the
-information in a meaningful way. The overall goal is to grab enough
-information to properly characterize a category while limiting the
+training data for the system. To do this, we extract words from the pages,
+thus building a corpus related to a given category.
+Finally, we have compiled enough information to properly characterize
+a category while limiting the
 amount of unnecessary content within the corpus. The problem with this
 approach is the page density varies greatly across the
-heterarchy. Each category within the DBpedia/Wikipedia heterarchy
+heterarchy. Each category within the DBpedia and Wikipedia heterarchy
 contains a set of information pages, P, corresponding to the concepts
@@
 \cite{Friedman97bayesiannetwork} to describe a particular
-category. Our assumption is that a node can be fully described by its
-ancestor, descendant, and spousal nodes (parent node of subcategory
-not equal to the category). While this does not completely solve the
+category. We hypothesize that the terms associated with a category
+can be found by identifying those terms associated with that category's
+ancestor, descendant, and spousal nodes (i.e., other parent nodes of a subcategory). While this does not completely solve the
 issue of a category residing in a sparse area of the graph, the amount
-of information that can be obtained per blanket is usually more
+of information that can be obtained per blanket is more
 helpful than per category.
 
-The subcategories of the category Automobiles (Driving, Traffic Law,
-Automobiles by Decade, and Auto Racing) can be seen as grabbing
-information specific to the category. The super categories (Road
-Vehicles) place the category in a higher perspective, abstractly
-describing basketball as a concept. The spousal categories
-(...Motor Sport, Individual Sport...) are an abstract description of
-the subcategories.
-
 Clustering the categories alone does not guarantee adequate corpus
-creation. Since the above model relies on the subcategories to
-describe specifics of a given category, the ideal situation would be
-that the subcategories have many more pages than the super categories
-and that there is a significant amount of information per page.  In
-the case of Wikipedia, there are an average of 25.7 pages per category
-\cite{1321474}. The assumption for collecting the training data is the
-more subcategory data we have, the more detailed our description of
-our category. Considering that there are many categories that have
-much more than 26 pages, we instituted a PlusOne mechanism to extract
+creation. Since our model relies on the subcategories to
+to provide terms associated with a given category, it will fail if
+the subcategories do not provide enough data to our corpus.
+For the purpose of gathering training data having more subcategory data
+yields a more representative collection of terms for that category. 
+The average number of pages per category in the Wikipedia is 25.7\cite{1321474}.
+We have found that this number of pages is insufficient to provide a representative collection of terms for a category.
+In order to gain more pages and expand the term base, we have used a
+PlusOne mechanism to extract
 extra information. This mechanism checks if a subcategory has an
-adequate number of pages α to fully describe its subtopic. We set this
-number to ten times the average, or 260. $Level$ represents how many
-extra levels we are to go down in the hierarchy, if
-necessary. SubjectSet is the overall set of all pages associated with
-the blanket structure along with any plusOne subjects obtained.
-
-\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival, basicstyle=\small]
-def BlanketSubjectRetreival(blanket, maxLevel):
-	for category in blanket:
-		subjectSet.add(grabsubjects(category))
-		diff = afterSize - beforeSize
-		if diff <= a and category is subcategory:
-			PlusOneMechanism(category, maxLevel)
-	return subjectSet
-\end{lstlisting}
-
-\begin{lstlisting}[language=Python, frame=none, tabsize=2, caption=PlusOneMechanism, label=PlusOneMechanism, basicstyle=\small]
-def PlusOneMechanism(category, level):
-	plusOneSet = grabPlusOneSubcategories(category)
-	for subcategory in plusOneSet:
-		subject.add(grabSubjects(subcategory))
-		diff = afterSize - beforeSize
-		if diff <= a and level > 0:
-			PlusOneMechanism(subcategory, level-1)
-
-\end{lstlisting}
+adequate number of pages to fully describe its subtopic.
+We have chosen this number to be approximately ten times the average
+number of Wikipedia pages per category, or 260.  If a cateogory
+does not contain the required number of pages, PlusOne continues to
+search another level deeper in the hierarchy until a sufficient
+number of pages has been reached.
 
@@
 
-The overall mechanism does not take into account the amount of
-information within each page, but generally that can be ignored when
-considering the size of the blanket corpus when we extract the text
-from the Wikipedia subject pages. Using this method on the category
-Automobiles, we can construct a corpus of 2255 subject pages and
-6,084,260 terms.
+Our approach to category corpus construction does not take into
+account the number of words contained within each page.
+However, we have found this method to be adequate to construct
+usable corpora. For example, when executed on the vehicle ontology,
+this method yields 2255 subject pages and a corpus containing
+1,691,727 unique terms and 6,084,260 total words.
 
-When a category's corpus is built, we then build our n-gram frequency
-distributions and store them in a database for the NLP processing. For
-the purpose of calculating term importance to a blanket, we aggregate
-the frequencies of all blankets and store this information as
-well. For this system, term importance refers to the prior probability
-of a category given an n-gram. We calculate this using Bayes Rule,
-since we can easily obtain the n-gram-category and n-gram-vocabulary
+After a category's corpus is built, we then build term frequency
+distributions and store them in a database for natural language processing.
+For this system, term importance refers to the prior probability
+of a category given a term. We calculate this using Bayes Rule,
+since we can easily obtain the term-category and term-corpus
 probabilities. The higher the probability, the more likely a term is

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
added better conclusion stuff

@@
 and how we are able to discover semantically similar queries.
+The Morpheus system still has a lot of room for optimization.
+However, we believe this new technique for question answering system will improve the exploration experience.
 
 \section{Acknowledgements}
-Our thanks to Jeff N. Depree, Guillermo Cordero, and Nick Antonelli for thier assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.
+Our thanks to Guillermo Cordero, and Nick Antonelli for thier assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
Hopefully done

@@
-\section{Results}
+\section{Sample Execution}
 % Walk through of example query
@@
 \includegraphics[width=85mm]{screen_intro.eps}
-\caption{Introductory screen}
+\caption{Morpheus input screen}
 \label{fig:screen_intro}
@@
 
-Initially, the user enters a query of interest, much as one would ask a question.
-When the user submits the query, the query is broken down into constituent parts of who, what when, and where.
-From there, a relevant answer is produced to respond to the requested information.
+Figure \ref{fig:screen_intro} shows the Morpheus input screen, which
+allows a user to ask a question.  The user enters a natural language
+question and the system follows the question answering process outlined
+in this document.
 
@@
 
-After execution, the user is presented with a list of relevant answers and a depiction of how the query was parsed.
+Figure \ref{fig:screen_result} shows the results of answering the question ``A 1997 Toyota Camry V6 needs what size tire?''
+In response to this question, the user is presented with a list of relevant answers and a depiction of how the query was parsed.
 In the above example, the query about tire size was executed and the most relevant result has been returned and displayed.
-Furthermore, the sequence of pages visited during execution are displayed as well.
+Furthermore, the sequence of pages visited during execution is displayed as well.
+
+Categories are assigned to the query's SSQ contexts using the method described in section \ref{sec:terms}. The prior probabilities for a variety of categories
+together with the likelihood and posterior probabilities for the term \emph{Camry}, e.g. $p(Camry | Automobiles)$ and $p(Automobiles | Camry )$, are as
+shown in Table \ref{tab:prob}.
+The QRM used to answer this query is selected based on the SSQ matching
+process described in section \ref{sec:oqom}.
+\begin{table}
+  \begin{tabular}{ | l | l | c | r | }
+    \hline
+    Category & Prior & Likelihood & Posterior \\ \hline
+    Automobiles & 0.59 & 3.48e-05 & 0.96 \\ 
+    Motorcycles & 0.13 & 2.26e-06 & 0.01 \\
+    Internet search engines & 0.16 & 6.29e-07 & 0.004 \\ 
+    Lists of countries & 0.06 & 1.50e-06 & 0.01 \\
+    Tires & 0.05 & 3.60e-06 & 0.02 \\
+    \hline
+  \end{tabular}
+\caption{Term/Category Probabilities}
+\label{tab:prob}
+\end{table}
 

### 2010-03-05 trunk/paper/semsearch10/content/example.tex
final update before ....

@@
-The end-user employs the Morpheus question-answering system much like a
-search engine with a natural-language interface. One can type a question
-in a text box and receive a response from the system. Those questions
-dealing with an ontological realm familiar to the system, whose form is
-similar to previously answered queries in that realm, and that can be
-answered using (possibly deep web) information from a source the system
-has encountered can yield relevant responses.
+%jnw
 
-\begin{figure}
-\caption{Typical Morpheus interaction}
-\label{fig:screenshot}
-\end{figure}
+The end-user employs the Morpheus question-answering system much like a search engine with a natural-language interface.
+One can type a question in a text box and receive a response from the system.
+The system uses previously answered queries to answer new questions.
+The reused questions have a similar form and the same ontological realm, and employ sources that will yield relevant solutions.
+We focus our reuse on the sources that are hidden behind web forms, or the \emph{deep web}.
 
-Figure \ref{fig:screenshot} shows a screenshot of a typical Morpheus
-interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
-received a response together with information describing assumptions
-about the question, the likely relevance of the answer provided,
+Suppose the user poses the question ``A 1997 Toyota Camry V6 needs what size tires?'' The answer (205-65-15) will be presented, together with information describing assumptions about the question, the likely relevance of the answer provided,
 the source of information, and the method of answer production.
 
-Each answer to a question is created using a {\it query response
+Each answer to a question is created using a \emph{query response
   method} (QRM). A QRM is constructed when a special user, known as a
-{\it guide} answers a question using an instrumented web browser (the
-{\it query response recorder} or QRR) that records web
+\emph{guide}, answers a question using an instrumented web browser (the
+\emph{query response recorder} or QRR) that records web
 interactions. The system extracts the relevant artifacts of the
 guide's actions and stores them in the QRM. The QRM is characterized
-by a {\it semi-structured query} (SSQ), a schematic representation of
-the information contained in the query, namely the inputs and output
-contexts---the {\it who, what, when,} and {\it where}
-categories---that characterize the question together with an
-appropriately generalized representation of the guide's browser
-interactions.  The {\it query response evaluator} (QRE) evaluates a
+by a \emph{semi-structured query} (SSQ), a schematic representation of
+the information contained in the natural language question, namely the input and output
+contexts---the \emph{who, what, when,} and \emph{where}
+categories---that characterize the question.  In addition, the QRR has categorized a generalized representation of the guide's browser
+interactions.  The \emph{query response evaluator} (QRE) evaluates a
 query by binding specific arguments to its input parameters and

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
final update before ....

--- 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
@@
 
-Because each QRM may be treated as a function, we plan on leveraging
+Because each QRM may be treated as a function, we plan to use
 previous work to allow new questions to be solved by connecting
@@
 
-Currently, the category heterarchy generated from the DBpedia
-categories and our SSQ ontologies is stored in separate XML files. We
-are in the process of moving these ontologies into an efficient
-ontology database. Similarly, employing user input brings about the
+Employing user input brings about the
 likelihood that redundant SSQ ontological elements will be inserted
@@
 structural information so that we can remove the redundancy in the
-database.
+database.  Currently, the category heterarchy generated from the DBpedia
+categories and our SSQ ontologies is stored in separate XML files. We
+are in the process of moving these ontologies into an efficient
+ontology database.
 
-We cannot rely on the DBpedia categories and the associated Wikipedia
-pages to provide corpora for all our realms.  The DBpedia categories
+The DBpedia categories
 and the associated Wikipedia documents are insufficient to
@@
 simply finding n-gram frequency within the related Wikipedia
-documents. We are investigating methods to identify categories within
-the deep web and to find new sources to construct \textit{weak} realms
-in our ontology hierarchy.
-
-%% I may have misstated the statistics that are unique/repeats
-% need to clarify the statistics 
-%% Add language about how we 
-Researchers have stated that somewhere from 39 to 63 percent of web
-queries are unique \cite{1277770,331405,621942}.  We believe that a
-large percentage of the stated unique queries are in-fact related and
-parameterizable, meaning, several subsets of unique queries may be all
-related and may be answered using a single QRM.  It is difficult to
-discover this property between queries.  Previous work suggest
-techniques to find related queries but it will take new efficient
-methods to discover parameterizable queries.
+documents.
 
@@
 answering system that uses previously answered user questions.  We
-described our method of modeling a users question answering process
+described our method of modeling a user's question answering process
 and how we are able to discover semantically similar queries.
+The Morpheus system provides many opportunities for optimization.
+However, we believe this new technique for question answering system will improve the exploration experience.
 
-\section{Acknowledgements}
+\section{Acknowledgments}
+Our thanks to Guillermo Cordero, and Nick Antonelli for their assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.

### 2010-06-20 trunk/paper/IIWAS2010/content/related_work.tex
Initial draft

\section{Related Work}

1. QA systems 
2. Ontology generators 
3. NLP interfaces

### 2010-06-20 paper/IIWAS2010/content/results_discussion.tex
Initial draft

\section{Results}

% 3-4 queries 
% Human made ontology 
% Topic Models

\subsection{Discussion}

% 2. Current stage of the project 
% 3. Expected contribution to the topics of interest supported by iiWAS2010

### 2010-06-20 paper/IIWAS2010/content/system_arch.tex
Initial draft

\section{System Architecure}

SSQ % Both

\subsection{Query Processing}

  \subsubsection{QRR} % Guide user

  \subsubsection{NLP interface} % Regular usr

\subsection{Query Matching}

\subsection{Quer Resolution Methods}

### 2010-06-20 paper/IIWAS2010/content/introduction.tex
Structural changes

--- 2010-03-04 trunk/paper/semsearch10/content/introduction.tex
@@
 \section{Introduction}
-% Christan
-When traveling though a jungle to a destination, it is easy to get lost.
-The first person to go somewhere may make a number of mistakes in trying to find the best path to their destination.
-However, those who come later will find it easy to reach that destination if a well-marked trail has been created.
-Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-Rather than treating a user's search as a unique entity and working without an example context, one can exploit the fact that a similar search may have been performed already.
-In one study, almost 40 percent of all queries were found to be repetitions of previous queries\cite{1277770}.
-This indicates the reuse of prior searches is a way to optimize the search process.
-We have built a prototype system for answering questions using deep-web sources that employs previously answered questions to obtain new answers.
-Using our analogy, the Morpheus question answering system follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+
+4. Motivation
+
+1. What are we proposing?
+
+2. Challenges
+
+  2.1 User query processing
+
+  2.1 Need of an ontology
+
+3. Realm based question answering
+
+3. About the paper structure
+
+When traveling though a jungle to a destination, it is easy to get
+lost.  The first person to go somewhere may make a number of mistakes
+in trying to find the best path to their destination.  However, those
+who come later will find it easy to reach that destination if a
+well-marked trail has been created. Olsen and Malizia describe this
+idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
+a user's search as a unique entity and working without an example
+context, one can exploit the fact that a similar search may have been
+performed already.  In one study, almost 40 percent of all queries
+were found to be repetitions of previous queries\cite{1277770}. This
+indicates the reuse of prior searches is a way to optimize the search
+process.
+Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer a user query.
+Using our analogy, the Morpheus question answering system follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take
+followers to similar destinations.
+
+The Morpheus system employs two types of users. One type is called a
+\textit{guide user} who \textit{types} queries in the Morpheus web interface and
+searches for an answer to the query in an instrumented web browser that can
+track answer pathways for a given query. This web tracking tool stores the query
+and necessary information to revisit the pathways to the page where he or she
+finds the answer. It also provides users a mechanism to highlight the answers.
+The other type is a \textit{regular user}, who uses the Morpheus system much
+like a regular search engine with a natural language interface. He can type a
+question in a text box and receive a response from the system. The system
+exploits previously answered queries to answer new questions.
+
+To exploit the prior searches one should represent queries in an elegant way so
+that similar queries can be found efficiently and their stored search path
+revisited to produce answer to the user.
+Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
+It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}.
+A category represents a \textit{topic} or \textit{class} that a term belongs.
+For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
+Morpheus assumes categories are come from a realm-based ontology and it defines  a similarity measure for categories based on the heterarchical structure of  category ontology.
+When a new user query comes the Morpheus system ranks the queries that are in the SSQ fomat based on the catgeory similarity.
+
+This paper starts with disussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
+In the section system architecture, we explain the Morpheus system and its implementations details.
+In the results section, we describe the available results and its interpretations.
+Finally, we concludes the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.

### 2010-06-20 trunk/paper/IIWAS2010/content/abstract.tex
Structural changes

\begin{abstract}

The Morpheus question answering system uses deep web search to answer user queries. Queries are represented by a semi-structured format that contains query terms and referenced classes within specific ontology. Morpheus answers questions by using methods stored in prior successful searches answering similar queries. We rank stored methods based on a similarity measure defined on assigned classes of queries. This measure depends on class heterarchy in a realm-based ontology and the associated text corpora. Finally, we revisit the prior search pathways of the top ranked SSQs to construct possible answers. This paper describes this entire process with emphasis on the matching of user queries to stored answering methods. In addition, the realm-based ontologies are created using the Wikipedia pages, associated categories, and the synset heterarchy of WordNet. Moreover, this paper discusses methods to improve generation of an ontology and the associated corpora using methods such as document categorization and other linguistic techniques.

\end{abstract}

### 2010-06-20 paper/IIWAS2010/content/system_arch.tex

@@
 \section{System Architecure}
+\label{sec:systemarch}
 
-SSQ % Both
+This section presents the core elements of the Morpheus system and its 
+role in the \textit{automated question answering} process.
 
@@
 
-  \subsubsection{QRR} % Guide user
+The \textit{Query Resolution Recorder} or QRR is an instrumented web browser used to
+track the search pathways to an answer for a \textit{guide user's} query. It
+also facilitates guide user to identify output categories. All this information
+is represented in an SSQ as described above.
+For example, suppose, a guide user tries to answer the query "a 1997 Toyota Camry V6 needs what size tires?" using Morpheus.
+With the help of QRR, he may choose relevant query terms and assign categories to them: Toyota as the category manufacturer, Camry V6 as category model, tire as the category automotive parts, and size as the output category size.
+In addition, he can log the search pathways to an answer (e.g.
+P215/60R16) to this query and select the query realm as automotive.
+Morpheus captures all these information in the format of SSQ.
 
-  \subsubsection{NLP interface} % Regular usr
+The \textit{Query Resolution Method} or QRM is a data structure that models the question answering process.
+A QRM is usually constructed by a guide user with the help of the QRR.
+Each QRM contains an ontological realm, an SSQ, and information to support the query answering process.
+QRMs are associated with an ontology that
+has a particular realm i.e. an ontological realm. The associated SSQ contains a
+user query, selected terms and category associations, and output categories for
+a given query. In addition, the QRM contains information required to visit each
+page needed to answer the query as well as the order of visitation. For each
+dyanamic page, it stores the list of inputs to the URL such as form inputs and
+the possible referrence outputs (highlighted portions of the web page).
 
-\subsection{Query Matching}
+A \textit{regular} user query is parsed into specific terms by \textit{NLP engine} using
+some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
+Engine contains user query and parsed terms.
 
-\subsection{Quer Resolution Methods}
+\subsection{Morpheus Ontology and Corpora}
+
+Morpheus requires a realm-based ontology that contains categories of a
+particular realm. For example, for the realm-ontology \textit{Automotive}
+contains categories that are relevant to the \textit{automotive} realm. In
+addition, every category in the ontology is associated with a corpus of words
+that belongs to that category.
+
+For realm ontology construction Morpheus uses the Wikipedia pages, categories, and the WordNet synset heterarchy.
+This approch is motivated from YAGO\cite{Suchanek2009phd}.
+Morpheus creates a realm ontology as follows: For a given realm, we first find a mapping category from the Wikipedia categories  ontology.
+Then we grab all the neighboring categories
+using a concept called a \textit{Markov Blanket} \cite{PRIS} in \textit{Bayesian
+Networks}. In fact, we grab the category's parents, its children, and its 
+children's other parents using the DBpedia ontology properties \textit{broader}
+and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
+of the categories in the blanket till it reaches root.
+Once we have the categories belongs to a particular domain, we associate them with WordNet synset heterarchy using an algorithm similar to YAGO.
+We determine head noun in the category name and search for it in the WordNet synsets\cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the our realm ontology.
+
+In order to build corpus for each of the categories in the ontology, 
+we extract words from the Wikipedia pages those are associated with the 
+the DBpedia categories \cite{Auer07dbpedia:a}. Every corpus is associated 
+with corresponding category in the Morpheus ontology.
+
+\subsection{QRM Ranking Mechanism}
+
+To answer a regular user's queries that is in SSQ format (a \textit{candidate
+SSQ}), Morpheus finds similar SSQs that belong to QRMs in the store (a
+\textit{qualified SSQ}).
+We need a similarity measure to match the candidate SSQ with a qualified SSQ within the Morpheus data store.
+For the SSQ similarity, we consider the SSQ components [\ref{sec:morpheus}] such as query-realm, input terms and output terms, and their assigned categories or classes.
+Thus, Class Divergence, a similarity measure, is defined for these classes based on ontology's class heterarchy.
+It is motivated by the concept of multiple dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for generic function type matches.
+Once we have the similarity measures between the candidate SSQ and qualified SSQs in the QRM data store, we order the relevant SSQs and associated QRMs.
+The order provides a ranking for the results to the user.
+Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe this in detail.
+
+\subsubsection{Class Divergence}
+\label{sec:ctd}
+
+We employ a measure of compatibility, which we call \textit{class divergence},
+between a source class and a target class using the \textit{topological
+structure} of the classes in an ontology. We write $S \prec T$ for the reflexive
+transitive closure of the superclass relation. Let $d(P,Q)$ represent the hop
+distance in the directed ontology inheritance graph from $P$ to $Q$. The
+divergence between a source and target class ranges from zero (for identical
+classes) to one (for incompatible classes). Let $S$ be the source class, $T$ be
+the target class, and let $C$ be a common ancestor class of $S$ and $T$
+minimizing $d(S,C) + d(T,C)$. The class divergence between $S$ and $T$, the
+unnormalized class dissimilarity, is defined given by:
+
+\begin{equation}
+d_{class}(S, T) = \begin{cases}
+0 & S.{Uri} \equiv T.{Uri}\\
+d(S, T)/(3h) & S \prec T\\
+1 & T \prec S\\
+(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/(3h) & otherwise
+\end{cases}
+\end{equation}
+
+\noindent where $h$ is the height of the ontology tree.
+
+Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) <
+d_{class}(S,Q)$, that is, the divergence of a source class to a target
+ancestor class is smaller than the divergence of a source class to any
+class that is not an ancestor. This is an important property in
+determining the compatibility of classes for answering queries.  If a
+SSQ answers queries concerning an ancestor class, it is more relevant
+that a SSQ that answers queries from any non-ancestral class.
+
+% Algorithm 1: figure  
+\begin{figure}[t]
+\centering
+\includegraphics[width=80mm]{img/class_divergence.eps}
+\caption{\textbf{An abbreviated graphical representation of an automotive
+ontology}: This is a manually created ontology, rooted at the class Ontology
+Root, from the Wikipedia category hierarchy and live Wikipedia pages. The arrows
+represent the inheritance relationships between the classes in a topology.}
+\label{fig:class_divergence}
+\end{figure}
+
+Figure \ref{fig:class_divergence} illustrates the calculation of class
+divergence. Suppose we want to find the class divergence
+$d_{class}$\textit{(Automotive
+  Industry, Racing Cars)}. The \textit{Automotive Industry} is the
+subclass of \textit{Automobiles} and \textit{Racing Cars} is the
+subclass of \textit{Auto Racing}, which is a subclass of \textit{Automobiles}. 
+Therefore, the common ancestor for
+these two classes is \textit{Automobiles} ($C$). They share
+the path from \textit{Automobiles} to the ontology root. So, the unnormalized
+divergence \textit{d(Automotive Industry, Ontology Root)} is 32 that is
+calculated from the path to the \textit{Ontology Root} class,
+\textit{d(Automotive Industry,
+Automobiles)} is one
+(dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two
+(dashed arrow). Suppose, the calculated ontology tree height is 294. Thus,
+$d_{class}$\textit{(Automotive Industry, Racing Cars)} is 35, 
+which corresponds to a normalized value of $35/3*294$.
+
+\subsubsection{SSQ Ontology Matching}
+\label{sec:oqom}
+
+We use category divergence to calculate the relevance between the candiate SSQ and a qualified SSQ associated with a QRM in the store.
+Each qualified SSQ will have input terms, output terms, and associated classes, and one realm.
+For the
+candidate SSQ, the relevant category for input terms are determined from the
+ontology corpora.
+From a category term corpus, we can find out the likelihood that a term belongs to a particular category.
+This is determined by the probability of a category given a term using \textit{Bayes Rule} (Eq.
+\ref{eq:bayesrule}), since we can easily obtain the term-category and term-corpus probabilities as relative frequencies.
+The higher the probability, the more likely a term is referring to a category.
+
+\begin{equation}
+\label{eq:bayesrule}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}
+
+The relevance of a qualified SSQ to the candidate SSQ is determined by aggregating the divergence measure of categories associated with them.
+
+\subsection{Query Resolution Methods}
+
+Usually, answering a question using the 
+deep web requires one to navigate through a sequence of one or 
+more web pages. Many of the accesses involve clicks through 
+web forms or links to resulting pages. QRM contains the necessary  
+information required to re-run this procedure. Once we have 
+relevant QRMs through QRM ranking for a given user query, we can  
+get answers by re-running the pathways with help of QRE.

### 2010-06-20 trunk/paper/IIWAS2010/content/introduction.tex
IIWAS 2010 submission: Initial draft

--- 2010-03-04 trunk/paper/semsearch10/content/introduction.tex
@@
 \section{Introduction}
-% Christan
-When traveling though a jungle to a destination, it is easy to get lost.
-The first person to go somewhere may make a number of mistakes in trying to find the best path to their destination.
-However, those who come later will find it easy to reach that destination if a well-marked trail has been created.
-Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-Rather than treating a user's search as a unique entity and working without an example context, one can exploit the fact that a similar search may have been performed already.
-In one study, almost 40 percent of all queries were found to be repetitions of previous queries\cite{1277770}.
-This indicates the reuse of prior searches is a way to optimize the search process.
-We have built a prototype system for answering questions using deep-web sources that employs previously answered questions to obtain new answers.
-Using our analogy, the Morpheus question answering system follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+
+% Outline 
+% ---------------------
+
+% 1. Motivation 
+% 2. What are we proposing?  
+% 3. Challenges
+% 		3.1 User query processing 
+% 		3.1 Need of an ontology 
+% 4. Realm based question answering 
+% 5. About the paper structure
+
+When traveling though a jungle to a destination, it is easy to get
+lost.  The first person to go somewhere may make a number of mistakes
+in trying to find the best path to their destination.  However, those
+who come later will find it easy to reach that destination if a
+well-marked trail has been created. Olsen and Malizia describe this
+idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
+a user's search as a unique entity and working without an example
+context, one can exploit the fact that a similar search may have been
+performed already.  In one study, almost 40 percent of all queries
+were found to be repetitions of previous queries\cite{1277770}. This
+indicates the reuse of prior searches is a way to optimize the search
+process.
+Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer a user query.
+Using our analogy, Morpheus  follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+
+The Morpheus system employs two types of users. One type is called a
+\textit{guide user} who types queries in the Morpheus web interface and
+searches for an answer to the query in an instrumented web browser that can
+track answer pathways for a given query. This web tracking tool stores the query
+and necessary information to revisit the pathways to the page where he or she
+finds the answer. It also provides users a mechanism to highlight the answers.
+The other type is a \textit{regular user}, who uses the Morpheus system much
+like a regular search engine with a natural language interface. He can type a
+question in a text box and receive a response from the system. The system
+exploits previously answered queries to answer new questions.
+
+To exploit the prior searches one should represent queries in an elegant way so
+that similar queries can be found efficiently and their stored search path
+revisited to produce answer to the user.
+Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
+It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}.
+A category represents a \textit{topic} or \textit{class} that a term belongs.
+For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
+
+In addition, Morpheus assumes term categories are come from a \textit{consistent} realm-based ontology.
+By consistency, we mean it has a clean taxonomy of classes in the ontology class heterachy.
+This is important because, our proposed similarity measure for categories is based on the heterarchical structure of category ontology.
+Moreover, when a regular user enters a query, Morpheus ranks SSQs in the store based on this catgeory similarity.
+Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}.
+In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries.
+Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browing \cite{Wu2008}.
+
+This paper starts with disussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
+The section system architecture explains the Morpheus system and its implementations details.
+In the results section, we describe current results and its interpretations.
+Finally, we conclude the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.

### 2010-06-20 trunk/paper/IIWAS2010/content/related_work.tex

@@
 \section{Related Work}
+\label{sec:relatedwork}
 
-1. QA systems 
-2. Ontology generators 
-3. NLP interfaces
+\subsection{Question Ansering Systems}
+
+\subsection{Ontology generators}
+
+An ontology formally models real world \textit{concepts} and their
+relationships. A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and
+language-independent format. The relationships and attributes of an
+ontological concept are defined using \textit{properties} and \textit{property
+restrictions}. An ontology definition contains all of
+these: classes, properties, and restrictions. A class in an ontology can have
+multiple \textit{super classes} and \textit{sub-classes}. Finally, a \textit{knowledge base} represents an ontology together with 
+instances of its classes.
+
+The DBpedia\footnote{http://dbpedia.org} project is based on extracting
+semantic information from the Wikipedia and making it available on the
+Web. Wikipedia semantics includes info-box templates, categorization
+information, images, Geo-coordinates, links to external Web pages,
+disambiguation pages, and redirects between pages in Wiki markup form
+\cite{Auer07dbpedia:a, Bizer2009}.
+
+The extraction procedure is as follows: Wikipedia categories are represented
+using skos:concepts and category relations are represented using skos:broader
+\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
+relation between the Wikipedia categories. The Wikipedia categories are
+extracted directly from Wikipedia pages and there is no quality check on the
+resultant ontology. Similarly, DBpedia uses the info-box attributes and values
+as the ontological relations and its ranges.
+
+YAGO is a partly automatically constructed ontology from Wikipedia and
+WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
+extract information from Wikipedia pages, info-boxes, and categories and to
+combine this information with the WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy.
+Since Wikipedia contains more individuals in the form of Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles are used as the YAGO ontology individuals.
+YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.
+
+In addition, YAGO uses Wikipedia categories as its ontology classes.
+The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
+YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
+The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
+
+Moreover, YAGO type extraction is mainly based on the assumption that
+each Wikipedia page has at least one tagged category, and the assigned Wikipedia
+categories are relevant to that Wikipedia page.
+The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages could be left unassigned i.e., they have no category unintentionally.
+In addition, we cannot completely rely on the relevance of these assigned Wikipedia page categories.
+To overcome these issues, we propose an automatic Wikipedia page categorization or classification and recommendation using a machine learning technique, topic modeling.
+
+\subsection{NLP Interfaces}

### 2010-06-21 trunk/paper/IIWAS2010/content/introduction.tex
small updates to the introduction

@@
 idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
-a user's search as a unique entity and working without an example
+a user's discovery experience as a unique entity and working without an example
 context, one can exploit the fact that a similar search may have been
@@
 process.
-Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer a user query.
+Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
 Using our analogy, Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
 
-The Morpheus system employs two types of users. One type is called a
-\textit{guide user} who types queries in the Morpheus web interface and
-searches for an answer to the query in an instrumented web browser that can
-track answer pathways for a given query. This web tracking tool stores the query
-and necessary information to revisit the pathways to the page where he or she
-finds the answer. It also provides users a mechanism to highlight the answers.
-The other type is a \textit{regular user}, who uses the Morpheus system much
-like a regular search engine with a natural language interface. He can type a
+The Morpheus system employs two types of users.
+The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser.
+This web browser is fitted with a browser plug-in that stores the query and collects information necessary to revisit the pathways to the answer.
+It also allows the user to highlight answers and other metadata.
+The second user, searches the Morpheus system much
+like a typical search engine with a natural language interface. She can type a
 question in a text box and receive a response from the system. The system

### 2010-06-21 paper/IIWAS2010/content/introduction.tex
intro changes

--- 2010-03-04 trunk/paper/semsearch10/content/introduction.tex
@@
 \section{Introduction}
-% Christan
-When traveling though a jungle to a destination, it is easy to get lost.
-The first person to go somewhere may make a number of mistakes in trying to find the best path to their destination.
-However, those who come later will find it easy to reach that destination if a well-marked trail has been created.
-Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
-Rather than treating a user's search as a unique entity and working without an example context, one can exploit the fact that a similar search may have been performed already.
-In one study, almost 40 percent of all queries were found to be repetitions of previous queries\cite{1277770}.
-This indicates the reuse of prior searches is a way to optimize the search process.
-We have built a prototype system for answering questions using deep-web sources that employs previously answered questions to obtain new answers.
-Using our analogy, the Morpheus question answering system follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+
+% Outline 
+% ---------------------
+
+% 1. Motivation 
+% 2. What are we proposing?  
+% 3. Challenges
+% 		3.1 User query processing 
+% 		3.1 Need of an ontology 
+% 4. Realm based question answering 
+% 5. About the paper structure
+
+When traveling though a jungle to a destination, it is easy to get
+lost.  The first person to go somewhere may make a number of mistakes
+in trying to find the best path to their destination.  However, those
+who come later will find it easy to reach that destination if a
+well-marked trail has been created. Olsen and Malizia describe this
+idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
+a user's discovery experience as a unique entity and working without an example
+context, one can exploit the fact that a similar search may have been
+performed already.  In one study, almost 40 percent of all queries
+were found to be repetitions of previous queries\cite{1277770}. This
+indicates the reuse of prior searches is a way to optimize the search
+process.
+Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
+Using our analogy, Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+
+The Morpheus system employs two types of users.
+The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser.
+This web browser is fitted with a browser plug-in that stores the query and collects information necessary to revisit the pathways to the answer.
+It also allows the user to highlight answers and other metadata.
+The second user, searches the Morpheus system much
+like a typical search engine with a natural language interface. She can type a
+question in a text box and receive a response from the system. The system
+exploits previously answered queries to answer new questions.
+
+To exploit the prior searches one should represent queries in an elegant way so
+that similar queries can be found efficiently and their stored search path
+revisited to produce answer to the user.
+Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
+It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}.
+A category represents a \textit{topic} or \textit{class} that a term belongs.
+For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
+
+In addition, Morpheus assumes term categories are come from a \textit{consistent} realm-based ontology.
+By consistency, we mean it has a clean taxonomy of classes in the ontology class heterachy.
+This is important because, our proposed similarity measure for categories is based on the heterarchical structure of category ontology.
+Moreover, when a regular user enters a query, Morpheus ranks SSQs in the store based on this catgeory similarity.
+Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}.
+In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries.
+Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browsing \cite{Wu2008}.
+
+This paper starts with discussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
+The section system architecture explains the Morpheus system and its implementations details.
+In the results section, we describe current results and its interpretations.
+Finally, we conclude the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.

### 2010-06-22 trunk/paper/IIWAS2010/content/system_arch.tex
Modifications to category divergence section.

--- 2010-06-20 paper/IIWAS2010/content/system_arch.tex
@@
 
-The \textit{Query Resolution Recorder} or QRR is an instrumented web browser used to
+The \textit{Query Resolution Recorder} or QRR is an instrumented web browser
+used to
 track the search pathways to an answer for a \textit{guide user's} query. It
 also facilitates guide user to identify output categories. All this information
-is represented in an SSQ as described above.
-For example, suppose, a guide user tries to answer the query "a 1997 Toyota Camry V6 needs what size tires?" using Morpheus.
-With the help of QRR, he may choose relevant query terms and assign categories to them: Toyota as the category manufacturer, Camry V6 as category model, tire as the category automotive parts, and size as the output category size.
-In addition, he can log the search pathways to an answer (e.g.
-P215/60R16) to this query and select the query realm as automotive.
-Morpheus captures all these information in the format of SSQ.
+is represented in an SSQ as described above. For example, suppose, a guide user
+tries to answer the query "a 1997 Toyota Camry V6 needs what size tires?" using
+Morpheus. With the help of QRR, he may choose relevant query terms and assign
+categories to them: Toyota as the category manufacturer, Camry V6 as category
+model, tire as the category automotive parts, and size as the output category
+size. In addition, he can log the search pathways to an answer (e.g. P215/60R16)
+to this query and select the query realm as automotive. Morpheus captures all
+these information in the format of SSQ.
 
-The \textit{Query Resolution Method} or QRM is a data structure that models the question answering process.
-A QRM is usually constructed by a guide user with the help of the QRR.
-Each QRM contains an ontological realm, an SSQ, and information to support the query answering process.
-QRMs are associated with an ontology that
+The \textit{Query Resolution Method} or QRM is a data structure that models the
+question answering process. A QRM is usually constructed by a guide user with
+the help of the QRR. Each QRM contains an ontological realm, an SSQ, and
+information to support the query answering process. QRMs are associated with an
+ontology that
 has a particular realm i.e. an ontological realm. The associated SSQ contains a
@@
 
-A \textit{regular} user query is parsed into specific terms by \textit{NLP engine} using
+A \textit{regular} user query is parsed into specific terms by \textit{NLP
+engine} using
 some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
@@
 
-For realm ontology construction Morpheus uses the Wikipedia pages, categories, and the WordNet synset heterarchy.
-This approch is motivated from YAGO\cite{Suchanek2009phd}.
-Morpheus creates a realm ontology as follows: For a given realm, we first find a mapping category from the Wikipedia categories  ontology.
-Then we grab all the neighboring categories
+For realm ontology construction Morpheus uses the Wikipedia pages, categories,
+and the WordNet synset heterarchy. This approch is motivated from
+YAGO\cite{Suchanek2009phd}. Morpheus creates a realm ontology as follows: For a
+given realm, we first find a mapping category from the Wikipedia categories 
+ontology. Then we grab all the neighboring categories
 using a concept called a \textit{Markov Blanket} \cite{PRIS} in \textit{Bayesian
@@
 and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
-of the categories in the blanket till it reaches root.
-Once we have the categories belongs to a particular domain, we associate them with WordNet synset heterarchy using an algorithm similar to YAGO.
-We determine head noun in the category name and search for it in the WordNet synsets\cite{Suchanek2009phd}.
-Those Wikipedia categories having no WordNet match are ignored in the our realm ontology.
+of the categories in the blanket till it reaches root. Once we have the
+categories belongs to a particular domain, we associate them with WordNet synset
+heterarchy using an algorithm similar to YAGO. We determine head noun in the
+category name and search for it in the WordNet synsets\cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the our realm
+ontology.
 
@@
 SSQ}), Morpheus finds similar SSQs that belong to QRMs in the store (a
-\textit{qualified SSQ}).
-We need a similarity measure to match the candidate SSQ with a qualified SSQ within the Morpheus data store.
-For the SSQ similarity, we consider the SSQ components [\ref{sec:morpheus}] such as query-realm, input terms and output terms, and their assigned categories or classes.
-Thus, Class Divergence, a similarity measure, is defined for these classes based on ontology's class heterarchy.
-It is motivated by the concept of multiple dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for generic function type matches.
-Once we have the similarity measures between the candidate SSQ and qualified SSQs in the QRM data store, we order the relevant SSQs and associated QRMs.
-The order provides a ranking for the results to the user.
-Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe this in detail.
+\textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
+with a qualified SSQ within the Morpheus data store. For the SSQ similarity, we
+consider the SSQ components [\ref{sec:morpheus}] such as query-realm, input
+terms and output terms, and their assigned categories or classes. Thus,
+\textit{category divergence}, a similarity measure, is defined for these classes
+based on ontology's class heterarchy. It is motivated by the concept of multiple
+dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for
+generic function type matches. Once we have the similarity measures between the
+candidate SSQ and qualified SSQs in the QRM data store, we order the relevant
+SSQs and associated QRMs. The order provides a ranking for the results to the
+user. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe this in detail.
 
-\subsubsection{Class Divergence}
+\subsubsection{Catgeory Divergence}
 \label{sec:ctd}
 
-We employ a measure of compatibility, which we call \textit{class divergence},
-between a source class and a target class using the \textit{topological
-structure} of the classes in an ontology. We write $S \prec T$ for the reflexive
-transitive closure of the superclass relation. Let $d(P,Q)$ represent the hop
+We employ a measure of compatibility, which we call \textit{category
+divergence},
+between a source category and a target category using the \textit{topological
+structure} of the categories in an ontology. We write $S \prec T$ for the
+reflexive
+transitive closure of the supercategory relation. Let $d(P,Q)$ represent the hop
 distance in the directed ontology inheritance graph from $P$ to $Q$. The
-divergence between a source and target class ranges from zero (for identical
-classes) to one (for incompatible classes). Let $S$ be the source class, $T$ be
-the target class, and let $C$ be a common ancestor class of $S$ and $T$
-minimizing $d(S,C) + d(T,C)$. The class divergence between $S$ and $T$, the
-unnormalized class dissimilarity, is defined given by:
+divergence between a source and target category ranges from zero (for identical
+categories) to one (for incompatible categories). Let $S$ be the source
+category, $T$ be
+the target category, and let $C$ be a least common ancestor category of $S$ and
+$T$
+minimizing $d(S,C) + d(T,C)$. The category divergence between $S$ and $T$ is
+defined given by:
 
 \begin{equation}
-d_{class}(S, T) = \begin{cases}
+d_{cat}(S, T) = \begin{cases}
 0 & S.{Uri} \equiv T.{Uri}\\
@@
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{class}(S,T) <
-d_{class}(S,Q)$, that is, the divergence of a source class to a target
-ancestor class is smaller than the divergence of a source class to any
-class that is not an ancestor. This is an important property in
-determining the compatibility of classes for answering queries.  If a
-SSQ answers queries concerning an ancestor class, it is more relevant
-that a SSQ that answers queries from any non-ancestral class.
+Note, if $S \prec T$ and $S \not\prec Q$ then $d_{cat}(S,T) <
+d_{cat}(S,Q)$, that is, the divergence of a source category to a target
+ancestor category is smaller than the divergence of a source category to any
+category that is not an ancestor. This is an important property in
+determining the compatibility of category for answering queries.  If a
+SSQ answers queries concerning an ancestor category, it is more relevant
+that a SSQ that answers queries from any non-ancestral category.
 
@@
 \centering
-\includegraphics[width=80mm]{img/class_divergence.eps}
-\caption{\textbf{An abbreviated graphical representation of an automotive
-ontology}: This is a manually created ontology, rooted at the class Ontology
-Root, from the Wikipedia category hierarchy and live Wikipedia pages. The arrows
-represent the inheritance relationships between the classes in a topology.}
-\label{fig:class_divergence}
+\includegraphics[width=90mm]{img/automotive_ontology.eps}
+\caption{An abbreviated graphical representation of an automotive
+ontology: This is a manually created ontology, from the Wikipedia category
+hierarchy and pages. The edges represent inheritance relationships between the
+category in a topology.}
+\label{fig:automotive_ontology}
 \end{figure}
 
-Figure \ref{fig:class_divergence} illustrates the calculation of class
-divergence. Suppose we want to find the class divergence
-$d_{class}$\textit{(Automotive
-  Industry, Racing Cars)}. The \textit{Automotive Industry} is the
-subclass of \textit{Automobiles} and \textit{Racing Cars} is the
-subclass of \textit{Auto Racing}, which is a subclass of \textit{Automobiles}. 
-Therefore, the common ancestor for
-these two classes is \textit{Automobiles} ($C$). They share
-the path from \textit{Automobiles} to the ontology root. So, the unnormalized
-divergence \textit{d(Automotive Industry, Ontology Root)} is 32 that is
-calculated from the path to the \textit{Ontology Root} class,
-\textit{d(Automotive Industry,
-Automobiles)} is one
-(dashed arrow), and \textit{d(Racing Cars, Automobiles)} is two
-(dashed arrow). Suppose, the calculated ontology tree height is 294. Thus,
-$d_{class}$\textit{(Automotive Industry, Racing Cars)} is 35, 
-which corresponds to a normalized value of $35/3*294$.
+Suppose we want to find the category divergence between \textit{Toyota Camry}
+and \textit{Coupes} [Figure \ref{fig:automotive_ontology}]. 
+\textit{Toyota Camry} is the subcategory of \textit{Sedans}, and \textit{Coupes}
+is the subcategory of \textit{Cars}. Therefore, the least common ancestor ($C$)
+for these two categories is \textit{Cars}. In addition, the tree height is $5$.
+So, the normalized divergence $d_{cat}$\textit{(Toyota Camry, Coupes)} is $7/15$
+that is calculated from \textit{d(Toyota Camry, Root)} is 5, \textit{d(Toyota
+Camry, Cars)} is two, and \textit{d(Coupes, Cars)} is one.
 
@@
 
-We use category divergence to calculate the relevance between the candiate SSQ and a qualified SSQ associated with a QRM in the store.
-Each qualified SSQ will have input terms, output terms, and associated classes, and one realm.
-For the
+We use category divergence to calculate the relevance between the candiate SSQ
+and a qualified SSQ associated with a QRM in the store. Each qualified SSQ will
+have input terms, output terms, and associated classes, and one realm. For the
 candidate SSQ, the relevant category for input terms are determined from the
-ontology corpora.
-From a category term corpus, we can find out the likelihood that a term belongs to a particular category.
-This is determined by the probability of a category given a term using \textit{Bayes Rule} (Eq.
-\ref{eq:bayesrule}), since we can easily obtain the term-category and term-corpus probabilities as relative frequencies.
-The higher the probability, the more likely a term is referring to a category.
+ontology corpora. From a category term corpus, we can find out the likelihood
+that a term belongs to a particular category. This is determined by the
+probability of a category given a term using \textit{Bayes Rule} (Eq.
+\ref{eq:bayesrule}), since we can easily obtain the term-category and
+term-corpus probabilities as relative frequencies. The higher the probability,
+the more likely a term is referring to a category.
 
@@
 
-The relevance of a qualified SSQ to the candidate SSQ is determined by aggregating the divergence measure of categories associated with them.
+The relevance of a qualified SSQ to the candidate SSQ is determined by
+aggregating the divergence measure of categories associated with them.
 

### 2010-06-22 paper/IIWAS2010/content/introduction.tex
small changes to intro

@@
 The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser.
-This web browser is fitted with a browser plug-in that stores the query and collects information necessary to revisit the pathways to the answer.
+This web browser is fitted with a browser plug-in that stores query and collects necessary information to revisit the pathways to the query answer.
 It also allows the user to highlight answers and other metadata.
-The second user, searches the Morpheus system much
-like a typical search engine with a natural language interface. She can type a
-question in a text box and receive a response from the system. The system
-exploits previously answered queries to answer new questions.
+The second user type, or \textit{regular user} searches the Morpheus system much like a typical search engine with a natural language interface.
+He or she can type a question in a text box and receive a response from the system.
+In this case, the Morpheus system exploits already answered queries to answer new questions.
 
-To exploit the prior searches one should represent queries in an elegant way so
-that similar queries can be found efficiently and their stored search path
-revisited to produce answer to the user.
+To utilize the prior searches one should represent queries in an elegant way so that similar queries can be found efficiently and their stored search path revisited to generate an answer to the user.
 Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
-It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}.
-A category represents a \textit{topic} or \textit{class} that a term belongs.
+It includes a user query in natural-language format, relevant terms for the query, place holders for the term \textit{categories}.
+A \textit{category} represents a topic or class that a term belongs.
 For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.

### 2010-06-22 trunk/paper/IIWAS2010/content/introduction.tex

--- 2010-06-20 trunk/paper/IIWAS2010/content/introduction.tex
@@
 process.
-Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer a user query.
+Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
 Using our analogy, Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
@@
 The Morpheus system employs two types of users. One type is called a
-\textit{guide user} who types queries in the Morpheus web interface and
+\textit{guide user} who \textit{types} queries in the Morpheus web interface and
 searches for an answer to the query in an instrumented web browser that can
@@
 Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
-It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}.
-A category represents a \textit{topic} or \textit{class} that a term belongs.
+It includes a user query in natural-language format, relevant terms for the query, place holders for the term \textit{categories}.
+A \textit{category} represents a topic or class that a term belongs.
 For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
@@
 In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries.
-Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browing \cite{Wu2008}.
+Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browsing \cite{Wu2008}.
 
-This paper starts with disussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
+This paper starts with discussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
 The section system architecture explains the Morpheus system and its implementations details.

### 2010-06-22 trunk/paper/IIWAS2010/content/introduction.tex
Changes after todays review

@@
 indicates the reuse of prior searches is a way to optimize the search
-process.
-Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
-Using our analogy, Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+process.  Morpheus is a question answering system motivated by reuse of prior
+web search pathways to yield an answer to a user query. Using our analogy,
+Morpheus follows path-finders to their destinations and not only marks the
+trail, but also provides a taxi service to take followers to similar
+destinations.
 
@@
 that similar queries can be found efficiently and their stored search path
-revisited to produce answer to the user.
-Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
-It includes a user query in natural-language format, relevant terms for the query, place holders for the term \textit{categories}.
-A \textit{category} represents a topic or class that a term belongs.
-For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
+revisited to produce answer to the user. Morpheus represents user-query details
+in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It
+includes a user query in natural-language format, relevant terms for the query,
+place holders for the term \textit{categories}. A \textit{category} represents a
+topic or class that a term belongs. For example, the term \textit{tire} can be
+classified into the category \textit{Automotive Parts}.
 
-In addition, Morpheus assumes term categories are come from a \textit{consistent} realm-based ontology.
-By consistency, we mean it has a clean taxonomy of classes in the ontology class heterachy.
-This is important because, our proposed similarity measure for categories is based on the heterarchical structure of category ontology.
-Moreover, when a regular user enters a query, Morpheus ranks SSQs in the store based on this catgeory similarity.
-Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}.
-In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries.
-Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browsing \cite{Wu2008}.
+In addition, Morpheus assumes term categories are come from a
+\textit{consistent} realm-based ontology. By consistency we mean it has two
+properties: (i) singly-rooted heterarchy (acyclic digraph wiyh unique 
+ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
+semantic interpretations. This is important because, our proposed similarity 
+measure for categories is based on the heterarchically
+structured category ontologies. Moreover, when a regular user enters a query,
+Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
+regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}. In
+this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
+and a predecessor of \textit{automobile models} is important, because this will
+help us grouping stored queries. Similarly, a clean ontology-taxonomy can
+improve the recall of such queries by supporting transitivity and other types of
+inference like faceted browsing \cite{Wu2008}.
 
-This paper starts with discussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
-The section system architecture explains the Morpheus system and its implementations details.
-In the results section, we describe current results and its interpretations.
-Finally, we conclude the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.
+[Need a paragraph for wiki page categorization and ontology construction]
+In this paper, we propose an automatic web page categorization or 
+classification and recommendation using a machine learning technique, topic modeling.
+In addition, we also describes how we can use the categorized pages for realm-ontology 
+creation.
+
+This paper starts by discussing state-of-the-art systems in the area of
+question answering, ontology generation, and query ranking. The system
+architecture section explains the Morpheus system and its implementations
+details. In the results section, we describe current results and its
+interpretations. Finally, we conclude the paper by describing the global impacts
+of our approaches in QA systems, WWW page categorization, and ontology
+generators.

### 2010-06-22 trunk/paper/IIWAS2010/content/related_work.tex
Changes after todays review

@@
 An ontology formally models real world \textit{concepts} and their
-relationships. A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and
+relationships. A concept or class in an ontology gives us an abstract and
+simplified view of the world\cite{Gruber1993} in a machine-readable and
 language-independent format. The relationships and attributes of an
@@
 these: classes, properties, and restrictions. A class in an ontology can have
-multiple \textit{super classes} and \textit{sub-classes}. Finally, a \textit{knowledge base} represents an ontology together with 
+multiple \textit{super classes} and \textit{sub-classes}. Finally, a
+\textit{knowledge base} represents an ontology together with 
 instances of its classes.
@@
 \cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
-relation between the Wikipedia categories. The Wikipedia categories are
+relations between the Wikipedia categories. The Wikipedia categories are
 extracted directly from Wikipedia pages and there is no quality check on the
@@
 
-YAGO is a partly automatically constructed ontology from Wikipedia and
+YAGO is a semi-automatically constructed ontology from Wikipedia and
 WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
 extract information from Wikipedia pages, info-boxes, and categories and to
-combine this information with the WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy.
-Since Wikipedia contains more individuals in the form of Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles are used as the YAGO ontology individuals.
-YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.
+combine this information with the WordNet\footnote{http://wordnet.princeton.edu}
+synsets heterarchy. Since Wikipedia contains more individuals in the form of
+Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles
+are used as the YAGO ontology individuals. YAGO concentrates mainly on the
+fields of people, cities, events, and movies\cite{Suchanek2009phd}.
 
-In addition, YAGO uses Wikipedia categories as its ontology classes.
-The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
-YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
-The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}.
-Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
+In addition, YAGO uses Wikipedia categories as its ontology classes. The
+ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym}
+relations of the WordNet synsets. YAGO uses only the nouns from WordNet and
+ignores the WordNet verbs and adjectives. The connection between a WordNet
+synset and a Wikipedia category is achieved by parsing the category names and
+matching the parsed category components with the WordNet
+synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet
+match are ignored in the YAGO ontology.
 
@@
 each Wikipedia page has at least one tagged category, and the assigned Wikipedia
-categories are relevant to that Wikipedia page.
-The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages could be left unassigned i.e., they have no category unintentionally.
-In addition, we cannot completely rely on the relevance of these assigned Wikipedia page categories.
-To overcome these issues, we propose an automatic Wikipedia page categorization or classification and recommendation using a machine learning technique, topic modeling.
+categories are relevant to that Wikipedia page. The Wikipedia page category
+assignments are subjectively assigned by human editors and some Wiki pages are
+unassigned i.e., they have no category. In addition, we cannot completely rely
+on the relevance of these assigned Wikipedia page categories.
 

### 2010-06-22 paper/IIWAS2010/content/introduction.tex
small changes to intro and sys arch

--- 2010-06-21 paper/IIWAS2010/content/introduction.tex
@@
 indicates the reuse of prior searches is a way to optimize the search
-process.
-Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
-Using our analogy, Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+process.  Morpheus is a question answering system motivated by reuse of prior
+web search pathways to yield an answer to a user query. Using our analogy,
+Morpheus follows path-finders to their destinations and not only marks the
+trail, but also provides a taxi service to take followers to similar
+destinations.
 
-The Morpheus system employs two types of users.
-The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser.
-This web browser is fitted with a browser plug-in that stores the query and collects information necessary to revisit the pathways to the answer.
-It also allows the user to highlight answers and other metadata.
-The second user, searches the Morpheus system much
-like a typical search engine with a natural language interface. She can type a
+The Morpheus system employs two types of users. One type is called a
+\textit{guide user} who \textit{types} queries in the Morpheus web interface and
+searches for an answer to the query in an instrumented web browser that can
+track answer pathways for a given query. This web tracking tool stores the query
+and necessary information to revisit the pathways to the page where he or she
+finds the answer. It also provides users a mechanism to highlight the answers.
+The other type is a \textit{regular user}, who uses the Morpheus system much
+like a regular search engine with a natural language interface. He can type a
 question in a text box and receive a response from the system. The system
@@
 that similar queries can be found efficiently and their stored search path
-revisited to produce answer to the user.
-Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}.
-It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}.
-A category represents a \textit{topic} or \textit{class} that a term belongs.
-For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
+revisited to produce answer to the user. Morpheus represents user-query details
+in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It
+includes a user query in natural-language format, relevant terms for the query,
+place holders for the term \textit{categories}. A \textit{category} represents a
+topic or class that a term belongs. For example, the term \textit{tire} can be
+classified into the category \textit{Automotive Parts}.
 
-In addition, Morpheus assumes term categories are come from a \textit{consistent} realm-based ontology.
-By consistency, we mean it has a clean taxonomy of classes in the ontology class heterachy.
-This is important because, our proposed similarity measure for categories is based on the heterarchical structure of category ontology.
-Moreover, when a regular user enters a query, Morpheus ranks SSQs in the store based on this catgeory similarity.
-Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}.
-In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries.
-Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browsing \cite{Wu2008}.
+In addition, Morpheus assumes term categories are come from a
+\textit{consistent} realm-based ontology. By consistency we mean it has two
+properties: (i) singly-rooted heterarchy (acyclic digraph wiyh unique 
+ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
+semantic interpretations. This is important because, our proposed similarity 
+measure for categories is based on the heterarchically
+structured category ontologies. Moreover, when a regular user enters a query,
+Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
+regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
+this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
+and a predecessor of \textit{automobile models} is important, because this will
+help us grouping stored queries. Similarly, a clean ontology-taxonomy can
+improve the recall of such queries by supporting transitivity and other types of
+inference like faceted browsing \cite{Wu2008}.
 
-This paper starts with discussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking.
-The section system architecture explains the Morpheus system and its implementations details.
-In the results section, we describe current results and its interpretations.
-Finally, we conclude the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.
+[Need a paragraph for wiki page categorization and ontology construction]
+In this paper, we propose an automatic web page categorization or 
+classification and recommendation using a machine learning technique, topic modeling.
+In addition, we also describes how we can use the categorized pages for realm-ontology 
+creation.
+
+This paper starts by discussing state-of-the-art systems in the area of
+question answering, ontology generation, and query ranking. The system
+architecture section explains the Morpheus system and its implementations
+details. In the results section, we describe current results and its
+interpretations. Finally, we conclude the paper by describing the global impacts
+of our approaches in QA systems, WWW page categorization, and ontology
+generators.

### 2010-06-22 paper/IIWAS2010/content/system_arch.tex
small changes to intro and sys arch

--- 2010-06-20 paper/IIWAS2010/content/system_arch.tex
@@
 
-  \subsubsection{QRR} % Guide user
+The \textit{Query Resolution Recorder} or QRR is an instrumented web browser
+used to track the search pathways to an answer for a \textit{guide user's} query. It
+also helps the guide user to identify output categories. All this information
+is represented in an SSQ as described above. For example, suppose, a guide user
+tries to answer the query - textit{a 1997 Toyota Camry V6 needs what size tires?}, using
+Morpheus. With the help of the QRR, she may choose relevant query terms and assign
+categories to them: Toyota : manufacturer, Camry V6 : 
+model, tire : automotive parts, and size as the output category
+. In addition, he can log the search pathways to an answer (e.g. P215/60R16)
+to this query and select the query realm as automotive. Morpheus captures all
+this information in the representation of an SSQ.
 
-  \subsubsection{NLP interface} % Regular usr
+The \textit{Query Resolution Method} or QRM is a data structure that models the
+question answering process. A QRM is usually constructed by a guide user with
+the help of the QRR. Each QRM contains an ontological realm, an SSQ, and
+information to support the query answering process. QRMs are associated with an
+ontology that
+has a particular realm i.e. an ontological realm. The associated SSQ contains a
+user query, selected terms and category associations, and output categories for
+a given query. In addition, the QRM contains information required to visit each
+page needed to answer the query as well as the order of visitation. For each
+dyanamic page, it stores the list of inputs to the URL such as form inputs and
+the possible referrence outputs (highlighted portions of the web page).
 
-\subsection{Query Matching}
+% NLP arch. 
+% Joir-dan
 
-\subsection{Quer Resolution Methods}
+A \textit{regular} user query is parsed into specific terms by an \textit{NLP
+engine} using
+some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
+Engine contains user query and parsed terms.
+
+\subsection{Morpheus Ontology and Corpora}
+
+Morpheus requires a realm-based ontology that contains categories of a
+particular realm of interest. For example, the realm-ontology \textit{Automotive}
+contains categories that are relevant to the \textit{automotive} realm. In
+addition, every category in the ontology is associated with a corpus of words
+that belongs to that category.
+
+For ontology construction Morpheus uses the Wikipedia pages, categories,
+and the WordNet synset heterarchy. This approch is motivated from
+YAGO\cite{Suchanek2009phd}. Morpheus creates a realm ontology as follows: For a
+given realm, we first find a mapping category from the Wikipedia categories 
+ontology. Then we grab all the neighboring categories
+using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
+the category's parents, its children, and its 
+children's other parents using the DBpedia ontology properties \textit{broader}
+and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
+of the categories in the blanket till it reaches root. Once we have the
+categories belongs to a particular domain, we associate them with WordNet synsets
+using an algorithm similar to YAGO. We determine head noun in the
+category name and search for it in the WordNet synsets\cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the our realm
+ontology.
+
+In order to build a corpus for each of the categories in the ontology, 
+we extract words from the Wikipedia pages associated with the 
+the DBpedia categories \cite{Auer07dbpedia:a}. Every corpus is associated 
+with corresponding category in the Morpheus ontology.
+
+\subsection{QRM Ranking Mechanism}
+
+To answer a regular user's queriy, a \textit{candidate
+SSQ}, Morpheus finds similar SSQs that belong to QRMs in the store (a
+\textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
+with a qualified SSQ within the Morpheus data store. For the SSQ similarity, we
+consider the SSQ components such as query-realm, input
+terms and output terms, and their assigned categories or classes. The,
+\textit{category divergence} of two categories characteristics their 
+similarity based on an ontology class heterarchy. 
+It is motivated by the concept of multiple
+dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for
+generic function type matches. We order relevant QRMs in the data store 
+in order by descreasing similarity of the candidate SSQ and the QRM's associated SSQ.   
+The order provides a ranking for the results to the
+user. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe this in detail.
+
+\subsubsection{Catgeory Divergence}
+\label{sec:ctd}
+
+We employ a quasimetric, \textit{category
+divergence},
+between a source category and a target category using the \textit{topological
+structure} of the categories in an ontology. We write $S \prec T$ for the
+reflexive
+transitive closure of the supercategory relation. Let $d(P,Q)$ represent the hop
+distance in the directed ontology inheritance graph from $P$ to $Q$. The
+divergence between a source and target category ranges from zero (for identical
+categories) to one (for incompatible categories). Let $S$ be the source
+category, $T$ be
+the target category, and let $C$ be a least common ancestor category of $S$ and
+$T$
+minimizing $d(S,C) + d(T,C)$. The category divergence between $S$ and $T$ is
+defined given by:
+
+\begin{equation}
+d_{cat}(S, T) = \begin{cases}
+0 & S.{Uri} \equiv T.{Uri}\\
+d(S, T)/(3h) & S \prec T\\
+1 & T \prec S\\
+(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/(3h) & otherwise
+\end{cases}
+\end{equation}
+
+\noindent where $h$ is the height of the ontology tree.
+
+Note, if $S \prec T$ and $S \not\prec Q$ then $d_{cat}(S,T) <
+d_{cat}(S,Q)$, that is, the divergence of a source category to a target
+ancestor category is smaller than the divergence of a source category to any
+category that is not an ancestor. This is an important property in
+determining the compatibility of category for answering queries.  If a
+SSQ answers queries concerning an ancestor category, it is more relevant
+that a SSQ that answers queries from any non-ancestral category.
+
+% Algorithm 1: figure  
+\begin{figure}[t]
+\centering
+\includegraphics[width=90mm]{img/automotive_ontology.eps}
+\caption{An abbreviated graphical representation of an automotive
+ontology: This is a manually created ontology, from the Wikipedia category
+hierarchy and pages. The edges represent inheritance relationships between the
+category in a topology.}
+\label{fig:automotive_ontology}
+\end{figure}
+
+Suppose we want to find the category divergence between \textit{Toyota Camry}
+and \textit{Coupes} [Figure \ref{fig:automotive_ontology}]. 
+\textit{Toyota Camry} is the subcategory of \textit{Sedans}, and \textit{Coupes}
+is the subcategory of \textit{Cars}. Therefore, the least common ancestor ($C$)
+for these two categories is \textit{Cars}. In addition, the tree height is $5$.
+So, the normalized divergence $d_{cat}$\textit{(Toyota Camry, Coupes)} is $7/15$
+that is calculated from \textit{d(Toyota Camry, Root)} is 5, \textit{d(Toyota
+Camry, Cars)} is two, and \textit{d(Coupes, Cars)} is one.
+
+\subsubsection{SSQ Ontology Matching}
+\label{sec:oqom}
+
+We use category divergence to calculate the relevance between the candiate SSQ
+and a qualified SSQ associated with a QRM in the store. Each qualified SSQ will
+have input terms, output terms, and associated classes, and one realm. For the
+candidate SSQ, the relevant category for input terms are determined from the
+ontology corpora. From a category term corpus, we can find out the likelihood
+that a term belongs to a particular category. This is determined by the
+probability of a category given a term using \textit{Bayes Rule} (Eq.
+\ref{eq:bayesrule}), since we can easily obtain the term-category and
+term-corpus probabilities as relative frequencies. The higher the probability,
+the more likely a term is referring to a category.
+
+\begin{equation}
+\label{eq:bayesrule}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}
+
+The relevance of a qualified SSQ to the candidate SSQ is determined by
+aggregating the divergence measure of categories associated with them.
+
+\subsection{Query Resolution Methods}
+
+Usually, answering a question using the 
+deep web requires one to navigate through a sequence of one or 
+more web pages. Many of the accesses involve clicks through 
+web forms or links to resulting pages. QRM contains the necessary  
+information required to re-run this procedure. Once we have 
+relevant QRMs through QRM ranking for a given user query, we can  
+get answers by re-running the pathways with help of QRE.

### 2010-06-23 paper/IIWAS2010/content/introduction.tex
Added QA related work section

@@
 \textit{consistent} realm-based ontology. By consistency we mean it has two
-properties: (i) singly-rooted heterarchy (acyclic digraph wiyh unique 
+properties: (i) singly-rooted heterarchy (acyclic digraph with unique 
 ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 

### 2010-06-23 paper/IIWAS2010/content/related_work.tex
Added QA related work section

--- 2010-06-22 trunk/paper/IIWAS2010/content/related_work.tex
@@
 \subsection{Question Ansering Systems}
+
+Question Answering (QA) is an old field and there has been a recent influx of QA work.
+The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.
+Closed domain QA systems are those in which the possible meanings of the questions given are finite.
+We define closed corpus sytems as those in which the sources used to answer questions are finite.
+QA systems that treat the web as a document collection is considered an open corpus system.
+The morpheus system is considered an open corpus system.
+It goes beyond current state of the art QA systems by examining deep web sources.
+
+Several community QA systems have been developed, one of the most popular being Yahoo!
+Answers \cite{yahooanswers2008}.
+These sites enlist a community of users to answer question posed by other users.
+This idea has evolved to invent socially integrated QA systems have emerged such as Aardvark \cite{vark2010}.
+In addition to having questions answered by users, aardvark is able to contact potential answers through several mediums beyond its webpage (e.g.
+instant message, mobile phone).
+This allows for a possibly faster answers to questions.
+The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.
 

### 2010-06-23 paper/IIWAS2010/content/system_arch.tex
updates to sys arch

@@
 \subsection{Query Processing}
+\label{sec:query_processing}
 
-The \textit{Query Resolution Recorder} or QRR is an instrumented web browser
+The \emph{Query Resolution Recorder} or QRR is an instrumented web browser
 used to track the search pathways to an answer for a \textit{guide user's} query. It
-also helps the guide user to identify output categories. All this information
-is represented in an SSQ as described above. For example, suppose, a guide user
-tries to answer the query - textit{a 1997 Toyota Camry V6 needs what size tires?}, using
+also helps the guide user to identify categories (optional) for the query terms. 
+Morpheus has two types of categories: \emph{intput categories} and \emph{output categories}.
+Input categories annotates the query terms into a class or category, which are 
+useful in finding similar queries. On the other hand, output categories give hints
+to the expected answer of a user query. Morpheus captures all
+this query information in the representation of an SSQ. For example, suppose, a guide user
+tries to answer the query ``A 1997 Toyota Camry V6 needs what size tires?'', using
 Morpheus. With the help of the QRR, she may choose relevant query terms and assign
-categories to them: Toyota : manufacturer, Camry V6 : 
-model, tire : automotive parts, and size as the output category
-. In addition, he can log the search pathways to an answer (e.g. P215/60R16)
-to this query and select the query realm as automotive. Morpheus captures all
-this information in the representation of an SSQ.
+\emph{input categories} to them: Toyota : manufacturer, Camry V6 : 
+model, tire : automotive parts, and size as the \emph{output category}. 
+In addition, she can log the search pathways to an answer (e.g. P215/60R16)
+to this query and select the query \emph{realm} as automotive.
 
-The \textit{Query Resolution Method} or QRM is a data structure that models the
-question answering process. A QRM is usually constructed by a guide user with
-the help of the QRR. Each QRM contains an ontological realm, an SSQ, and
+The \emph{Query Resolution Method} or QRM is a data structure that models the
+question answering process. A QRM is usually constructed by a \emph{guide user} with
+the help of the QRR. Each QRM contains an \emph{ontological realm}, an SSQ, and
 information to support the query answering process. QRMs are associated with an
-ontology that
-has a particular realm i.e. an ontological realm. The associated SSQ contains a
-user query, selected terms and category associations, and output categories for
-a given query. In addition, the QRM contains information required to visit each
-page needed to answer the query as well as the order of visitation. For each
+ontology that has a particular realm i.e. an ontological realm. In addition, 
+the QRM contains information required to visit each page needed to 
+answer the query as well as the order of visitation. For each
 dyanamic page, it stores the list of inputs to the URL such as form inputs and
@@
 
-A \textit{regular} user query is parsed into specific terms by an \textit{NLP
-engine} using
-some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
+A \textit{regular user} query is parsed into specific terms by an \textit{NLP
+engine} using some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
 Engine contains user query and parsed terms.
@@
 \subsection{Morpheus Ontology and Corpora} 
+\label{sec:ontology_corpora}
 
@@
 contains categories that are relevant to the \textit{automotive} realm. In
-addition, every category in the ontology is associated with a corpus of words
+addition, every leaf node in the category ontology is associated with a corpus of words
 that belongs to that category.
@@
 and the WordNet synset heterarchy. This approch is motivated from
-YAGO\cite{Suchanek2009phd}. Morpheus creates a realm ontology as follows: For a
-given realm, we first find a mapping category from the Wikipedia categories 
-ontology. Then we grab all the neighboring categories
+YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
+from the DBpedia categories\cite{Auer07dbpedia:a} (these are extracted from 
+the Wikipedia pages). Then we grab all the neighboring categories
 using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
@@
 categories belongs to a particular domain, we associate them with WordNet synsets
-using an algorithm similar to YAGO. We determine head noun in the
-category name and search for it in the WordNet synsets\cite{Suchanek2009phd}.
+using an algorithm similar to YAGO\cite{Suchanek2009phd}. We determine head noun in the
+category name and search for it in the WordNet synsets.
 Those Wikipedia categories having no WordNet match are ignored in the our realm
-ontology.
+ontology. In fact we uses the WordNet synset heterarchy as the backbone of the   
+realm ontology.
 
-In order to build a corpus for each of the categories in the ontology, 
-we extract words from the Wikipedia pages associated with the 
-the DBpedia categories \cite{Auer07dbpedia:a}. Every corpus is associated 
-with corresponding category in the Morpheus ontology.
+To build a corpus for each of the leaf nodes in the ontology, 
+we extract \emph{n-grams} or \emph{terms} from the Wikipedia pages associated with the 
+the DBpedia categories \cite{Auer07dbpedia:a}. From this category-term corpora, 
+we can find out the likelihood that a term belongs to a particular category, 
+which is useful in categorizing the terms in a \emph{regular user's} query [section \ref{sec:qrm_ranking}].    
+This likelihood is determined by the probability of a category given a term 
+using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
+easily obtain the term-category and term-corpus probabilities as 
+relative frequencies. The higher the probability, the more likely a 
+term is referring to a category.
+
+\begin{equation}
+\label{eq:bayesrule}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}
+
+\subsection{Topic Models and Dcoument Classification }
+\label{sec:topicmodels}
 
 \subsection{QRM Ranking Mechanism} 
+\label{sec:qrm_ranking}
 
-To answer a regular user's queriy, a \textit{candidate
-SSQ}, Morpheus finds similar SSQs that belong to QRMs in the store (a
+To answer a regular user's query, a \textit{candidate
+SSQ}, Morpheus finds similar SSQs that belong to QRMs the Morpheus data store (a
 \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
-with a qualified SSQ within the Morpheus data store. For the SSQ similarity, we
+with a qualified SSQ. For the SSQ similarity, we
 consider the SSQ components such as query-realm, input
@@
 dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for
-generic function type matches. We order relevant QRMs in the data store 
-in order by descreasing similarity of the candidate SSQ and the QRM's associated SSQ.   
-The order provides a ranking for the results to the
-user. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe this in detail.
+generic function type matches.
+
+We use \emph{category divergence} to calculate the relevance between the candiate SSQ
+and a qualified SSQ. Each qualified SSQ will
+have input terms, output terms, and associated classes, and one realm. For the
+candidate SSQ, the relevant category for input terms are determined from the
+ontology corpora [section \ref{sec:ontology_corpora}]. The relevance 
+of a qualified SSQ to the candidate SSQ is determined by
+aggregating the divergence measure of categories associated with them. In addition, 
+We order QRMs in the data store in order by descreasing relevance. 
+The order provides a ranking for the results to the user. 
+The following subsection \ref{sec:ctd} describe \emph{category divergence} in detail.
 
@@
 
-\subsubsection{SSQ Ontology Matching}
-\label{sec:oqom}
-
-We use category divergence to calculate the relevance between the candiate SSQ
-and a qualified SSQ associated with a QRM in the store. Each qualified SSQ will
-have input terms, output terms, and associated classes, and one realm. For the
-candidate SSQ, the relevant category for input terms are determined from the
-ontology corpora. From a category term corpus, we can find out the likelihood
-that a term belongs to a particular category. This is determined by the
-probability of a category given a term using \textit{Bayes Rule} (Eq.
-\ref{eq:bayesrule}), since we can easily obtain the term-category and
-term-corpus probabilities as relative frequencies. The higher the probability,
-the more likely a term is referring to a category.
-
-\begin{equation}
-\label{eq:bayesrule}
-P (category | term) = \frac{P(term | category) P(category)}{P(term)}
-\end{equation}
-
-The relevance of a qualified SSQ to the candidate SSQ is determined by
-aggregating the divergence measure of categories associated with them.
-
-\subsection{Query Resolution Methods}
+\subsection{Query Resolution Execution}
 
@@
 relevant QRMs through QRM ranking for a given user query, we can  
-get answers by re-running the pathways with help of QRE.
+get answers by re-running the pathways with help of 
+the Query Resolution Engine or QRE of Morpheus.

### 2010-06-25 trunk/paper/IIWAS2010/content/results_discussion.tex
Small updates to the results section

\section{Results}
\label{sec:results}

% 3-4 queries 
% Human made ontology 
% Topic Models

As an initial step we created a man-made realm-ontology for the automotive realm  exploiting the Wikipedia pages, categories, and WordNet synsets. For each of the categories in the realm-ontolgy we built corpora by grabbing the corresponding Wikipedia pages. The following section describes question answering process for a user query ``a 1997 Toyota Camry V6 needs what size tires?''.

The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora. The table \ref{tbl:term_categories} shows top categories and their probabilities for each of the query term:

\begin{table}[h]\footnotesize

\begin{tabular}{l | l | r}
Term & Category & $P(Category|Term)$ \\
\hline
1997 & Sedans & 4.04e-09\\
1997 Toyota & Engines & 7.90e-14\\
Toyota  & Sedans & 3.48e-08\\
Toyota Camry & Sedans & 1.20e-10\\
Toyota Camry V6 & Coupes & 1.38e-13\\
Camry & Sedans & 3.12e-09\\
Camry V6 & Coupes & 1.38e-13\\
V6 & Sedans & 4.46e-08\\
\hline
\end{tabular}

\caption{Terms' top categories and probabilities}
\label{tbl:term_categories}

\end{table}

\subsection{Discussion}

% 2. Current stage of the project 
% 3. Expected contribution to the topics of interest supported by iiWAS2010

### 2010-06-25 trunk/paper/IIWAS2010/content/system_arch.tex
changes to introduction-ontology generation, category divergence, and results

@@
 \subsection{Query Processing}
+\label{sec:query_processing}
 
-The \textit{Query Resolution Recorder} or QRR is an instrumented web browser
-used to
-track the search pathways to an answer for a \textit{guide user's} query. It
-also facilitates guide user to identify output categories. All this information
-is represented in an SSQ as described above. For example, suppose, a guide user
-tries to answer the query "a 1997 Toyota Camry V6 needs what size tires?" using
-Morpheus. With the help of QRR, he may choose relevant query terms and assign
-categories to them: Toyota as the category manufacturer, Camry V6 as category
-model, tire as the category automotive parts, and size as the output category
-size. In addition, he can log the search pathways to an answer (e.g. P215/60R16)
-to this query and select the query realm as automotive. Morpheus captures all
-these information in the format of SSQ.
+The \emph{Query Resolution Recorder} or QRR is an instrumented web browser
+used to track the search pathways to an answer for a \textit{guide user's} query. It
+also helps the guide user to identify categories (optional) for the query terms. 
+Morpheus has two types of categories: \emph{intput categories} and \emph{output categories}.
+Input categories annotates the query terms into a class or category, which are 
+useful in finding similar queries. On the other hand, output categories give hints
+to the expected answer of a user query. Morpheus captures all
+this query information in the representation of an SSQ. For example, suppose, a guide user
+tries to answer the query ``A 1997 Toyota Camry V6 needs what size tires?'', using
+Morpheus. With the help of the QRR, she may choose relevant query terms and assign
+\emph{input categories} to them: Toyota : manufacturer, Camry V6 : 
+model, tire : automotive parts, and size as the \emph{output category}. 
+In addition, she can log the search pathways to an answer (e.g. P215/60R16)
+to this query and select the query \emph{realm} as automotive.
 
-The \textit{Query Resolution Method} or QRM is a data structure that models the
-question answering process. A QRM is usually constructed by a guide user with
-the help of the QRR. Each QRM contains an ontological realm, an SSQ, and
+The \emph{Query Resolution Method} or QRM is a data structure that models the
+question answering process. A QRM is usually constructed by a \emph{guide user} with
+the help of the QRR. Each QRM contains an \emph{ontological realm}, an SSQ, and
 information to support the query answering process. QRMs are associated with an
-ontology that
-has a particular realm i.e. an ontological realm. The associated SSQ contains a
-user query, selected terms and category associations, and output categories for
-a given query. In addition, the QRM contains information required to visit each
-page needed to answer the query as well as the order of visitation. For each
+ontology that has a particular realm i.e. an ontological realm. In addition, 
+the QRM contains information required to visit each page needed to 
+answer the query as well as the order of visitation. For each
 dyanamic page, it stores the list of inputs to the URL such as form inputs and
@@
 
-A \textit{regular} user query is parsed into specific terms by \textit{NLP
-engine} using
-some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
+% NLP arch. 
+% Joir-dan
+
+A \textit{regular user} query is parsed into specific terms by an \textit{NLP
+engine} using some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
 Engine contains user query and parsed terms.
@@
 \subsection{Morpheus Ontology and Corpora} 
+\label{sec:ontology_corpora}
 
 Morpheus requires a realm-based ontology that contains categories of a
-particular realm. For example, for the realm-ontology \textit{Automotive}
+particular realm of interest. For example, the realm-ontology \textit{Automotive}
 contains categories that are relevant to the \textit{automotive} realm. In
-addition, every category in the ontology is associated with a corpus of words
+addition, every leaf node in the category ontology is associated with a corpus of words
 that belongs to that category.
 
-For realm ontology construction Morpheus uses the Wikipedia pages, categories,
+For ontology construction Morpheus uses the Wikipedia pages, categories,
 and the WordNet synset heterarchy. This approch is motivated from
-YAGO\cite{Suchanek2009phd}. Morpheus creates a realm ontology as follows: For a
-given realm, we first find a mapping category from the Wikipedia categories 
-ontology. Then we grab all the neighboring categories
-using a concept called a \textit{Markov Blanket} \cite{PRIS} in \textit{Bayesian
-Networks}. In fact, we grab the category's parents, its children, and its 
+YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
+from the DBpedia categories\cite{Auer07dbpedia:a} (these are extracted from 
+the Wikipedia pages). Then we grab all the neighboring categories
+using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
+the category's parents, its children, and its 
 children's other parents using the DBpedia ontology properties \textit{broader}
@@
 of the categories in the blanket till it reaches root. Once we have the
-categories belongs to a particular domain, we associate them with WordNet synset
-heterarchy using an algorithm similar to YAGO. We determine head noun in the
-category name and search for it in the WordNet synsets\cite{Suchanek2009phd}.
+categories belongs to a particular domain, we associate them with WordNet synsets
+using an algorithm similar to YAGO\cite{Suchanek2009phd}. We determine head noun in the
+category name and search for it in the WordNet synsets.
 Those Wikipedia categories having no WordNet match are ignored in the our realm
-ontology.
+ontology. In fact we uses the WordNet synset heterarchy as the backbone of the   
+realm ontology.
 
-In order to build corpus for each of the categories in the ontology, 
-we extract words from the Wikipedia pages those are associated with the 
-the DBpedia categories \cite{Auer07dbpedia:a}. Every corpus is associated 
-with corresponding category in the Morpheus ontology.
+To build a corpus for each of the leaf nodes in the ontology, 
+we extract \emph{n-grams} or \emph{terms} from the Wikipedia pages associated with the 
+the DBpedia categories \cite{Auer07dbpedia:a}. From this category-term corpora, 
+we can find out the likelihood that a term belongs to a particular category, 
+which is useful in categorizing the terms in a \emph{regular user's} query [section \ref{sec:qrm_ranking}].    
+This likelihood is determined by the probability of a category given a term 
+using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
+easily obtain the term-category and term-corpus probabilities as 
+relative frequencies. The higher the probability, the more likely a 
+term is referring to a category.
+
+\begin{equation}
+\label{eq:bayesrule}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}
 
 \subsection{QRM Ranking Mechanism} 
+\label{sec:qrm_ranking}
 
-To answer a regular user's queries that is in SSQ format (a \textit{candidate
-SSQ}), Morpheus finds similar SSQs that belong to QRMs in the store (a
+To answer a regular user's query, a \textit{candidate
+SSQ}, Morpheus finds similar SSQs that belong to QRMs the Morpheus data store (a
 \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
-with a qualified SSQ within the Morpheus data store. For the SSQ similarity, we
-consider the SSQ components [\ref{sec:morpheus}] such as query-realm, input
-terms and output terms, and their assigned categories or classes. Thus,
-\textit{category divergence}, a similarity measure, is defined for these classes
-based on ontology's class heterarchy. It is motivated by the concept of multiple
+with a qualified SSQ. For the SSQ similarity, we
+consider the SSQ components such as query-realm, input
+terms and output terms, and their assigned categories or classes. The,
+\textit{category divergence} of two categories characteristics their 
+similarity based on an ontology class heterarchy. 
+It is motivated by the concept of multiple
 dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for
-generic function type matches. Once we have the similarity measures between the
-candidate SSQ and qualified SSQs in the QRM data store, we order the relevant
-SSQs and associated QRMs. The order provides a ranking for the results to the
-user. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe this in detail.
+generic function \emph{type} matches.
+
+We consider the category match as a type match and we use \emph{category divergence} 
+to calculate the relevance between the candiate SSQ
+and a qualified SSQ. Each qualified SSQ will
+have input terms, output terms, and associated classes, and one realm. For the
+candidate SSQ, the relevant category for input terms are determined from the
+ontology corpora [section \ref{sec:ontology_corpora}]. The relevance 
+of a qualified SSQ to the candidate SSQ is determined by
+aggregating the divergence measure of categories associated with them. In addition, 
+We order QRMs in the data store in order by descreasing relevance. 
+The order provides a ranking for the results to the user. 
+The following subsection describes \emph{category divergence} in detail.
 
@@
 
-We employ a measure of compatibility, which we call \textit{category
+We employ a quasimetric, \textit{category
 divergence},

### 2010-06-25 paper/IIWAS2010/content/related_work.tex
changes to introduction-ontology generation, category divergence, and results

@@
 \subsection{Ontology generators} 
+\label{sec:ontology_generators}
 
@@
 The DBpedia\footnote{http://dbpedia.org} project is based on extracting 
-semantic information from the Wikipedia and making it available on the
-Web. Wikipedia semantics includes info-box templates, categorization
-information, images, Geo-coordinates, links to external Web pages,
-disambiguation pages, and redirects between pages in Wiki markup form
-\cite{Auer07dbpedia:a, Bizer2009}.
-
-The extraction procedure is as follows: Wikipedia categories are represented
-using skos:concepts and category relations are represented using skos:broader
-\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
-relations between the Wikipedia categories. The Wikipedia categories are
-extracted directly from Wikipedia pages and there is no quality check on the
-resultant ontology. Similarly, DBpedia uses the info-box attributes and values
-as the ontological relations and its ranges.
+semantic information from the Wikipedia and making it available on the Web. 
+Wikipedia semantics includes info-box templates, categorization information, 
+images, Geo-coordinates, links to external Web pages, disambiguation pages, 
+and redirects between pages in Wiki markup form \cite{Auer07dbpedia:a, Bizer2009}. 
+DBpedia represents the Wikipedia categories using skos:concepts and category 
+relations using skos:broader \cite{Auer07dbpedia:a, Bizer2009}. In fact, 
+DBpedia does not define any new relations between the Wikipedia categories. 
+The Wikipedia categories are extracted directly from Wikipedia pages, and there 
+is no quality check on the resultant ontology. Similarly, additional ontological 
+relations in DBpedia are generated from the info-box attributes and their values.
 
@@
 
-Moreover, YAGO type extraction is mainly based on the assumption that
+However, YAGO type extraction is mainly based on the assumption that
 each Wikipedia page has at least one tagged category, and the assigned Wikipedia

### 2010-06-25 paper/IIWAS2010/content/results_discussion.tex
changes to introduction-ontology generation, category divergence, and results

@@
 \section{Results}
+\label{sec:results}
 
@@
 
+As an initial step we created a man-made realm-ontology for the automotive realm
+ exploiting the Wikipedia pages, categories, and WordNet synsets. For each of
+the categories in the realm-ontolgy we built corpora by grabbing the
+corresponding Wikipedia pages. The following section describes question
+answering process for a user query ``a 1997 Toyota Camry V6 needs what size
+tires?''.
+
+The Morpheus NLP engine parses this query into the constructs: WH:what,
+Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
+descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
+Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
+each of the terms, we determined relevant categories (non-increasing order of
+relevance) from the ontology corpora. The table \ref{tbl:term_categories} shows
+top categories and their probabilities for each of the query term:
+
+\begin{table}[h]\footnotesize
+
+\begin{tabular}{l | l | r}
+Term & Category & $P(Category|Term)$ \\
+\hline
+1997 & Sedans & 4.04e-09\\
+1997 Toyota & Engines & 7.90e-14\\
+Toyota  & Sedans & 3.48e-08\\
+Toyota Camry & Sedans & 1.20e-10\\
+Toyota Camry V6 & Coupes & 1.38e-13\\
+Camry & Sedans & 3.12e-09\\
+Camry V6 & Coupes & 1.38e-13\\
+V6 & Sedans & 4.46e-08\\
+\hline
+\end{tabular}
+
+\caption{Terms' top categories and probabilities}
+\label{tbl:term_categories}
+
+\end{table}
+
+We used this top category of each of the terms in the candidate SSQ and
+determined the category divergence with the qualified SSQ categories in the QRM
+store. We assumed that all of them belong to the same realm or domain (but, it
+is different in real time). In the end, we combine the divergence measure and
+ranked QRMs based on the relevance score. The table \ref{tbl:ranked_queries}
+shows the top ranked queries that belong to the QRMs in store for the above
+query.
+
+\begin{table}[h]\footnotesize
+
+\begin{tabular}{l | r}
+Query & Score\\
+\hline
+The tire size of a 1997 Toyota Camry V6 is what? & 0.11\\ 
+\hline
+\end{tabular}
+
+\caption{Top ranked queries and their relevance score}
+\label{tbl:ranked_queries}
+
+\end{table}
+
 \subsection{Discussion}
+This query matching strategy assumes that query terms are available in the
+category corpus. The candidate query's category annotation will fail if the
+query terms are not available in the corpus. We are working on improving this
+approach by using a probabilistic approach as used in the Topic
+Models\cite{Blei2003latentdirichlet}. Similarly, the Morpheus ontology building
+process needs categorized web pages. As explained in section
+\ref{sec:ontology_generators}, the Wikipedia page categories have some
+limitations for this purpose. Without a super vision, the page categorization is
+often a challenging problem, because topics in the pages that belong to a realm
+(e.g. automotive) usually overlap. So we are experimenting the applicability of
+probabilistic topic models into this web page categorization, and automatic
+generation of a realm-ontology based on the topics being extracted.
 

### 2010-06-25 trunk/paper/IIWAS2010/content/related_work.tex
fri meeting comments

@@
 
+Question Answering (QA) is an old field and there has been a recent influx of QA work.
+The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.
+Closed domain QA systems are those in which the possible meanings of the questions given are finite.
+We define closed corpus sytems as those in which the sources used to answer questions are finite.
+QA systems that treat the web as a document collection is considered an open corpus system.
+The morpheus system is considered an open corpus system.
+It goes beyond current state of the art QA systems by examining deep web sources.
+
+Several community QA systems have been developed, one of the most popular being Yahoo!
+Answers \cite{yahooanswers2008}.
+These sites enlist a community of users to answer question posed by other users.
+This idea has evolved to invent socially integrated QA systems have emerged such as Aardvark \cite{vark2010}.
+In addition to having questions answered by users, aardvark is able to contact potential answers through several mediums beyond its webpage (e.g.
+instant message, mobile phone).
+This allows for a possibly faster answers to questions.
+The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.
+
 \subsection{Ontology generators} 
+\label{sec:ontology_generators}
 
@@
 
-\subsection{NLP Interfaces}
+%\subsection{NLP Interfaces}

### 2010-06-25 trunk/paper/IIWAS2010/content/results_discussion.tex
fri meeting comments

@@
 
-As an initial step we created a man-made realm-ontology for the automotive realm  exploiting the Wikipedia pages, categories, and WordNet synsets.
-For each of the categories in the realm-ontolgy we built corpora by grabbing the corresponding Wikipedia pages.
-The following section describes question answering process for a user query ``a 1997 Toyota Camry V6 needs what size tires?''.
+As an initial step we created a man-made realm-ontology for the automotive realm
+ exploiting the Wikipedia pages, categories, and WordNet synsets. For each of
+the categories in the realm-ontolgy we built corpora by grabbing the
+corresponding Wikipedia pages. The following section describes question
+answering process for a user query ``a 1997 Toyota Camry V6 needs what size
+tires?''.
 
-The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires.
-From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6.
-For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora.
-The table \ref{tbl:term_categories} shows top categories and their probabilities for each of the query term:
+The Morpheus NLP engine parses this query into the constructs: WH:what,
+Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
+descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
+Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
+each of the terms, we determined relevant categories (non-increasing order of
+relevance) from the ontology corpora. The table \ref{tbl:term_categories} shows
+top categories and their probabilities for each of the query term:
 
@@
 
-\subsection{Discussion}
+We used this top category of each of the terms in the candidate SSQ and
+determined the category divergence with the qualified SSQ categories in the QRM
+store. We assumed that all of them belong to the same realm or domain (but, it
+is different in real time). In the end, we combine the divergence measure and
+ranked QRMs based on the relevance score. The table \ref{tbl:ranked_queries}
+shows the top ranked queries that belong to the QRMs in store for the above
+query.
+
+\begin{table}[h]\footnotesize
+
+\begin{tabular}{l | r}
+Query & Score\\
+\hline
+The tire size of a 1997 Toyota Camry V6 is what? & 0.11\\ 
+\hline
+\end{tabular}
+
+\caption{Top ranked queries and their relevance score}
+\label{tbl:ranked_queries}
+
+\end{table}
+
+%\subsection{Discussion}
+\section{Conclusion}
+This query matching strategy assumes that query terms are available in the
+category corpus. The candidate query's category annotation will fail if the
+query terms are not available in the corpus. We are working on improving this
+approach by using a probabilistic approach as used in the Topic
+Models\cite{Blei2003latentdirichlet}. Similarly, the Morpheus ontology building
+process needs categorized web pages. As explained in section
+\ref{sec:ontology_generators}, the Wikipedia page categories have some
+limitations for this purpose. Without a super vision, the page categorization is
+often a challenging problem, because topics in the pages that belong to a realm
+(e.g. automotive) usually overlap. So we are experimenting the applicability of
+probabilistic topic models into this web page categorization, and automatic
+generation of a realm-ontology based on the topics being extracted.
 

### 2010-06-25 trunk/dobson/DobsonLibrary/DataAccess/BaseDA.cs
Changes made: ContextClassDA.cs reads classes from morpheus3DB rather than sdb to avoid foreign key violations when saving the data

@@ -91,12 +91,14 @@ namespace DobsonLibrary.DataAccess
         {
             if (paramNames.Length != paramValues.Length) throw new ArgumentException("paramNames and paramValues must have same length");
             NpgsqlCommand command = makeCommand(query);
-
+            string str = "";
             for (int i = 0; i < paramNames.Length; i++)
             {
                 command.Parameters.Add(paramNames[i], paramValues[i]);
+                str += paramNames[i] + " " + paramValues[i] + "\n";
+                   
             }
-            //printQuery(command.CommandText);
+            printQuery(command.CommandText + str);
 
             return command.ExecuteNonQuery();
         }
@@ -159,7 +161,7 @@ namespace DobsonLibrary.DataAccess
                 conn.Close();
         }
 
-        /*prints the query for debuging purposes into the databaseDebug.txt, appending the new query every time
+        /*prints the query for debuging purposes into the databaseDebug.txt, appending the new query every time* */
         protected static void printQuery(string query)
         {
             StreamWriter s = new StreamWriter(debugPath + "\\databaseDebug.txt", true);
@@ -168,7 +170,7 @@ namespace DobsonLibrary.DataAccess
             s.WriteLine();
             s.Close();
         }
-         * */
+         
         protected bool testConnection()
         {
             try

### 2010-06-25 trunk/dobson/DobsonLibrary/DataAccess/ContextClassDA.cs

@@ -11,19 +11,29 @@ namespace DobsonLibrary.DataAccess
     {
         public List<ContextClass> getContextClassList()
         {
-            List<ContextClass> results = new List<ContextClass>();
+            //List<ContextClass> results = new List<ContextClass>();
+            List<ContextClass> results0 = new List<ContextClass>();
 
+            NpgsqlDataReader reader0 = performQuery(SQLQueries.getAllContextClassesMorpheus3DB, DatabaseConnection.DBName.Morpheus3DB);
+            while (reader0.Read() != false)
+            {
+                ContextClass cc = new ContextClass(reader0.GetInt32(0), -1, reader0.GetString(1));
+                results0.Add(cc);
+            }
+            reader0.Close();
+            /*base.DatabaseConnection = new DatabaseConnection(DatabaseConnection.DBName.sdb);
             NpgsqlDataReader reader = performQuery(SQLQueries.getAllContextClassesQuery,DatabaseConnection.DBName.sdb);
-
             while (reader.Read() != false)
             {
                 ContextClass cc = ContextClass.parseClass(reader.GetInt32(0), reader.GetString(1));
-                results.Add(cc);
+                //only add cc if string isn't null
+                if(cc.name != null)
+                    results.Add(cc);
             }
 
-            reader.Close();
+            reader.Close(); */
 
-            return results;
+            return results0;
         }
 
         internal void insertContextClass(ContextClass newclass)

### 2010-06-25 trunk/dobson/DobsonLibrary/Domain/ContextClass.cs

@@ -21,10 +21,17 @@ namespace DobsonLibrary.Domain
 
         internal static ContextClass parseClass(int id, string uri)
         {
+            
             int i = uri.IndexOf("#");
-
-            string c = uri.Substring(i+1);
-
+            string c;
+            //make string c = null if a # isn't found
+            if (i == -1) { c = null; }
+            else
+            {
+                    c = uri.Substring(i + 1);
+            }
+            
+            
             return new ContextClass(id, -1, c);
         }
     }

### 2010-06-25 dobson/DobsonGUI/MainWindow.Designer.cs
Changes made: ContextClassDA.cs reads classes from morpheus3DB rather than sdb to avoid foreign key violations when saving the data

@@ -56,6 +56,7 @@
             this.inCancelToolStripMenuItem = new System.Windows.Forms.ToolStripMenuItem();
             this.outItem = new System.Windows.Forms.ToolStripMenuItem();
             this.outContextMenuDropDown = new System.Windows.Forms.ToolStripComboBox();
+            this.outClassMenuDropDown = new System.Windows.Forms.ToolStripComboBox();
             this.outputDoneToolStripMenuItem = new System.Windows.Forms.ToolStripMenuItem();
             this.outCancelToolStripMenuItem = new System.Windows.Forms.ToolStripMenuItem();
             this.modifierItem = new System.Windows.Forms.ToolStripMenuItem();
@@ -105,7 +106,7 @@
             // optionsToolStripMenuItem
             // 
             this.optionsToolStripMenuItem.Name = "optionsToolStripMenuItem";
-            this.optionsToolStripMenuItem.Size = new System.Drawing.Size(73, 20);
+            this.optionsToolStripMenuItem.Size = new System.Drawing.Size(81, 20);
             this.optionsToolStripMenuItem.Text = "Connection";
             this.optionsToolStripMenuItem.Click += new System.EventHandler(this.optionsToolStripMenuItem_Click);
             // 
@@ -254,7 +255,7 @@
             this.outItem,
             this.modifierItem});
             this.selectionMenu.Name = "selectionMenu";
-            this.selectionMenu.Size = new System.Drawing.Size(122, 70);
+            this.selectionMenu.Size = new System.Drawing.Size(153, 92);
             // 
             // inItem
             // 
@@ -264,7 +265,7 @@
             this.inputDoneToolStripMenuItem,
             this.inCancelToolStripMenuItem});
             this.inItem.Name = "inItem";
-            this.inItem.Size = new System.Drawing.Size(121, 22);
+            this.inItem.Size = new System.Drawing.Size(152, 22);
             this.inItem.Text = "In";
             // 
             // contextMenuDropDown
@@ -272,7 +273,7 @@
             this.contextMenuDropDown.AutoCompleteMode = System.Windows.Forms.AutoCompleteMode.SuggestAppend;
             this.contextMenuDropDown.AutoCompleteSource = System.Windows.Forms.AutoCompleteSource.ListItems;
             this.contextMenuDropDown.Name = "contextMenuDropDown";
-            this.contextMenuDropDown.Size = new System.Drawing.Size(121, 21);
[…]

### 2010-06-25 dobson/DobsonGUI/MainWindow.cs

@@ -184,6 +184,8 @@ namespace DobsonGUI
                 contextClasses.Add(c.name, c);
 
                 classMenuDropDown.Items.Add(c.name);
+
+                outClassMenuDropDown.Items.Add(c.name);
             }
 
         }
@@ -924,9 +926,9 @@ namespace DobsonGUI
 
             }
 
-            if (islink == false && thisPage.baseURL.Contains("www.google.com") && sequenceNumber == 0)
-                throw new Exception("Scraping from google is not supported at this time, please re-run this query " +
-                    "using a different site.");
+            //if (islink == false && thisPage.baseURL.Contains("www.google.com") && sequenceNumber == 0)
+            //    throw new Exception("Scraping from google is not supported at this time, please re-run this query " +
+            //        "using a different site.");
 
             //Insert the page object
 
@@ -1339,8 +1341,8 @@ namespace DobsonGUI
             foreach (Realm realmCheck in allRealms)
             {
 
-                if (realmCheck.realm == realmString)
-                {
+                if (realmCheck.realm == realmString) // TODO: Lowercaps checking to prevent unnecessary duplicates
+                {                                    // I.E. Automotive vs automotive... change this plz!!!
 
                     realmID = realmCheck.realmid;
 
@@ -1512,8 +1514,10 @@ namespace DobsonGUI
 
                 if (e.ElementContext.contextID == -1)
                     bl.insertContext(e.ElementContext);
-
-                Phrase phrase = new Phrase(e.Individual, e.ElementContext.contextID, c.classId);
+                int cls = -1;
+                if (c != null)
+                    cls = c.classId;
+                Phrase phrase = new Phrase(e.Individual, e.ElementContext.contextID, cls);
 
                 PhraseBL PhraseBl = new PhraseBL();
 
@@ -1668,6 +1672,11 @@ namespace DobsonGUI
 
         private void inputDoneToolStripMenuItem_Click(object sender, EventArgs e)
         {
+            if (contextMenuDropDown.Text == "Context")
+            {
+                MessageBox.Show("Please select a context");
+                return;
+            }
             if (classMenuDropDown.Text == "Class")
             {
                 MessageBox.Show("Please select a class");
@@ -1717,22 +1726,38 @@ namespace DobsonGUI
                 return;
             }
 
+            if (outClassMenuDropDown.Text == "Class")
+            {
+                MessageBox.Show("Please select a class");
+                return;
+            }
+
[…]

### 2010-06-25 dobson/DobsonLibrary/DataAccess/SQLQueries.Designer.cs

@@ -1,7 +1,7 @@
 ﻿//------------------------------------------------------------------------------
 // <auto-generated>
 //     This code was generated by a tool.
-//     Runtime Version:2.0.50727.3603
+//     Runtime Version:2.0.50727.4200
 //
 //     Changes to this file may cause incorrect behavior and will be lost if
 //     the code is regenerated.
@@ -71,6 +71,15 @@ namespace DobsonLibrary.DataAccess {
         internal static string getAllAnswersQuery {
             get {
                 return ResourceManager.GetString("getAllAnswersQuery", resourceCulture);
+            }
+        }
+        
+        /// <summary>
+        ///   Looks up a localized string similar to SELECT classid,name FROM class.
+        /// </summary>
+        internal static string getAllContextClassesMorpheus3DB {
+            get {
+                return ResourceManager.GetString("getAllContextClassesMorpheus3DB", resourceCulture);
             }
         }
         

### 2010-06-26 trunk/paper/IIWAS2010/content/abstract.tex
updates from friday meeting

@@
 The Morpheus question answering system uses deep web search to answer user queries.
-Queries are represented by a semi-structured format that contains query terms and referenced classes within specific ontology.
+Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology.
 Morpheus answers questions by using methods stored in prior successful searches answering similar queries.
@@
 This measure depends on class heterarchy in a realm-based ontology and the associated text corpora.
-Finally, we revisit the prior search pathways of the top ranked SSQs to construct possible answers.
-This paper describes this entire process with emphasis on the matching of user queries to stored answering methods.
-In addition, the realm-based ontologies are created using the Wikipedia pages, associated categories, and the synset heterarchy of WordNet.
-Moreover, this paper discusses methods to improve generation of an ontology and the associated corpora using methods such as document categorization and other linguistic techniques.
+Finally, we revisit the prior search pathways of the stored searches to construct possible answers.
+The realm-based ontologies are created using the Wikipedia pages, associated categories, and the synset heterarchy of WordNet.
+This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.
+The paper also discusses methods to improve generation of an ontology and the associated corpora using methods such as document categorization.
 

### 2010-06-26 trunk/paper/IIWAS2010/content/introduction.tex
updates from friday meeting

@@
 
-When traveling though a jungle to a destination, it is easy to get
+When traveling though a jungle to a destination, it is easier to get
 lost.  The first person to go somewhere may make a number of mistakes
@@
 a user's discovery experience as a unique entity and working without an example
-context, one can exploit the fact that a similar search may have been
-performed already.  In one study, almost 40 percent of all queries
+context, one can exploit the fact that a similar search may have already been
+performed.  In one study, almost 40 percent of all queries
 were found to be repetitions of previous queries\cite{1277770}. This
@@
 
-The Morpheus system employs two types of users. One type is called a
-\textit{guide user} who \textit{types} queries in the Morpheus web interface and
+The Morpheus system employs two distinct roles. One type is called a
+\textit{guide} who types queries in the Morpheus web interface and
 searches for an answer to the query in an instrumented web browser that can
 track answer pathways for a given query. This web tracking tool stores the query
-and necessary information to revisit the pathways to the page where he or she
-finds the answer. It also provides users a mechanism to highlight the answers.
-The other type is a \textit{regular user}, who uses the Morpheus system much
-like a regular search engine with a natural language interface. He can type a
+and necessary information to revisit the pathways to the page where the guide 
+found the answer. It also provides a mechanism for guides to highlight the answers.
+The other role is a \textit{user}, who searches with the Morpheus system much
+like a regular search engine, having a natural language interface. The users type a
 question in a text box and receive a response from the system. The system
-exploits previously answered queries to answer new questions.
+exploits previously answered queries to these answer new questions.
 
@@
 that similar queries can be found efficiently and their stored search path
-revisited to produce answer to the user. Morpheus represents user-query details
+revisited to produce the answer to the user. Morpheus represents user-query details
 in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It
@@
 place holders for the term \textit{categories}. A \textit{category} represents a
-topic or class that a term belongs. For example, the term \textit{tire} can be
+topic or class to which a term belongs. For example, the term \textit{tire} can be
 classified into the category \textit{Automotive Parts}.
 
-In addition, Morpheus assumes term categories are come from a
-\textit{consistent} realm-based ontology. By consistency we mean it has two
-properties: (i) singly-rooted heterarchy (acyclic digraph wiyh unique 
+Morpheus assumes the term categories are classes of a
+\textit{consistent} realm-based ontology. By consistant we mean the ontology has two
+properties: (i) singly-rooted heterarchy (acyclic digraph with unique 
 ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
@@
 Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
-regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}. In
+regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
 this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
@@
 
-[Need a paragraph for wiki page categorization and ontology construction]
+[[Need a paragraph for wiki page categorization and ontology construction]]
 In this paper, we propose an automatic web page categorization or 
@@
 This paper starts by discussing state-of-the-art systems in the area of
-question answering, ontology generation, and query ranking. The system
+question answering and ontology generation. The system
 architecture section explains the Morpheus system and its implementations

### 2010-06-26 paper/IIWAS2010/content/related_work.tex
updates from friday meeting

@@
 We define closed corpus sytems as those in which the sources used to answer questions are finite.
-QA systems that treat the web as a document collection is considered an open corpus system.
+QA systems that treat the web as a document collection are open corpus systems.
 The morpheus system is considered an open corpus system.
@@
 These sites enlist a community of users to answer question posed by other users.
-This idea has evolved to invent socially integrated QA systems have emerged such as Aardvark \cite{vark2010}.
-In addition to having questions answered by users, aardvark is able to contact potential answers through several mediums beyond its webpage (e.g.
-instant message, mobile phone).
-This allows for a possibly faster answers to questions.
+This idea has evolved to invent socially integrated QA systems such as Aardvark \cite{vark2010}.
+In addition to having questions answered by users, Aardvark is able to contact potential question answerers through several media beyond webpages (e.g.
+instant messages, mobile phones).
+This allows for possibly faster answers to questions.
 The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.

### 2010-06-26 paper/IIWAS2010/content/related_work.tex
Modifications to ontology generators section: YAGO

@@
 images, Geo-coordinates, links to external Web pages, disambiguation pages, 
-and redirects between pages in Wiki markup form \cite{Auer07dbpedia:a, Bizer2009}. 
+and redirects between pages in Wiki markup form \cite{Bizer2009}. 
 DBpedia represents the Wikipedia categories using skos:concepts and category 
-relations using skos:broader \cite{Auer07dbpedia:a, Bizer2009}. In fact, 
+relations using skos:broader \cite{Bizer2009}. In fact, 
 DBpedia does not define any new relations between the Wikipedia categories. 
@@
 
-YAGO is a semi-automatically constructed ontology from Wikipedia and
-WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
-extract information from Wikipedia pages, info-boxes, and categories and to
-combine this information with the WordNet\footnote{http://wordnet.princeton.edu}
-synsets heterarchy. Since Wikipedia contains more individuals in the form of
-Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles
-are used as the YAGO ontology individuals. YAGO concentrates mainly on the
-fields of people, cities, events, and movies\cite{Suchanek2009phd}.
+YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite{Suchanek2009phd}.
+YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes.
+The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
+YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
+The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 
-In addition, YAGO uses Wikipedia categories as its ontology classes. The
-ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym}
-relations of the WordNet synsets. YAGO uses only the nouns from WordNet and
-ignores the WordNet verbs and adjectives. The connection between a WordNet
-synset and a Wikipedia category is achieved by parsing the category names and
-matching the parsed category components with the WordNet
-synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet
-match are ignored in the YAGO ontology.
-
-However, YAGO type extraction is mainly based on the assumption that
-each Wikipedia page has at least one tagged category, and the assigned Wikipedia
-categories are relevant to that Wikipedia page. The Wikipedia page category
-assignments are subjectively assigned by human editors and some Wiki pages are
-unassigned i.e., they have no category. In addition, we cannot completely rely
-on the relevance of these assigned Wikipedia page categories.
-
-%\subsection{NLP Interfaces}
+However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page.
+The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category.
+In addition, we cannot fully rely on the relevance of these assigned Wikipedia page categories.
+In addition, YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.

### 2010-06-26 paper/IIWAS2010/content/system_arch.tex
Changes after Friday's meeting

@@
 YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
-from the DBpedia categories\cite{Auer07dbpedia:a} (these are extracted from 
-the Wikipedia pages). Then we grab all the neighboring categories
+from the DBpedia categories, which are extracted from 
+the Wikipedia pages\cite{Bizer2009}. Then we grab all the neighboring categories
 using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
@@
 we extract \emph{n-grams} or \emph{terms} from the Wikipedia pages associated with the 
-the DBpedia categories \cite{Auer07dbpedia:a}. From this category-term corpora, 
+the DBpedia categories\cite{Bizer2009}. From this category-term corpora, 
 we can find out the likelihood that a term belongs to a particular category, 
@@
 
-\subsection{Topic Models and Dcoument Classification }
-\label{sec:topicmodels}
-
 \subsection{QRM Ranking Mechanism} 
@@
 It is motivated by the concept of multiple
-dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for
-generic function type matches.
+dispatch in CLOS and Dylan programming for generic function \emph{type} matches.
 
-We use \emph{category divergence} to calculate the relevance between the candiate SSQ
-and a qualified SSQ. Each qualified SSQ will
-have input terms, output terms, and associated classes, and one realm. For the
-candidate SSQ, the relevant category for input terms are determined from the
-ontology corpora [section \ref{sec:ontology_corpora}]. The relevance 
-of a qualified SSQ to the candidate SSQ is determined by
-aggregating the divergence measure of categories associated with them. In addition, 
-We order QRMs in the data store in order by descreasing relevance. 
-The order provides a ranking for the results to the user. 
-The following subsection \ref{sec:ctd} describe \emph{category divergence} in detail.
+We consider the category match as a type match and we use 
+\emph{category divergence} to calculate the relevance between 
+the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
+have input terms, output terms, and associated classes, and one realm. 
+For the candidate SSQ, the relevant category for input terms 
+are determined from the ontology corpora [section \ref{sec:ontology_corpora}]. The relevance of a qualified SSQ to the candidate SSQ is 
+determined by aggregating the divergence measure of categories 
+associated with them. In addition, we order QRMs in the data store 
+by descreasing relevance. The order provides a ranking for the results 
+to the user. The following subsection describes \emph{category divergence} 
+in detail.
 
@@
 We employ a quasimetric, \textit{category
-divergence},
+divergence (cd)},
 between a source category and a target category using the \textit{topological
@@
 divergence between a source and target category ranges from zero (for identical
-categories) to one (for incompatible categories). Let $S$ be the source
+categories) to one (for type incompatible categories). Let $S$ be the source
 category, $T$ be
-the target category, and let $C$ be a least common ancestor category of $S$ and
-$T$
-minimizing $d(S,C) + d(T,C)$. The category divergence between $S$ and $T$ is
-defined given by:
+the target category, and $C$ be a least common ancestor category of $S$ and
+$T$ i.e., one that minimizes $d(S,C) + d(T,C)$. The category divergence between $S$ and $T$ is defined given by:
 
 \begin{equation}
-d_{cat}(S, T) = \begin{cases}
+cd(S, T) = \begin{cases}
 0 & S.{Uri} \equiv T.{Uri}\\
@@
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $d_{cat}(S,T) <
-d_{cat}(S,Q)$, that is, the divergence of a source category to a target
+Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) <
+cd(S,Q)$, that is, the divergence of a source category to a target
 ancestor category is smaller than the divergence of a source category to any
 category that is not an ancestor. This is an important property in
-determining the compatibility of category for answering queries.  If a
+determining the compatibility of categories for answering queries.  If a
 SSQ answers queries concerning an ancestor category, it is more relevant
@@
 \centering
-\includegraphics[width=90mm]{img/automotive_ontology.eps}
-\caption{An abbreviated graphical representation of an automotive
-ontology: This is a manually created ontology, from the Wikipedia category
-hierarchy and pages. The edges represent inheritance relationships between the
-category in a topology.}
+\includegraphics[width=85mm]{img/automotive_ontology.eps}
+\caption{An abbreviated man-made automotive ontology: Arrows represent inheritance relationships between the ontological classes.}
 \label{fig:automotive_ontology}
@@
 
-Suppose we want to find the category divergence between \textit{Toyota Camry}
-and \textit{Coupes} [Figure \ref{fig:automotive_ontology}]. 
-\textit{Toyota Camry} is the subcategory of \textit{Sedans}, and \textit{Coupes}
-is the subcategory of \textit{Cars}. Therefore, the least common ancestor ($C$)
-for these two categories is \textit{Cars}. In addition, the tree height is $5$.
-So, the normalized divergence $d_{cat}$\textit{(Toyota Camry, Coupes)} is $7/15$
-that is calculated from \textit{d(Toyota Camry, Root)} is 5, \textit{d(Toyota
-Camry, Cars)} is two, and \textit{d(Coupes, Cars)} is one.
+Suppose we want to find the category divergence between \textit{Sedans}
+and \textit{Trucks} [Figure \ref{fig:automotive_ontology}]. 
+\textit{Sedans} is the subcategory of \textit{Cars}, and \textit{Trucks}
+is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
+for these two categories is \textit{Automobiles}. In addition, the tree height \textit{h = 4}.
+So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}
+that is calculated from \textit{d(Sedans, Root) = 4}, \textit{d(Sedans, Automobiles) = 2}, and \textit{d(Trucks, Automobiles) = 1}.
 

### 2010-06-28 paper/IIWAS2010/content/system_arch.tex
Changes to the system arch. section

@@
 particular realm of interest. For example, the realm-ontology \textit{Automotive}
-contains categories that are relevant to the \textit{automotive} realm. In
+contains categories that are relevant to the automotive realm. In
 addition, every leaf node in the category ontology is associated with a corpus of words
@@
 YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
-from the DBpedia categories, which are extracted from 
-the Wikipedia pages\cite{Bizer2009}. Then we grab all the neighboring categories
-using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
+from the DBpedia categories\cite{Bizer2009}. Then we grab all the neighboring categories using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
 the category's parents, its children, and its 
@@
 Those Wikipedia categories having no WordNet match are ignored in the our realm
-ontology. In fact we uses the WordNet synset heterarchy as the backbone of the   
-realm ontology.
+ontology. In addition, we uses the WordNet synset heterarchy relationships for building the ontologcial structure.
 
@@
 To answer a regular user's query, a \textit{candidate
-SSQ}, Morpheus finds similar SSQs that belong to QRMs the Morpheus data store (a
-\textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
+SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
 with a qualified SSQ. For the SSQ similarity, we
 consider the SSQ components such as query-realm, input
-terms and output terms, and their assigned categories or classes. The,
+terms and output terms, and their assigned categories or classes [To be changed]. The,
 \textit{category divergence} of two categories characteristics their 
@@
 the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
-have input terms, output terms, and associated classes, and one realm. 
+have input terms, output terms[what do we do with this??], and associated classes, and one realm. 
 For the candidate SSQ, the relevant category for input terms 
-are determined from the ontology corpora [section \ref{sec:ontology_corpora}]. The relevance of a qualified SSQ to the candidate SSQ is 
-determined by aggregating the divergence measure of categories 
+are determined from the ontology corpora [section \ref{sec:ontology_corpora}].
+We match QRMs that belong to the same \emph{realm} of the candidate SSQ.
+The relevance of a qualified SSQ to the candidate SSQ is
+determined by aggregating the divergence measure of input-term-categories 
 associated with them. In addition, we order QRMs in the data store 

### 2010-06-28 paper/IIWAS2010/content/results_discussion.tex
Changes after Friday's meeting

@@
 corresponding Wikipedia pages. The following section describes question
-answering process for a user query ``a 1997 Toyota Camry V6 needs what size
-tires?''.
+answering process for a user query, ``A 1997 Toyota Camry V6 needs what size
+tires?''
 
@@
 each of the terms, we determined relevant categories (non-increasing order of
-relevance) from the ontology corpora. The table \ref{tbl:term_categories} shows
-top categories and their probabilities for each of the query term:
+relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
+the top categories and their probabilities for each of the query term:
 
@@
 \hline
-1997 & Sedans & 4.04e-09\\
+1997 & Sedans & 404132.77e-14\\
 1997 Toyota & Engines & 7.90e-14\\
-Toyota  & Sedans & 3.48e-08\\
-Toyota Camry & Sedans & 1.20e-10\\
-Toyota Camry V6 & Coupes & 1.38e-13\\
-Camry & Sedans & 3.12e-09\\
-Camry V6 & Coupes & 1.38e-13\\
-V6 & Sedans & 4.46e-08\\
+Toyota  & Sedans & 3486670.15e-14\\
+Toyota Camry & Sedans & 12147.23e-14\\
+Toyota Camry V6 & Coupes & 13.80e-14\\
+Camry & Sedans & 312034.20e-14\\
+Camry V6 & Coupes & 13.80e-14\\
+V6 & Sedans & 4464535.40e-14\\
 \hline
@@
 store. We assumed that all of them belong to the same realm or domain (but, it
-is different in real time). In the end, we combine the divergence measure and
-ranked QRMs based on the relevance score. The table \ref{tbl:ranked_queries}
+is different in real time). In the end, we combined the divergence measure and
+ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries}
 shows the top ranked queries that belong to the QRMs in store for the above
@@
 \hline
-The tire size of a 1997 Toyota Camry V6 is what? & 0.11\\ 
+A 1997 Toyota Camry V6 needs what size tires? & 0.91\\ 
+What is the tire size for a 1998 Sienna XLE Van? & 0.72\\ 
+What is the tire size for a 1996 Infiniti I30 Sedan? & 0.88\\ 
 \hline
@@
 
-\caption{Top ranked queries and their relevance score}
+\caption{Top ranked queries and relevance scores}
 \label{tbl:ranked_queries}
@@
 
-\subsection{Discussion}
-This query matching strategy assumes that query terms are available in the
-category corpus. The candidate query's category annotation will fail if the
-query terms are not available in the corpus. We are working on improving this
-approach by using a probabilistic approach as used in the Topic
-Models\cite{Blei2003latentdirichlet}. Similarly, the Morpheus ontology building
+%\subsection{Discussion}
+\section{Conclusion}
+
+In this paper, we proposed a novel question answering method based on a realm-based ontology.
+[How do we calculate relam for a candidate query?
+and NLP].
+This query matching strategy assumes that candidate query terms are available in the category corpus.
+The candidate query's category annotation will fail if the
+query terms are not available in the corpus.
+In addition, classification of a term or n-gram into a category is based on the term frequency distributions in a classified web document.
+We are working on improving this
+approach by using a probabilistic generative approach as used in the Topic
+Models\cite{Blei2003latentdirichlet}.
+
+Similarly, the Morpheus ontology building
 process needs categorized web pages. As explained in section
 \ref{sec:ontology_generators}, the Wikipedia page categories have some
-limitations for this purpose. Without a super vision, the page categorization is
+limitations for this purpose. Without supervision, the page categorization is
 often a challenging problem, because topics in the pages that belong to a realm
-(e.g. automotive) usually overlap. So we are experimenting the applicability of
-probabilistic topic models into this web page categorization, and automatic
+(e.g. automotive) usually overlap. So we are evaluating the applicability of
+probabilistic topic models to web page categorization, and automatic
 generation of a realm-ontology based on the topics being extracted.

### 2010-06-28 trunk/paper/IIWAS2010/content/results_discussion.tex
small space saving change
update to conclusion

--- 2010-06-25 trunk/paper/IIWAS2010/content/results_discussion.tex
@@
 
-As an initial step we created a man-made realm-ontology for the automotive realm  exploiting the Wikipedia pages, categories, and WordNet synsets.
-For each of the categories in the realm-ontolgy we built corpora by grabbing the corresponding Wikipedia pages.
-The following section describes question answering process for a user query ``a 1997 Toyota Camry V6 needs what size tires?''.
+As an initial step we created a man-made realm-ontology for the automotive realm
+ exploiting the Wikipedia pages, categories, and WordNet synsets. For each of
+the categories in the realm-ontolgy we built corpora by grabbing the
+corresponding Wikipedia pages. The following section describes question
+answering process for a user query, ``A 1997 Toyota Camry V6 needs what size
+tires?''
 
-The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires.
-From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6.
-For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora.
-The table \ref{tbl:term_categories} shows top categories and their probabilities for each of the query term:
+The Morpheus NLP engine parses this query into the constructs: WH:what,
+Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
+descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
+Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
+each of the terms, we determined relevant categories (non-increasing order of
+relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
+the top categories and their probabilities for each of the query term:
 
@@
 
-\subsection{Discussion}
+We used this top category of each of the terms in the candidate SSQ and
+determined the category divergence with the qualified SSQ categories in the QRM
+store. We assumed that all of them belong to the same realm or domain (but, it
+is different in real time). In the end, we combined the divergence measure and
+ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries}
+shows the top ranked queries that belong to the QRMs in store for the above
+query.
+
+\begin{table}[h]\footnotesize
+
+\begin{tabular}{l | r}
+Query & Score\\
+\hline
+A 1997 Toyota Camry V6 needs what size tires? & 0.91\\ 
+What is the tire size for a 1998 Sienna XLE Van? & 0.72\\ 
+What is the tire size for a 1996 Infiniti I30 Sedan? & 0.88\\ 
+\hline
+\end{tabular}
+
+\caption{Top ranked queries and relevance scores}
+\label{tbl:ranked_queries}
+
+\end{table}
+
+%\subsection{Discussion}
+\section{Conclusion}
+
+In this paper, we proposed a novel question answering system that uses previously answered user queries to answer similar questions using deep web site.
+The system uses a guide user to annotate answer paths so folowing users can discover answers to complicated questions.
+Each question answer pair is assigned a realm, and new questions are matched to the new question answer pairs.
+[How do we calculate relam for a candidate query?
+and NLP].
+This question matching strategy assumes that candidate query terms are available in the category corpus.
+The candidate query's category annotation will fail if the
+query terms are not available in the corpus.
+In addition, classification of a term or n-gram into a category is based on the term frequency distributions in a classified web document.
+We are working on improving this
+approach by using a probabilistic generative approach as used in the Topic
+Models\cite{Blei2003latentdirichlet}.
+
+Similarly, the Morpheus ontology building
+process needs categorized web pages. As explained in section
+\ref{sec:ontology_generators}, the Wikipedia page categories have some
+limitations for this purpose. Without supervision, the page categorization is
+often a challenging problem, because topics in the pages that belong to a realm
+(e.g. automotive) usually overlap. So we are evaluating the applicability of
+probabilistic topic models to web page categorization, and automatic
+generation of a realm-ontology based on the topics being extracted.
 

### 2010-06-28 trunk/paper/IIWAS2010/content/introduction.tex
changes to introduction

@@
 
-[[Need a paragraph for wiki page categorization and ontology construction]]
-In this paper, we propose an automatic web page categorization or 
-classification and recommendation using a machine learning technique, topic modeling.
-In addition, we also describes how we can use the categorized pages for realm-ontology 
-creation.
-
 This paper starts by discussing state-of-the-art systems in the area of
@@
 interpretations. Finally, we conclude the paper by describing the global impacts
-of our approaches in QA systems, WWW page categorization, and ontology
-generators.
+of our approaches in QA systems.

### 2010-06-28 trunk/paper/IIWAS2010/content/system_arch.tex
changes to sys arch and results

@@
 The \emph{Query Resolution Recorder} or QRR is an instrumented web browser
-used to track the search pathways to an answer for a \textit{guide user's} query. It
-also helps the guide user to identify categories (optional) for the query terms. 
+used to track the search pathways to an answer for a \textit{guide's} query. It
+also helps guide to identify categories (optional) for the query terms. 
 Morpheus has two types of categories: \emph{intput categories} and \emph{output categories}.
@@
 to the expected answer of a user query. Morpheus captures all
-this query information in the representation of an SSQ. For example, suppose, a guide user
+this query information in the representation of an SSQ. For example, suppose, a guide 
 tries to answer the query ``A 1997 Toyota Camry V6 needs what size tires?'', using
-Morpheus. With the help of the QRR, she may choose relevant query terms and assign
+Morpheus. With the help of the QRR, guide may choose relevant query terms and assign
 \emph{input categories} to them: Toyota : manufacturer, Camry V6 : 
 model, tire : automotive parts, and size as the \emph{output category}. 
-In addition, she can log the search pathways to an answer (e.g. P215/60R16)
+In addition, guide can log the search pathways to an answer (e.g. P215/60R16)
 to this query and select the query \emph{realm} as automotive.
@@
 The \emph{Query Resolution Method} or QRM is a data structure that models the
-question answering process. A QRM is usually constructed by a \emph{guide user} with
+question answering process. A QRM is usually constructed by a \emph{guide} with
 the help of the QRR. Each QRM contains an \emph{ontological realm}, an SSQ, and
@@
 
-A \textit{regular user} query is parsed into specific terms by an \textit{NLP
-engine} using some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
-Engine contains user query and parsed terms.
+Rather than working blindly, forming all possible ngrams from the query 
+and running probabilities, it seemed to be a better approach to identify 
+important noun phrases within the query, and work with those. Using our 
+query parser, we proceed to tokenize, parse, and chunk our candidate query, 
+extracting verb groups, answer classes, and descriptive info from each query. 
+In the example query "What is the tire size of a 1997 Toyota Camry?," 
+the verb group is the verb "is," the answer class is "tire size," and descriptive 
+info is "of a 1997 Toyota Camry." The next step is to create ngrams from these chunks. 
+Using these ngrams, we will query our database for frequencies associated with 
+each ngram: overall frequency and categorical frequency, alongside category 
+term count and overall term count, to calculate categorical probabilities 
+and establish a realm for the candidate query, choosing realm with highest probability.
 
@@
 YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
-from the DBpedia categories\cite{Auer07dbpedia:a} (these are extracted from 
-the Wikipedia pages). Then we grab all the neighboring categories
-using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
+from the DBpedia categories\cite{Bizer2009}. Then we grab all the neighboring 
+categories using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
 the category's parents, its children, and its 
@@
 
+Alternately, we are evaluating Latent Dirichlet Allocation (LDA), a probabilistic graphic model, for
+representing latent topics of the documents in a text corpus\cite{Blei2003latentdirichlet}.
+Due to its fully generative semantics, even at 
+the level of documents, LDA could address the drawbacks 
+(such as dimensionality and failure in finding the discriminative set of 
+words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI. In
+this Bayesian model, LDA represents a document in the corpus by
+distributions over topics, and a topic itself is a distribution over all 
+terms in the corpus.  For example, for the Wikipedia pages, the latent
+topics reflect the thematic structure of the pages. Thus, LDA
+can find out relevant topic proportions in a document using posterior inference
+\cite{Blei2003latentdirichlet}. Additionally, given a text document, using LDA
+we could tag related documents by matching the similarity over the estimated
+topic proportions, which is useful in the ontology and corpora building.
+
 \subsection{QRM Ranking Mechanism} 
@@
 
-To answer a regular user's query, a \textit{candidate
-SSQ}, Morpheus finds similar SSQs that belong to QRMs the Morpheus data store (a
-\textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
+To answer a user's query, a \textit{candidate
+SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
 with a qualified SSQ. For the SSQ similarity, we
 consider the SSQ components such as query-realm, input
-terms and output terms, and their assigned categories or classes. The,
+terms and output terms, and their assigned categories or classes [To be changed]. The,
 \textit{category divergence} of two categories characteristics their 
@@
 It is motivated by the concept of multiple
-dispatch in CLOS \cite{Steele1990} and Dylan programming \cite{Barrett1996} for
-generic function \emph{type} matches.
+dispatch in CLOS and Dylan programming for generic function \emph{type} matches.
 
-We consider the category match as a type match and we use \emph{category divergence} 
-to calculate the relevance between the candiate SSQ
-and a qualified SSQ. Each qualified SSQ will
-have input terms, output terms, and associated classes, and one realm. For the
-candidate SSQ, the relevant category for input terms are determined from the
-ontology corpora [section \ref{sec:ontology_corpora}]. The relevance 
-of a qualified SSQ to the candidate SSQ is determined by
-aggregating the divergence measure of categories associated with them. In addition, 
-We order QRMs in the data store in order by descreasing relevance. 
-The order provides a ranking for the results to the user. 
-The following subsection describes \emph{category divergence} in detail.
+We consider the category match as a type match and we use 
+\emph{category divergence} to calculate the relevance between 
+the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
+have input terms, output terms, and associated classes, and one realm (from QRM). 
+For the candidate SSQ, the relevant categories for terms 
+are determined from the NLP engine and corpora. The calculation of a realm 
+for a candidate query is done using the ngrams found within said query 
+and the probabilities (if any) found using frequencies within the database.
+We match QRMs that belong to the same \emph{realm} of the candidate SSQ. 
+The relevance of a qualified SSQ to the candidate SSQ is 
+determined by aggregating the divergence measure of input-term-categories 
+associated with them. In addition, we order QRMs in the data store 
+by descreasing relevance. The order provides a ranking for the results 
+to the user. The following subsection describes \emph{category divergence} 
+in detail.
 
@@
 \centering
-\includegraphics[width=90mm]{img/automotive_ontology.eps}
-\caption{An abbreviated graphical representation of an automotive
-ontology: This is a manually created ontology, from the Wikipedia category
-hierarchy and pages. The edges represent inheritance relationships between the
-category in a topology.}
+\includegraphics[width=85mm]{img/automotive_ontology.eps}
+\caption{An abbreviated man-made automotive ontology - arrows represent inheritance relationships between the ontological classes.}
 \label{fig:automotive_ontology}
@@
 
-Suppose we want to find the category divergence between \textit{Toyota Camry}
-and \textit{Coupes} [Figure \ref{fig:automotive_ontology}]. 
-\textit{Toyota Camry} is the subcategory of \textit{Sedans}, and \textit{Coupes}
-is the subcategory of \textit{Cars}. Therefore, the least common ancestor ($C$)
-for these two categories is \textit{Cars}. In addition, the tree height is $5$.
-So, the normalized divergence $d_{cat}$\textit{(Toyota Camry, Coupes)} is $7/15$
-that is calculated from \textit{d(Toyota Camry, Root)} is 5, \textit{d(Toyota
-Camry, Cars)} is two, and \textit{d(Coupes, Cars)} is one.
+Suppose we want to find the category divergence between \textit{Sedans}
+and \textit{Trucks} (Figure \ref{fig:automotive_ontology}). 
+\textit{Sedans} is the subcategory of \textit{Cars}, and \textit{Trucks}
+is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
+for these two categories is \textit{Automobiles}. In addition, the tree height \textit{h = 4}.
+So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}
+that is calculated from \textit{d(Sedans, Root) = 4}, \textit{d(Sedans, Automobiles) = 2}, and \textit{d(Trucks, Automobiles) = 1}.
 

### 2010-06-28 trunk/paper/IIWAS2010/content/results_discussion.tex
changes to results

@@
 
-\begin{tabular}{l | l | r}
-Term & Category & $P(Category|Term)$ \\
+\begin{tabular}{| p{3.2cm} | l | r |}
 \hline 
+Term & Category & $P(Category|Term)$ \\ \hline
 1997 & Sedans & 404132.77e-14\\ 
@@
 Camry V6 & Coupes & 13.80e-14\\ 
-V6 & Sedans & 4464535.40e-14\\
-\hline
+V6 & Sedans & 4464535.40e-14\\ \hline
 \end{tabular}
@@
 
-\begin{tabular}{l | r}
-Query & Score\\
+\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
 \hline
-A 1997 Toyota Camry V6 needs what size tires? & 0.91\\ 
-What is the tire size for a 1998 Sienna XLE Van? & 0.72\\ 
-What is the tire size for a 1996 Infiniti I30 Sedan? & 0.88\\ 
-\hline
+Query & Tagged Categories & Score\\ \hline
+A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
+What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
+Where can I buy an engine for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
+What is the cost of a Toyota Camry V6 engine? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
 \end{tabular}
 
-\caption{Top ranked queries and relevance scores}
+\caption{Top ranked queries and relevance scores: IC - input categories, OC - output categories}
 \label{tbl:ranked_queries}
@@
 
-In this paper, we proposed a novel question answering system that uses previously answered user queries to answer similar questions using deep web site.
-The system uses a guide user to annotate answer paths so folowing users can discover answers to complicated questions.
-Each question answer pair is assigned a realm, and new questions are matched to the new question answer pairs.
-[How do we calculate relam for a candidate query?
-and NLP].
-This question matching strategy assumes that candidate query terms are available in the category corpus.
-The candidate query's category annotation will fail if the
-query terms are not available in the corpus.
-In addition, classification of a term or n-gram into a category is based on the term frequency distributions in a classified web document.
-We are working on improving this
+In this paper, we proposed a novel question answering system that uses previously 
+answered user queries to answer similar questions using deep web site.  
+The system uses a guide to annotate answer paths so folowing users 
+can discover answers to complicated questions.  Each question answer pair is 
+assigned a realm, and new questions are matched to the new question answer pairs. 
+This query matching strategy assumes that candidate query terms are
+available in the category corpus. The candidate query's category annotation will
+fail if the query terms are not available. In addition, classification of a
+term or n-gram into a category is based on the term frequency distributions in a
+classified web document. We are working on improving this
 approach by using a probabilistic generative approach as used in the Topic

### 2010-06-28 paper/IIWAS2010/content/introduction.tex
After Monday's meeting

@@
 in trying to find the best path to their destination.  However, those
-who come later will find it easy to reach that destination if a
+who come later will find it easier to reach that destination if a
 well-marked trail has been created. Olsen and Malizia describe this
@@
 
-The Morpheus system employs two types of users. One type is called a
-\textit{guide user} who \textit{types} queries in the Morpheus web interface and
-searches for an answer to the query in an instrumented web browser that can
-track answer pathways for a given query. This web tracking tool stores the query
-and necessary information to revisit the pathways to the page where he or she
-finds the answer. It also provides users a mechanism to highlight the answers.
-The other type is a \textit{regular user}, who uses the Morpheus system much
-like a regular search engine with a natural language interface. He can type a
-question in a text box and receive a response from the system. The system
-exploits previously answered queries to answer new questions.
+The Morpheus system employs two distinct user roles. One role is a
+\textit{path finder} who enters queries in the Morpheus web interface and
+searches for an answer to the query using an instrumented web browser. 
+This web tracking tool stores the query
+and necessary information to revisit the pathways to the page where the guide 
+found the answer.
+The other role is a \textit{path follower}, who uses the Morpheus system much like a regular search engine with a natural language interface.
+The path follower enters a question in a text box and receives a guided path to the answer.
+The system exploits previously found paths to provide an answer.
 
-To exploit the prior searches one should represent queries in an elegant way so
-that similar queries can be found efficiently and their stored search path
-revisited to produce answer to the user. Morpheus represents user-query details
-in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It
-includes a user query in natural-language format, relevant terms for the query,
-place holders for the term \textit{categories}. A \textit{category} represents a
-topic or class that a term belongs. For example, the term \textit{tire} can be
-classified into the category \textit{Automotive Parts}.
+To exploit prior paths, Morpheus represents user-query details in a format called a Semi-Structured Query or \textit{SSQ}.
+It includes a user query in natural-language format, relevant terms for the query, and place holders for the term \textit{categories}.
+A \textit{category} represents a
+topic or class to which a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Part}.
 
-In addition, Morpheus assumes term categories are come from a
-\textit{consistent} realm-based ontology. By consistency we mean it has two
-properties: (i) singly-rooted heterarchy (acyclic digraph with unique 
-ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
-semantic interpretations. This is important because, our proposed similarity 
+Morpheus assumes the term categories are classes of a
+\textit{consistent} realm-based ontology.
+We define a consistant ontology to have the following two properties.
+First, a singly-rooted heterarchy that has an acyclic digraph with unique ancestor of all nodes.
+Second, subclass and superclass relations must have meaningful semantic interpretations.
+This is important because, our proposed similarity
 measure for categories is based on the heterarchically
@@
 
-[Need a paragraph for wiki page categorization and ontology construction]
-In this paper, we propose an automatic web page categorization or 
-classification and recommendation using a machine learning technique, topic modeling.
-In addition, we also describes how we can use the categorized pages for realm-ontology 
-creation.
-
 This paper starts by discussing state-of-the-art systems in the area of
-question answering, ontology generation, and query ranking. The system
+question answering and ontology generation. The system
 architecture section explains the Morpheus system and its implementations

### 2010-06-29 trunk/paper/IIWAS2010/content/abstract.tex
After Monday's meeting
latest stuff

@@
 Morpheus answers questions by using methods stored in prior successful searches answering similar queries.
-We rank stored methods based on a similarity measure defined on assigned classes of queries.
-This measure depends on class heterarchy in a realm-based ontology and the associated text corpora.
+We rank stored methods based on a similarity quasi-metric defined on assigned classes of queries.
+Similarity depends on the class heterarchy in an ontology and its associated text corpora.
 Finally, we revisit the prior search pathways of the stored searches to construct possible answers.
-The realm-based ontologies are created using the Wikipedia pages, associated categories, and the synset heterarchy of WordNet.
+The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet.
 This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.
-The paper also discusses methods to improve generation of an ontology and the associated corpora using methods such as document categorization.
 

### 2010-06-29 trunk/paper/IIWAS2010/content/related_work.tex
latest stuff

--- 2010-06-22 trunk/paper/IIWAS2010/content/related_work.tex
@@
 
+The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
+Morpheus uses the web as its dynamic, open corpus and examines deep web sources 
+to answer questions.
+
+Several community QA systems have been developed, such as Yahoo!
+Answers \cite{yahooanswers2008}.
+These sites enlist a community of users to answer questions posed by other users.
+This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}.
+In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond webpages (e.g.
+instant messages, mobile phones).
+This allows for faster responses to questions.
+Morpheus relies on both its user interface and previous similar questions answered by a community of users to give a fast reliable answer.
+
 \subsection{Ontology generators} 
+\label{sec:ontology_generators}
 
-An ontology formally models real world \textit{concepts} and their
-relationships. A concept or class in an ontology gives us an abstract and
-simplified view of the world\cite{Gruber1993} in a machine-readable and
-language-independent format. The relationships and attributes of an
-ontological concept are defined using \textit{properties} and \textit{property
-restrictions}. An ontology definition contains all of
-these: classes, properties, and restrictions. A class in an ontology can have
-multiple \textit{super classes} and \textit{sub-classes}. Finally, a
-\textit{knowledge base} represents an ontology together with 
-instances of its classes.
+% This section needs to be reworkd. It should be about 1 paragraph. It should define
+% what these (ontology, dbpedia, wordnet) mean to morpheus
+% What rigors boone invest to my pyramids? <<-- randomly generated
 
-The DBpedia\footnote{http://dbpedia.org} project is based on extracting
-semantic information from the Wikipedia and making it available on the
-Web. Wikipedia semantics includes info-box templates, categorization
-information, images, Geo-coordinates, links to external Web pages,
-disambiguation pages, and redirects between pages in Wiki markup form
-\cite{Auer07dbpedia:a, Bizer2009}.
+%An ontology formally models real world \textit{concepts} and theirrelationships.
+A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and language-independent format.
+The relationships and attributes of an ontological concept are defined using \textit{properties} and \textit{property restrictions}.
+An ontology definition contains all of these: classes, properties, and restrictions.
+A class in an ontology can have multiple \textit{super classes} and \textit{sub-classes}.
+Finally, a \textit{knowledge base} represents an ontology together with instances of its classes.
 
-The extraction procedure is as follows: Wikipedia categories are represented
-using skos:concepts and category relations are represented using skos:broader
-\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
-relations between the Wikipedia categories. The Wikipedia categories are
-extracted directly from Wikipedia pages and there is no quality check on the
-resultant ontology. Similarly, DBpedia uses the info-box attributes and values
-as the ontological relations and its ranges.
+%% use dbpedia instead of wikipedia here
 
-YAGO is a semi-automatically constructed ontology from Wikipedia and
-WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
-extract information from Wikipedia pages, info-boxes, and categories and to
-combine this information with the WordNet\footnote{http://wordnet.princeton.edu}
-synsets heterarchy. Since Wikipedia contains more individuals in the form of
-Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles
-are used as the YAGO ontology individuals. YAGO concentrates mainly on the
-fields of people, cities, events, and movies\cite{Suchanek2009phd}.
+The DBpedia\footnote{http://dbpedia.org} project is based on extracting  semantic information from the Wikipedia and making it available on the Web.
+Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages,  and redirects between pages in Wiki markup form \cite{Bizer2009}.
+DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}.
+In fact,  DBpedia does not define any new relations between the Wikipedia categories.
+The Wikipedia categories are extracted directly from Wikipedia pages, and there  is no quality check on the resultant ontology.
+Similarly, additional ontological relations in DBpedia are generated from the info-box attributes and their values.
 
-In addition, YAGO uses Wikipedia categories as its ontology classes. The
-ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym}
-relations of the WordNet synsets. YAGO uses only the nouns from WordNet and
-ignores the WordNet verbs and adjectives. The connection between a WordNet
-synset and a Wikipedia category is achieved by parsing the category names and
-matching the parsed category components with the WordNet
-synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet
-match are ignored in the YAGO ontology.
+YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite {Suchanek2009phd}.
+YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes.
+The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
+YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
+The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 
-Moreover, YAGO type extraction is mainly based on the assumption that
-each Wikipedia page has at least one tagged category, and the assigned Wikipedia
-categories are relevant to that Wikipedia page. The Wikipedia page category
-assignments are subjectively assigned by human editors and some Wiki pages are
-unassigned i.e., they have no category. In addition, we cannot completely rely
-on the relevance of these assigned Wikipedia page categories.
-
-\subsection{NLP Interfaces}
+However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page.
+The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category.
+In addition, we cannot fully rely on the relevance of these assigned Wikipedia page categories.
+In addition, YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.

### 2010-06-29 paper/IIWAS2010/content/introduction.tex
latest stuff

@@
 lost.  The first person to go somewhere may make a number of mistakes
-in trying to find the best path to their destination.  However, those
-who come later will find it easier to reach that destination if a
+in trying to find the best path to their destination. Those
+who come later find it easier to reach the destination if a
 well-marked trail has been created. Olsen and Malizia describe this
 idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
-a user's discovery experience as a unique entity and working without an example
-context, one can exploit the fact that a similar search may have already been
+a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been
 performed.  In one study, almost 40 percent of all queries
-were found to be repetitions of previous queries\cite{1277770}. This
-indicates the reuse of prior searches is a way to optimize the search
+were repetitions of previous queries\cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
 process.  Morpheus is a question answering system motivated by reuse of prior
-web search pathways to yield an answer to a user query. Using our analogy,
-Morpheus follows path-finders to their destinations and not only marks the
+web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the
 trail, but also provides a taxi service to take followers to similar
@@
 
-The Morpheus system employs two distinct user roles. One role is a
-\textit{path finder} who enters queries in the Morpheus web interface and
+There are two distinct Morpheus user roles. A
+\textit{path finder} enters queries in the Morpheus web interface and
 searches for an answer to the query using an instrumented web browser. 
@@
 found the answer.
-The other role is a \textit{path follower}, who uses the Morpheus system much like a regular search engine with a natural language interface.
+A \textit{path follower} uses the Morpheus system much like a regular search engine with a natural language interface.
 The path follower enters a question in a text box and receives a guided path to the answer.
@@
 
-To exploit prior paths, Morpheus represents user-query details in a format called a Semi-Structured Query or \textit{SSQ}.
+Morpheus represents user-query details in a semi-structured query (SSQ).
 It includes a user query in natural-language format, relevant terms for the query, and place holders for the term \textit{categories}.
@@
 Morpheus assumes the term categories are classes of a
-\textit{consistent} realm-based ontology.
-We define a consistant ontology to have the following two properties.
-First, a singly-rooted heterarchy that has an acyclic digraph with unique ancestor of all nodes.
-Second, subclass and superclass relations must have meaningful semantic interpretations.
-This is important because, our proposed similarity
-measure for categories is based on the heterarchically
-structured category ontologies. Moreover, when a regular user enters a query,
-Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
+\textit{consistent} realm-based ontology, that is, one having a singly rooted heterachy whose
+subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on category similarity. Suppose a
 regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
@@
 and a predecessor of \textit{automobile models} is important, because this will
-help us grouping stored queries. Similarly, a clean ontology-taxonomy can
-improve the recall of such queries by supporting transitivity and other types of
-inference like faceted browsing \cite{Wu2008}.
+help us grouping stored queries.
 
-This paper starts by discussing state-of-the-art systems in the area of
-question answering and ontology generation. The system
-architecture section explains the Morpheus system and its implementations
-details. In the results section, we describe current results and its
-interpretations. Finally, we conclude the paper by describing the global impacts
+This paper discusses related question answering and ontology generation systems in section \ref{sec:relatedwork}.
+Section \ref{sec:systemarch} explains the Morpheus system and its implementation.
+Section \ref{sec:results}, we describe current results and their
+interpretation. We conclude by describing the global impacts
 of our approaches in QA systems.

### 2010-06-29 paper/IIWAS2010/content/system_arch.tex
latest stuff

@@
 
-This section presents the core elements of the Morpheus system and its 
-role in the \textit{automated question answering} process.
+This section presents ontology and copora, query processing, ranking queries, and query executing.
 
-\subsection{Query Processing}
+\subsection{Using Ontology and Corpora} 
+\label{sec:ontology_corpora}
+
+Morpheus uses an ontology that contains categories of a particular realm of interest.
+Every leaf node in the ontology is associated with a corpus of words belonging to a category.
+For example, we have constructed an automotive ontology containing categories relevant to the automotive realm.
+This ontology provides a structure for reference in the following sections.
+
+Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies.
+This approch is motivated by YAGO \cite{Suchanek2009phd}.
+First a realm is mapped to a DBpedia category \cite{Bizer2009}.
+Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}.
+From here, the system recursively includes all categories up to the root.
+
+Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO\cite{Suchanek2009phd}.
+We determine a \emph{head noun} in the category name and search for it in the WordNet synsets.
+DBpedia categories having no WordNet synset match are excluded from our ontology.
+
+To build a corpus for each of the leaf nodes in the ontology, 
+we extract \emph{terms} from the Wikipedia pages associated with the 
+the DBpedia categories. From this term corpus, 
+we can find the likelihood of a term belonging to a particular category. This assists in categorizing terms in a \emph{path-follower} query.
+The likelihood is determined by the probability of a category given a term 
+using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
+easily obtain the term-category and term-corpus probabilities as 
+relative frequencies.
+
+\begin{equation}
+\label{eq:bayesrule}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}
+
+In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.
+LDA is Bayesian model represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
+For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages.
+Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
+Additionally, given a text document, using LDA we could tag related documents by matching the similarity over the estimated topic proportions, which is useful in the ontology and corpora building.
+Due to its fully generative semantics, even at the level of documents, LDA could address the drawbacks (such as dimensionality and failure in finding the discriminative set of words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI.
+
+\subsection{ Recording}
 \label{sec:query_processing}
 
-The \emph{Query Resolution Recorder} or QRR is an instrumented web browser
-used to track the search pathways to an answer for a \textit{guide user's} query. It
-also helps the guide user to identify categories (optional) for the query terms. 
-Morpheus has two types of categories: \emph{intput categories} and \emph{output categories}.
+The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser
+used to track the search pathways to an answer for a \textit{path-finders} query. It
+also helps guide to identify categories (optional) for the query terms. 
+Morpheus has two types of categories: \emph{input categories} and \emph{output categories}.
 Input categories annotates the query terms into a class or category, which are 
@@
 to the expected answer of a user query. Morpheus captures all
-this query information in the representation of an SSQ. For example, suppose, a guide user
+this query information in the representation of an SSQ. For example, suppose, a guide 
 tries to answer the query ``A 1997 Toyota Camry V6 needs what size tires?'', using
-Morpheus. With the help of the QRR, she may choose relevant query terms and assign
+Morpheus. With the help of the QRR, guide may choose relevant query terms and assign
 \emph{input categories} to them: Toyota : manufacturer, Camry V6 : 
 model, tire : automotive parts, and size as the \emph{output category}. 
-In addition, she can log the search pathways to an answer (e.g. P215/60R16)
+In addition, guide can log the search pathways to an answer (e.g. P215/60R16)
 to this query and select the query \emph{realm} as automotive.
 
-The \emph{Query Resolution Method} or QRM is a data structure that models the
-question answering process. A QRM is usually constructed by a \emph{guide user} with
+The \emph{Query Resolution Method} (QRM) is a data structure that models the
+question answering process. A QRM is usually constructed by a \emph{guide} with
 the help of the QRR. Each QRM contains an \emph{ontological realm}, an SSQ, and
@@
 
-A \textit{regular user} query is parsed into specific terms by an \textit{NLP
-engine} using some linguistic techniques [Need to be completed]. The SSQ generated by the NLP
-Engine contains user query and parsed terms.
+Rather than working blindly, forming all possible n-grams from the query 
+and running probabilities, it seemed to be a better approach to identify 
+important noun phrases within the query, and work with those. Using our 
+query parser, we proceed to tokenize, parse, and chunk our candidate query, 
+extracting verb groups, answer classes, and descriptive info from each query. 
+In the example query "What is the tire size of a 1997 Toyota Camry?," 
+the verb group is the verb "is," the answer class is "tire size," and descriptive 
+info is "of a 1997 Toyota Camry." The next step is to create n-grams from these chunks. 
+Using these n-grams, we will query our database for frequencies associated with 
+each n-gram: overall frequency and categorical frequency, alongside category 
+term count and overall term count, to calculate categorical probabilities 
+and establish a realm for the candidate query, choosing realm with highest probability.
 
-\subsection{Morpheus Ontology and Corpora} 
-\label{sec:ontology_corpora}
-
-Morpheus requires a realm-based ontology that contains categories of a
-particular realm of interest. For example, the realm-ontology \textit{Automotive}
-contains categories that are relevant to the automotive realm. In
-addition, every leaf node in the category ontology is associated with a corpus of words
-that belongs to that category.
-
-For ontology construction Morpheus uses the Wikipedia pages, categories,
-and the WordNet synset heterarchy. This approch is motivated from
-YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
-from the DBpedia categories\cite{Bizer2009}. Then we grab all the neighboring categories using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
-the category's parents, its children, and its 
-children's other parents using the DBpedia ontology properties \textit{broader}
-and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
-of the categories in the blanket till it reaches root. Once we have the
-categories belongs to a particular domain, we associate them with WordNet synsets
-using an algorithm similar to YAGO\cite{Suchanek2009phd}. We determine head noun in the
-category name and search for it in the WordNet synsets.
-Those Wikipedia categories having no WordNet match are ignored in the our realm
-ontology. In addition, we uses the WordNet synset heterarchy relationships for building the ontologcial structure.
-
-To build a corpus for each of the leaf nodes in the ontology, 
-we extract \emph{n-grams} or \emph{terms} from the Wikipedia pages associated with the 
-the DBpedia categories\cite{Bizer2009}. From this category-term corpora, 
-we can find out the likelihood that a term belongs to a particular category, 
-which is useful in categorizing the terms in a \emph{regular user's} query [section \ref{sec:qrm_ranking}].    
-This likelihood is determined by the probability of a category given a term 
-using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
-easily obtain the term-category and term-corpus probabilities as 
-relative frequencies. The higher the probability, the more likely a 
-term is referring to a category.
-
-\begin{equation}
-\label{eq:bayesrule}
-P (category | term) = \frac{P(term | category) P(category)}{P(term)}
-\end{equation}
-
-\subsection{QRM Ranking Mechanism} 
+\subsection{Ranking} 
 \label{sec:qrm_ranking}
 
-To answer a regular user's query, a \textit{candidate
+To answer a user's query, a \textit{candidate
 SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
@@
 the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
-have input terms, output terms[what do we do with this??], and associated classes, and one realm. 
-For the candidate SSQ, the relevant category for input terms 
-are determined from the ontology corpora [section \ref{sec:ontology_corpora}].
+have input terms, output terms, and associated classes, and one realm (from QRM). 
+For the candidate SSQ, the relevant categories for terms 
+are determined from the NLP engine and corpora. The calculation of a realm 
+for a candidate query is done using the n-grams found within said query 
+and the probabilities (if any) found using frequencies within the database.
 We match QRMs that belong to the same \emph{realm} of the candidate SSQ. 
@@
 \includegraphics[width=85mm]{img/automotive_ontology.eps}
-\caption{An abbreviated man-made automotive ontology: Arrows represent inheritance relationships between the ontological classes.}
+\caption{An abbreviated man-made automotive ontology - arrows represent inheritance relationships between the ontological classes.}
 \label{fig:automotive_ontology}
@@
 Suppose we want to find the category divergence between \textit{Sedans}
-and \textit{Trucks} [Figure \ref{fig:automotive_ontology}]. 
+and \textit{Trucks} (Figure \ref{fig:automotive_ontology}). 
 \textit{Sedans} is the subcategory of \textit{Cars}, and \textit{Trucks}
 is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
-for these two categories is \textit{Automobiles}. In addition, the tree height \textit{h = 4}.
+for these twoThis section presents ontology and copora, Query processing, ranking queries, and the query resolution mechanism.
+categories is \textit{Automobiles}.
+In addition, the tree height \textit{h = 4}.
 So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}
@@
 
-\subsection{Query Resolution Execution}
+\subsection{Executing}
 
-Usually, answering a question using the 
-deep web requires one to navigate through a sequence of one or 
-more web pages. Many of the accesses involve clicks through 
-web forms or links to resulting pages. QRM contains the necessary  
-information required to re-run this procedure. Once we have 
+QRM contains the necessary  
+information required to re-run this procedure.Once we have 
 relevant QRMs through QRM ranking for a given user query, we can  
 get answers by re-running the pathways with help of 
-the Query Resolution Engine or QRE of Morpheus.
+the \emph{Query Resolution Engine} (QRE) of Morpheus.

### 2010-06-29 trunk/paper/IIWAS2010/content/related_work.tex
edit section 2.2

@@
 
-% This section needs to be reworkd. It should be about 1 paragraph. It should define
+% This section needs to be reworked. It should be about 1 paragraph. It should define
 % what these (ontology, dbpedia, wordnet) mean to morpheus
@@
 
-%An ontology formally models real world \textit{concepts} and theirrelationships.
+%An ontology formally models real world \textit{concepts} and their relationships.
 A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and language-independent format.
@@
 
-The DBpedia\footnote{http://dbpedia.org} project is based on extracting  semantic information from the Wikipedia and making it available on the Web.
+The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making it available on the Web.
 Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages, and redirects between pages in Wiki markup form \cite{Bizer2009}.
-DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}.
+DBpedia does not define any new relations between the Wikipedia categories.
+Morpheus the DBpedia categories and its semantics to construct its ontology.
+%  DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}.
 In fact,  DBpedia does not define any new relations between the Wikipedia categories.
@@
 
-YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite {Suchanek2009phd}.
+YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}.
 YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes.
+YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
+YAGO discovers connections between a WordNet synsets and a Wikipedia categories parsing the category names and matching the parsed category components with the WordNet synsets \cite{Suchanek2009phd}.
+Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
-YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
-The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}.
-Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
+Morpheus uses many of the same ideas made when using YAGO to develop its own ontology as explained in Section \ref{sec:ontology_corpora}.
 
-However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page.
+%However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page.
 The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category.

### 2010-06-29 trunk/paper/IIWAS2010/content/system_arch.tex
edit section 2.2

@@
 
-This section presents the core elements of the Morpheus system and its 
-role in the \textit{automated question answering} process.
+This section presents ontology and copora, query processing, ranking queries, and query executing.
 
-\subsection{Query Processing}
+\subsection{Using Ontology and Corpora} 
+\label{sec:ontology_corpora}
+
+Morpheus uses an ontology that contains categories of a particular realm of interest.
+Every leaf node in the ontology is associated with a corpus of words belonging to a category.
+For example, we have constructed an automotive ontology containing categories relevant to the automotive realm.
+This ontology provides a structure for reference in the following sections.
+
+Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies.
+This approch is motivated by YAGO \cite{Suchanek2009phd}.
+First a realm is mapped to a DBpedia category \cite{Bizer2009}.
+Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}.
+From here, the system recursively includes all categories up to the root.
+
+Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO\cite{Suchanek2009phd}.
+We determine a \emph{head noun} in the category name and search for it in the WordNet synsets.
+DBpedia categories having no WordNet synset match are excluded from our ontology.
+
+To build a corpus for each of the leaf nodes in the ontology, 
+we extract \emph{terms} from the Wikipedia pages associated with the 
+the DBpedia categories. From this term corpus, 
+we can find the likelihood of a term belonging to a particular category. This assists in categorizing terms in a \emph{path-follower} query.
+The likelihood is determined by the probability of a category given a term 
+using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
+easily obtain the term-category and term-corpus probabilities as 
+relative frequencies.
+
+\begin{equation}
+\label{eq:bayesrule}
+P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+\end{equation}
+
+In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.
+LDA is Bayesian model represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
+For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages.
+Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
+Additionally, given a text document, using LDA we could tag related documents by matching the similarity over the estimated topic proportions, which is useful in the ontology and corpora building.
+Due to its fully generative semantics, even at the level of documents, LDA could address the drawbacks (such as dimensionality and failure in finding the discriminative set of words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI.
+
+\subsection{ Recording}
 \label{sec:query_processing}
 
-The \emph{Query Resolution Recorder} or QRR is an instrumented web browser
-used to track the search pathways to an answer for a \textit{guide's} query. It
+The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser
+used to track the search pathways to an answer for a \textit{path-finders} query. It
 also helps guide to identify categories (optional) for the query terms. 
-Morpheus has two types of categories: \emph{intput categories} and \emph{output categories}.
+Morpheus has two types of categories: \emph{input categories} and \emph{output categories}.
 Input categories annotates the query terms into a class or category, which are 
@@
 
-The \emph{Query Resolution Method} or QRM is a data structure that models the
+The \emph{Query Resolution Method} (QRM) is a data structure that models the
 question answering process. A QRM is usually constructed by a \emph{guide} with
@@
 
-Rather than working blindly, forming all possible ngrams from the query 
+Rather than working blindly, forming all possible n-grams from the query 
 and running probabilities, it seemed to be a better approach to identify 
@@
 the verb group is the verb "is," the answer class is "tire size," and descriptive 
-info is "of a 1997 Toyota Camry." The next step is to create ngrams from these chunks. 
-Using these ngrams, we will query our database for frequencies associated with 
-each ngram: overall frequency and categorical frequency, alongside category 
+info is "of a 1997 Toyota Camry." The next step is to create n-grams from these chunks. 
+Using these n-grams, we will query our database for frequencies associated with 
+each n-gram: overall frequency and categorical frequency, alongside category 
 term count and overall term count, to calculate categorical probabilities 
@@
 
-\subsection{Morpheus Ontology and Corpora} 
-\label{sec:ontology_corpora}
-
-Morpheus requires a realm-based ontology that contains categories of a
-particular realm of interest. For example, the realm-ontology \textit{Automotive}
-contains categories that are relevant to the automotive realm. In
-addition, every leaf node in the category ontology is associated with a corpus of words
-that belongs to that category.
-
-For ontology construction Morpheus uses the Wikipedia pages, categories,
-and the WordNet synset heterarchy. This approch is motivated from
-YAGO\cite{Suchanek2009phd}. For a given realm, we first find a mapping category 
-from the DBpedia categories\cite{Bizer2009}. Then we grab all the neighboring 
-categories using a \textit{Markov Blanket} \cite{PRIS}. In fact, we grab 
-the category's parents, its children, and its 
-children's other parents using the DBpedia ontology properties \textit{broader}
-and \textit{narrower}. Once the blanket is ready, it grabs all parent categories
-of the categories in the blanket till it reaches root. Once we have the
-categories belongs to a particular domain, we associate them with WordNet synsets
-using an algorithm similar to YAGO\cite{Suchanek2009phd}. We determine head noun in the
-category name and search for it in the WordNet synsets.
-Those Wikipedia categories having no WordNet match are ignored in the our realm
-ontology. In addition, we uses the WordNet synset heterarchy relationships for building the ontologcial structure.
-
-To build a corpus for each of the leaf nodes in the ontology, 
-we extract \emph{n-grams} or \emph{terms} from the Wikipedia pages associated with the 
-the DBpedia categories\cite{Bizer2009}. From this category-term corpora, 
-we can find out the likelihood that a term belongs to a particular category, 
-which is useful in categorizing the terms in a \emph{regular user's} query [section \ref{sec:qrm_ranking}].    
-This likelihood is determined by the probability of a category given a term 
-using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
-easily obtain the term-category and term-corpus probabilities as 
-relative frequencies. The higher the probability, the more likely a 
-term is referring to a category.
-
-\begin{equation}
-\label{eq:bayesrule}
-P (category | term) = \frac{P(term | category) P(category)}{P(term)}
-\end{equation}
-
-Alternately, we are evaluating Latent Dirichlet Allocation (LDA), a probabilistic graphic model, for
-representing latent topics of the documents in a text corpus\cite{Blei2003latentdirichlet}.
-Due to its fully generative semantics, even at 
-the level of documents, LDA could address the drawbacks 
-(such as dimensionality and failure in finding the discriminative set of 
-words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI. In
-this Bayesian model, LDA represents a document in the corpus by
-distributions over topics, and a topic itself is a distribution over all 
-terms in the corpus.  For example, for the Wikipedia pages, the latent
-topics reflect the thematic structure of the pages. Thus, LDA
-can find out relevant topic proportions in a document using posterior inference
-\cite{Blei2003latentdirichlet}. Additionally, given a text document, using LDA
-we could tag related documents by matching the similarity over the estimated
-topic proportions, which is useful in the ontology and corpora building.
-
-\subsection{QRM Ranking Mechanism} 
+\subsection{Ranking} 
 \label{sec:qrm_ranking}
@@
 are determined from the NLP engine and corpora. The calculation of a realm 
-for a candidate query is done using the ngrams found within said query 
+for a candidate query is done using the n-grams found within said query 
 and the probabilities (if any) found using frequencies within the database.
@@
 is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
-for these two categories is \textit{Automobiles}. In addition, the tree height \textit{h = 4}.
+for these twoThis section presents ontology and copora, Query processing, ranking queries, and the query resolution mechanism.
+categories is \textit{Automobiles}.
+In addition, the tree height \textit{h = 4}.
 So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}

### 2010-06-30 trunk/paper/IIWAS2010/content/system_arch.tex
current latest, changed need to be made

@@
 
-QRM contains the necessary  
-information required to re-run this procedure.Once we have 
-relevant QRMs through QRM ranking for a given user query, we can  
-get answers by re-running the pathways with help of 
-the \emph{Query Resolution Engine} (QRE) of Morpheus.
+Once we have relevant QRMs through QRM ranking for a given user query, we can get answers by re-running the pathways with help of the \emph{Query Resolution Engine} (QRE) of Morpheus.
+The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of datato form a text answer.
+
+%When a user submits a new query to the Morpheus system, one or more stored QRMs are executed to obtain results.
+A QRM contains an XML script representing an algorithm that will obtain the required result.
+The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, highlighting data, cutting and pasting text, and constructing an answer in the form of a text string.
+There is greater complexity in dealing with web forms than with links.
+At present, the GET form submission method is used.
+This means that in preparation to submit a form, the Morpheus System builds a querystring consisting of name-value pairs.
+For a given form, there may be text fields, drop-down boxes, and among other components.
+In order to support form submission in such circumstances, the QRE performs different actions based upon the input type.
+For text fields, simply adding a key/value pair to the query string suffices.
+For a drop-down box, the QRE extracts the form element to find the appropriate value to include in the query string.
+It does this by examine each option in the drop-down and matching the user’s input to the text field in the option.
+The value attribute of the option is then added to the querystring.
+The value and text attributes of a dropdown option might be the same, but they are not guaranteed to be.
+All input data are kept in an internal table.
+The QRM script contains keys that allow the QRE to map SSQ inputs from the table to the appropriate form inputs.
+Furthermore, highlighted text segments collected during execution of the script are stored in the table.
+Once all actions in the script have been carried out, the QRE returns the textual answer this process has created.
+This answer is then be rendered in a browser displayed to the user.

### 2010-06-30 paper/IIWAS2010/content/system_arch.tex
Joir-dan updated the system_arch section

@@
 
-This section presents ontology and copora, query processing, ranking queries, and query executing.
+% This was corrected in my version... (Joir-dan performing diff 2010-06-30)
+This section presents ontology and corpora, query processing, ranking queries, and query executing.
 
@@
 
+%% Comment made by Joir-dan (2010-06-29)
+ %%Need to remove any references to Markov Blanket... since we abandoned that ship a while ago...
+
 Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies.
-This approch is motivated by YAGO \cite{Suchanek2009phd}.
+This approach is motivated by YAGO \cite{Suchanek2009phd}.
 First a realm is mapped to a DBpedia category \cite{Bizer2009}.
@@
 From here, the system recursively includes all categories up to the root.
+
+%% ^^^ Needs to remove references to blanket
 
@@
 relative frequencies.
+
+%% Comment by Joir-dan 2010-06-30: Term should prolly be replaced by n-gram
 
@@
 
-The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser
-used to track the search pathways to an answer for a \textit{path-finders} query. It
-also helps guide to identify categories (optional) for the query terms. 
-Morpheus has two types of categories: \emph{input categories} and \emph{output categories}.
-Input categories annotates the query terms into a class or category, which are 
-useful in finding similar queries. On the other hand, output categories give hints
-to the expected answer of a user query. Morpheus captures all
-this query information in the representation of an SSQ. For example, suppose, a guide 
-tries to answer the query ``A 1997 Toyota Camry V6 needs what size tires?'', using
-Morpheus. With the help of the QRR, guide may choose relevant query terms and assign
-\emph{input categories} to them: Toyota : manufacturer, Camry V6 : 
-model, tire : automotive parts, and size as the \emph{output category}. 
-In addition, guide can log the search pathways to an answer (e.g. P215/60R16)
-to this query and select the query \emph{realm} as automotive.
+%% Was edited and shortened by Joir-dan and Wilson (2010-06-29)
+The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question.
+The path-finder also uses the tool to identify ontological categories associated with search terms.
+Morpheus stores the query together with its terms and categories as an SSQ (Figure \ref{fig:ssq_example}).
+Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.
 
+%% Was added by Joir-dan and Wilson (2010-06-29)... but may need to be better formatted
+\begin{figure}[t]
+\label{fig:ssq_example}
+("An  1997 Toyota Camry V6 has what size tires", 
+     (1997: Date, Toyota: Manufacturer, Camry: Model, V6: Engine ),
+     (tire: Part, size: Measurement))
+
+%% Comment made by Joir-dan Gumbs (2010-06-29) 
+%%Need to talk a bit about this SSQ Structure: Does anyone see anything wrong with this representation?
+\caption{An example SSQ for the question: A 1997 Toyota Camry V6 has what size tires?}
+\end{figure}
+
+%% Edited by Joir-dan and Wilson (2010-06-29)
 The \emph{Query Resolution Method} (QRM) is a data structure that models the
-question answering process. A QRM is usually constructed by a \emph{guide} with
-the help of the QRR. Each QRM contains an \emph{ontological realm}, an SSQ, and
-information to support the query answering process. QRMs are associated with an
-ontology that has a particular realm i.e. an ontological realm. In addition, 
-the QRM contains information required to visit each page needed to 
-answer the query as well as the order of visitation. For each
-dyanamic page, it stores the list of inputs to the URL such as form inputs and
-the possible referrence outputs (highlighted portions of the web page).
+question answering process.
+A QRM represents a generalized executable realization of the search process that the path-finder followed.
+The QRM is able to reconstruct the page search path followed by the path-finder.
+Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process.
+For each dynamic page, it stores the list of inputs to the URL such as form inputs and the possible reference outputs (highlighted portions of the web page).
 
 % NLP arch. 
-% Joir-dan
+% This may need to be moved somewhere... but not sure where.... Joir-dan Gumbs (2010-06-29)
 
-Rather than working blindly, forming all possible n-grams from the query 
-and running probabilities, it seemed to be a better approach to identify 
-important noun phrases within the query, and work with those. Using our 
-query parser, we proceed to tokenize, parse, and chunk our candidate query, 
-extracting verb groups, answer classes, and descriptive info from each query. 
-In the example query "What is the tire size of a 1997 Toyota Camry?," 
-the verb group is the verb "is," the answer class is "tire size," and descriptive 
-info is "of a 1997 Toyota Camry." The next step is to create n-grams from these chunks. 
-Using these n-grams, we will query our database for frequencies associated with 
-each n-gram: overall frequency and categorical frequency, alongside category 
-term count and overall term count, to calculate categorical probabilities 
-and establish a realm for the candidate query, choosing realm with highest probability.
+Queries inserted by path-followers take a different approach.
+The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams.
+The system then assigns the most probable realm to the query using \textit{realm}|\textit{n-gram} priors calculated from realm-specific corpora.
+Once the realm is assigned, an ontology search is performed to assign classes to the n-grams.
+An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user.
+Rather than matching n-grams, the goal is to match input and output classes, since the paths can potentially answer similar queries.
 
@@
 \emph{category divergence} to calculate the relevance between 
-the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
+the candidate SSQ and a qualified SSQ. Each qualified SSQ will 
 have input terms, output terms, and associated classes, and one realm (from QRM). 
@@
 associated with them. In addition, we order QRMs in the data store 
-by descreasing relevance. The order provides a ranking for the results 
+by decreasing relevance. The order provides a ranking for the results 
 to the user. The following subsection describes \emph{category divergence} 

### 2010-06-30 trunk/paper/IIWAS2010/content/system_arch.tex
merged changes

@@
 
-Once we have relevant QRMs through QRM ranking for a given user query, we can get answers by re-running the pathways with help of the \emph{Query Resolution Engine} (QRE) of Morpheus.
-The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of datato form a text answer.
+Once we have relevant QRMs through QRM ranking for a given user query, we can produce answers by re-running the pathways.
+
+ The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of data to form a text answer.
+The QRE assumes that becuase of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.
+It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.
 

### 2010-06-30 trunk/paper/IIWAS2010/content/system_arch.tex
latest

@@
 
-Morpheus uses an ontology that contains categories of a particular realm of interest.
-Every leaf node in the ontology is associated with a corpus of words belonging to a category.
-For example, we have constructed an automotive ontology containing categories relevant to the automotive realm.
+Morpheus uses an ontology that contains classes of a particular realm of interest.
+Each leaf node in the ontology is associated with a corpus of words belonging to a class.
+For example, we have constructed an automotive ontology containing classes relevant to the automotive realm.
 This ontology provides a structure for reference in the following sections.
 
-%% Comment made by Joir-dan (2010-06-29)
- %%Need to remove any references to Markov Blanket... since we abandoned that ship a while ago...
+%% Need ontology paragraph
 
-Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies.
+Morpheus uses the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages.
 This approach is motivated by YAGO \cite{Suchanek2009phd}.
@@
 Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}.
-From here, the system recursively includes all categories up to the root.
 
-%% ^^^ Needs to remove references to blanket
+To build a corpus for each of the leaf nodes in the ontology, we extract \emph{terms} from the Wikipedia pages associated with the DBpedia categories found in its blanket.
+From this term corpus, we can find the likelihood of a term belonging to a particular category.
+This assists in categorizing terms in a \emph{path-follower} query.
+The likelihood is determined by the probability of a category given a term using \textit{Bayes Rule} (Eq.
+\ref{eq:bayesrule}), since we can easily obtain the term-category and term-corpus probabilities as relative frequencies.
 
-Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO\cite{Suchanek2009phd}.
+%Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO.
 We determine a \emph{head noun} in the category name and search for it in the WordNet synsets.
 DBpedia categories having no WordNet synset match are excluded from our ontology.
-
-To build a corpus for each of the leaf nodes in the ontology, 
-we extract \emph{terms} from the Wikipedia pages associated with the 
-the DBpedia categories. From this term corpus, 
-we can find the likelihood of a term belonging to a particular category. This assists in categorizing terms in a \emph{path-follower} query.
-The likelihood is determined by the probability of a category given a term 
-using \textit{Bayes Rule} (Eq. \ref{eq:bayesrule}), since we can 
-easily obtain the term-category and term-corpus probabilities as 
-relative frequencies.
-
-%% Comment by Joir-dan 2010-06-30: Term should prolly be replaced by n-gram
+<--- by Gordon
 
@@
 The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams.
-The system then assigns the most probable realm to the query using \textit{realm}|\textit{n-gram} priors calculated from realm-specific corpora.
+The system then assigns the most probable realm to the query using $p(realm|n-gram)$ priors calculated from realm-specific corpora.
 Once the realm is assigned, an ontology search is performed to assign classes to the n-grams.
@@
 To answer a user's query, a \textit{candidate
-SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}). We need a similarity measure to match the candidate SSQ
-with a qualified SSQ. For the SSQ similarity, we
-consider the SSQ components such as query-realm, input
-terms and output terms, and their assigned categories or classes [To be changed]. The,
-\textit{category divergence} of two categories characteristics their 
-similarity based on an ontology class heterarchy. 
-It is motivated by the concept of multiple
-dispatch in CLOS and Dylan programming for generic function \emph{type} matches.
+SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}).  To determine SSQ similarity, we
+consider the SSQ's realm, input terms, output terms, and their assigned classes.
 
-We consider the category match as a type match and we use 
-\emph{category divergence} to calculate the relevance between 
-the candidate SSQ and a qualified SSQ. Each qualified SSQ will 
-have input terms, output terms, and associated classes, and one realm (from QRM). 
-For the candidate SSQ, the relevant categories for terms 
-are determined from the NLP engine and corpora. The calculation of a realm 
-for a candidate query is done using the n-grams found within said query 
-and the probabilities (if any) found using frequencies within the database.
-We match QRMs that belong to the same \emph{realm} of the candidate SSQ. 
-The relevance of a qualified SSQ to the candidate SSQ is 
-determined by aggregating the divergence measure of input-term-categories 
-associated with them. In addition, we order QRMs in the data store 
+The \emph{class divergence} of two classes within the ontology characterizes their similarity.
+This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches.
+
+We consider the category match as a type match and we use \emph{category divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ.
+Each qualified SSQ will have input terms, output terms, and associated classes, and one realm (from the QRM).
+For the candidate SSQ, the relevant categories for terms are determined from the NLP engine and corpora.
+The calculation of a realm for a candidate query is performed using the n-grams found within the query and any probabilities as found with $p(realm|n\-gram)$.
+%% TODO - specify freq and reference joirdans stuff in section 3.2
+We match QRMs that belong to the same realm of the candidate SSQ.
+The relevance of a qualified SSQ to the candidate SSQ is determined by aggregating the divergence measure of input term classes associated with each SSQ.
+In addition, we order QRMs in the data store
 by decreasing relevance. The order provides a ranking for the results 
-to the user. The following subsection describes \emph{category divergence} 
+to the user. The following describes \emph{category divergence} 
 in detail.
 
-\subsubsection{Catgeory Divergence}
-\label{sec:ctd}
+%\subsubsection{Catgeory Divergence}
+%\label{sec:ctd}
 
@@
  The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of data to form a text answer.
-The QRE assumes that becuase of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.
+The QRE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.
 It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.

### 2010-06-30 paper/IIWAS2010/content/related_work.tex
latest

@@
 
-Question Answering (QA) is an old field and there has been a recent influx of QA work.
-The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.
-Closed domain QA systems are those in which the possible meanings of the questions given are finite.
-We define closed corpus sytems as those in which the sources used to answer questions are finite.
-QA systems that treat the web as a document collection are open corpus systems.
-The morpheus system is considered an open corpus system.
-It goes beyond current state of the art QA systems by examining deep web sources.
+The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
+Morpheus uses the web as its dynamic, open corpus and examines deep web sources 
+to answer questions.
 
-Several community QA systems have been developed, one of the most popular being Yahoo!
+Several community QA systems have been developed, such as Yahoo!
 Answers \cite{yahooanswers2008}.
-These sites enlist a community of users to answer question posed by other users.
-This idea has evolved to invent socially integrated QA systems such as Aardvark \cite{vark2010}.
-In addition to having questions answered by users, Aardvark is able to contact potential question answerers through several media beyond webpages (e.g.
+These sites enlist a community of users to answer questions posed by other users.
+This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}.
+In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond web pages (e.g.
 instant messages, mobile phones).
-This allows for possibly faster answers to questions.
-The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.
+This allows for faster responses to questions.
+Morpheus relies on both its user interface and previous similar questions answered by a community of users to give a fast reliable answer.
 
@@
 
-An ontology formally models real world \textit{concepts} and their
-relationships. A concept or class in an ontology gives us an abstract and
-simplified view of the world\cite{Gruber1993} in a machine-readable and
-language-independent format. The relationships and attributes of an
-ontological concept are defined using \textit{properties} and \textit{property
-restrictions}. An ontology definition contains all of
-these: classes, properties, and restrictions. A class in an ontology can have
-multiple \textit{super classes} and \textit{sub-classes}. Finally, a
-\textit{knowledge base} represents an ontology together with 
-instances of its classes.
+% This section needs to be reworked. It should be about 1 paragraph. It should define
+% what these (ontology, dbpedia, wordnet) mean to morpheus
+% What rigors boone invest to my pyramids? <<-- randomly generated
 
-The DBpedia\footnote{http://dbpedia.org} project is based on extracting 
-semantic information from the Wikipedia and making it available on the Web. 
-Wikipedia semantics includes info-box templates, categorization information, 
-images, Geo-coordinates, links to external Web pages, disambiguation pages, 
-and redirects between pages in Wiki markup form \cite{Bizer2009}. 
-DBpedia represents the Wikipedia categories using skos:concepts and category 
-relations using skos:broader \cite{Bizer2009}. In fact, 
+%An ontology formally models real world \textit{concepts} and their relationships.
+A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and language-independent format.
+The relationships and attributes of an ontological concept are defined using \textit{properties} and \textit{property restrictions}.
+An ontology definition contains all of these: classes, properties, and restrictions.
+A class in an ontology can have multiple \textit{super classes} and \textit{sub-classes}.
+Finally, a \textit{knowledge base} represents an ontology together with instances of its classes.
+
+%% use dbpedia instead of wikipedia here
+
+The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making it available on the Web.
+Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages, and redirects between pages in Wiki markup form \cite{Bizer2009}.
 DBpedia does not define any new relations between the Wikipedia categories.
-The Wikipedia categories are extracted directly from Wikipedia pages, and there 
-is no quality check on the resultant ontology. Similarly, additional ontological 
-relations in DBpedia are generated from the info-box attributes and their values.
 
-YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy\cite{Suchanek2009phd}.
+%Morpheus uses the DBpedia categories and its semantics to construct its ontology.
+%  DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}.
+In fact,  DBpedia does not define any new relations between the Wikipedia categories.
+The Wikipedia categories are extracted directly from Wikipedia pages, and there  is no quality check on the resultant ontology.
+Similarly, additional ontological relations in DBpedia are generated from the info-box attributes and their values.
+
+YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}.
 YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes.
+YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
+YAGO discovers connections between a WordNet synsets and a Wikipedia categories parsing the category names and matching the parsed category components with the WordNet synsets.
+Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
-YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
-The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}.
-Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 
-However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page.
+We have attempted to use similar techniques to construct ontologies for question answering realms.
+Thus far, these ontologies can be use to classifiy terms, but their classes do not appropriately categorize deep web query parameters.
+Therefore we have been relegated to manually generating ontologies.
+% TODO - add "this is under investigation"
+
+%Morpheus uses many of the same ideas made when using YAGO to develop its own ontology as explained in Section \ref{sec:ontology_corpora}.
+
+%However, YAGO type extraction assumes that each Wikipedia page has at least one tagged category, and the assigned Wikipedia categories are relevant to that Wikipedia page.
 The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages are unassigned i.e., they have no category.

### 2010-06-30 paper/IIWAS2010/content/results_discussion.tex
latest

--- 2010-06-20 paper/IIWAS2010/content/results_discussion.tex
@@
 
-\subsection{Discussion}
+First, we created an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets.
+For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
+Table describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
+
+%% TODO - need to refer back to the table which is figure one.
+The Morpheus NLP engine parses this query into the constructs: WH:what,
+Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
+descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
+Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
+each of the terms, we determined relevant categories (non-increasing order of
+relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
+the top categories and their probabilities for each of the query term:
+
+\begin{table}[h]\footnotesize
+
+\begin{tabular}{| p{3.2cm} | l | r |}
+\hline 
+Term & Category & $P(Category|Term)$ \\ \hline
+1997 & Sedans & 404132.77e-14\\ 
+1997 Toyota & Engines & 7.90e-14\\ 
+Toyota  & Sedans & 3486670.15e-14\\ 
+Toyota Camry & Sedans & 12147.23e-14\\ 
+Toyota Camry V6 & Coupes & 13.80e-14\\ 
+Camry & Sedans & 312034.20e-14\\ 
+Camry V6 & Coupes & 13.80e-14\\ 
+V6 & Sedans & 4464535.40e-14\\ \hline
+\end{tabular}
+
+\caption{Terms' top categories and probabilities}
+\label{tbl:term_categories}
+
+\end{table}
+
+We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
+ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.
+
+\begin{table}[h]\footnotesize
+
+\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
+\hline
+Query & Tagged Classes & Score\\ \hline
+A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
+What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
+Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
+What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
+\end{tabular}
+
+\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
+\label{tbl:ranked_queries}
+
+\end{table}
+
+%\subsection{Discussion}
+\section{Conclusion}
+
+In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions.
+The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.
+Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs.
+Classification of terms into classes is based on term frequency distributions in our corpora of web documents.
+We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.
+
+Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task.
+Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
+%The Wikipedia page categories has limitations.
+Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g.
+automotive) usually overlap.
+So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.
 

### 2010-07-01 trunk/paper/IIWAS2010/content/introduction.tex
updated with clints changes

@@
 
-When traveling though a jungle to a destination, it is easier to get
+When traveling though a jungle to a destination, it is easy to get
 lost.  The first person to go somewhere may make a number of mistakes
-in trying to find the best path to their destination.  However, those
-who come later will find it easy to reach that destination if a
+in trying to find the best path to their destination. Those
+who come later find it easier to reach the destination if a
 well-marked trail has been created. Olsen and Malizia describe this
 idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
-a user's discovery experience as a unique entity and working without an example
-context, one can exploit the fact that a similar search may have already been
+a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been
 performed.  In one study, almost 40 percent of all queries
-were found to be repetitions of previous queries\cite{1277770}. This
-indicates the reuse of prior searches is a way to optimize the search
+were repetitions of previous queries\cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
 process.  Morpheus is a question answering system motivated by reuse of prior
-web search pathways to yield an answer to a user query. Using our analogy,
-Morpheus follows path-finders to their destinations and not only marks the
+web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the
 trail, but also provides a taxi service to take followers to similar
@@
 
-The Morpheus system employs two distinct roles. One type is called a
-\textit{guide} who types queries in the Morpheus web interface and
-searches for an answer to the query in an instrumented web browser that can
-track answer pathways for a given query. This web tracking tool stores the query
-and necessary information to revisit the pathways to the page where the guide 
-found the answer. It also provides a mechanism for guides to highlight the answers.
-The other role is a \textit{user}, who searches with the Morpheus system much
-like a regular search engine, having a natural language interface. The users type a
-question in a text box and receive a response from the system. The system
-exploits previously answered queries to these answer new questions.
+There are two distinct Morpheus user roles. A
+\textit{path-finder} enters queries in the Morpheus web interface and
+searches for an answer to the query using an instrumented web browser. 
+This web tracking tool stores the query
+and necessary information to revisit the pathways to the page where the path-finder 
+found the answer.
+A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface.
+The path-follower enters a question in a text box and receives a guided path to the answer.
+The system exploits previously found paths to provide an answer.
 
-To exploit the prior searches one should represent queries in an elegant way so
-that similar queries can be found efficiently and their stored search path
-revisited to produce the answer to the user. Morpheus represents user-query details
-in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It
-includes a user query in natural-language format, relevant terms for the query,
-place holders for the term \textit{categories}. A \textit{category} represents a
-topic or class to which a term belongs. For example, the term \textit{tire} can be
-classified into the category \textit{Automotive Parts}.
+Morpheus represents user-query details in a semi-structured query (SSQ).
+It includes a user query in natural-language format, relevant terms for the query, and place holders for the term \textit{categories}.
+A \textit{category} represents a
+topic or class to which a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Part}.
 
 Morpheus assumes the term categories are classes of a
-\textit{consistent} realm-based ontology. By consistant we mean the ontology has two
-properties: (i) singly-rooted heterarchy (acyclic digraph with unique 
-ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
-semantic interpretations. This is important because, our proposed similarity 
-measure for categories is based on the heterarchically
-structured category ontologies. Moreover, when a regular user enters a query,
-Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
+\textit{consistent} realm-based ontology, that is, one having a singly rooted heterachy whose
+subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on category similarity. Suppose a
 regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In

### 2010-07-01 trunk/paper/IIWAS2010/content/results_discussion.tex
updated with clints changes

@@
 
-As an initial step we created a man-made realm-ontology for the automotive realm
- exploiting the Wikipedia pages, categories, and WordNet synsets. For each of
-the categories in the realm-ontolgy we built corpora by grabbing the
-corresponding Wikipedia pages. The following section describes question
-answering process for a user query, ``A 1997 Toyota Camry V6 needs what size
-tires?''
+First, we built an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets.
+For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
+Figure \ref{fig:automotive_ontology} shows a subsection of this ontology.
 
-The Morpheus NLP engine parses this query into the constructs: WH:what,
-Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
-descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
-Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
-each of the terms, we determined relevant categories (non-increasing order of
-relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
-the top categories and their probabilities for each of the query term:
+ describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
+
+%% TODO - need to refer back to the table which is figure one.
+%The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires.
+From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6.
+For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora.
+Table \ref{tbl:term_categories} shows the top categories and their probabilities for each of the query term.
+In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .  It extracts the WH question
+
+\begin{table}[h]\footnotesize
+	\begin{tabular}{|l|p{4.2cm}|}
+		\hline 
+		WH & what \\
+		\hline 
+		Descriptive Information & 1997 Toyota Camry V6 \\
+		\hline 
+		Asking for & size tires \\
+		\hline 
+		ngrams & 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
+		\hline
+	\end{tabular}
+	\caption{The output of NLP engine parse}
+	\label{tbl:nlp_engine_parse} 
+\end{table}
 
@@
 
-We used this top category of each of the terms in the candidate SSQ and
-determined the category divergence with the qualified SSQ categories in the QRM
-store. We assumed that all of them belong to the same realm or domain (but, it
-is different in real time). In the end, we combined the divergence measure and
-ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries}
-shows the top ranked queries that belong to the QRMs in store for the above
-query.
+We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
+ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.
 
@@
 \hline
-Query & Tagged Categories & Score\\ \hline
+Query & Tagged Classes & Score\\ \hline
 A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
 What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
-Where can I buy an engine for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
-What is the cost of a Toyota Camry V6 engine? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
+%Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
+%What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
 \end{tabular}
 
-\caption{Top ranked queries and relevance scores: IC - input categories, OC - output categories}
+\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
 \label{tbl:ranked_queries}
@@
 
-In this paper, we proposed a novel question answering system that uses previously 
-answered user queries to answer similar questions using deep web site.  
-The system uses a guide to annotate answer paths so folowing users 
-can discover answers to complicated questions.  Each question answer pair is 
-assigned a realm, and new questions are matched to the new question answer pairs. 
-This query matching strategy assumes that candidate query terms are
-available in the category corpus. The candidate query's category annotation will
-fail if the query terms are not available. In addition, classification of a
-term or n-gram into a category is based on the term frequency distributions in a
-classified web document. We are working on improving this
-approach by using a probabilistic generative approach as used in the Topic
-Models\cite{Blei2003latentdirichlet}.
+In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions.
+The system uses a path-finder to annotate answer paths so path-followers can discover answers to similar questions.
+Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs.
+Classification of terms into classes is based on term frequency distributions in our corpora of web documents.
+We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.
 
-Similarly, the Morpheus ontology building
-process needs categorized web pages. As explained in section
-\ref{sec:ontology_generators}, the Wikipedia page categories have some
-limitations for this purpose. Without supervision, the page categorization is
-often a challenging problem, because topics in the pages that belong to a realm
-(e.g. automotive) usually overlap. So we are evaluating the applicability of
-probabilistic topic models to web page categorization, and automatic
-generation of a realm-ontology based on the topics being extracted.
+Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task.
+Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
+%The Wikipedia page categories has limitations.
+Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g.
+automotive) usually overlap.
+So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.
 

### 2010-07-01 paper/IIWAS2010/content/system_arch.tex
updated with clints changes

@@
 In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.
-LDA is Bayesian model represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
+LDA is Bayesian model that represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
 For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages.
@@
 
-%% Was edited and shortened by Joir-dan and Wilson (2010-06-29)
 The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question.
 The path-finder also uses the tool to identify ontological categories associated with search terms.
-Morpheus stores the query together with its terms and categories as an SSQ (Figure \ref{fig:ssq_example}).
+Morpheus stores the query together with its terms and categories as an SSQ (Table \ref{tab:ssq_example}).
 Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.
 
-%% Was added by Joir-dan and Wilson (2010-06-29)... but may need to be better formatted
-\begin{figure}[t]
-\label{fig:ssq_example}
-("An  1997 Toyota Camry V6 has what size tires", 
-     (1997: Date, Toyota: Manufacturer, Camry: Model, V6: Engine ),
-     (tire: Part, size: Measurement))
+%	\begin{figure}[t]
+%\label{fig:ssq_example}
+%("An  1997 Toyota Camry V6 has what size tires", 
+%     (1997: Date, Toyota: Manufacturer, Camry: Model, V6: Engine ),
+%     (tire: Part, size: Measurement))
+%\caption{An example SSQ for the question: A 1997 Toyota Camry V6 has what size tires?}
+%\end{figure}
 
-%% Comment made by Joir-dan Gumbs (2010-06-29) 
-%%Need to talk a bit about this SSQ Structure: Does anyone see anything wrong with this representation?
-\caption{An example SSQ for the question: A 1997 Toyota Camry V6 has what size tires?}
-\end{figure}
+%Query & \multicolumn{9}{|c|}{A 1997 Toyota Camry V6 has what size tires?}\\
 
-%% Edited by Joir-dan and Wilson (2010-06-29)
+\begin{table}
+\scalebox{0.76}{
+	\rowcolors{1}{white}{white}
+	\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
+		\hline
+		\textbf{Terms} & 1997 & Toyota & Camry & V6 & size & tires \\
+		\hline
+		\textbf{Input} & Date & Manufacturer & Model & Engine & &  \\
+		\textbf{Output} & & & & & Measurement & Part \\
+		\hline
+	\end{tabular}
+	}
+	\caption{An SSQ for the question: ``A 1997 Toyota Camry V6 has what size tires?"  Cells represent categories}
+	\label{tab:ssq_example}
+\end{table}
+
 The \emph{Query Resolution Method} (QRM) is a data structure that models the
@@
 Queries inserted by path-followers take a different approach.
-The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams.
-The system then assigns the most probable realm to the query using \textit{realm}|\textit{n-gram} priors calculated from realm-specific corpora.
-Once the realm is assigned, an ontology search is performed to assign classes to the n-grams.
+The Morpheus search system parses, tags, and processes the queries in order to pull important terms.
+The system then assigns the most probable realm to the query using $p(realm|term)$ priors calculated from realm-specific corpora.
+Once the realm is assigned, an ontology search is performed to assign classes to the terms.
 An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user.
-Rather than matching n-grams, the goal is to match input and output classes, since the paths can potentially answer similar queries.
+Rather than matching terms, the goal is to match input and output classes, since the paths can potentially answer similar queries.
 
@@
 	\centering
-\includegraphics[width=85mm]{img/automotive_ontology.eps}
+%\includegraphics[width=85mm]{../img/automotive_ontology.eps}
+\includegraphics[width=85mm]{automotive_ontology.eps}
 \caption{An abbreviated man-made automotive ontology - arrows represent inheritance relationships between the ontological classes.}
@@
 
-QRM contains the necessary  
-information required to re-run this procedure.Once we have 
-relevant QRMs through QRM ranking for a given user query, we can  
-get answers by re-running the pathways with help of 
-the \emph{Query Resolution Engine} (QRE) of Morpheus.
+Once we have relevant QRMs through QRM ranking for a given user query, we can produce answers by re-running the pathways.
+
+The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.
+It simulates a human clicking buttons to follow links, submitting forms, and highlighting of data to form a textual answer.
+The QE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.
+It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.
+
+%When a user submits a new query to the Morpheus system, one or more stored QRMs are executed to obtain results.
+A QRM contains an XML script representing an algorithm that will obtain the required result.
+The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, highlighting data, cutting and pasting text, and constructing an answer in the form of a text string.
+There is greater complexity in dealing with web forms than with links.
+At present, the GET form submission method is used.
+This means that in preparation to submit a form, the Morpheus System builds a querystring consisting of name-value pairs.
+For a given form, there may be text fields, drop-down boxes, and among other components.
+In order to support form submission in such circumstances, the QRE performs different actions based upon the input type.
+For text fields, simply adding a key/value pair to the query string suffices.
+For a drop-down box, the QRE extracts the form element to find the appropriate value to include in the query string.
+It does this by examine each option in the drop-down and matching the user’s input to the text field in the option.
+The value attribute of the option is then added to the querystring.
+The value and text attributes of a dropdown option might be the same, but they are not guaranteed to be.
+All input data are kept in an internal table.
+The QRM script contains keys that allow the QRE to map SSQ inputs from the table to the appropriate form inputs.
+Furthermore, highlighted text segments collected during execution of the script are stored in the table.
+Once all actions in the script have been carried out, the QRE returns the textual answer this process has created.
+This answer is then be rendered in a browser displayed to the user.

### 2010-07-01 paper/IIWAS2010/content/abstract.tex
IIWAS 2010 submission: Initial draft
latest commit before added joirdan altered diagram

--- 2010-03-03 paper/semsearch10/content/abstract.tex
@@
 \begin{abstract}
-- It is difficult to answer question that change over time
-- However, if the method of answering the question can be realized, the question can be easily answered
-- We are building a system that supports a learning how to answer particular questions
-- We can answer questions that are semantically similar to our store of questions
-- We do this by building a semantic library ...
+
+The Morpheus question answering system uses deep web search to answer user queries.
+Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology.
+Morpheus answers questions by using methods from prior successful searches.
+The system ranks stored methods based on a similarity quasi-metric defined on assigned classes of queries.
+Similarity depends on the class heterarchy in an ontology and its associated text corpora.
+Finally, Morpheus revisits the prior search pathways of the stored searches to construct possible answers.
+The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet.
+This paper describes the entire process with emphasis on the matching of user queries to stored answering methods.
+
 \end{abstract}

### 2010-07-01 paper/IIWAS2010/content/introduction.tex
small intro change
latest commit before added joirdan altered diagram

@@
 
-When traveling though a jungle to a destination, it is easy to get
-lost.  The first person to go somewhere may make a number of mistakes
-in trying to find the best path to their destination. Those
-who come later find it easier to reach the destination if a
-well-marked trail has been created. Olsen and Malizia describe this
-idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
-a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been
-performed.  In one study, almost 40 percent of all queries
-were repetitions of previous queries\cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
-process.  Morpheus is a question answering system motivated by reuse of prior
-web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the
-trail, but also provides a taxi service to take followers to similar
+When traveling though a jungle to a destination, it is easy to get lost.
+The first person to journey somewhere may make a number of mistakes when trying to find the best path to their destination.
+Those who come later find it easier to reach the destination if a well-marked trail has been created.
+Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.
+Rather than treating a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been performed.
+In one study, almost 40 percent of all queries were repetitions of previous queries\cite{1277770}.
+Thus, reuse of prior searches is one way to optimize the search
+process.
+Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
+Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar
 destinations.
@@
 There are two distinct Morpheus user roles. A
-\textit{path finder} enters queries in the Morpheus web interface and
+\textit{path-finder} enters queries in the Morpheus web interface and
 searches for an answer to the query using an instrumented web browser. 
 This web tracking tool stores the query
-and necessary information to revisit the pathways to the page where the guide 
+and necessary information to revisit the pathways to the page where the path-finder 
 found the answer.
-A \textit{path follower} uses the Morpheus system much like a regular search engine with a natural language interface.
-The path follower enters a question in a text box and receives a guided path to the answer.
+A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface.
+The path-follower enters a question in a text box and receives a guided path to the answer.
 The system exploits previously found paths to provide an answer.
@@
 Morpheus represents user-query details in a semi-structured query (SSQ).
-It includes a user query in natural-language format, relevant terms for the query, and place holders for the term \textit{categories}.
-A \textit{category} represents a
-topic or class to which a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Part}.
-
-Morpheus assumes the term categories are classes of a
-\textit{consistent} realm-based ontology, that is, one having a singly rooted heterachy whose
-subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on category similarity. Suppose a
-regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
-this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
-and a predecessor of \textit{automobile models} is important, because this will
-help us grouping stored queries.
+It assumes the terms belong to classes of a \textit{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations.
+When a path-follower enters a query, Morpheus ranks SSQs in the store based on class similarity.
+Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g.
+\emph{Manufacturer} with \emph{Toyota}, helps us identify similar queries.
 
@@
 Section \ref{sec:systemarch} explains the Morpheus system and its implementation.
-Section \ref{sec:results}, we describe current results and their
-interpretation. We conclude by describing the global impacts
-of our approaches in QA systems.
+In Section \ref{sec:results} we describe the current results of our approach.
+Finally, we conclude with future goals for the system.

### 2010-07-01 trunk/paper/IIWAS2010/content/related_work.tex
latest commit before added joirdan altered diagram

@@
 This idea has led to socially integrated QA systems such as Aardvark \cite{vark2010}.
-In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond webpages (e.g.
+In addition to having questions answered by users, Aardvark can contact potential question answerers through media beyond web pages (e.g.
 instant messages, mobile phones).
 This allows for faster responses to questions.
-Morpheus relies on both its user interface and previous similar questions answered by a community of users to give a fast reliable answer.
+Morpheus relies on both its user interface and referencing similar questions previously answered.
 
@@
 
-The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making it available on the Web.
-Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages, and redirects between pages in Wiki markup form \cite{Bizer2009}.
+The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making this information available on the Web.
+Wikipedia semantics includes info-box templates, categorization information,  images, geo-coordinates, links to external web pages, disambiguation pages, and redirects to pages in Wiki markup form \cite{Bizer2009}.
 DBpedia does not define any new relations between the Wikipedia categories.
-Morpheus the DBpedia categories and its semantics to construct its ontology.
+
+%Morpheus uses the DBpedia categories and its semantics to construct its ontology.
 %  DBpedia represents the Wikipedia categories using skos:concepts and category relations using skos:broader \cite{Bizer2009}.
@@
 
-YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}.
-YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes.
+YAGO is a semi-automatically constructed ontology obtained from the Wikipedia pages, info-boxes, categories, and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}.
+YAGO uses the Wikipedia page \emph{titles} as its ontology \emph{individuals} and \emph{categories} as its ontology \emph{classes}.
 YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
-YAGO discovers connections between a WordNet synsets and a Wikipedia categories parsing the category names and matching the parsed category components with the WordNet synsets \cite{Suchanek2009phd}.
+YAGO discovers connections between WordNet synsets and Wikipedia categories, parsing the category names and matching the parsed category components with the WordNet synsets.
 Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
-Morpheus uses many of the same ideas made when using YAGO to develop its own ontology as explained in Section \ref{sec:ontology_corpora}.
+
+We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.
+Thus far, these ontologies can be used to classifiy terms, however their classes do not always appropriately categorize query parameters.
+Therefore, we are researching XXX in order to XXX.% TODO - fill in the XXX
+
+%Morpheus uses many of the same ideas made when using YAGO to develop its own ontology as explained in Section \ref{sec:ontology_corpora}.
 

### 2010-07-01 trunk/paper/IIWAS2010/content/results_discussion.tex
latest commit before added joirdan altered diagram

@@
 
-First, we built an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets.
+First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, categories, and WordNet synsets.
 For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
-Figure \ref{fig:automotive_ontology} shows a subsection of this ontology.
+Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.
 
- describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
+%describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
 
@@
 Table \ref{tbl:term_categories} shows the top categories and their probabilities for each of the query term.
-In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .  It extracts the WH question
+In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .
+It extracts the WH question, that is, the the term that identifies the sentence as a question.
+Next, the engine locates the descriptive information that can be used to describe the answer.
+Then the engine extracts the terms that describe what is being requested.
+Finally, the engine produces n-grams from the terms in the descriptive information sections.
+
+Using the data in \ref{tbl:nlp_engine_parse} we determined relevant classes (non-increasing order of relevance) from the ontology given each n-gram.
+Table \ref{tbl:term_categories} shows the top classes and their probabilities for our example.
 
@@
 		\hline 
-		ngrams & 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
+		n-grams & 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
 		\hline
@@
 	\hline
-Query & Tagged Classes & Score\\ \hline
-A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
-What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
-%Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
+	Query & Tagged Classes & Score\\ 
+	\hline
+	A 1997 Toyota Camry V6 needs what size tires? & inputs(Sedans, Cars, Engines, Manufactures) & 0.91\\ 
+	\hline 
+	What is the tire size for a 1998 Sienna XLE Van? & inputs(1998 Toyota Sienna XLE Van: Vans, Toyota : Manufacturers) & 0.72\\ 	\hline 
+	Where can I buy an engine for a Toyota Camry V6? & inputs(Toyota Camry : Sedans, Toyota Camry V6 : Automobile_Engines, Toyota : Manufacturers) & 0.74 \\
+	\hline 
 %What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
@@
 Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g.
-automotive) usually overlap.
+vehicular) usually overlap.
 So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.

### 2010-07-01 trunk/paper/IIWAS2010/content/system_arch.tex
latest commit before added joirdan altered diagram

@@
 Each leaf node in the ontology is associated with a corpus of words belonging to a class.
-For example, we have constructed an automotive ontology containing classes relevant to the automotive realm.
+For example, we have constructed an vehicular ontology containing classes relevant to the vehicular realm.
 This ontology provides a structure for reference in the following sections.
@@
 Morpheus uses the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages.
-This approach is motivated by YAGO \cite{Suchanek2009phd}.
 First a realm is mapped to a DBpedia category \cite{Bizer2009}.
@@
 In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.
-LDA is Bayesian model represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
+LDA is Bayesian model that represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
 For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages.
 Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
-Additionally, given a text document, using LDA we could tag related documents by matching the similarity over the estimated topic proportions, which is useful in the ontology and corpora building.
-Due to its fully generative semantics, even at the level of documents, LDA could address the drawbacks (such as dimensionality and failure in finding the discriminative set of words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI.
+Given a text document, we tag related documents by matching their similarity over the estimated topic proportions, assisting in ontology and corpora construction.
+Due to its fully generative semantics, this usage of LDA could address drawbacks of frequency based approaches (e.g.
+TF-IDF, LSI, and pLSI) such as dimensionality and failure to find the discriminative set of words for a document.
+%of frequency based approaches.% such as TF-IDF, LSI, and pLSI.
 
@@
 
-%% Was edited and shortened by Joir-dan and Wilson (2010-06-29)
 The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question.
 The path-finder also uses the tool to identify ontological categories associated with search terms.
-Morpheus stores the query together with its terms and categories as an SSQ (Figure \ref{fig:ssq_example}).
+Morpheus stores the query together with its terms and categories as an SSQ.
+Table \ref{tab:ssq_example} is an example showing the SSQ model of the query ``A 1997 Toyota Camry V6 has what size tires?".
+The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified.
 Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.
 
-%% Was added by Joir-dan and Wilson (2010-06-29)... but may need to be better formatted
-\begin{figure}[t]
-\label{fig:ssq_example}
-("An  1997 Toyota Camry V6 has what size tires", 
-     (1997: Date, Toyota: Manufacturer, Camry: Model, V6: Engine ),
-     (tire: Part, size: Measurement))
+%	\begin{figure}[t]
+%\label{fig:ssq_example}
+%("An  1997 Toyota Camry V6 has what size tires", 
+%     (1997: Date, Toyota: Manufacturer, Camry: Model, V6: Engine ),
+%     (tire: Part, size: Measurement))
+%\caption{An example SSQ for the question: A 1997 Toyota Camry V6 has what size tires?}
+%\end{figure}
 
-%% Comment made by Joir-dan Gumbs (2010-06-29) 
-%%Need to talk a bit about this SSQ Structure: Does anyone see anything wrong with this representation?
-\caption{An example SSQ for the question: A 1997 Toyota Camry V6 has what size tires?}
-\end{figure}
+%Query & \multicolumn{9}{|c|}{A 1997 Toyota Camry V6 has what size tires?}\\
 
-%% Edited by Joir-dan and Wilson (2010-06-29)
-The \emph{Query Resolution Method} (QRM) is a data structure that models the
-question answering process.
+%% TODO - we need the table here
+\begin{table}\footnotesize
+\scalebox{0.76}{
+	\rowcolors{1}{white}{white}
+	\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
+		\hline
+		\textbf{Terms} & 1997 & Toyota & Camry & V6 & size & tires \\
+		\hline
+		\textbf{Input} & Date & Manufacturer & Model & Engine & &  \\
+		\hline
+		\textbf{Output} & & & & & Measurement & Part \\
+		\hline
+	\end{tabular}
+	}
+	\caption{Example SSQ Model.}
+	\label{tab:ssq_example}
+\end{table}
+
+The \emph{Query Resolution Method} (QRM) is a data structure that models the question answering process.
 A QRM represents a generalized executable realization of the search process that the path-finder followed.
@@
 Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process.
-For each dynamic page, it stores the list of inputs to the URL such as form inputs and the possible reference outputs (highlighted portions of the web page).
+For each dynamic page, the QRM contains a list of inputs to the URL such as form inputs and the possible reference outputs.
 
@@
 Queries inserted by path-followers take a different approach.
-The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams.
-The system then assigns the most probable realm to the query using $p(realm|n-gram)$ priors calculated from realm-specific corpora.
-Once the realm is assigned, an ontology search is performed to assign classes to the n-grams.
-An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user.
-Rather than matching n-grams, the goal is to match input and output classes, since the paths can potentially answer similar queries.
+The Morpheus search process parses and tags queries in order to record important terms.
+The system assigns the most probable realm given the terms in the query as calculated from realm-specific copora.
+Once the realm is assigned, an ontology search is performed to assign classes to the terms.
+An SSQ is constructed and the system attempts to match this candidate SSQ to existing QRM SSQs.
+Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer similar queries.
 
@@
 
-To answer a user's query, a \textit{candidate
-SSQ}, Morpheus finds similar SSQs that belong to QRMs in the Morpheus data store (a \textit{qualified SSQ}).  To determine SSQ similarity, we
-consider the SSQ's realm, input terms, output terms, and their assigned classes.
+To answer a user's query, a candidate SSQ, Morpheus finds similar qualified SSQs that are associated with QRMs in the Morpheus data store.
+To determine SSQ similarity, we consider the SSQ's realm, input terms, output terms, and their assigned classes.
 
@@
 
-We employ a quasimetric, \textit{category
-divergence (cd)},
-between a source category and a target category using the \textit{topological
-structure} of the categories in an ontology. We write $S \prec T$ for the
-reflexive
-transitive closure of the supercategory relation. Let $d(P,Q)$ represent the hop
-distance in the directed ontology inheritance graph from $P$ to $Q$. The
-divergence between a source and target category ranges from zero (for identical
-categories) to one (for type incompatible categories). Let $S$ be the source
-category, $T$ be
-the target category, and $C$ be a least common ancestor category of $S$ and
-$T$ i.e., one that minimizes $d(S,C) + d(T,C)$. The category divergence between $S$ and $T$ is defined given by:
+We employ a quasimetric, \textit{category divergence (cd)}, between a source category and a target category using the \textit{topological structure} of the categories in an ontology.
+We write $S \prec T$ for the reflexive transitive closure of the supercategory relation.
+Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
+The divergence between a source and target category ranges from zero (for identical categories) to one (for type incompatible categories).
+Let $S$ be the source category, $T$ be the target category, and $C$ be a least common ancestor category of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
+The category divergence between $S$ and $T$ is defined given by:
 
@@
 
-\noindent where $h$ is the height of the ontology tree.
+\noindent where $h$ is the longest path in the ontology class heterarchy.
 
@@
 	\centering
-\includegraphics[width=85mm]{img/automotive_ontology.eps}
-\caption{An abbreviated man-made automotive ontology - arrows represent inheritance relationships between the ontological classes.}
-\label{fig:automotive_ontology}
+%\includegraphics[width=85mm]{../img/vehicular_ontology.eps}
+\includegraphics[width=85mm]{vehicular_ontology.eps}
+\caption{Abbreviated Vehicular Ontology}% - arrows represent inheritance relationships between the ontological classes.}
+\label{fig:vehicular_ontology}
 \end{figure}
 
-Suppose we want to find the category divergence between \textit{Sedans}
-and \textit{Trucks} (Figure \ref{fig:automotive_ontology}). 
-\textit{Sedans} is the subcategory of \textit{Cars}, and \textit{Trucks}
-is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
-for these twoThis section presents ontology and copora, Query processing, ranking queries, and the query resolution mechanism.
-categories is \textit{Automobiles}.
+Suppose we want to find the category divergence between \textit{Sedan} and \textit{Bus} Figure \ref{fig:vehicular_ontology}.
+\textit{Sedan} is the subcategory of \textit{Sedan}, and \textit{Bus} is the subcategory of \textit{Automobile}.
+Therefore, the least common ancestor ($C$) for these two.
+This section presents ontology and copora, query processing, ranking queries, and the query resolution mechanism.
+categories is \textit{Automobile}.
 In addition, the tree height \textit{h = 4}.
-So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}
-that is calculated from \textit{d(Sedans, Root) = 4}, \textit{d(Sedans, Automobiles) = 2}, and \textit{d(Trucks, Automobiles) = 1}.
+So, the normalized divergence $cd$\textit{(Sedan, Bus)} is \textit{7/12} that is calculated from \textit{d(Sedan, Root) = 4}, \textit{d(Sedan, Automobile) = 2}, and \textit{d(Bus, Automobile) = 1}.
 
@@
 
- The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, and highlighting of data to form a text answer.
-The QRE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.
+The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.
+It simulates a human clicking buttons to follow links, submitting forms, and highlighting of data to form a textual answer.
+The QE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.
 It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.

### 2010-07-01 trunk/paper/IIWAS2010/content/system_arch.tex
latest version

@@
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) <
-cd(S,Q)$, that is, the divergence of a source category to a target
-ancestor category is smaller than the divergence of a source category to any
-category that is not an ancestor. This is an important property in
-determining the compatibility of categories for answering queries.  If a
-SSQ answers queries concerning an ancestor category, it is more relevant
-that a SSQ that answers queries from any non-ancestral category.
+Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source category to a target ancestor category is smaller than the divergence of a source category to any category that is not an ancestor.
+This is an important property in determining the compatibility of categories for answering queries.
+If a SSQ answers queries concerning an ancestor category, it is more relevant that a SSQ that answers queries from any non-ancestral category.
 
 % Algorithm 1: figure  
+%\begin{figure}[t]
+%	\centering
+%\includegraphics[width=85mm]{../img/vehicular_ontology.eps}
+%\includegraphics[width=85mm]{vehicular_ontology.eps}
+%\includegraphics[width=85mm]{img/OntologyDiagram.eps}
+%\caption{Abbreviated Vehicular Ontology}% - arrows represent inheritance relationships between the ontological classes.}
+%\label{fig:vehicular_ontology}
+%\end{figure}
+
 \begin{figure}[t]
-	\centering
-%\includegraphics[width=85mm]{../img/vehicular_ontology.eps}
-\includegraphics[width=85mm]{vehicular_ontology.eps}
-\caption{Abbreviated Vehicular Ontology}% - arrows represent inheritance relationships between the ontological classes.}
+	\includegraphics[scale=.65]{../img/OntologyDiagram.png}
+	\caption{Abbreviated Vehicular Ontology}
 	\label{fig:vehicular_ontology}
@@
 In addition, the tree height \textit{h = 4}.
-So, the normalized divergence $cd$\textit{(Sedan, Bus)} is \textit{7/12} that is calculated from \textit{d(Sedan, Root) = 4}, \textit{d(Sedan, Automobile) = 2}, and \textit{d(Bus, Automobile) = 1}.
+So, the normalized divergence $cd$\textit{(Sedan, Bus)} is \textit{7/12} that is calculated from \textit{d(Sedan, Root) = 4}, \textit{d(Sedan, Automobile) = 2}, and \textit{d (Bus, Automobile)=1}.
 

### 2010-07-01 paper/IIWAS2010/content/results_discussion.tex
modified figure 4

@@
 
-First, we created an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets.
+First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, categories, and WordNet synsets.
 For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
-Table describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
+Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.
+
+%describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
 
 %% TODO - need to refer back to the table which is figure one.
-The Morpheus NLP engine parses this query into the constructs: WH:what,
-Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
-descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
-Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
-each of the terms, we determined relevant categories (non-increasing order of
-relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
-the top categories and their probabilities for each of the query term:
+%The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires.
+From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6.
+For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora.
+Table \ref{tbl:term_categories} shows the top categories and their probabilities for each of the query term.
+In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .
+It extracts the WH question, that is, the the term that identifies the sentence as a question.
+Next, the engine locates the descriptive information that can be used to describe the answer.
+Then the engine extracts the terms that describe what is being requested.
+Finally, the engine produces n-grams from the terms in the descriptive information sections.
+
+Using the data in \ref{tbl:nlp_engine_parse} we determined relevant classes (non-increasing order of relevance) from the ontology given each n-gram.
+Table \ref{tbl:term_categories} shows the top classes and their probabilities for our example.
+
+\begin{table}[h]\footnotesize
+	\begin{tabular}{|l|p{4.2cm}|}
+		\hline 
+		WH & what \\
+		\hline 
+		Descriptive Information & 1997 Toyota Camry V6 \\
+		\hline 
+		Asking for & size tires \\
+		\hline 
+		n-grams & 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
+		\hline
+	\end{tabular}
+	\caption{The output of NLP engine parse}
+	\label{tbl:nlp_engine_parse} 
+\end{table}
 
@@
 	\hline
-Query & Tagged Classes & Score\\ \hline
-A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
-What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
-Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
-What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
+	Query & Tagged Classes & Score\\ 
+	\hline
+	A 1997 Toyota Camry V6 needs what size tires? & Sedan, Car, Engine, Manufacture & 0.91\\ 
+	\hline 
+	What is the tire size for a 1998 Sienna XLE Van? & 1998 Toyota Sienna XLE Van: Van, Toyota : Manufacturers & 0.72\\
+	\hline 
+	Where can I buy an engine for a Toyota Camry V6? & Toyota Camry : Sedan, Toyota Camry V6 : Automobile Engine, Toyota : Manufacturers & 0.74 \\
+	\hline 
+%What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
 \end{tabular}
@@
 In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions.
-The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.
+The system uses a path-finder to annotate answer paths so path-followers can discover answers to similar questions.
 Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs.

### 2010-07-02 paper/IIWAS2010/content/system_arch.tex
Modified the example based on the new figure

@@
 Each leaf node in the ontology is associated with a corpus of words belonging to a class.
-For example, we have constructed an automotive ontology containing classes relevant to the automotive realm.
+For example, we have constructed a vehicular ontology containing classes relevant to the vehicular realm.
 This ontology provides a structure for reference in the following sections.
@@
 Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
-Additionally, given a text document, using LDA we could tag related documents by matching the similarity over the estimated topic proportions, which is useful in the ontology and corpora building.
-Due to its fully generative semantics, even at the level of documents, LDA could address the drawbacks (such as dimensionality and failure in finding the discriminative set of words for a document) of frequency based approaches such as TF-IDF, LSI, and pLSI.
+Given a text document, we tag related documents by matching their similarity over the estimated topic proportions, assisting in ontology and corpora construction.
+Due to its fully generative semantics, this usage of LDA could address drawbacks of frequency based approaches (e.g.
+TF-IDF, LSI, and pLSI) such as dimensionality and failure to find the discriminative set of words for a document.
+%of frequency based approaches.% such as TF-IDF, LSI, and pLSI.
 
@@
 The path-finder also uses the tool to identify ontological categories associated with search terms.
-Morpheus stores the query together with its terms and categories as an SSQ (Table \ref{tab:ssq_example}).
+Morpheus stores the query together with its terms and categories as an SSQ.
+Table \ref{tab:ssq_example} is an example showing the SSQ model of the query ``A 1997 Toyota Camry V6 has what size tires?".
+The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified.
 Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.
@@
 
-\begin{table}
+%% TODO - we need the table here
+\begin{table}[h]
 \scalebox{0.76}{
-	\rowcolors{1}{white}{white}
 	\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
@@
 		\textbf{Input} & Date & Manufacturer & Model & Engine & &  \\
+		\hline
 		\textbf{Output} & & & & & Measurement & Part \\
@@
 	}
-	\caption{An SSQ for the question: ``A 1997 Toyota Camry V6 has what size tires?"  Cells represent categories}
+	\caption{Example SSQ Model.}
 	\label{tab:ssq_example}
@@
 
-The \emph{Query Resolution Method} (QRM) is a data structure that models the
-question answering process.
+The \emph{Query Resolution Method} (QRM) is a data structure that models the question answering process.
 A QRM represents a generalized executable realization of the search process that the path-finder followed.
@@
 Queries inserted by path-followers take a different approach.
-The Morpheus search system parses, tags, and processes the queries in order to pull important terms.
-The system then assigns the most probable realm to the query using $p(realm|term)$ priors calculated from realm-specific corpora.
+The Morpheus search process parses and tags queries in order to record important terms.
+The system assigns the most probable realm given the terms in the query as calculated from realm-specific copora.
 Once the realm is assigned, an ontology search is performed to assign classes to the terms.
-An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user.
-Rather than matching terms, the goal is to match input and output classes, since the paths can potentially answer similar queries.
+An SSQ is constructed and the system attempts to match this candidate SSQ to existing QRM SSQs.
+Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer similar queries.
 
@@
 
-\noindent where $h$ is the height of the ontology tree.
+\noindent where $h$ is the longest path in the ontology class heterarchy.
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) <
-cd(S,Q)$, that is, the divergence of a source category to a target
-ancestor category is smaller than the divergence of a source category to any
-category that is not an ancestor. This is an important property in
-determining the compatibility of categories for answering queries.  If a
-SSQ answers queries concerning an ancestor category, it is more relevant
-that a SSQ that answers queries from any non-ancestral category.
+Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source category to a target ancestor category is smaller than the divergence of a source category to any category that is not an ancestor.
+This is an important property in determining the compatibility of categories for answering queries.
+If a SSQ answers queries concerning an ancestor category, it is more relevant that a SSQ that answers queries from any non-ancestral category.
 
-% Algorithm 1: figure  
-\begin{figure}[t]
+Suppose we want to find the category divergence between \textit{Bus} and \textit{Sedan} (Figure \ref{fig:vehicular_ontology}).
+\textit{Sedan} is a subcategory of \textit{Automobile}, and \textit{Bus} is a subcategory of \textit{Land\_Vechicle}.
+Therefore, the least common ancestor ($C$) for these two is \textit{Land\_Vechicle}.
+In addition, the tree height \textit{h = 4}.
+So, the normalized divergence $cd$\textit{(Bus, Sedan)} is \textit{0.5} that is calculated from \textit{d(Bus, Root) = 3}, \textit{d(Bus, Land\_Vehicle) = 1}, and \textit{d (Sedan, Land\_Vehicle) = 2}.
+
+\begin{figure}[h]
 	\centering
-%\includegraphics[width=85mm]{../img/automotive_ontology.eps}
-\includegraphics[width=85mm]{automotive_ontology.eps}
-\caption{An abbreviated man-made automotive ontology - arrows represent inheritance relationships between the ontological classes.}
-\label{fig:automotive_ontology}
+	\includegraphics[scale=0.90]{OntologyDiagram.png}
+	\caption{Abbreviated Vehicular Ontology}
+	\label{fig:vehicular_ontology}
 \end{figure}
-
-Suppose we want to find the category divergence between \textit{Sedans}
-and \textit{Trucks} (Figure \ref{fig:automotive_ontology}). 
-\textit{Sedans} is the subcategory of \textit{Cars}, and \textit{Trucks}
-is the subcategory of \textit{Automobiles}. Therefore, the least common ancestor ($C$)
-for these twoThis section presents ontology and copora, Query processing, ranking queries, and the query resolution mechanism.
-categories is \textit{Automobiles}.
-In addition, the tree height \textit{h = 4}.
-So, the normalized divergence $cd$\textit{(Sedans, Trucks)} is \textit{7/12}
-that is calculated from \textit{d(Sedans, Root) = 4}, \textit{d(Sedans, Automobiles) = 2}, and \textit{d(Trucks, Automobiles) = 1}.
 

### 2010-07-02 paper/IIWAS2010/content/introduction.tex
latest working copy
latest version

@@
 Rather than treating a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been performed.
-In one study, almost 40 percent of all queries were repetitions of previous queries\cite{1277770}.
+In one study, almost 40 percent of all queries were repetitions of previous queries \cite{1277770}.
 Thus, reuse of prior searches is one way to optimize the search
@@
 Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
-Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar
-destinations.
+Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
 
-There are two distinct Morpheus user roles. A
-\textit{path-finder} enters queries in the Morpheus web interface and
-searches for an answer to the query using an instrumented web browser. 
-This web tracking tool stores the query
-and necessary information to revisit the pathways to the page where the path-finder 
-found the answer.
+Morpheus focuses on the deep (or hidden) web to answer questions because its scale and database driven property implies the existence of huge stores of quality information \cite{1453931}.
+Web forms act as an interface to this information.
+Morpheus employs user exploration through these web forms to learn the types of data each deep web location provides.
+
+There are two distinct Morpheus user roles.
+A \textit{path-finder} enters queries in the Morpheus web interface and searches for an answer to the query using an instrumented web browser.
+This web tracking tool stores the query and necessary information to revisit the pathways to the page where the path-finder found the answer.
 A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface.
@@
 Morpheus represents user-query details in a semi-structured query (SSQ).
-It assumes the terms belong to classes of a \textit{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations.
+It assumes the query terms belong to classes of a \textit{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations.
 When a path-follower enters a query, Morpheus ranks SSQs in the store based on class similarity.
-Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g.
-\emph{Manufacturer} with \emph{Toyota}, helps us identify similar queries.
+Suppose a path follower asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g.
+\emph{Manufacturer} with \emph{Toyota}, help us identify similar queries.
 

### 2010-07-02 paper/IIWAS2010/content/related_work.tex
latest version

@@
 This allows for faster responses to questions.
-Morpheus relies on both its user interface and previous similar questions answered by a community of users to give a fast reliable answer.
+Morpheus relies on both its user interface and referencing similar questions previously answered.
 
@@
 
-The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making it available on the Web.
-Wikipedia semantics includes info-box templates, categorization information,  images, Geo-coordinates, links to external Web pages, disambiguation pages, and redirects between pages in Wiki markup form \cite{Bizer2009}.
+The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making this information available on the Web.
+Wikipedia semantics includes info-box templates, categorization information,  images, geo-coordinates, links to external web pages, disambiguation pages, and redirects to pages in Wiki markup form \cite{Bizer2009}.
 DBpedia does not define any new relations between the Wikipedia categories.
@@
 
-YAGO is a semi-automatically constructed ontology from the Wikipedia pages, info-boxes, categories and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}.
-YAGO uses the Wikipedia page titles as its ontology individuals and categories as its ontology classes.
+YAGO is a semi-automatically constructed ontology obtained from the Wikipedia pages, info-boxes, categories, and WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy \cite{Suchanek2009phd}.
+YAGO uses the Wikipedia page \emph{titles} as its ontology \emph{individuals} and \emph{categories} as its ontology \emph{classes}.
 YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives.
-YAGO discovers connections between a WordNet synsets and a Wikipedia categories parsing the category names and matching the parsed category components with the WordNet synsets.
-Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
+YAGO discovers connections between WordNet synsets and Wikipedia categories, parsing the category names and matching the parsed category components with the WordNet synsets.
+Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
 The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
 
-We have attempted to use similar techniques to construct ontologies for question answering realms.
-Thus far, these ontologies can be use to classifiy terms, but their classes do not appropriately categorize deep web query parameters.
-Therefore we have been relegated to manually generating ontologies.
-% TODO - add "this is under investigation"
+We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.
+Thus far, these ontologies can be used to classifiy terms, however their classes do not always appropriately categorize query parameters.
+Therefore, we are researching XXX in order to XXX.% TODO - fill in the XXX
 

### 2010-07-02 paper/IIWAS2010/content/system_arch.tex
latest version

@@
 To build a corpus for each of the leaf nodes in the ontology, we extract \emph{terms} from the Wikipedia pages associated with the DBpedia categories found in its blanket.
-From this term corpus, we can find the likelihood of a term belonging to a particular category.
-This assists in categorizing terms in a \emph{path-follower} query.
-The likelihood is determined by the probability of a category given a term using \textit{Bayes Rule} (Eq.
-\ref{eq:bayesrule}), since we can easily obtain the term-category and term-corpus probabilities as relative frequencies.
+From this term corpus, we can find the likelihood of a term belonging to a particular class.
+This assists in classifying terms in a \emph{path-follower} query.
+The likelihood is determined by the probability of a class given a term using \textit{Bayes Rule} (Eq.
+\ref{eq:bayesrule}), since we can easily obtain the term-class and term-corpus probabilities as relative frequencies.
 
@@
 \label{eq:bayesrule}
-P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+P (class | term) = \frac{P(term | class) P(class)}{P(term)}
 \end{equation}
@@
 The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question.
-The path-finder also uses the tool to identify ontological categories associated with search terms.
-Morpheus stores the query together with its terms and categories as an SSQ.
+The path-finder also uses the tool to identify ontological classes associated with search terms.
+Morpheus stores the query together with its terms and classes as an SSQ.
 Table \ref{tab:ssq_example} is an example showing the SSQ model of the query ``A 1997 Toyota Camry V6 has what size tires?".
@@
 An SSQ is constructed and the system attempts to match this candidate SSQ to existing QRM SSQs.
-Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer similar queries.
+Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer many similar queries.
 
@@
 
-The \emph{class divergence} of two classes within the ontology characterizes their similarity.
+The \emph{class divergence} of two classes within the ontology characterizes their dissimilarity.
 This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches.
 
-We consider the category match as a type match and we use \emph{category divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ.
+We consider the class match as a type match and we use \emph{class divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ.
 Each qualified SSQ will have input terms, output terms, and associated classes, and one realm (from the QRM).
-For the candidate SSQ, the relevant categories for terms are determined from the NLP engine and corpora.
+For the candidate SSQ, the relevant classes for terms are determined from the NLP engine and corpora.
 The calculation of a realm for a candidate query is performed using the n-grams found within the query and any probabilities as found with $p(realm|n\-gram)$.
@@
 by decreasing relevance. The order provides a ranking for the results 
-to the user. The following describes \emph{category divergence} 
+to the user. The following describes \emph{class divergence} 
 in detail.
@@
 
-We employ a quasimetric, \textit{category divergence (cd)}, between a source category and a target category using the \textit{topological structure} of the categories in an ontology.
-We write $S \prec T$ for the reflexive transitive closure of the supercategory relation.
+We employ a quasi-metric, \textit{class divergence (cd)}, between a source class and a target class using the \textit{topological structure} of the classes in an ontology.
+We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
 Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target category ranges from zero (for identical categories) to one (for type incompatible categories).
-Let $S$ be the source category, $T$ be the target category, and $C$ be a least common ancestor category of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
-The category divergence between $S$ and $T$ is defined given by:
+The divergence between a source and target class ranges from zero (for identical classes) to one (for type incompatible classes).
+Let $S$ be the source class, $T$ be the target class, and $C$ be a least common ancestor class of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
+The class divergence between $S$ and $T$ is defined given by:
 
@@
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source category to a target ancestor category is smaller than the divergence of a source category to any category that is not an ancestor.
-This is an important property in determining the compatibility of categories for answering queries.
-If a SSQ answers queries concerning an ancestor category, it is more relevant that a SSQ that answers queries from any non-ancestral category.
+Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
+This is an important property in determining the compatibility of classes for answering queries.
+If an SSQ answers queries concerning an ancestor class, it is more relevant that an SSQ that answers queries from any non-ancestral class.
 
-Suppose we want to find the category divergence between \textit{Bus} and \textit{Sedan} (Figure \ref{fig:vehicular_ontology}).
-\textit{Sedan} is a subcategory of \textit{Automobile}, and \textit{Bus} is a subcategory of \textit{Land\_Vechicle}.
-Therefore, the least common ancestor ($C$) for these two is \textit{Land\_Vechicle}.
-In addition, the tree height \textit{h = 4}.
-So, the normalized divergence $cd$\textit{(Bus, Sedan)} is \textit{0.5} that is calculated from \textit{d(Bus, Root) = 3}, \textit{d(Bus, Land\_Vehicle) = 1}, and \textit{d (Sedan, Land\_Vehicle) = 2}.
+Suppose we want to find the class divergence between \emph{Bus} and \emph{Sedan} from the ontology shown in Figure \ref{fig:vehicular_ontology}.
+\emph{Sedan} is a subclass of \emph{Automobile} which is a subclass of \emph{Land\_Vehicle}.
+\emph{Bus} is a subclass of \emph{Land\_Vehicle}, which is their least common ancestor $C$.
+
+The longest path to the tree root is $h = 4$.
+Therefore, the normalized divergence $cd(Bus, Sedan)$ is $0.5$.
+The value is calculated from $d(Bus, Root) = 3$, $d(Bus, Land\_Vehicle) = 1$, and $d(Sedan, Land\_Vehicle) = 2$.
 
@@
 
-Once we have relevant QRMs through QRM ranking for a given user query, we can produce answers by re-running the pathways.
+Once we have ranked the QRMs for a given user query, we can produce answers by re-running the pathways stored in the QRMs.
 
@@
 It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.
-
-%When a user submits a new query to the Morpheus system, one or more stored QRMs are executed to obtain results.
-A QRM contains an XML script representing an algorithm that will obtain the required result.
-The evaluation of this script by the QRE simulates the behavior of a human browsing the web, that is, clicking buttons to follow links, submitting forms, highlighting data, cutting and pasting text, and constructing an answer in the form of a text string.
-There is greater complexity in dealing with web forms than with links.
-At present, the GET form submission method is used.
-This means that in preparation to submit a form, the Morpheus System builds a querystring consisting of name-value pairs.
-For a given form, there may be text fields, drop-down boxes, and among other components.
-In order to support form submission in such circumstances, the QRE performs different actions based upon the input type.
-For text fields, simply adding a key/value pair to the query string suffices.
-For a drop-down box, the QRE extracts the form element to find the appropriate value to include in the query string.
-It does this by examine each option in the drop-down and matching the user’s input to the text field in the option.
-The value attribute of the option is then added to the querystring.
-The value and text attributes of a dropdown option might be the same, but they are not guaranteed to be.
-All input data are kept in an internal table.
-The QRM script contains keys that allow the QRE to map SSQ inputs from the table to the appropriate form inputs.
-Furthermore, highlighted text segments collected during execution of the script are stored in the table.
-Once all actions in the script have been carried out, the QRE returns the textual answer this process has created.
-This answer is then be rendered in a browser displayed to the user.

### 2010-07-02 trunk/paper/IIWAS2010/content/results_discussion.tex
latest version

@@
 
-%describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
-
-%% TODO - need to refer back to the table which is figure one.
-%The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires.
-From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6.
-For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora.
-Table \ref{tbl:term_categories} shows the top categories and their probabilities for each of the query term.
 In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .
-It extracts the WH question, that is, the the term that identifies the sentence as a question.
+It extracts the WH-question, that is, the the term that identifies the sentence as a question.
 Next, the engine locates the descriptive information that can be used to describe the answer.
@@
 Using the data in \ref{tbl:nlp_engine_parse} we determined relevant classes (non-increasing order of relevance) from the ontology given each n-gram.
-Table \ref{tbl:term_categories} shows the top classes and their probabilities for our example.
+Table \ref{tbl:term_classes} shows the top classes and their probabilities for our example.
 
@@
 		\hline 
-		n-grams & 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
+		n-grams & \small 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
 		\hline
@@
 \hline 
-Term & Category & $P(Category|Term)$ \\ \hline
+Term & Class & $P(Class|Term)$ \\ \hline
 1997 & Sedans & 404132.77e-14\\ 
@@
 
-\caption{Terms' top categories and probabilities}
-\label{tbl:term_categories}
+\caption{Terms' top classes and probabilities}
+\label{tbl:term_classes}
 
@@
 
-We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
-ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.
+We found the top class of the terms in the candidate SSQ and determined the class divergence with the qualified SSQ classes in the QRM store.
+Then, we combined the divergence measure and ranked QRMs based on the relevance score.
+Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.
+Finally, we execute the selected QRM and display the results to the user.
 
@@
 	\hline
-	A 1997 Toyota Camry V6 needs what size tires? & inputs(Sedans, Cars, Engines, Manufactures) & 0.91\\ 
+	\small A 1997 Toyota Camry V6 needs what size tires? & \small Sedan, Car, Engine, Manufacture & 0.91\\ 
 	\hline 
-	What is the tire size for a 1998 Sienna XLE Van? & inputs(1998 Toyota Sienna XLE Van: Vans, Toyota : Manufacturers) & 0.72\\ 	\hline 
-	Where can I buy an engine for a Toyota Camry V6? & inputs(Toyota Camry : Sedans, Toyota Camry V6 : Automobile_Engines, Toyota : Manufacturers) & 0.74 \\
+	\small What is the tire size for a 1998 Sienna XLE Van? & \small 1998 Toyota Sienna XLE Van: Van, Toyota : Manufacturers & 0.72\\
+	\hline 
+	\small Where can I buy an engine for a Toyota Camry V6? & \small Toyota Camry : Sedan, Toyota Camry V6 : Automobile Engine, Toyota : Manufacturers & 0.74 \\
 	\hline 
@@
 The system uses a path-finder to annotate answer paths so path-followers can discover answers to similar questions.
-Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs.
-Classification of terms into classes is based on term frequency distributions in our corpora of web documents.
-We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.
+Each $(question, answer\_path)$ pair is assigned a realm, and new questions are matched to existing $(question, answer\_path)$ pairs.
+Classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.
+These terms are the input to existing answer path and we re-execute answers-paths with these new inputs to produce answers.
 
-Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task.
-Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
-%The Wikipedia page categories has limitations.
-Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g.
-vehicular) usually overlap.
-So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.
+Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task.
+Topic Modeling provides a promising approach to identifying pages relevant to given class in a more automated manner \cite{Blei2003latentdirichlet}.
+We believe a mix between our web form entry annotation methods and \cite{1453931} can yield promising results.
+Additionally, this approach along with the ideas in \cite{1687749} may completely remove the user out of the answer path generation process.
+
+Additionally, we are investigating methods of combining and merging QRMs to answer new questions.  We will build on previous Morpheus detailing transform composition \cite{transformscout}.
 

### 2010-07-02 trunk/paper/IIWAS2010/content/system_arch.tex
latest working copy
The submitted copy of the paper

--- 2010-07-01 trunk/paper/IIWAS2010/content/system_arch.tex
@@
 Each leaf node in the ontology is associated with a corpus of words belonging to a class.
-For example, we have constructed an vehicular ontology containing classes relevant to the vehicular realm.
+For example, we have constructed a vehicular ontology containing classes relevant to the vehicular realm.
 This ontology provides a structure for reference in the following sections.
@@
 
-Morpheus uses the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages.
+Morpheus references the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages.
 First a realm is mapped to a DBpedia category \cite{Bizer2009}.
-Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}.
+Using the DBpedia ontology properties \emph{broader} and \emph{narrower}, a \emph{Markov Blanket} \cite{PRIS} is created covers all neighboring categories.
 
 To build a corpus for each of the leaf nodes in the ontology, we extract \emph{terms} from the Wikipedia pages associated with the DBpedia categories found in its blanket.
-From this term corpus, we can find the likelihood of a term belonging to a particular category.
-This assists in categorizing terms in a \emph{path-follower} query.
-The likelihood is determined by the probability of a category given a term using \textit{Bayes Rule} (Eq.
-\ref{eq:bayesrule}), since we can easily obtain the term-category and term-corpus probabilities as relative frequencies.
-
-%Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO.
-We determine a \emph{head noun} in the category name and search for it in the WordNet synsets.
-DBpedia categories having no WordNet synset match are excluded from our ontology.
-<--- by Gordon
-
+From this term corpus, we can find the likelihood of a term belonging to a particular class.
+This assists in classifying terms in a \emph{path follower} query.
+The likelihood is determined by the probability of a class given a term using \textit{Bayes Rule} (Eq.
+\ref{eq:bayesrule}), since we can easily obtain the term-class and term-corpus probabilities as relative frequencies.
 \begin{equation}
 \label{eq:bayesrule}
-P (category | term) = \frac{P(term | category) P(category)}{P(term)}
+P (class | term) = \frac{P(term | class) P(class)}{P(term)}
 \end{equation}
@@
 LDA is Bayesian model that represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all  terms in the corpus.
-For example, for the Wikipedia pages, the latent topics reflect the thematic structure of the pages.
+For example, the latent topics reflect the thematic structure of Wikipedia pages.
 Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
@@
 
-\subsection{ Recording}
+\subsection{Recording}
 \label{sec:query_processing}
 
-The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question.
-The path-finder also uses the tool to identify ontological categories associated with search terms.
-Morpheus stores the query together with its terms and categories as an SSQ.
-Table \ref{tab:ssq_example} is an example showing the SSQ model of the query ``A 1997 Toyota Camry V6 has what size tires?".
-The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified.
-Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.
+The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path finder answering a question.
+The path finder also uses the tool to identify ontological classes associated with search terms.
+Morpheus stores the query, its terms, and its classes as an SSQ.
+Table \ref{tab:ssq_example} is an example showing the SSQ model of the query: \emph{ A 1997 Toyota Camry V6 needs what size tires?} The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified.
+Using the QRR, the path finder is also able to identify where answers can be found within traversed pages.
 
@@
 
-%% TODO - we need the table here
-\begin{table}\footnotesize
+\begin{table}[h]
 \scalebox{0.76}{
-	\rowcolors{1}{white}{white}
 	\begin{tabular}{|r|l|l|l|l|l|l|l|l|}
@@
 	}
-	\caption{Example SSQ Model.}
+	\caption{Example SSQ model}
 	\label{tab:ssq_example}
@@
 The \emph{Query Resolution Method} (QRM) is a data structure that models the question answering process.
-A QRM represents a generalized executable realization of the search process that the path-finder followed.
-The QRM is able to reconstruct the page search path followed by the path-finder.
+A QRM represents a generalized executable realization of the search process that the path finder followed.
+The QRM is able to reconstruct the page search path followed by the path finder.
 Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process.
-For each dynamic page, the QRM contains a list of inputs to the URL such as form inputs and the possible reference outputs.
+For each dynamic page, the QRM contains a list of inputs and reference outputs from the URL.
 
@@
 
-Queries inserted by path-followers take a different approach.
+Queries inserted by path followers take a different approach.
 The Morpheus search process parses and tags queries in order to record important terms.
@@
 Once the realm is assigned, an ontology search is performed to assign classes to the terms.
-An SSQ is constructed and the system attempts to match this candidate SSQ to existing QRM SSQs.
-Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer similar queries.
+An SSQ is constructed and the system attempts to match this new SSQ to existing QRM SSQs.
+Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer many similar queries.
 
@@
 
-To answer a user's query, a candidate SSQ, Morpheus finds similar qualified SSQs that are associated with QRMs in the Morpheus data store.
+To answer a user's query, a \emph{candidate} SSQ, Morpheus finds similar qualified SSQs that are associated with QRMs in the Morpheus data store.
 To determine SSQ similarity, we consider the SSQ's realm, input terms, output terms, and their assigned classes.
 
-The \emph{class divergence} of two classes within the ontology characterizes their similarity.
-This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches.
+The \emph{class divergence} of two classes within the ontology characterizes their dissimilarity.
+This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches \cite{Barrett1996}.
 
-We consider the category match as a type match and we use \emph{category divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ.
-Each qualified SSQ will have input terms, output terms, and associated classes, and one realm (from the QRM).
-For the candidate SSQ, the relevant categories for terms are determined from the NLP engine and corpora.
-The calculation of a realm for a candidate query is performed using the n-grams found within the query and any probabilities as found with $p(realm|n\-gram)$.
+We consider the class match as a type match and we use \emph{class divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ.
+Each qualified SSQ will have input terms, output terms, associated classes, and one realm from the QRM.
+For the candidate SSQ, the relevant classes for terms are determined from the natural language processing engine and corpora.
+The calculation of a realm for a candidate query is performed using the n-grams found within the query and any probabilities found with $p(realm|n\-gram)$.
 %% TODO - specify freq and reference joirdans stuff in section 3.2
@@
 The relevance of a qualified SSQ to the candidate SSQ is determined by aggregating the divergence measure of input term classes associated with each SSQ.
-In addition, we order QRMs in the data store
-by decreasing relevance. The order provides a ranking for the results 
-to the user. The following describes \emph{category divergence} 
-in detail.
+In addition, we order QRMs in the data store by decreasing relevance.
+The order provides a ranking for the results to the user.
+The following describes \emph{class divergence} in detail.
 
@@
 
-We employ a quasimetric, \textit{category divergence (cd)}, between a source category and a target category using the \textit{topological structure} of the categories in an ontology.
-We write $S \prec T$ for the reflexive transitive closure of the supercategory relation.
+We employ a quasi-metric, \textit{class divergence (cd)}, between a source class and a target class using the \textit{topological structure} of the classes in an ontology.
+We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
 Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target category ranges from zero (for identical categories) to one (for type incompatible categories).
-Let $S$ be the source category, $T$ be the target category, and $C$ be a least common ancestor category of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
-The category divergence between $S$ and $T$ is defined given by:
-
+The divergence between a source and target class ranges from zero (for identical classes) to one (for type incompatible classes).
+Let $S$ be the source class, $T$ be the target class, and $C$ be a least common ancestor class of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
+The class divergence between $S$ and $T$ is defined given by:
 \begin{equation}
@@
 \end{equation}
+where $h$ is the longest path in the ontology class heterarchy.
 
-\noindent where $h$ is the longest path in the ontology class heterarchy.
+Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor.
+This is an important property in determining the compatibility of classes for answering queries.
+If an SSQ answers queries concerning an ancestor class, it is more relevant than an SSQ that answers queries from any non-ancestral class.
 
-Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) <
-cd(S,Q)$, that is, the divergence of a source category to a target
-ancestor category is smaller than the divergence of a source category to any
-category that is not an ancestor. This is an important property in
-determining the compatibility of categories for answering queries.  If a
-SSQ answers queries concerning an ancestor category, it is more relevant
-that a SSQ that answers queries from any non-ancestral category.
+Suppose we want to find the class divergence between \emph{Bus} and \emph{Sedan} from the ontology shown in Figure \ref{fig:vehicular_ontology}.
+\emph{Sedan} is a subclass of \emph{Automobile} which is a subclass of \emph{Land\_Vehicle}.
+\emph{Bus} is a subclass of \emph{Land\_Vehicle}, which is their least common ancestor $C$.
 
-% Algorithm 1: figure  
+The longest path to the tree root is $h = 4$.
+Therefore, the normalized divergence $cd(Bus, Sedan) = 6/12$.
+The value is calculated from $d(Bus, Root) = 3$, $d(Bus, Land\_Vehicle) = 1$, and $d(Sedan, Land\_Vehicle) = 2$.
+
 \begin{figure}[t]
 	\centering
-%\includegraphics[width=85mm]{../img/vehicular_ontology.eps}
-\includegraphics[width=85mm]{vehicular_ontology.eps}
-\caption{Abbreviated Vehicular Ontology}% - arrows represent inheritance relationships between the ontological classes.}
+	\includegraphics[scale=0.90]{OntologyDiagram.png}
+	\caption{Abbreviated vehicular ontology}
 	\label{fig:vehicular_ontology}
@@
 
-Suppose we want to find the category divergence between \textit{Sedan} and \textit{Bus} Figure \ref{fig:vehicular_ontology}.
-\textit{Sedan} is the subcategory of \textit{Sedan}, and \textit{Bus} is the subcategory of \textit{Automobile}.
-Therefore, the least common ancestor ($C$) for these two.
-This section presents ontology and copora, query processing, ranking queries, and the query resolution mechanism.
-categories is \textit{Automobile}.
-In addition, the tree height \textit{h = 4}.
-So, the normalized divergence $cd$\textit{(Sedan, Bus)} is \textit{7/12} that is calculated from \textit{d(Sedan, Root) = 4}, \textit{d(Sedan, Automobile) = 2}, and \textit{d(Bus, Automobile) = 1}.
-
 \subsection{Executing}
 
-Once we have relevant QRMs through QRM ranking for a given user query, we can produce answers by re-running the pathways.
-
+Once we have ranked the QRMs for a given user query, we can produce answers by re-running the pathways stored in the QRMs.
 The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.

### 2010-07-02 paper/IIWAS2010/content/abstract.tex
latest version
The submitted copy of the paper

@@
 
-The Morpheus question answering system uses deep web search to answer user queries.
-Queries are represented by a semi-structured format that contains query terms and referenced classes within a specific ontology.
+When users search the deep web, the essence of their search is often found in a previously answered query.
+The Morpheus question answering system reuses prior searches to answer similar user queries.
+Queries are represented in a semi-structured format that contains query terms and referenced classes within a specific ontology.
 Morpheus answers questions by using methods from prior successful searches.
@@
 Similarity depends on the class heterarchy in an ontology and its associated text corpora.
-Finally, Morpheus revisits the prior search pathways of the stored searches to construct possible answers.
+Morpheus revisits the prior search pathways of the stored searches to construct possible answers.
 The realm-based ontologies are created using Wikipedia pages, associated categories, and the synset heterarchy of WordNet.

### 2010-07-02 paper/IIWAS2010/content/introduction.tex
The submitted copy of the paper

@@
 Rather than treating a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been performed.
-In one study, almost 40 percent of all queries were repetitions of previous queries \cite{1277770}.
-Thus, reuse of prior searches is one way to optimize the search
-process.
+In one study, almost 40 percent of web queries were repetitions of previous queries \cite{1277770}.
+Thus, reuse of prior searches is one way to optimize the search process.
 Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer to a user query.
-Morpheus follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
+Morpheus follows path finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.
 
-Morpheus focuses on the deep (or hidden) web to answer questions because its scale and database driven property implies the existence of huge stores of quality information \cite{1453931}.
+Morpheus focuses on the deep (or hidden) web to answer questions because of the large stores of quality information provided by the databases that support it \cite{1453931}.
 Web forms act as an interface to this information.
@@
 There are two distinct Morpheus user roles.
-A \textit{path-finder} enters queries in the Morpheus web interface and searches for an answer to the query using an instrumented web browser.
-This web tracking tool stores the query and necessary information to revisit the pathways to the page where the path-finder found the answer.
-A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface.
-The path-follower enters a question in a text box and receives a guided path to the answer.
+A \emph{path finder} enters queries in the Morpheus web interface and searches for an answer to the query using an instrumented web browser.
+This web tracking tool stores the query and necessary information to revisit the pathways to the page where the path finder found the answer.
+A \emph{path follower} uses the Morpheus system much like a regular search engine with a natural language interface.
+The path follower enters a question in a text box and receives a guided path to the answer.
 The system exploits previously found paths to provide an answer.
 
-Morpheus represents user-query details in a semi-structured query (SSQ).
-It assumes the query terms belong to classes of a \textit{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations.
-When a path-follower enters a query, Morpheus ranks SSQs in the store based on class similarity.
-Suppose a path follower asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g.
+Morpheus represents a user question as a semi-structured query (SSQ).
+It assumes the query terms belong to classes of a \emph{consistent} realm-based ontology, that is, one having a singly rooted heterarchy whose subclass/superclass relations have meaningful semantic interpretations.
+When a path follower enters a query, Morpheus ranks SSQs in the store based on class similarity.
+Suppose a path follower asks: \emph{ A 1997 Toyota Camry V6 needs what size tires?} In this query the classes associated with terms, e.g.
 \emph{Manufacturer} with \emph{Toyota}, help us identify similar queries.

### 2010-07-02 paper/IIWAS2010/content/related_work.tex
The submitted copy of the paper

@@
 The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
-Morpheus uses the web as its dynamic, open corpus and examines deep web sources 
-to answer questions.
+Morpheus uses the web as its dynamic, open corpus and examines deep web sources to answer questions.
 
@@
 This allows for faster responses to questions.
-Morpheus relies on both its user interface and referencing similar questions previously answered.
+Morpheus relies on its user interface and referencing previously answered questions.
 
@@
 
-The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making this information available on the Web.
+The DBpedia\footnote{http://dbpedia.org} project is a community of contributors extracting semantic information from Wikipedia and makes this information available on the Web.
 Wikipedia semantics includes info-box templates, categorization information,  images, geo-coordinates, links to external web pages, disambiguation pages, and redirects to pages in Wiki markup form \cite{Bizer2009}.
@@
 YAGO discovers connections between WordNet synsets and Wikipedia categories, parsing the category names and matching the parsed category components with the WordNet synsets.
-Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
+Each Wikipedia category not having a WordNet match is ignored in the YAGO ontology.
 The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
@@
 Thus far, these ontologies can be used to classifiy terms, however their classes do not always appropriately categorize query parameters.
-Therefore, we are researching XXX in order to XXX.% TODO - fill in the XXX
+It is necessary to provide an appropriate level of class granularity.
+Therefore, we are investigating  methods of identifying classes and their instances from deep web forms and documents.
 

### 2010-07-02 paper/IIWAS2010/content/results_discussion.tex
The submitted copy of the paper

--- 2010-06-30 paper/IIWAS2010/content/results_discussion.tex
@@
 
-First, we created an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets.
+First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets.
 For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
-Table describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''
+Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.
 
-%% TODO - need to refer back to the table which is figure one.
-The Morpheus NLP engine parses this query into the constructs: WH:what,
-Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
-descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
-Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
-each of the terms, we determined relevant categories (non-increasing order of
-relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
-the top categories and their probabilities for each of the query term:
+In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query.
+It extracts the \emph{wh}-term that identifies the sentence as a question, identifies the answer class, and locates descriptive phrases that can be used to identify the answer.
+Finally, the engine produces n-grams from the phrases in the descriptive information sections.
 
-\begin{table}[h]\footnotesize
+Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance.
+Table \ref{tbl:term_classes} shows the top classes and their probabilities for automotive queries.
+
+\begin{table}[!]\footnotesize
+	\begin{tabular}{|l|p{4.2cm}|}
+		\hline 
+		\emph{wh}-term & what \\
+		\hline 
+		descriptive phrases & \small 1997 Toyota Camry V6 \\
+		\hline 
+		asking for & size tires \\
+		\hline 
+		n-grams & \small 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
+		\hline
+	\end{tabular}
+	\caption{The output of NLP engine parse}
+	\label{tbl:nlp_engine_parse} 
+\end{table}
+
+\begin{table}[!]\footnotesize
 
@@
 
-We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
-ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.
+We found the top class of the terms in the candidate SSQ and determined the class divergence with the qualified SSQ classes in the QRM store.
+Then, we combined the divergence measure and ranked QRMs based on the relevance score.
+Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.
+Finally, we execute the best QRMs and display the results to the user.
 
-\begin{table}[h]\footnotesize
+\begin{table}[!]\footnotesize
 
@@
 	\hline
-Query & Tagged Classes & Score\\ \hline
-A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
-What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
-Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
-What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
+	Query & Tagged Classes & Score\\ 
+	\hline
+	\small A 1997 Toyota Camry V6 needs what size tires? & \small Sedan, Automobile, Engine, Manufacturer & 0.91\\ 
+	\hline 
+	\small What is the tire size for a 1998 Sienna XLE Van? & \small Van, Manufacturer & 0.72\\
+	\hline 
+	\small Where can I buy an engine for a Toyota Camry V6? & \small Sedan, Automobile Engine, Manufacturers & 0.74 \\
+	\hline 
+%What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
 \end{tabular}
 
-\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
+\caption{Top ranked queries}
 \label{tbl:ranked_queries}
@@
 The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.
-Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs.
-Classification of terms into classes is based on term frequency distributions in our corpora of web documents.
-We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.
+Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs.
+Classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.
+These terms are the input to existing answer paths and we re-execute these paths with the new input to produce results.
 
-Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task.
-Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
-%The Wikipedia page categories has limitations.
-Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g.
-automotive) usually overlap.
-So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.
+Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task.
+Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner \cite{Blei2003latentdirichlet}.
+We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results.
+Combining this with the method of Elmeleegy et al.
+\cite{1687749} may completely remove the user from the answer path generation process.
+
+Additionally, we are investigating methods of merging QRMs to answer compound questions.  We will also chain QRMs using the principles of transform composition \cite{transformscout}.
 

### 2010-07-13 trunk/paper/IIWAS2010/content/results_discussion.tex
july 13 version

@@
 
-First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, categories, and WordNet synsets.
+First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets.
 For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
@@
 
-In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .
-It extracts the WH-question, that is, the the term that identifies the sentence as a question.
-Next, the engine locates the descriptive information that can be used to describe the answer.
-Then the engine extracts the terms that describe what is being requested.
-Finally, the engine produces n-grams from the terms in the descriptive information sections.
+In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query.
+It extracts the \emph{wh}-term that identifies the sentence as a question, identifies the answer class, and locates descriptive phrases that can be used to identify the answer.
+Finally, the engine produces n-grams from the phrases in the descriptive information sections.
 
-Using the data in \ref{tbl:nlp_engine_parse} we determined relevant classes (non-increasing order of relevance) from the ontology given each n-gram.
-Table \ref{tbl:term_classes} shows the top classes and their probabilities for our example.
+Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance.
+Table \ref{tbl:term_classes} shows the top classes and their probabilities for automotive queries.
 
-\begin{table}[h]\footnotesize
-	\begin{tabular}{|l|p{4.2cm}|}
+\begin{table}[!]\footnotesize
+	\begin{tabular}{|l|p{4.9cm}|}
 		\hline 
-		WH & what \\
+		\emph{wh}-term & what \\
 		\hline 
-		Descriptive Information & 1997 Toyota Camry V6 \\
+		descriptive phrases & \small 1997 Toyota Camry V6 \\
 		\hline 
-		Asking for & size tires \\
+		asking for & size tires \\
 		\hline 
@@
 
-\begin{table}[h]\footnotesize
+\begin{table}[!]\footnotesize
 
-\begin{tabular}{| p{3.2cm} | l | r |}
+\begin{tabular}{| p{3.5cm} | p{1.45cm} | r |}
 \hline 
@@
 Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.
-Finally, we execute the selected QRM and display the results to the user.
+Finally, we execute the best QRMs and display the results to the user.
 
-\begin{table}[h]\footnotesize
+\begin{table}[!]\footnotesize
 
@@
 	\hline
-	\small A 1997 Toyota Camry V6 needs what size tires? & \small Sedan, Car, Engine, Manufacture & 0.91\\ 
+	\small A 1997 Toyota Camry V6 needs what size tires? & \small Sedan, Automobile, Engine, Manufacturer & 0.91\\ 
 	\hline 
-	\small What is the tire size for a 1998 Sienna XLE Van? & \small 1998 Toyota Sienna XLE Van: Van, Toyota : Manufacturers & 0.72\\
+	\small What is the tire size for a 1998 Sienna XLE Van? & \small Van, Manufacturer & 0.72\\
 	\hline 
-	\small Where can I buy an engine for a Toyota Camry V6? & \small Toyota Camry : Sedan, Toyota Camry V6 : Automobile Engine, Toyota : Manufacturers & 0.74 \\
+	\small Where can I buy an engine for a Toyota Camry V6? & \small Sedan, Automobile Engine, Manufacturers & 0.74 \\
 	\hline 
@@
 
-\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
+\caption{Top ranked queries}
 \label{tbl:ranked_queries}
@@
 In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions.
-The system uses a path-finder to annotate answer paths so path-followers can discover answers to similar questions.
-Each $(question, answer\_path)$ pair is assigned a realm, and new questions are matched to existing $(question, answer\_path)$ pairs.
+The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.
+Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs.
 Classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.
-These terms are the input to existing answer path and we re-execute answers-paths with these new inputs to produce answers.
+These terms are the input to existing answer paths and we re-execute these paths with the new input to produce results.
 
 Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task.
-Topic Modeling provides a promising approach to identifying pages relevant to given class in a more automated manner \cite{Blei2003latentdirichlet}.
-We believe a mix between our web form entry annotation methods and \cite{1453931} can yield promising results.
-Additionally, this approach along with the ideas in \cite{1687749} may completely remove the user out of the answer path generation process.
+Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner \cite{Blei2003latentdirichlet}.
+We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results.
+Combining this with the method of Elmeleegy et al.
+\cite{1687749} may completely remove the user from the answer path generation process.
 
-Additionally, we are investigating methods of combining and merging QRMs to answer new questions.  We will build on previous Morpheus detailing transform composition \cite{transformscout}.
+Additionally, we are investigating methods of merging QRMs to answer compound questions.  We will also chain QRMs using the principles of transform composition \cite{transformscout}.
 

### 2010-07-13 paper/IIWAS2010/content/system_arch.tex
july 13 version

@@
 
-Morpheus uses the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages.
+Morpheus references the DBpedia categories, Wikipedia pages, and the WordNet synset heterarchy to find class-relevant web pages.
 First a realm is mapped to a DBpedia category \cite{Bizer2009}.
-Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}.
+Using the DBpedia ontology properties \emph{broader} and \emph{narrower}, a \emph{Markov Blanket} \cite{PRIS} is created covers all neighboring categories.
 
@@
 From this term corpus, we can find the likelihood of a term belonging to a particular class.
-This assists in classifying terms in a \emph{path-follower} query.
+This assists in classifying terms in a \emph{path follower} query.
 The likelihood is determined by the probability of a class given a term using \textit{Bayes Rule} (Eq.
 \ref{eq:bayesrule}), since we can easily obtain the term-class and term-corpus probabilities as relative frequencies.
-
-%Once we have the categories belonging to a particular realm, we associate them with WordNet synsets using an approach similar to YAGO.
-We determine a \emph{head noun} in the category name and search for it in the WordNet synsets.
-DBpedia categories having no WordNet synset match are excluded from our ontology.
-<--- by Gordon
-
 \begin{equation}
@@
 
-\subsection{ Recording}
+\subsection{Recording}
 \label{sec:query_processing}
 
-The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question.
-The path-finder also uses the tool to identify ontological classes associated with search terms.
-Morpheus stores the query together with its terms and classes as an SSQ.
-Table \ref{tab:ssq_example} is an example showing the SSQ model of the query ``A 1997 Toyota Camry V6 has what size tires?".
-The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified.
-Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.
+The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path finder answering a question.
+The path finder also uses the tool to identify ontological classes associated with search terms.
+Morpheus stores the query, its terms, and its classes as an SSQ.
+Table \ref{tab:ssq_example} is an example showing the SSQ model of the query: \emph{ A 1997 Toyota Camry V6 needs what size tires?} The SSQ in Table \ref{tab:ssq_example} is said to be \emph{qualified} because the classes associated with its terms have been identified.
+Using the QRR, the path finder is also able to identify where answers can be found within traversed pages.
 
@@
 
-%% TODO - we need the table here
 \begin{table}[h]
@@
 The \emph{Query Resolution Method} (QRM) is a data structure that models the question answering process.
-A QRM represents a generalized executable realization of the search process that the path-finder followed.
-The QRM is able to reconstruct the page search path followed by the path-finder.
-Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process.
-For each dynamic page, the QRM contains a list of inputs to the URL such as form inputs and the possible reference outputs.
+A QRM represents a generalized executable realization of the search process that the path finder followed.
+The QRM is able to reconstruct the page search path followed by the path finder.
+Each QRM contains a realm from our ontology, an SSQ, and information to support the query answering process.
+For each dynamic page, the QRM contains a list of inputs and reference outputs from the URL.
 
@@
 Once the realm is assigned, an ontology search is performed to assign classes to the terms.
-An SSQ is constructed and the system attempts to match this candidate SSQ to existing QRM SSQs.
+An SSQ is constructed and the system attempts to match this new SSQ to existing QRM SSQs.
 Rather than matching exact query terms, the system matches input and output classes, because a QRM can potentially answer many similar queries.
@@
 
-To answer a user's query, a candidate SSQ, Morpheus finds similar qualified SSQs that are associated with QRMs in the Morpheus data store.
+To answer a user's query, a \emph{candidate} SSQ, Morpheus finds similar qualified SSQs that are associated with QRMs in the Morpheus data store.
 To determine SSQ similarity, we consider the SSQ's realm, input terms, output terms, and their assigned classes.
@@
 The \emph{class divergence} of two classes within the ontology characterizes their dissimilarity.
-This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches.
+This solution is motivated by the concept of multiple dispatch in CLOS and Dylan programming for generic function type matches \cite{Barrett1996}.
 
 We consider the class match as a type match and we use \emph{class divergence} to calculate the relevance between the candidate SSQ and a qualified SSQ.
-Each qualified SSQ will have input terms, output terms, and associated classes, and one realm (from the QRM).
-For the candidate SSQ, the relevant classes for terms are determined from the NLP engine and corpora.
-The calculation of a realm for a candidate query is performed using the n-grams found within the query and any probabilities as found with $p(realm|n\-gram)$.
+Each qualified SSQ will have input terms, output terms, associated classes, and one realm from the QRM.
+For the candidate SSQ, the relevant classes for terms are determined from the natural language processing engine and corpora.
+The calculation of a realm for a candidate query is performed using the terms found within the query and any probabilities found with $p(realm|term)$.
 %% TODO - specify freq and reference joirdans stuff in section 3.2
@@
 The relevance of a qualified SSQ to the candidate SSQ is determined by aggregating the divergence measure of input term classes associated with each SSQ.
-In addition, we order QRMs in the data store
-by decreasing relevance. The order provides a ranking for the results 
-to the user. The following describes \emph{class divergence} 
-in detail.
+In addition, we order QRMs in the data store by decreasing relevance.
+The order provides a ranking for the results to the user.
+The following describes \emph{class divergence} in detail.
 
@@
 The class divergence between $S$ and $T$ is defined given by:
-
 \begin{equation}
@@
 \end{equation}
-
-\noindent where $h$ is the longest path in the ontology class heterarchy.
+where $h$ is the longest path in the ontology class heterarchy.
 
@@
 This is an important property in determining the compatibility of classes for answering queries.
-If an SSQ answers queries concerning an ancestor class, it is more relevant that an SSQ that answers queries from any non-ancestral class.
+If an SSQ answers queries concerning an ancestor class, it is more relevant than an SSQ that answers queries from any non-ancestral class.
 
@@
 The longest path to the tree root is $h = 4$.
-Therefore, the normalized divergence $cd(Bus, Sedan)$ is $0.5$.
+Therefore, the normalized divergence $cd(Bus, Sedan) = 6/12$.
 The value is calculated from $d(Bus, Root) = 3$, $d(Bus, Land\_Vehicle) = 1$, and $d(Sedan, Land\_Vehicle) = 2$.
 
-\begin{figure}[h]
+\begin{figure}[t]
 	\centering
 	\includegraphics[scale=0.90]{OntologyDiagram.png}
-	\caption{Abbreviated Vehicular Ontology}
+	\caption{Abbreviated vehicular ontology}
 	\label{fig:vehicular_ontology}
@@
 Once we have ranked the QRMs for a given user query, we can produce answers by re-running the pathways stored in the QRMs.
-
 The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.

### 2010-07-15 nqparser/NQParser/src/extractor.py
Added NQParser to repository

@@ -1,0 +1,258 @@
+'''
+Created on May 26, 2010
+
+@author: Joir-dan
+'''
+
+import nltk;
+from nltk import tokenize;
+import re;
+
+class TermExtractor(object):
+    def __init__(self):
+        self.__baseGrammar = """ 
+                                 VG: {<RB>?<V.*>+<RB|ADJPh>?}
+                                  N: {(<NN.*>+)|<PRP>}
+                                ADV: {<RB>}
+                                  P: {<IN|TO>}
+                                 WH: {<W.*>}
+                                POS: {<POS>}
+                              ADJPh: { <RBS>?(<JJ.*>+)?<CD>? }
+                            PreNoun: {<DT|PRP\$|WP\$>}
+                                END: {<\.>} """
+        self.__lvl1Grammar = "NPh: {<PreNoun>?(<ADJPh>*)?<N>}"
+        self.__lvl2Grammar = "PPh: {<P><NPh|ADJPh>}"
+        self.__lvl3Grammar = "NPh: {<NPh>(<POS><NPh>)+}"
+        self.__lvl4Grammar = "NPh: {<NPh><PPh>}"
+        self.__lvl5Grammar = "WHNPh: {<WH><NPh>}"
+        self.__lvl6Grammar = "VPh: {<VG><NPh|WHNPh|PPh|WH>}"
+        #END: Grammars 
+        self.__grammarList = [self.__baseGrammar, self.__lvl1Grammar, self.__lvl2Grammar, 
+                              self.__lvl3Grammar, self.__lvl4Grammar, self.__lvl5Grammar, 
+                              self.__lvl6Grammar]
+        
+    def run(self, query, verboseMode):
+        print
+        self.__query = query
+        self.__resetVars(verboseMode)
+        self.__firstTokenize(query)
+        self.__thenChunkQuery()
+        self.__andFinallyExtractTerms()
+        self.__createNGramsForExporting()
+        self.__formatForExporting()
+        return self.__returnGroup
+
+    def __firstTokenize(self, query):
+        self.__terms = tokenize.word_tokenize(query)
+        self.__taggedSentence = nltk.pos_tag(self.__terms)
+        if self.__VERBOSE: 
+            print(self.__taggedSentence)
+            print
+
+    def __thenChunkQuery(self):
+        tempChunk = self.__taggedSentence
+        for i in range(len(self.__grammarList)):
+            grammar = self.__grammarList[i]
+            chunkParser = nltk.RegexpParser(grammar)
[…]

### 2010-07-15 nqparser/NQParser/src/main.py

@@ -1,0 +1,38 @@
+'''
+Created on May 26, 2010
+
+@author: Joir-dan
+'''
+import extractor as ext
+
+
+def showChoices():
+    print(
+          '''
+          1) Parse Query
+          2) Exit
+          ''');
+
+def choice1():
+    #verboseMode = True if raw_input("Verbose Mode: ").lower() == "true" else False
+    query = raw_input("Question: ")
+    extractor = ext.TermExtractor()
+    extractor.run(query, verboseMode = True)
+    extractor.showResults()
+    print(extractor.getExportString())
+    #ext.subjectExtractor(query);
+    return;
+
+choice = "0";
+
+while(choice != "2"):
+    showChoices();
+    choice = raw_input("Option #: ");
+ 
+    if(choice == "1"):
+        choice1();
+    else:
+        print("Done");
+        
+
+        

### 2010-07-15 trunk/nqparser/NQParser/src/tagTest.py
Added NQParser to repository

@@ -1,0 +1,24 @@
+'''
+Created on Jun 4, 2010
+
+@author: Joir-dan
+'''
+import nltk
+from nltk.tagger.brill import *
+    
+
+
+print("Training tagger")
+backoffTagger = nltk.data.load(nltk.tag._POS_TAGGER)
+uniTagger = nltk.tag.UnigramTagger(nltk.corpus.treebank.tagged_sents()[:2000], backoff = backoffTagger)
+print("Done Training...")
+
+choice = "";
+while choice != "2":
+    print("1: Run test \n 2: Exit \n")
+    choice = raw_input("Choice: ")
+    if choice == "1":
+        text = raw_input("Question: ")
+        terms = nltk.tokenize.word_tokenize(text)
+        taggedTerms = uniTagger.tag(terms)
+        print(taggedTerms)

### 2010-07-15 trunk/nqparser/NQParser/src/test.py

@@ -1,0 +1,50 @@
+'''
+Created on May 30, 2010
+
+@author: Joir-dan
+'''
+import nltk
+import nltk.corpus
+
+whatList = ["what", "What"]
+tagCount = {}
+tagSentenceIsQuestion = []
+nextGram = {"isVerb" : 0, "isNoun": 0, "isOther" : 0}
+isQuestion = {"yes":0, "no": 0}
+brownText = nltk.corpus.brown;
+file = open("/Users/Hikari/Desktop/brown-corpus.info", "a")
+file.write("Analysis of brown corpus: sentences with [what] in them\n")
+for sentence in brownText.tagged_sents():
+    finish = 0
+    for i in range(len(sentence) -1):
+        j = i+1;
+        word, tag = sentence[i]
+        word2, tag2 = sentence[j]
+        if word in whatList:
+            if tagCount.has_key(tag): tagCount[tag] += 1
+            else: tagCount[tag] = 1   
+            if tag2[0] is 'V': nextGram["isVerb"] += 1
+            elif tag2[0] is 'N': nextGram["isNoun"] += 1
+            else: nextGram["isOther"] += 1
+            finish = 1;
+            break
+    if finish == 1:
+        lastTerm = sentence[len(sentence)-1]
+        lastWord, lastTag = lastTerm
+        q = "yes" if lastWord is '?' else "no"
+        isQuestion[q]+= 1
+        untagged = nltk.tag.untag(sentence);
+        tagSentenceIsQuestion.append((tag, untagged, q))
+    
+for tag, count in tagCount.items():
+    file.write("Tag: "+ tag+ ", Count: "+ str(count)+ "\n")
+    for sentTag, sent, isQuery in tagSentenceIsQuestion:
+        if(sentTag == tag):
+            if(isQuery is "yes"):
+                file.write(sentTag+":"+isQuery+":"+" ".join(sent)+"\n")
+                
+file.write("Bigram Information... frequency of tagType for w2\n")
+for gramType, count in nextGram.items():
+    file.write(gramType+": "+str(count)+"\n")
+file.close()
+    

### 2010-07-16 dobson/DobsonLibrary/DataAccess/SQLQueries.Designer.cs
SQLQueries.resx changed to pick up latest version of classes from class table

@@ -75,7 +75,7 @@ namespace DobsonLibrary.DataAccess {
         }
         
         /// <summary>
-        ///   Looks up a localized string similar to SELECT classid,name FROM class.
+        ///   Looks up a localized string similar to SELECT classid,name FROM class WHERE version = (SELECT max(version) from class).
         /// </summary>
         internal static string getAllContextClassesMorpheus3DB {
             get {

### 2010-09-23 trunk/paper/IIWAS2010/content/results_discussion.tex
updated to the paper

@@
 
-Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task.
-Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner \cite{Blei2003latentdirichlet}.
+%Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. 
+Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner.
 We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results.

### 2010-09-23 paper/IIWAS2010/content/system_arch.tex
updated to the paper

@@
 This ontology provides a structure for reference in the following sections.
-
+Proceedings
 %% Need ontology paragraph
@@
 
-In addition, we evaluate Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.
+In addition, we employ Latent Dirichlet Allocation (LDA) to identify latent topics of the documents in a corpus \cite{Blei2003latentdirichlet}.
 LDA is Bayesian model that represents a document in the corpus by distributions over topics, and a topic itself is a distribution over all terms in the corpus.
 For example, the latent topics reflect the thematic structure of Wikipedia pages.
-Thus, LDA can discover relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
+Thus, LDA discovers relevant topic proportions in a document using posterior inference \cite{Blei2003latentdirichlet}.
 Given a text document, we tag related documents by matching their similarity over the estimated topic proportions, assisting in ontology and corpora construction.
+We use LDA as a dimensionality reduction tool.
+LDA's topic mixture are represented as feature vectors for each document.
+We are evaluating SVN as a classifier over the documents-topic proportions.
 Due to its fully generative semantics, this usage of LDA could address drawbacks of frequency based approaches (e.g.
 TF-IDF, LSI, and pLSI) such as dimensionality and failure to find the discriminative set of words for a document.
-%of frequency based approaches.% such as TF-IDF, LSI, and pLSI.
 

### 2010-09-23 paper/IIWAS2010/content/related_work.tex
updated to the paper
latest updates

@@
 
-\subsection{Question Ansering Systems}
+\subsection{Question Answering Systems}
 
-The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
+The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they support a finite amount of questions on copora containing a fixed set of documents.
 Morpheus uses the web as its dynamic, open corpus and examines deep web sources to answer questions.
+This process is federated question answering.
 
-Several community QA systems have been developed, such as Yahoo!
+%Several community QA systems have been developed, such as Yahoo!
 Answers \cite{yahooanswers2008}.
@@
 Morpheus relies on its user interface and referencing previously answered questions.
+
+Several other QA systems that use the web as a resource have been developed.
+Most famously, START\footnote{start.csail.mit.edu}, and most recently these include Swingly\footnote{swingly.com}.
+These systems and those as Ephyra \cite{Schlaefer06apattern} use web pages from searches to find answer.
+Morpheus differs in that it only seeks out relevant deep web sources, and instead of using a web search engine it uses only the pages referenced in a previously answered question.
+We expect this approach to add a greater degree precision to user answers.
 

### 2010-09-24 paper/IIWAS2010/content/system_arch.tex
latest paper

@@
-\section{System Architecure}
+\section{System Architecture}
 \label{sec:systemarch}
@@
 
-We employ a quasi-metric, \textit{class divergence (cd)}, between a source class and a target class using the \textit{topological structure} of the classes in an ontology.
+We define \textit{class divergence} (Eq.
+\ref{eq:cd}), a quasi-metric, between a source class and a target class using the \textit{topological structure} of the classes in an ontology.
 We write $S \prec T$ for the reflexive transitive closure of the superclass relation.
 Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$.
-The divergence between a source and target class ranges from zero (for identical classes) to one (for type incompatible classes).
+The class divergence $cd$, between a source and target class ranges from zero (for identical classes) to one (for type incompatible classes).
 Let $S$ be the source class, $T$ be the target class, and $C$ be a least common ancestor class of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
@@
 \begin{equation}
+\label{eq:cd}
 cd(S, T) = \begin{cases}

### 2010-09-24 paper/IIWAS2010/content/results_discussion.tex
iiWAS2010 paper - correction of spelling errors.

@@
 First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets.
-For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages.
+For each of the classes in the ontology we built corpora from the corresponding Wikipedia pages.
 Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.
@@
 \begin{table}[!]\footnotesize
-	\begin{tabular}{|l|p{4.2cm}|}
+	\begin{tabular}{|l|p{4.9cm}|}
 		\hline 
@@
 
-\begin{tabular}{| p{3.2cm} | l | r |}
+\begin{tabular}{| p{3.5cm} | p{1.45cm} | r |}
 \hline 

### 2010-09-25 trunk/paper/IIWAS2010/content/related_work.tex
latest changes

@@
 
-\subsection{Question Ansering Systems}
+\subsection{Question Answering Systems}
 
-The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they supported finitely many questions on copora containing a fixed set of documents.
-Morpheus uses the web as its dynamic, open corpus and examines deep web sources 
-to answer questions.
+The earliest question answering systems such as BASEBALL \cite{Green1961} and Lunar \cite{woods1973} had \emph{closed domains} and \emph{closed corpora}, that is, they support a finite amount of questions on copora containing a fixed set of documents.
+Morpheus uses the web as its dynamic, open corpus and examines deep web sources to answer questions.
+This process is federated question answering.
 
-Several community QA systems have been developed, such as Yahoo!
+%Several community QA systems have been developed, such as Yahoo!
 Answers \cite{yahooanswers2008}.
@@
 This allows for faster responses to questions.
-Morpheus relies on both its user interface and referencing similar questions previously answered.
+Morpheus relies on its user interface and referencing previously answered questions.
+
+Several other QA systems that use the web as a resource have been developed.
+Example systems are START\footnote{start.csail.mit.edu} and Swingly\footnote{swingly.com}.
+These systems use web pages from searches web crawlers or search engines to find answers.
+Morpheus differs in that it seeks out relevant deep web sources, and instead of using a web search engine, it uses only the pages referenced in a previously answered question.
 
@@
 
-The DBpedia\footnote{http://dbpedia.org} project is based on a community of contributors extracting semantic information from the Wikipedia and making this information available on the Web.
-Wikipedia semantics includes info-box templates, categorization information,  images, geo-coordinates, links to external web pages, disambiguation pages, and redirects to pages in Wiki markup form \cite{Bizer2009}.
+The DBpedia\footnote{http://dbpedia.org} project is a community of contributors extracting semantic information from Wikipedia and making this information available on the Web.
+Wikipedia semantics includes disambiguation pages, geo-coordinates, categorization information, images, info-box templates, links to external web pages,  and redirects to pages in Wiki markup form \cite{Bizer2009}.
 DBpedia does not define any new relations between the Wikipedia categories.
@@
 YAGO discovers connections between WordNet synsets and Wikipedia categories, parsing the category names and matching the parsed category components with the WordNet synsets.
-Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.
+Each Wikipedia category not having a WordNet match is ignored in the YAGO ontology.
 The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets.
@@
 We use YAGO's principles to construct ontologies that provide similarity measures for answering questions within the same domain.
-Thus far, these ontologies can be used to classifiy terms, however their classes do not always appropriately categorize query parameters.
-Therefore, we are researching XXX in order to XXX.% TODO - fill in the XXX
+Thus far, these ontologies can be used to classify terms, however their classes do not always appropriately categorize query parameters.
+It is necessary to provide an appropriate level of class granularity.
+Therefore, we are investigating  methods of identifying classes and their instances from deep web forms and documents.
 

### 2010-09-25 paper/IIWAS2010/content/system_arch.tex
latest changes

@@
 This ontology provides a structure for reference in the following sections.
-Proceedings
+
 %% Need ontology paragraph
@@
 First a realm is mapped to a DBpedia category \cite{Bizer2009}.
-Using the DBpedia ontology properties \emph{broader} and \emph{narrower}, a \emph{Markov Blanket} \cite{PRIS} is created covers all neighboring categories.
+Using the DBpedia ontology properties \emph{broader} and \emph{narrower}, a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories.
 
@@
 From this term corpus, we can find the likelihood of a term belonging to a particular class.
-This assists in classifying terms in a \emph{path follower} query.
+This assists in classifying terms in a path follower query.
 The likelihood is determined by the probability of a class given a term using \textit{Bayes Rule} (Eq.
@@
 LDA's topic mixture are represented as feature vectors for each document.
-We are evaluating SVN as a classifier over the documents-topic proportions.
+We are evaluating support vector machines as a classifier over the documents-topic proportions.
 Due to its fully generative semantics, this usage of LDA could address drawbacks of frequency based approaches (e.g.
@@
 
-Queries inserted by path followers take a different approach.
-The Morpheus search process parses and tags queries in order to record important terms.
+When a path follower submits a query the Morpheus search process parses and tags queries in order to record important terms.
 The system assigns the most probable realm given the terms in the query as calculated from realm-specific copora.
@@
 Let $S$ be the source class, $T$ be the target class, and $C$ be a least common ancestor class of $S$ and $T$ i.e., one that minimizes $d(S,C) + d(T,C)$.
-The class divergence between $S$ and $T$ is defined given by:
+The class divergence between $S$ and $T$ is defined by:
 \begin{equation}

### 2010-09-25 paper/IIWAS2010/content/results_discussion.tex
final after working with Pete

@@
 First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets.
-For each of the classes in the ontology we built corpora from the corresponding Wikipedia pages.
+For each of the classes in the ontology we built corpora from the corresponding pWikipedia pages.
 Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.
 
-In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query.
-It extracts the \emph{wh}-term that identifies the sentence as a question, identifies the answer class, and locates descriptive phrases that can be used to identify the answer.
-Finally, the engine produces n-grams from the phrases in the descriptive information sections.
+In Table \ref{tbl:nlp_engine_parse} we show the data output by the Morpheus parse of the query.
+It extracts the \emph{wh}-term that classifies the sentence as a question, identifies the answer class, and locates descriptive phrases to produce the answer.
+Finally, the engine produces n-grams from phrases in the descriptive information sections.
 
 Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance.
-Table \ref{tbl:term_classes} shows the top classes and their probabilities for automotive queries.
+Table \ref{tbl:term_classes} shows the eight best term classes and their probabilities for automotive queries.
 
@@
 	\end{tabular}
-	\caption{The output of NLP engine parse}
+	\caption{The output of NLP engine}
 	\label{tbl:nlp_engine_parse} 
@@
 
-\caption{Terms' top classes and probabilities}
+\caption{Term classes and probabilities}
 \label{tbl:term_classes}
@@
 
-We found the top class of the terms in the candidate SSQ and determined the class divergence with the qualified SSQ classes in the QRM store.
-Then, we combined the divergence measure and ranked QRMs based on the relevance score.
-Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.
+We found the best classes for the terms in the candidate SSQ.
+We calculated the class divergence between these classes and the qualified SSQ classes in the QRM store.
+QRMs are ranked based upon the relevance score and the class divergence measure.
+Table \ref{tbl:ranked_queries} shows the thAnswers are produced by the QRE, a python back end.ree highest ranked queries.
 Finally, we execute the best QRMs and display the results to the user.
@@
 
-\caption{Top ranked queries}
+\caption{Highest ranked queries}
 \label{tbl:ranked_queries}
@@
 Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs.
-Classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.
-These terms are the input to existing answer paths and we re-execute these paths with the new input to produce results.
+The classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.
+These terms are the input to existing answer paths and we re-execute these paths with the new input to produce answers.
+
+Our solution is composed a web front end where users can ask questions.
+The QRR was developed as a Firefox plugin and an associated C\# application.
+Our similarity measures were coded using Java and open source libraries.
+Answers are produced by the QRE, a python back end.
+The data is stored in a PostresSQL database.
 
 %Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. 
-Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner.
-We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results.
+Topic modeling provides a promising approach to identifying pages relevant to a class in a more automated manner.
+We believe our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results.
 Combining this with the method of Elmeleegy et al.
-\cite{1687749} may completely remove the user from the answer path generation process.
+\cite{1687749} may remove the user from the answer path generation process.
 
-Additionally, we are investigating methods of merging QRMs to answer compound questions.  We will also chain QRMs using the principles of transform composition \cite{transformscout}.
+Additionally, we are investigating methods of merging QRMs to answer compound questions.  This will allow us to chain QRMs using the principles of transform composition \cite{transformscout}.
 

### 2010-09-25 paper/IIWAS2010/content/system_arch.tex
final after working with Pete

@@
 This is an important property in determining the compatibility of classes for answering queries.
-If an SSQ answers queries concerning an ancestor class, it is more relevant than an SSQ that answers queries from any non-ancestral class.
+If an SSQ answers queries concerning an ancestor class, it is more relevant than an SSQ that anwers queries from any non-ancestral class.
 
 Suppose we want to find the class divergence between \emph{Bus} and \emph{Sedan} from the ontology shown in Figure \ref{fig:vehicular_ontology}.
-\emph{Sedan} is a subclass of \emph{Automobile} which is a subclass of \emph{Land\_Vehicle}.
-\emph{Bus} is a subclass of \emph{Land\_Vehicle}, which is their least common ancestor $C$.
+\emph{Land\_Vehicle} is their least common ancestor because \emph{Sedan} is a subclass of \emph{Automobile}, which is a subclass of \emph{Land\_Vehicle}, and \emph{Bus} is a subclass of \emph{Land\_Vehicle}.
 
-The longest path to the tree root is $h = 4$.
-Therefore, the normalized divergence $cd(Bus, Sedan) = 6/12$.
-The value is calculated from $d(Bus, Root) = 3$, $d(Bus, Land\_Vehicle) = 1$, and $d(Sedan, Land\_Vehicle) = 2$.
+The longest path from \emph{Bus} and \emph{sedan} to the tree root is four ($h = 4$).
+By formula \ref{eq:cd}, $cd(Bus, Sedan)$ = $( d(Bus, Root)$ + $d(Bus, Land\_Vehicle)$ + $d(Sedan, Land\_Vehicle)) / (3h)$ thus $(3 + 1 + 2) / (3 * 4) = 6/12$.
 
@@
 
-Once we have ranked the QRMs for a given user query, we can produce answers by re-running the pathways stored in the QRMs.
+Once we have ranked the QRMs for a given user query, we can produce answers by re-visiting the pathways stored in the QRMs.
 The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.
-It simulates a human clicking buttons to follow links, submitting forms, and highlighting of data to form a textual answer.
+It simulates a human clicking buttons to follow links, submit forms, and highlight data, forming a textual answer.
 The QE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.

### 2010-09-25 trunk/paper/IIWAS2010/content/related_work.tex
final after working with Pete

@@
 Several other QA systems that use the web as a resource have been developed.
-Example systems are START\footnote{start.csail.mit.edu} and Swingly\footnote{swingly.com}.
+Example systems include START\footnote{http://start.csail.mit.edu} and Swingly\footnote{http://swingly.com}.
 These systems use web pages from searches web crawlers or search engines to find answers.
@@
 It is necessary to provide an appropriate level of class granularity.
-Therefore, we are investigating  methods of identifying classes and their instances from deep web forms and documents.
+Section \ref{sec:systemarch} discusses our approach for identifying classes and their instances from deep web forms and documents.
 
